### 2017-06-01 paper.tex
Abstract update

\documentclass[aps,prl,twocolumn,groupedaddress]{revtex4-1}
% \documentclass[aps,twocolumn,secnumarabic,balancelastpage,amsmath,amssymb,nofootinbib]{revtex4-1}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{chapterbib}
\usepackage{color}
\usepackage{graphics}
\usepackage[pdftex]{graphicx}
\usepackage[utf8x]{inputenc}
\usepackage[colorlinks=true]{hyperref}

\newcommand{\ud}{\mathrm{d}}
\newcommand{\ue}{\mathrm{e}}
\newcommand{\ui}{\mathrm{i}}
\newcommand{\res}{\mathrm{Res}}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\dsum}{\displaystyle\sum}
\newcommand{\dprod}{\displaystyle\prod}
\newcommand{\dlim}{\displaystyle\lim}
\newcommand{\dint}{\displaystyle\int}
\newcommand{\fsno}[1]{{\!\not\!{#1}}}
\newcommand{\texp}[2]{\ensuremath{{#1}\times10^{#2}}}
\newcommand{\dexp}[2]{\ensuremath{{#1}\cdot10^{#2}}}
\newcommand{\eval}[2]{{\left.{#1}\right|_{#2}}}
\newcommand{\paren}[1]{{\left({#1}\right)}}
\newcommand{\lparen}[1]{{\left({#1}\right.}}
\newcommand{\rparen}[1]{{\left.{#1}\right)}}
\newcommand{\abs}[1]{{\left|{#1}\right|}}
\newcommand{\sqr}[1]{{\left[{#1}\right]}}
\newcommand{\crly}[1]{{\left\{{#1}\right\}}}
\newcommand{\angl}[1]{{\left\langle{#1}\right\rangle}}
\newcommand{\tpdiff}[4][{}]{{\paren{\frac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}_{#4}}}
\newcommand{\tpsdiff}[4][{}]{{\paren{\frac{\partial^{#1}}{\partial {#3}{}^{#1}}{#2}}_{#4}}}
\newcommand{\pdiff}[3][{}]{{\frac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}}
\newcommand{\diff}[3][{}]{{\frac{\ud^{#1} {#2}}{\ud {#3}{}^{#1}}}}
\newcommand{\psdiff}[3][{}]{{\frac{\partial^{#1}}{\partial {#3}{}^{#1}} {#2}}}
\newcommand{\sdiff}[3][{}]{{\frac{\ud^{#1}}{\ud {#3}{}^{#1}} {#2}}}
\newcommand{\tpddiff}[4][{}]{{\left(\dfrac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}\right)_{#4}}}
\newcommand{\tpsddiff}[4][{}]{{\paren{\dfrac{\partial^{#1}}{\partial {#3}{}^{#1}}{#2}}_{#4}}}
\newcommand{\pddiff}[3][{}]{{\dfrac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}}
\newcommand{\ddiff}[3][{}]{{\dfrac{\ud^{#1} {#2}}{\ud {#3}{}^{#1}}}}
\newcommand{\psddiff}[3][{}]{{\frac{\partial^{#1}}{\partial{}^{#1} {#3}} {#2}}}
\newcommand{\sddiff}[3][{}]{{\frac{\ud^{#1}}{\ud {#3}{}^{#1}} {#2}}}

\begin{document}
\title{Motional Quantum Ground-State Cooing of a Single Sodium Atom}
\author{Yichao Yu}
\author{Nicholas R. Hutzler}
\author{Jessie T. Zhang}
\author{Lee R. Liu}
\author{Kang-Kuen Ni}
\email{ni@chemistry.harvard.edu}
\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts, 02138, USA}
\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts, 02138, USA}
\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts, 02138, USA}

\date{\today}

\begin{abstract}
  % (add a general sentence on the importance or motivation of the work)
  % Controlling quantum motion of...
  % (state the challenge),
  % (Give the result and brief solutions),
  % (outlook)
  We report Raman sideband cooling of a single neutral sodium atom to its three-dimensional
  motional ground state in an optical tweezer.
  Despite having a very large Lamb-Dicke parameter, high initial temperature and
  large differential AC Stark shift in the excited state,
  we observe a ground state preparation fidelity of $XX\%$ after a few hundred ms of cooling.
  We demonstrate that Raman sideband cooling to the 3D motional ground state is applicable to
  systems where tight confinement or low initial cooling is hard to achieve.  The is particularly relevant for systems which are challenging to laser-cool, such as molecules and exotic atoms, and opens up a new approach for further cooling of these systems.
\end{abstract}

\maketitle

\begin{figure*}
  \includegraphics[height=5.2cm]{imgs/Na_RSC_schematic.pdf}
  \includegraphics[height=4.5cm]{sequence.pdf}
  \caption{(A) Energy levels and schematics of Raman sideband cooling.
    The Raman transitions has a one photon detuning $\Delta=25GHz$ from the D2 line.
    We use D1 light with $\sigma^-$ polarization to repump atom out of $|F=2,m_F=-1\rangle$
    state to minimize heating on the atom in $|F=2,m_F=-2\rangle$ state.
    (B) Geometry and polarizations of the Raman and optical pumping beams relative to the
    optical tweezer and bias magnetic field.
    (C) Schematics of the cooling sequence. The tweezer is switching at $3\text{MHz}$ to
    reduce light shift during optical pumping. Each cooling cycle consists of $8$ pulses.
    The four axial pulses are addressing two neighboring cooling orders.
    The two pulses in each radial directions are either addressing two neighboring cooling orders
    or having different length on the first order when most of the population are below $n=3$
    towards then end of the cooling sequence.
    \label{f-setup}}
\end{figure*}
\begin{figure}[b]
  \includegraphics[width=8.5cm]{imgs/fig2_raman_op.pdf}
  \caption{Matrix elements and heating probabilities as a function of motional state.
    The range plotted covers $99\%$ of the initial thermal distribution.
    (A) Matrix elements for Raman transition in the axial direction showing deviation from
    $\sqrt{n}$ scaling and multiple minimums for different sideband orders.
    (B) Heating probability during the optical pumping step for all three axis.
    Due to the large Lamb-Dicke parameter,
    there is a high probability of heating especially in the axial direction.
    \label{f-ld}}
\end{figure}
\begin{figure*}
  \includegraphics[height=4.3cm]{imgs/spectrum_r.pdf}
  \includegraphics[height=4.3cm]{imgs/rabi_flop_r3_0.pdf}
  \includegraphics[height=4.3cm]{imgs/rabi_flop_r3_p1.pdf}
  \caption{Radial Raman sideband spectrum of first order heating, first order cooling and
    second order cooling (A) before and (B) after Raman sideband cooling.
    Rabi flopping on axis 3 (C) carrier and (D) first order heating sideband
    after cooling.
    Solid lines in (C) and (D) are theoretical fit with a ground state probability of $????\%$.
    Horizontal dashed lines in (A) to (D) are total survival and detection efficiency.
    \label{f-radial}}
\end{figure*}

Single neutral atoms trapped in optical tweezers provide a promising system
for various applications including quantum information, quantum chemistry
and quantum simulation of many-body systems.
The interaction between different sites can be controlled by creating Rydberg excitation
or by creating dipolar molecules from two trapped atoms.
Combined with the ability to move, detect and manipulate individual sites,
arrays of optical tweezers can be used to prepare complex interacting system
with high fidelity.
In order to achieve long coherence time and full quantum control of the system needed for
these applications,
it is usually necessary to control the thermal motion of the atoms by cooling to the
three dimensional motional ground state in the optical tweezer,
which has already been demonstrated with heavy alkali atoms including rubidium and cesium.
However, some of the important properties of previous experiments,
for example low initial temperature and small Lamb-Dicke parameter,
may not be easily achievable for other systems and
the versatility of this approach requires being able to perform ground motional state cooling
in the more general case. In this letter, we present our work on cooling single sodium atoms
trapped in optical tweezers to the motional ground state with Raman sideband cooling.
Despite having a large Lamb-Dicke parameter and high initial temperature,
by utilizing several new cooling techniques and a well optimized cooling sequence,
we are able to achieve a ground state probability of $80\%$.

The Raman sideband cooling we used to achieve the high ground state preparation fidelity
consists of multiple cycles of laser pulses to manipulate the internal and
motional states of the atoms.
Figure \ref{f-setup}A shows the schematic of the energy levels and the cooling sequence
in our setup.
Each cooling cycle starts with the sodium atom in the $|F=2, m_F=-2\rangle$
ground electronic state and a certain vibration state $n$.
In the first step, a Raman pulse drives a transition to the motional state $n-\Delta n$
to reduce the motional energy while also changing the internal state to $|F=1, m_F=-1\rangle$.
In the second step, which finishes the cooling cycle,
an optical pumping pulse bring the atom back to the $|F=2, m_F=-2\rangle$ state to take away
the entropy. The second step could also change the motional state of the atoms which
could cause heating. The possibility for this to happen for an atom in the motional level $n$
is approximately proportional to the effective Lamb-Dicke parameter
$\eta^{OP}_{eff}=\sqrt{2n+1}\eta^{OP}$ where $\eta^{OP}=???$ is the Lamb-Dicke parameter for
optical pumping.
The geometry of the relevant beams (???and their polarizations) is showed in figure \ref{f-setup}B.
The optical tweezer has one weakly confined axial direction (axis $1$) and
two more strongly confined radial directions (axis $2$ and $3$).
Multiple pairs of beams are used to drive the Raman transition during cooling in order to
isolate and maximize the coupling to different trap axis.

Although Raman sideband cooling to motional ground state has already been successfully
implemented on neutral atoms in other experiments using heavier species like Rubidium [????]
and Cesium [????], such experiments generally use good polarization gradient cooling
and a tight confinement to achieve a small Lamb-Dicke parameter and effective Lamb-Dicke parameter.
However, this regime is harder to achieve with sodium atoms, creating additional challenges for
us to realize ground state cooling. On the other hand, since these conditions can also be difficult
to meet for other interesting systems like directly laser cooled molecules, the techniques we
use to overcome these challenges could be useful for a wider variety of systems.

As mentioned previously, in order to perform Raman sideband cooling efficiently and
minimize the heating during the optical pumping, we need to have a low initial temperature and
a small Lamb-Dicke parameter. However, since the Lamb-Dicke parameter $\eta$ is inversely
proportional to $\sqrt{m}$ (???) where $m$ is the mass of the atom, it is larger for sodium
given the same trap depth (???).
With $45mW$ of power at the focus of the trap, we measured a trapping frequency of
$\{\omega_1,\omega_2,\omega_3\}/2\pi = \{67, 420, 580\}\ \text{\text{kHz}}$
which corresponds to optical pumping Lamb-Dicke parameters of
$\{\eta^{OP}_1,\eta^{OP}_2,\eta^{OP}_3\} = \{???, ???, ???\}$.
Moreover, due to the unresolved(?) hyperfine structure in the $3^2P_{3/2}$ manifold,
the sub-Doppler cooling in sodium is also less efficient and we start the
Raman sideband cooling with a initial temperature of $40\mu K$. Combined with the high Lamb-Dicke
parameters, this gives us a initial effective optical pumping Lamb-Dicke parameters of
$\{\eta^{OP}_{1eff},\eta^{OP}_{2eff},\eta^{OP}_{3eff}\} = \{???, ???, ???\}$
As a result, there is a very high probability of heating during the optical pumping step
(figure \ref{f-ld}B) causing a $30\%$ average heating probability during optical pumping
in the weakly confined axial direction. Fortunately, the high Lamb-Dicke parameters also
provide us tools to overcome this issue. From our geometry, the Lamb-Dicke parameters for
Raman transitions are $\{\eta^R_{1},\eta^R_{2},\eta^R_{3}\} = \{???, ???, ???\}$. As shown in
figure \ref{f-ld}A, the high Raman Lamb-Dicke parameters causes a strong coupling to higher orders
of cooling sidebands, especially for high motional states.
This enables us to cool atoms in high motional states by driving on high order Raman sidebands,
removing more motional energy in a single cooling pulse and offsetting the effect of
strong heating. Since the heating probability is higher for high motional states,
cooling on these high order sidebands can greatly suppress the high heating during
optical pumping during the initial cooling. Since the coupling strength of different orders
do not reach their minimums at the same time, using multiple orders of motional sidebands
for cooling also avoids accumulation of population near the coupling minimum of a particular
order, which improves the overall efficiency of the cooling process.

In additional to improving the cooling efficiency, the large Raman Lamb-Dicke parameters $\eta^R$
also creates difficulties for measuring the temperature. Traditional sideband thermometry uses
the ratio of the cooling and heating sidebands to measure $\bar n / (\bar n + 1)$, which relies
on the coupling strength to be proportional to $\sqrt{n}$. However, since we are not in the
Lamb-Dicke regime, the coupling strength deviates from this simple scaling rule quickly as already
shown in figure \ref{f-ld}A, causing the normal sideband thermometry to break down.
In order to solve this problem, when the atom temperature is still high,
we measure the heights of multiple sidebands to make sure no population is hidden at the
minimum of one sideband order. And when the atom is cooled down, we estimate the temperature
and ground state population under the assumption that only a few states are populated.
This result is then verified using independent measure of Rabi flopping on the carrier and heating
sidebands since they provide more information about the distribution of coupling strength.

Another issue caused by the high initial temperature is trap anharmonicity.
Although the potential near the center of a focused Gaussian beam can be approximated
by a harmonic trap, when a large number of levels are populated due to high initial temperature
the anharmonicity of the trap can lead to broadening of the sideband and decrease of
the sideband signal. In our setup, this effect limits the Rabi frequency of the Raman pulse
on the radial sidebands to be no lower than tens of kilo-Hertz in order to drive atoms in
different motional states equally.

Finally, the deep trap that is needed to trap and image single sodium atom also creates
a very large AC Stark shift in the excited state. For the trap depth we are using, the
light shift in the center of the trap is as large as $300\text{MHz}$.
In additional to creating a large and position dependent detuning for the optical pumping light,
it also mixes the excited state state hyperfine levels,
affecting the branching ratio and increasing the number of photons needed during optical pumping.
Similar to our loading and imaging process [???], we solve this issue by switching the
trapping light at $3\text{MHz}$ during the whole cooling sequence.
Due to the large light shift, the optical pumping is effectively off when the trap light is on.
Since the atom can only be addressed by the optical pumping light when the trap light is off,
the effect of light shift on optical pumping fidelity is suppressed.

Taking all the features of our system into account, we use a Monte-Carlo simulation to verify
the validity of our method.
In the simulation, we can observe the high heating rate due to the high Lamb-Dicke parameters
and confirm that by using high order Raman sideband transition in the cooling sequence we can
suppress this effect and reduces the motional energy of the atom faster.
The simulation is also used to guide the optimization of the cooling sequence by exploring the
large parameter space and finding a robust cooling strategy. As shown in figure (?),
we found that instead of cooling on only one sideband order at a time, it is generally more
efficient to alternate the cooling pulse between two neighboring orders (axial) or pulse lengths.
A cooling sequence like this minimizes the accumulation of atom in a state not addressed by a
particular Raman pulse parameter.

For the more tightly confined radial directions,
we starts the cooling with $\{\bar n_2, \bar n_3\}=????, ????$.
The radial sideband spectra of the initial distribution is shown in figure \ref{f-radial}A
where we can clearly see the first order heating, first order cooling and
second order cooling sidebands.
After applying about 1000 cooling pulses cooling in all three dimensions
starting with cooling on the radial second order,
the Raman spectrum with the same parameter is shown in figure \ref{f-radial}B,
where the first and second order cooling sidebands on both axis are suppressed.
Given the absence of the second order cooling sideband,
we can estimate the ground state probability in each direction based on the height of
the first order cooling and heating sideband to be $????$ and $????$.
Due to the complexity of the sideband structure,
we measured the Rabi flopping on the carrier and heating sideband before and after cooling
(\ref{f-radial}C and \ref{f-radial}D)
as a independent way to obtain the population in different motional states.
Fitting the Rabi flopping data give a ground state probability of $????$ and $????$,
showing good agreement between the two methods.
\begin{figure*}
  \includegraphics[height=4.3cm]{imgs/spectrum_a1.pdf}
  \includegraphics[height=4.3cm]{imgs/rabi_flop_a1_0.pdf}
  \includegraphics[height=4.3cm]{imgs/rabi_flop_a1_p1.pdf}
  \caption{Axial Raman sideband spectrum from first order heating to eighth order cooling
    (A) before and (B) after Raman sideband cooling.
    Rabi flopping on axial (C) carrier and (D) first order heating sideband
    after cooling.
    Solid lines in (C) and (D) are theoretical fit with a ground state probability of $????\%$.
    Horizontal dashed lines in (C) and (D) are total survival and detection efficiency.
    \label{f-axial}}
\end{figure*}

The axial direction is much less confined and therefore has a much higher initial effective
Lamb-Dicke parameter of $\eta^{OP}_{eff1}\approx3.3$.
The line in figure \ref{f-axial}A shows the Raman spectrum in the axial direction
before applying Raman sideband cooling where we can see clearly resolved Raman cooling sidebands
up to the eighth order suggesting that we have many motional states populated in this direction.
Therefore, we starts our cooling sequence by driving Raman transitions on the eighth order axial
cooling sideband. After applying the cooling sequence identical to the one we use to cool
the radial directions, the spectrum is shown in figure \ref{f-axial}B.
All of the high order ($\geqslant2$) axial cooling sidebands disappeared and the first order
cooling sideband is also strongly suppressed.
The ground state probability calculated from this spectrum is $????$.
We can also use Rabi flopping on the carrier and heating sideband to verify this result
similar to the radial direction. In this case, we see very good agreement on the carrier
(figure \ref{f-axial}B) but there is additional decoherence on the axial first order
heating sideband (figure \ref{f-axial}C).
We believe this decoherence is caused by technical noise in our setup which
produces the strongest effect on this transition due to its slow Rabi frequency.
The decoherence time scale agree with the magnetic field fluctuation we measured which produces
a Zeeman shift of around $5\text{kHz}$.

Combining the axial and radial cooling results, we have achieved a ground state probability of
$....$. We believe this is currently limited by off-resonant scattering from the Raman beams
and the resonance shift caused by magnetic field fluctuation.
Improvements on these should improve the cooling performance even further.

% Missing:
% ?? D1 OP
% ?? Blackman pulse

\bibliography{paper}
\end{document}

### 2017-06-01 paper.tex

@@
 and quantum simulation of many-body systems.
-The interaction between different sites can be controlled by creating Rydberg excitation
-or by creating dipolar molecules from two trapped atoms.
-Combined with the ability to move, detect and manipulate individual sites,
-arrays of optical tweezers can be used to prepare complex interacting system
+Long-range interactions between the sites can be achieved by using Rydberg atoms, polar molecules, or dipolar atoms.
+Polar molecules offer the additional advantage of a high degree of tunability, including the shape, range, and strength of the interaction.
+Arrays of optical tweezers offer the ability to move, detect, and manipulate individual sites, andcan be used to prepare complex interacting systems
 with high fidelity.
@@
 for example low initial temperature and small Lamb-Dicke parameter,
-may not be easily achievable for other systems and
-the versatility of this approach requires being able to perform ground motional state cooling
-in the more general case. In this letter, we present our work on cooling single sodium atoms
+may not be easily achievable for other systems, such as directly laser-cooled polar molecules, or atoms with challenging sub-Doppler cooling such as Na, K, and Li.
+To extend the versatility of this approach, we must be able to apply it in a more general case. 
+In this letter, we cool single sodium atoms
 trapped in optical tweezers to the motional ground state with Raman sideband cooling.
-Despite having a large Lamb-Dicke parameter and high initial temperature,
-by utilizing several new cooling techniques and a well optimized cooling sequence,
-we are able to achieve a ground state probability of $80\%$.
+Despite having a large Lamb-Dicke parameter and high initial temperature, we are able to achieve a ground state probability of $XX\%$
+by utilizing several new cooling techniques and a carefully optimized cooling sequence.
 

### 2017-06-01 paper.tex
Mostly grammar and style, some comments added

@@
 
-The Raman sideband cooling we used to achieve the high ground state preparation fidelity
+The Raman sideband cooling (RSC) scheme that we use to achieve high ground state preparation fidelity
 consists of multiple cycles of laser pulses to manipulate the internal and
@@
 In the second step, which finishes the cooling cycle,
-an optical pumping pulse bring the atom back to the $|F=2, m_F=-2\rangle$ state to take away
-the entropy. The second step could also change the motional state of the atoms which
-could cause heating. The possibility for this to happen for an atom in the motional level $n$
-is approximately proportional to the effective Lamb-Dicke parameter
-$\eta^{OP}_{eff}=\sqrt{2n+1}\eta^{OP}$ where $\eta^{OP}=???$ is the Lamb-Dicke parameter for
+an optical pumping pulse bring the atom back to the $|F=2, m_F=-2\rangle$ state.
+The second step could also change the motional state of the atoms, which
+could result in heating. The possibility for this to happen for an atom in the motional level $n$
+is approximately proportional to the effective Lamb-Dicke (LD) parameter
+$\eta^{OP}_{ef\! f}=\sqrt{2n+1}\eta^{OP}$ where $\eta^{OP}=???$ is the LD parameter for
 optical pumping.
-The geometry of the relevant beams (???and their polarizations) is showed in figure \ref{f-setup}B.
+The geometry of the relevant beams (??? and their polarizations) is shown in figure \ref{f-setup}B.
 The optical tweezer has one weakly confined axial direction (axis $1$) and
@@
 Multiple pairs of beams are used to drive the Raman transition during cooling in order to
-isolate and maximize the coupling to different trap axis.
+isolate and maximize the coupling to different trap axes, each of which is independent and must be cooled individually.
 
-Although Raman sideband cooling to motional ground state has already been successfully
-implemented on neutral atoms in other experiments using heavier species like Rubidium [????]
-and Cesium [????], such experiments generally use good polarization gradient cooling
-and a tight confinement to achieve a small Lamb-Dicke parameter and effective Lamb-Dicke parameter.
-However, this regime is harder to achieve with sodium atoms, creating additional challenges for
-us to realize ground state cooling. On the other hand, since these conditions can also be difficult
-to meet for other interesting systems like directly laser cooled molecules, the techniques we
-use to overcome these challenges could be useful for a wider variety of systems.
+Although RSC to the motional ground state has already been successfully
+implemented in heavier neutral atoms like Rubidium [????]
+and Cesium [????], such experiments generally use combine efficient sub-Doppler cooling
+with tight confinement to achieve small LD parameters.
+Since sub-Doppler cooling is challenging with sodium atoms, we begin the cooling sequence with a considerably larger LD parameter.
+However, since these challenges will likely present themselves in other interesting systems like directly laser cooled molecules, the techniques we use to overcome these challenges will be useful for a wide variety of systems.
 
-As mentioned previously, in order to perform Raman sideband cooling efficiently and
-minimize the heating during the optical pumping, we need to have a low initial temperature and
-a small Lamb-Dicke parameter. However, since the Lamb-Dicke parameter $\eta$ is inversely
-proportional to $\sqrt{m}$ (???) where $m$ is the mass of the atom, it is larger for sodium
-given the same trap depth (???).
-With $45mW$ of power at the focus of the trap, we measured a trapping frequency of
+BRIEFLY DESCRIBE NA TRAPPING SETUP.
+
+%As mentioned previously, in order to perform RSC efficiently and
+%minimize the heating during the optical pumping, we need to have a small LD parameter, which for an optical tweezer means a low atom temperature. However, since the LD parameter $\eta$ is inversely
+%proportional to $\sqrt{m}$ (???) where $m$ is the mass of the atom, it is larger for sodium
+%given the same trap depth (???).
+
+With $45mW$ of power at the focus of the trap, we measure trapping frequencies of
 $\{\omega_1,\omega_2,\omega_3\}/2\pi = \{67, 420, 580\}\ \text{\text{kHz}}$
-which corresponds to optical pumping Lamb-Dicke parameters of
+which corresponds to optical pumping LD parameters of
 $\{\eta^{OP}_1,\eta^{OP}_2,\eta^{OP}_3\} = \{???, ???, ???\}$.
-Moreover, due to the unresolved(?) hyperfine structure in the $3^2P_{3/2}$ manifold,
+Moreover, due to hyperfine structure in the $3^2P_{3/2}$ manifold,
 the sub-Doppler cooling in sodium is also less efficient and we start the
-Raman sideband cooling with a initial temperature of $40\mu K$. Combined with the high Lamb-Dicke
-parameters, this gives us a initial effective optical pumping Lamb-Dicke parameters of
+RSC with a initial temperature of $40\mu K$. Combined with the high LD
+parameters, this gives us a initial effective optical pumping LD parameters of
 $\{\eta^{OP}_{1eff},\eta^{OP}_{2eff},\eta^{OP}_{3eff}\} = \{???, ???, ???\}$
-As a result, there is a very high probability of heating during the optical pumping step
-(figure \ref{f-ld}B) causing a $30\%$ average heating probability during optical pumping
-in the weakly confined axial direction. Fortunately, the high Lamb-Dicke parameters also
-provide us tools to overcome this issue. From our geometry, the Lamb-Dicke parameters for
+As a result, there is a very high probability of heating during each optical pumping step
+(figure \ref{f-ld}B), resulting in a $30\%$ average heating probability during optical pumping
+in the weakly-confined axial direction.
+
+Fortunately, the high LD parameters also
+provide us with tools to overcome this issue. From our geometry, the LD parameters for
 Raman transitions are $\{\eta^R_{1},\eta^R_{2},\eta^R_{3}\} = \{???, ???, ???\}$. As shown in
-figure \ref{f-ld}A, the high Raman Lamb-Dicke parameters causes a strong coupling to higher orders
+figure \ref{f-ld}A, this results in a strong coupling to higher orders
 of cooling sidebands, especially for high motional states.
-This enables us to cool atoms in high motional states by driving on high order Raman sidebands,
-removing more motional energy in a single cooling pulse and offsetting the effect of
-strong heating. Since the heating probability is higher for high motional states,
+This enables us to cool atoms in high motional states by driving on higher order Raman sidebands,
+thereby removing more motional energy in a single cooling pulse and offsetting the effect of
+additional heating. Since the heating probability is higher for high motional states,
 cooling on these high order sidebands can greatly suppress the high heating during
-optical pumping during the initial cooling. Since the coupling strength of different orders
-do not reach their minimums at the same time, using multiple orders of motional sidebands
-for cooling also avoids accumulation of population near the coupling minimum of a particular
-order, which improves the overall efficiency of the cooling process.
+optical pumping during the initial cooling.
 
-In additional to improving the cooling efficiency, the large Raman Lamb-Dicke parameters $\eta^R$
-also creates difficulties for measuring the temperature. Traditional sideband thermometry uses
-the ratio of the cooling and heating sidebands to measure $\bar n / (\bar n + 1)$, which relies
-on the coupling strength to be proportional to $\sqrt{n}$. However, since we are not in the
-Lamb-Dicke regime, the coupling strength deviates from this simple scaling rule quickly as already
+As shown in Figure \ref{f-ld}, the relationship between coupling strength, sideband order, and motional state is complicated.
+There are also motional states where the coupling vanishes, providing an accumulation point for cooling processes that use a fixed sideband order, and halting cooling.
+By using multiple orders of motional sidebands for the cooling cycles, we can avoid these accumulation points and achieve high efficiency cooling.
+
+The large Raman LD parameters $\eta^R$
+also create difficulties for measuring the temperature. Traditional sideband thermometry relies on
+a relationship between the cooling/heating sideband heights and $\bar n$ that is only valid in the regime where the LD is small.
+However, since we are not in this regime, the coupling strength deviates from this simple scaling rule quickly as already
 shown in figure \ref{f-ld}A, causing the normal sideband thermometry to break down.
@@
 we measure the heights of multiple sidebands to make sure no population is hidden at the
-minimum of one sideband order. And when the atom is cooled down, we estimate the temperature
-and ground state population under the assumption that only a few states are populated.
+minimum of one sideband order [THIS NEEDS TO BE EXPLAINED MORE CLEARLY]. After the atom is cooled and only occupies a small number of motional states, the LD approximation becomes valid.
 This result is then verified using independent measure of Rabi flopping on the carrier and heating
@@
 the anharmonicity of the trap can lead to broadening of the sideband and decrease of
-the sideband signal. In our setup, this effect limits the Rabi frequency of the Raman pulse
-on the radial sidebands to be no lower than tens of kilo-Hertz in order to drive atoms in
-different motional states equally.
+the sideband signal. In our setup, this limits the Rabi frequency of the Raman pulse
+on the radial sidebands to be no lower than tens of kiloHertz in order to drive atoms in
+different motional states equally. [EXPLAIN THIS FURTHER]
 
@@
 light shift in the center of the trap is as large as $300\text{MHz}$.
-In additional to creating a large and position dependent detuning for the optical pumping light,
+In addition to creating a large and position dependent detuning for the optical pumping light,
 it also mixes the excited state state hyperfine levels,
 affecting the branching ratio and increasing the number of photons needed during optical pumping.
-Similar to our loading and imaging process [???], we solve this issue by switching the
-trapping light at $3\text{MHz}$ during the whole cooling sequence.
+Similar to our loading and imaging process [???], we solve this issue by modulating the
+tweezer at $3\text{MHz}$ during the whole cooling sequence.
 Due to the large light shift, the optical pumping is effectively off when the trap light is on.
@@
 the validity of our method.
-In the simulation, we can observe the high heating rate due to the high Lamb-Dicke parameters
-and confirm that by using high order Raman sideband transition in the cooling sequence we can
-suppress this effect and reduces the motional energy of the atom faster.
+In the simulation, we can observe the high heating rate due to the high LD parameters
+and confirm our cooling sequence we can
+overcome this effect and cool the atom successfully.
 The simulation is also used to guide the optimization of the cooling sequence by exploring the
@@
 For the more tightly confined radial directions,
-we starts the cooling with $\{\bar n_2, \bar n_3\}=????, ????$.
+we begin the cooling with $\{\bar n_2, \bar n_3\}=????, ????$.
 The radial sideband spectra of the initial distribution is shown in figure \ref{f-radial}A
@@
 second order cooling sidebands.
-After applying about 1000 cooling pulses cooling in all three dimensions
-starting with cooling on the radial second order,
-the Raman spectrum with the same parameter is shown in figure \ref{f-radial}B,
-where the first and second order cooling sidebands on both axis are suppressed.
+The results of applying approximately 1000 cooling cycles in all three dimensions,
+starting with the radial second order sideband,
+are shown in figure \ref{f-radial}B,
+where the first and second order cooling sidebands on both axes are suppressed.
 Given the absence of the second order cooling sideband,
@@
   \caption{Axial Raman sideband spectrum from first order heating to eighth order cooling
-    (A) before and (B) after Raman sideband cooling.
+    (A) before and (B) after RSC.
     Rabi flopping on axial (C) carrier and (D) first order heating sideband
@@
 The axial direction is much less confined and therefore has a much higher initial effective
-Lamb-Dicke parameter of $\eta^{OP}_{eff1}\approx3.3$.
+LD parameter of $\eta^{OP}_{eff1}\approx3.3$.
 The line in figure \ref{f-axial}A shows the Raman spectrum in the axial direction
-before applying Raman sideband cooling where we can see clearly resolved Raman cooling sidebands
-up to the eighth order suggesting that we have many motional states populated in this direction.
-Therefore, we starts our cooling sequence by driving Raman transitions on the eighth order axial
-cooling sideband. After applying the cooling sequence identical to the one we use to cool
-the radial directions, the spectrum is shown in figure \ref{f-axial}B.
-All of the high order ($\geqslant2$) axial cooling sidebands disappeared and the first order
-cooling sideband is also strongly suppressed.
+before applying RSC, where we can see clearly resolved sidebands
+up to the eighth order, suggesting that we have many motional states populated in this direction.
+Therefore, we begin our cooling sequence by driving Raman transitions on the eighth order axial
+cooling sideband. After applying a cooling sequence similar to that used to cool
+the radial directions, we obtain the spectrum shown in figure \ref{f-axial}B.
+All of the higher order ($\geqslant2$) axial cooling sidebands disappear, and the first order
+cooling sideband is strongly suppressed.
 The ground state probability calculated from this spectrum is $????$.
@@
 and the resonance shift caused by magnetic field fluctuation.
-Improvements on these should improve the cooling performance even further.
+Improvements on these should improve the cooling performance even further.  [EXPAND ON THIS]
 

### 2017-06-04 paper.tex
Expand conclusion and abstract

--- 2017-06-01 paper.tex
@@
 \begin{abstract}
-  % (add a general sentence on the importance or motivation of the work)
-  % Controlling quantum motion of...
-  % (state the challenge),
-  % (Give the result and brief solutions),
-  % (outlook)
-  We report Raman sideband cooling of a single neutral sodium atom to its three-dimensional
+  Single neutral atom trapped in optical tweezer is a promising system for various applications
+  in quantum information and simulation.
+  The control of the motional states for such a system is crucial
+  for exploiting its full potential.
+  We report Raman sideband cooling of a single sodium atom to its three-dimensional
   motional ground state in an optical tweezer.
@@
   large differential AC Stark shift in the excited state,
-  we observe a ground state preparation fidelity of $XX\%$ after a few hundred ms of cooling.
+  we achieved a ground state preparation fidelity of $XX\%$ after a few hundred ms of cooling
+  by using a few new cooling techniques including addressing high order Raman sideband.
   We demonstrate that Raman sideband cooling to the 3D motional ground state is applicable to
   systems where tight confinement or low initial cooling is hard to achieve.
-The is particularly relevant for systems which are challenging to laser-cool, such as molecules and exotic atoms, and opens up a new approach for further cooling of these systems.
+  The is particularly relevant for systems which are challenging to laser-cool,
+  such as molecules and exotic atoms, and opens up a new approach for further cooling
+  of these systems.
 \end{abstract}
@@
 and quantum simulation of many-body systems.
-Long-range interactions between the sites can be achieved by using Rydberg atoms, polar molecules, or dipolar atoms.
-Polar molecules offer the additional advantage of a high degree of tunability, including the shape, range, and strength of the interaction.
-Arrays of optical tweezers offer the ability to move, detect, and manipulate individual sites, andcan be used to prepare complex interacting systems
-with high fidelity.
+Long-range interactions between the sites can be achieved by using Rydberg atoms,
+polar molecules, or dipolar atoms.
+Polar molecules offer the additional advantage of a high degree of tunability,
+including the shape, range, and strength of the interaction.
+Arrays of optical tweezers offer the ability to move, detect, and manipulate individual sites,
+and can be used to prepare complex interacting systems with high fidelity.
 In order to achieve long coherence time and full quantum control of the system needed for
@@
 for example low initial temperature and small Lamb-Dicke parameter,
-may not be easily achievable for other systems, such as directly laser-cooled polar molecules, or atoms with challenging sub-Doppler cooling such as Na, K, and Li.
+may not be easily achievable for other systems, such as directly laser-cooled polar molecules,
+or atoms with challenging sub-Doppler cooling such as Na, K, and Li.
 To extend the versatility of this approach, we must be able to apply it in a more general case.
@@
 
-Combining the axial and radial cooling results, we have achieved a ground state probability of
-$....$. We believe this is currently limited by off-resonant scattering from the Raman beams
+Combining the axial and radial cooling results,
+we have achieved a ground state probability of $....$.
+We believe this is currently limited by off-resonant scattering from the Raman beams
 and the resonance shift caused by magnetic field fluctuation.
 Improvements on these should improve the cooling performance even further.
+We have shown that despite the difficulty in cooling sodium atoms,
+it is possible to achieve reliable three dimensional cooling with significant ground state
+probability using new cooling techniques and a optimized cooling sequence.
+This opens up the possibility of cooling a large variety of systems to their motional ground
+state using Raman sideband cooling that is challenging to laser cool
+including molecules and exotic atoms.
 

### 2017-06-05 paper.tex
Add some references

@@
 \usepackage{amsfonts}
-\usepackage{chapterbib}
 \usepackage{color}
@@
 Although Raman sideband cooling to motional ground state has already been successfully
-implemented on neutral atoms in other experiments using heavier species like Rubidium [????]
+implemented on neutral atoms in other experiments using heavier species like Rubidium
+\cite{Thompson2013,Kaufman2012}
 and Cesium [????], such experiments generally use good polarization gradient cooling

### 2017-06-05 plot_rabi_flop.jl
Include before in plotting again

@@ -143,8 +143,8 @@ data_after_a1_0 = NaCsData.map_params((i, v)->v * 1e6, data_d)
 data_after_a1_p1 = NaCsData.map_params((i, v)->v * 1e6, data_c)
 
 function f1_prob(Ωs, pΩ::AbstractArray, Γ::AbstractMatrix{T},
-                 rates::AbstractVector{T}, tmax::T, atol=0.005, n::Integer=100000,
-                 rd=thread_rng()) where T<:AbstractFloat
+                 rates::AbstractVector{T}, tmax::T, atol=0.005, δΩ=T(0),
+                 n::Integer=100000, rd=thread_rng()) where T<:AbstractFloat
     nΩ = length(Ωs)
     nstates = length(rates)
     count = 0
@@ -157,7 +157,8 @@ function f1_prob(Ωs, pΩ::AbstractArray, Γ::AbstractMatrix{T},
                 break
             end
         end
-        i_final = propagate_multistates(T(Ωs[j]), 1, 6, Γ, rates, 1, tmax, rd)
+        Ω = T(sqrt(Ωs[j]^2 + (δΩ * randn(rd))^2))
+        i_final = propagate_multistates(Ω, 1, 6, Γ, rates, 1, tmax, rd)
         if i_final > 5
             # count F1
             count += 1
@@ -172,14 +173,15 @@ function f1_prob(Ωs, pΩ::AbstractArray, Γ::AbstractMatrix{T},
     return binomial_estimate(count, n)[1]
 end
 
-function f1_prop_getter(Γ, scale=1)
+function f1_prop_getter(Γ, scale=1, δΩ=0)
     Γ32 = Float32.(Γ)
     rates32 = Γ_to_rates(Γ32)
-    (Ωs, pΩ, t, atol=0.005)->f1_prob(Ωs, pΩ, Γ32, rates32, t, atol) * scale
+    (Ωs, pΩ, t, atol=0.005)->f1_prob(Ωs, pΩ, Γ32, rates32, t, atol, δΩ) * scale
 end
 
[…]

### 2017-06-05 paper.tex
Try combining spectrum plots

@@
   large differential AC Stark shift in the excited state,
-  we achieved a ground state preparation fidelity of $XX\%$ after a few hundred ms of cooling
+  we achieved a ground state preparation fidelity of $??\%$ after a few hundred ms of cooling
   by using a few new cooling techniques including addressing high order Raman sideband.
@@
 \begin{figure*}
-  \includegraphics[height=4.3cm]{imgs/spectrum_r.pdf}
-  \includegraphics[height=4.3cm]{imgs/rabi_flop_r3_0.pdf}
-  \includegraphics[height=4.3cm]{imgs/rabi_flop_r3_p1.pdf}
+  \includegraphics[height=4.2cm]{imgs/spectrum_r.pdf}
+  \includegraphics[height=4.2cm]{imgs/rabi_flop_r3_0.pdf}
+  \includegraphics[height=4.2cm]{imgs/rabi_flop_r3_p1.pdf}
   \caption{Radial Raman sideband spectrum of first order heating, first order cooling and
@@
     \label{f-radial}}
+\end{figure*}
+\begin{figure*}
+  \includegraphics[height=4.2cm]{imgs/spectrum_a1.pdf}
+  \includegraphics[height=4.2cm]{imgs/rabi_flop_a1_0.pdf}
+  \includegraphics[height=4.2cm]{imgs/rabi_flop_a1_p1.pdf}
+  \caption{Axial Raman sideband spectrum from first order heating to eighth order cooling
+    (A) before and (B) after Raman sideband cooling.
+    The data for the second and higher orders of cooling sidebands are taken with $150\mu s$
+    pulse time and the rest are taken with $125\mu s$ pulse time.
+    Rabi flopping on axial (C) carrier and (D) first order heating sideband
+    after cooling.
+    Solid lines in (C) and (D) are theoretical fit with a ground state probability of $????\%$.
+    Horizontal dashed lines in (C) and (D) are total survival and detection efficiency.
+    \label{f-axial}}
 \end{figure*}
@@
 is approximately proportional to the effective Lamb-Dicke parameter
-$\eta^{OP}_{eff}=\sqrt{2n+1}\eta^{OP}$ where $\eta^{OP}=???$ is the Lamb-Dicke parameter for
+$\eta^{OP}_{eff}=\sqrt{2n+1}\eta^{OP}$ where $\eta^{OP}=k^{OP}???$ is the Lamb-Dicke parameter for
 optical pumping.
-The geometry of the relevant beams (???and their polarizations) is showed in figure \ref{f-setup}B.
+The geometry of the relevant beams and their polarizations is showed in figure \ref{f-setup}B.
 The optical tweezer has one weakly confined axial direction (axis $1$) and
@@
 With $45mW$ of power at the focus of the trap, we measured a trapping frequency of
-$\{\omega_1,\omega_2,\omega_3\}/2\pi = \{67, 420, 580\}\ \text{\text{kHz}}$
+$\{\omega_1,\omega_2,\omega_3\}/2\pi = \{69, 430, 590\}\ \text{\text{kHz}}$
 which corresponds to optical pumping Lamb-Dicke parameters of
-$\{\eta^{OP}_1,\eta^{OP}_2,\eta^{OP}_3\} = \{???, ???, ???\}$.
-Moreover, due to the unresolved(?) hyperfine structure in the $3^2P_{3/2}$ manifold,
+$\{\eta^{OP}_1,\eta^{OP}_2,\eta^{OP}_3\} = \{0.60, 0.24, 0.21\}$.
+Moreover, due to the small hyperfine structure in the $3^2P_{3/2}$ manifold,
 the sub-Doppler cooling in sodium is also less efficient and we start the
@@
 parameters, this gives us a initial effective optical pumping Lamb-Dicke parameters of
-$\{\eta^{OP}_{1eff},\eta^{OP}_{2eff},\eta^{OP}_{3eff}\} = \{???, ???, ???\}$
+$\{\eta^{OP}_{1eff},\eta^{OP}_{2eff},\eta^{OP}_{3eff}\} = \{2.97, 0.52, 0.40\}$
 As a result, there is a very high probability of heating during the optical pumping step
@@
 provide us tools to overcome this issue. From our geometry, the Lamb-Dicke parameters for
-Raman transitions are $\{\eta^R_{1},\eta^R_{2},\eta^R_{3}\} = \{???, ???, ???\}$. As shown in
+Raman transitions are $\{\eta^R_{1},\eta^R_{2},\eta^R_{3}\} = \{???, 0.34, 0.29\}$. As shown in
 figure \ref{f-ld}A, the high Raman Lamb-Dicke parameters causes a strong coupling to higher orders
@@
 affecting the branching ratio and increasing the number of photons needed during optical pumping.
-Similar to our loading and imaging process [???], we solve this issue by switching the
-trapping light at $3\text{MHz}$ during the whole cooling sequence.
+Similar to our loading and imaging process \cite{Hutzler2016},
+we solve this issue by switching the trapping light at $3\text{MHz}$
+during the whole cooling sequence.
 Due to the large light shift, the optical pumping is effectively off when the trap light is on.
@@
 The simulation is also used to guide the optimization of the cooling sequence by exploring the
-large parameter space and finding a robust cooling strategy. As shown in figure (?),
+large parameter space and finding a robust cooling strategy. As shown in figure \ref{f-setup}B,
 we found that instead of cooling on only one sideband order at a time, it is generally more
@@
 For the more tightly confined radial directions,
-we starts the cooling with $\{\bar n_2, \bar n_3\}=????, ????$.
+we starts the cooling with $\{\bar n_2, \bar n_3\}=2.2, 1.9$.
 The radial sideband spectra of the initial distribution is shown in figure \ref{f-radial}A
@@
 showing good agreement between the two methods.
-\begin{figure*}
-  \includegraphics[height=4.3cm]{imgs/spectrum_a1.pdf}
-  \includegraphics[height=4.3cm]{imgs/rabi_flop_a1_0.pdf}
-  \includegraphics[height=4.3cm]{imgs/rabi_flop_a1_p1.pdf}
-  \caption{Axial Raman sideband spectrum from first order heating to eighth order cooling
-    (A) before and (B) after Raman sideband cooling.
-    Rabi flopping on axial (C) carrier and (D) first order heating sideband
-    after cooling.
-    Solid lines in (C) and (D) are theoretical fit with a ground state probability of $????\%$.
-    Horizontal dashed lines in (C) and (D) are total survival and detection efficiency.
-    \label{f-axial}}
-\end{figure*}
 
@@
 % Missing:
-% ?? D1 OP
 % ?? Blackman pulse

### 2017-06-05 plot_rabi_flop.jl
Tweak Rabi flopping plot

@@ -42,7 +42,7 @@ const rates_coprop = rates_f1_coprop + rates_f2_coprop
 
 # Matrix elements
 const m_Na = 23e-3 / 6.02e23
-const η_a1 = Trap.η(m_Na, 68.8e3, 2π / 589e-9) / √(2)
+const η_a1 = Trap.η(m_Na, 68.8e3, 2π / 589e-9) * 0.67
 const η_r2 = Trap.η(m_Na, 430e3, 2π / 589e-9) * √(2)
 const η_r3 = Trap.η(m_Na, 589.5e3, 2π / 589e-9) * √(2)
 
@@ -173,26 +173,25 @@ function f1_prob(Ωs, pΩ::AbstractArray, Γ::AbstractMatrix{T},
     return binomial_estimate(count, n)[1]
 end
 
-function f1_prop_getter(Γ, scale=1, δΩ=0)
+function f1_prop_getter(Γ)
     Γ32 = Float32.(Γ)
     rates32 = Γ_to_rates(Γ32)
-    (Ωs, pΩ, t, atol=0.005)->f1_prob(Ωs, pΩ, Γ32, rates32, t, atol, δΩ) * scale
+    (Ωs, pΩ, t, atol=0.005, δΩ=0)->f1_prob(Ωs, pΩ, Γ32, rates32, t, atol, δΩ)
 end
 
-const f_r3 = f1_prop_getter(rates_r3, 0.85)
-const f_r2 = f1_prop_getter(rates_r2, 0.85)
-# const f_a1 = f1_prop_getter(rates_a1, 0.85, 2π * 2e3)
-const f_a1 = f1_prop_getter(rates_a1, 0.85)
+const f_r3 = f1_prop_getter(rates_r3)
+const f_r2 = f1_prop_getter(rates_r2)
+const f_a1 = f1_prop_getter(rates_a1)
 
-function plot_f1(f, ts, Ωs, pΩ; kws...)
+function plot_f1(f, ts, Ωs, pΩ, δΩ=0, scale=0.85; kws...)
     res = zeros(length(ts))
     @time Threads.@threads for i in 1:length(ts)
-        res[i] = f(Ωs, pΩ, Float32(ts[i]), 0.002)
+        res[i] = f(Ωs, pΩ, Float32(ts[i]), 0.002) * scale
     end
     plot(ts * 1e6, res; kws...)
 end
 
-function diviation(f, data, Ωs, pΩ, scale=1 / 0.85)
[…]

### 2017-06-10 paper.tex
Update todo
Update results

@@
   large differential AC Stark shift in the excited state,
-  we achieved a ground state preparation fidelity of $??\%$ after a few hundred ms of cooling
+  we achieved a ground state preparation fidelity of $77.1(35)\%$ after a few hundred ms of cooling
   by using a few new cooling techniques including addressing high order Raman sideband.
@@
 trapped in optical tweezers to the motional ground state with Raman sideband cooling.
-Despite having a large Lamb-Dicke parameter and high initial temperature, we are able to achieve a ground state probability of $XX\%$
+Despite having a large Lamb-Dicke parameter and high initial temperature, we are able to achieve a ground state probability of $77.1(35)\%$
 by utilizing several new cooling techniques and a carefully optimized cooling sequence.
@@
 provide us tools to overcome this issue. From our geometry, the Lamb-Dicke parameters for
-Raman transitions are $\{\eta^R_{1},\eta^R_{2},\eta^R_{3}\} = \{???, 0.34, 0.29\}$. As shown in
+Raman transitions are $\{\eta^R_{1},\eta^R_{2},\eta^R_{3}\} = \{0.40, 0.34, 0.29\}$. As shown in
 figure \ref{f-ld}A, the high Raman Lamb-Dicke parameters causes a strong coupling to higher orders
@@
 we can estimate the ground state probability in each direction based on the height of
-the first order cooling and heating sideband to be $????$ and $????$.
+the first order cooling and heating sideband to be $89.7(19)\%$ and $93.8(26)\%$.
 Due to the complexity of the sideband structure,
@@
 Combining the axial and radial cooling results,
-we have achieved a ground state probability of $....$.
+we have achieved a ground state probability of $77.1(35)\%$.
 We believe this is currently limited by off-resonant scattering from the Raman beams
@@
 % Missing:
-% ?? Blackman pulse
+% ?? Blackman pulse vs square pulse
 

### 2017-06-18 plot_rabi_flop.jl
Update plot numbers

@@ -110,6 +110,10 @@ end
 
 function maybe_save(name)
     if !interactive()
+        dir = dirname(name)
+        if !isempty(dir)
+            mkpath(dir, 0o755)
+        end
         savefig("$name.pdf"; bbox_inches="tight", transparent=true)
         savefig("$name.png"; bbox_inches="tight", transparent=true)
         savefig("$name.svg", bbox_inches="tight", transparent=true)
@@ -186,27 +190,30 @@ const f_a1 = f1_prop_getter(rates_a1)
 function plot_f1(f, ts, Ωs, pΩ, δΩ=0, scale=0.85; kws...)
     res = zeros(length(ts))
     @time Threads.@threads for i in 1:length(ts)
-        res[i] = f(Ωs, pΩ, Float32(ts[i]), 0.002) * scale
+        res[i] = f(Ωs, pΩ, Float32(ts[i]), 0.002, δΩ) * scale
     end
     plot(ts * 1e6, res; kws...)
 end
 
-function diviation(f, data, Ωs, pΩ, scale=1 / 0.85, δΩ=0)
-    params, ratios, uncs = NaCsData.get_values(data)
-    perm = sortperm(params)
-    params = params[perm] * 1e-6
-    ratios = ratios[perm, 2] .* scale
-    uncs = uncs[perm, 2] .* scale
-    n = length(params)
-    s = 0.0
-    for i in 1:n
-        s += ((f(Ωs, pΩ, Float32(params[i]), 0.001, δΩ) - ratios[i]) / uncs[i])^2
-    end
-    return s, n
-end
+# function diviation(f, data, Ωs, pΩ, scale=1 / 0.85, δΩ=0)
+#     params, ratios, uncs = NaCsData.get_values(data)
+#     perm = sortperm(params)
+#     params = params[perm] * 1e-6
+#     ratios = ratios[perm, 2] .* scale
+#     uncs = uncs[perm, 2] .* scale
+#     n = length(params)
+#     s = 0.0
+#     for i in 1:n
+#         s += ((f(Ωs, pΩ, Float32(params[i]), 0.001, δΩ) - ratios[i]) / uncs[i])^2
[…]

### 2017-06-19 plot_rabi_flop.jl
Fit before cooling

@@ -46,15 +46,15 @@ const η_a1 = Trap.η(m_Na, 68.8e3, 2π / 589e-9) * 0.67
 const η_r2 = Trap.η(m_Na, 430e3, 2π / 589e-9) * √(2)
 const η_r3 = Trap.η(m_Na, 589.5e3, 2π / 589e-9) * √(2)
 
-const ns_a1 = 0:75
+const ns_a1 = 0:150
 const meles_a1_0 = Trap.sideband.(ns_a1, ns_a1, η_a1)
 const meles_a1_p1 = Trap.sideband.(ns_a1, ns_a1 .+ 1, η_a1)
 
-const ns_r2 = 0:25
+const ns_r2 = 0:50
 const meles_r2_0 = Trap.sideband.(ns_r2, ns_r2, η_r2)
 const meles_r2_p1 = Trap.sideband.(ns_r2, ns_r2 .+ 1, η_r2)
 
-const ns_r3 = 0:25
+const ns_r3 = 0:50
 const meles_r3_0 = Trap.sideband.(ns_r3, ns_r3, η_r3)
 const meles_r3_p1 = Trap.sideband.(ns_r3, ns_r3 .+ 1, η_r3)
 
@@ -161,11 +161,15 @@ function f1_prob(Ωs, pΩ::AbstractArray, Γ::AbstractMatrix{T},
                 break
             end
         end
-        Ω = T(sqrt(Ωs[j]^2 + (δΩ * randn(rd))^2))
+        Ω0 = Ωs[j]
+        δ = δΩ * randn(rd)
+        Ω = T(sqrt(Ω0^2 + δ^2))
         i_final = propagate_multistates(Ω, 1, 6, Γ, rates, 1, tmax, rd)
         if i_final > 5
-            # count F1
-            count += 1
+            if rand(rd) < Ω0^2 / Ω^2
+                # count F1
+                count += 1
+            end
         end
         if i % 256 == 0
             r, s = binomial_estimate(count, i)
@@ -195,6 +199,23 @@ function plot_f1(f, ts, Ωs, pΩ, δΩ=0, scale=0.85; kws...)
     plot(ts * 1e6, res; kws...)
 end
 
[…]

### 2017-06-19 paper.tex
Number update; Remove almost all "?"

@@
     after cooling.
-    Solid lines in (C) and (D) are theoretical fit with a ground state probability of $????\%$.
-    Horizontal dashed lines in (A) to (D) are total survival and detection efficiency.
+    Solid lines in (C) and (D) are theoretical fit with a ground state probability of $93\%$.
     \label{f-radial}}
@@
     after cooling.
-    Solid lines in (C) and (D) are theoretical fit with a ground state probability of $????\%$.
-    Horizontal dashed lines in (C) and (D) are total survival and detection efficiency.
+    Solid lines in (C) and (D) are theoretical fit with a ground state probability of $92\%$.
     \label{f-axial}}
@@
 is approximately proportional to the effective Lamb-Dicke parameter
-$\eta^{OP}_{eff}=\sqrt{2n+1}\eta^{OP}$ where $\eta^{OP}=k^{OP}???$ is the Lamb-Dicke parameter for
+$\eta^{OP}_{eff}=\sqrt{2n+1}\eta^{OP}$ where $\eta^{OP}=k^{OP}\sqrt{\hbar/2m\omega}$ is the Lamb-Dicke parameter for
 optical pumping.
@@
 \cite{Thompson2013,Kaufman2012}
-and Cesium [????], such experiments generally use good polarization gradient cooling
+and Cesium [??], such experiments generally use good polarization gradient cooling
 and a tight confinement to achieve a small Lamb-Dicke parameter and effective Lamb-Dicke parameter.
@@
 a small Lamb-Dicke parameter. However, since the Lamb-Dicke parameter $\eta$ is inversely
-proportional to $\sqrt{m}$ (???) where $m$ is the mass of the atom, it is larger for sodium
-given the same trap depth (???).
+proportional to $\sqrt[4]{m}/\lambda$ where $m$ is the mass of the atom and $\lambda$
+is the wavelength of the atomic transition,
+it is larger for sodium given the same trap depth due to its low mass and short D line wavelength.
 With $45mW$ of power at the focus of the trap, we measured a trapping frequency of
@@
 the sub-Doppler cooling in sodium is also less efficient and we start the
-Raman sideband cooling with a initial temperature of $40\mu K$. Combined with the high Lamb-Dicke
+Raman sideband cooling with a initial temperature of $70\mu K$. Combined with the high Lamb-Dicke
 parameters, this gives us a initial effective optical pumping Lamb-Dicke parameters of
-$\{\eta^{OP}_{1eff},\eta^{OP}_{2eff},\eta^{OP}_{3eff}\} = \{2.97, 0.52, 0.40\}$
+$\{\eta^{OP}_{1eff},\eta^{OP}_{2eff},\eta^{OP}_{3eff}\} = \{3.97, 0.67, 0.50\}$
 As a result, there is a very high probability of heating during the optical pumping step
@@
 as a independent way to obtain the population in different motional states.
-Fitting the Rabi flopping data give a ground state probability of $????$ and $????$,
+Fitting the Rabi flopping data give a ground state probability of $90\%$ and $92\%$,
 showing good agreement between the two methods.
@@
 The axial direction is much less confined and therefore has a much higher initial effective
-Lamb-Dicke parameter of $\eta^{OP}_{eff1}\approx3.3$.
+Lamb-Dicke parameter of $\eta^{OP}_{eff1}\approx3.97$.
 The line in figure \ref{f-axial}A shows the Raman spectrum in the axial direction
@@
 cooling sideband is also strongly suppressed.
-The ground state probability calculated from this spectrum is $????$.
+The ground state probability calculated from this spectrum is $91.6(28)\%$.
 We can also use Rabi flopping on the carrier and heating sideband to verify this result

### 2017-06-19 calc_eta_eff.jl

@@ -1,0 +1,27 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
+import NaCsCalc: Trap
+
+# Matrix elements
+const m_Na = 23e-3 / 6.02e23
+const ν_a1 = 68.8e3
+const ν_r2 = 430e3
+const ν_r3 = 589.5e3
+const η_a1_op = Trap.η(m_Na, ν_a1, 2π / 589e-9)
+const η_r2_op = Trap.η(m_Na, ν_r2, 2π / 589e-9)
+const η_r3_op = Trap.η(m_Na, ν_r3, 2π / 589e-9)
+const η_a1 = η_a1_op * 0.67
+const η_r2 = η_r2_op * √(2)
+const η_r3 = η_r3_op * √(2)
+
+function calc_η_eff(TμK)
+    ħ = 1.0545718e-34
+    k_B = 1.38064852e-23
+    Hz_per_μK = k_B * 1e-6 / ħ / 2π
+    THz = TμK * Hz_per_μK
+    nbars = THz ./ (ν_a1, ν_r2, ν_r3)
+    return sqrt.(2 .* nbars .+ 1) .* (η_a1_op, η_r2_op, η_r3_op)
+end
+
+@show calc_η_eff(70)

### 2017-06-19 plot_rabi_flop.jl

@@ -230,7 +230,7 @@ end
 #     return s, n
 # end
 
-# r3 0.90±0.02
+# r3 0.90±0.05
 
 const τ_r3 = 11.445e-6
 const p_r3 = [0.93, 0.057, 0.013]
@@ -271,7 +271,7 @@ text(10, 0.9, "(D)")
 grid()
 maybe_save("$(prefix)_r3_p1")
 
-# r2 0.90±0.03
+# r2 0.90±0.06
 
 const τ_r2 = 11.608e-6
 const p_r2 = [0.896, 0.048, 0.056]
@@ -320,7 +320,7 @@ const p_a1 = [0.92, 0.05, 0.02]
 const δΩ_a1 = 15e3
 
 const τ_a1_init = 65e-6
-const nbar_init_a1 = 27.0
+const nbar_init_a1 = 20.0
 const δΩ_a1_init = 25e3
 
 figure()

### 2017-06-19 paper.tex
Fix conflicts but include edits I made on this branch so far

@@
 \begin{document}
-\title{Motional Quantum Ground-State Cooing of a Single Sodium Atom}
+\title{Motional Quantum Ground-State Cooing Outside the Lamb-Dicke Regime}
 \author{Yichao Yu}
@@
   large differential AC Stark shift in the excited state,
-  we achieved a ground state preparation fidelity of $77.1(35)\%$ after a few hundred ms of cooling
+  we achieved a ground state preparation fidelity of $77(4)\%$ after a few hundred ms of cooling
   by using a few new cooling techniques including addressing high order Raman sideband.
@@
 
-Single neutral atoms trapped in optical tweezers provide a promising system
-for various applications including quantum information, quantum chemistry
-and quantum simulation of many-body systems.
-Long-range interactions between the sites can be achieved by using Rydberg atoms,
-polar molecules, or dipolar atoms.
-Polar molecules offer the additional advantage of a high degree of tunability,
-including the shape, range, and strength of the interaction.
-Arrays of optical tweezers offer the ability to move, detect, and manipulate individual sites,
-and can be used to prepare complex interacting systems with high fidelity.
-In order to achieve long coherence time and full quantum control of the system needed for
-these applications,
-it is usually necessary to control the thermal motion of the atoms by cooling to the
-three dimensional motional ground state in the optical tweezer,
-which has already been demonstrated with heavy alkali atoms including rubidium and cesium.
-However, some of the important properties of previous experiments,
-for example low initial temperature and small Lamb-Dicke parameter,
-may not be easily achievable for other systems, such as directly laser-cooled polar molecules,
-or atoms with challenging sub-Doppler cooling such as Na, K, and Li.
-To extend the versatility of this approach, we must be able to apply it in a more general case.
+Systems of single neutral atoms trapped in optical tweezers are an exciting platform to study quantum information, quantum chemistry,
+and quantum simulation of many-body systems [REF].
+This approach provides full single-site resolution and control, and can feature long-range interactions via Rydberg atoms,
+polar molecules, or dipolar atoms [REF].
+Polar molecules in particular offer the additional advantages of long-lived internal states and a high degree of tunability,
+including the shape, range, and strength of the interaction [REF].
+Optical tweezers can also be re-arranged in real-time, allowing rapid preparation of atoms in complex geometries with high fidelity [REF].
+
+In order to achieve long coherence times and full quantum control of the system,
+it is typically necessary to cool the atom to the
+three dimensional motional ground state in the optical tweezer.
+This has been demonstrated for neutral Rb and Cs [REF] in experiments that had low initial temperature and small Lamb-Dicke parameter.  
+These features
+may not be easily achievable for other systems, such as directly laser-cooled polar molecules [REF],
+or atoms with challenging sub-Doppler cooling such as Na, K, and Li [REF].
 In this letter, we cool single sodium atoms
 trapped in optical tweezers to the motional ground state with Raman sideband cooling.
-Despite having a large Lamb-Dicke parameter and high initial temperature, we are able to achieve a ground state probability of $77.1(35)\%$
-by utilizing several new cooling techniques and a carefully optimized cooling sequence.
-
-The Raman sideband cooling we used to achieve the high ground state preparation fidelity
-consists of multiple cycles of laser pulses to manipulate the internal and
-motional states of the atoms.
-Figure \ref{f-setup}A shows the schematic of the energy levels and the cooling sequence
-in our setup.
-Each cooling cycle starts with the sodium atom in the $|F=2, m_F=-2\rangle$
-ground electronic state and a certain vibration state $n$.
-In the first step, a Raman pulse drives a transition to the motional state $n-\Delta n$
-to reduce the motional energy while also changing the internal state to $|F=1, m_F=-1\rangle$.
-In the second step, which finishes the cooling cycle,
-an optical pumping pulse bring the atom back to the $|F=2, m_F=-2\rangle$ state to take away
-the entropy. The second step could also change the motional state of the atoms which
-could cause heating. The possibility for this to happen for an atom in the motional level $n$
-is approximately proportional to the effective Lamb-Dicke parameter
-$\eta^{OP}_{eff}=\sqrt{2n+1}\eta^{OP}$ where $\eta^{OP}=k^{OP}\sqrt{\hbar/2m\omega}$ is the Lamb-Dicke parameter for
-optical pumping.
-The geometry of the relevant beams and their polarizations is showed in figure \ref{f-setup}B.
-The optical tweezer has one weakly confined axial direction (axis $1$) and
-two more strongly confined radial directions (axis $2$ and $3$).
-Multiple pairs of beams are used to drive the Raman transition during cooling in order to
-isolate and maximize the coupling to different trap axis.
-
-Although Raman sideband cooling to motional ground state has already been successfully
-implemented on neutral atoms in other experiments using heavier species like Rubidium
-\cite{Thompson2013,Kaufman2012}
-and Cesium [??], such experiments generally use good polarization gradient cooling
-and a tight confinement to achieve a small Lamb-Dicke parameter and effective Lamb-Dicke parameter.
-However, this regime is harder to achieve with sodium atoms, creating additional challenges for
-us to realize ground state cooling. On the other hand, since these conditions can also be difficult
-to meet for other interesting systems like directly laser cooled molecules, the techniques we
-use to overcome these challenges could be useful for a wider variety of systems.
+Despite having a large Lamb-Dicke parameter and high initial temperature, we are able to achieve a ground state probability of $77(4)\%$
+by utilizing several new cooling techniques and a carefully optimized cooling sequence.  Our approach is quite general, and opens up ground-state cooling for other systems.
 

### 2017-06-19 paper.tex
Mostly style/grammar, some suggestions, moved temperature measurement discussion

@@
   \includegraphics[height=4.5cm]{sequence.pdf}
-  \caption{(A) Energy levels and schematics of Raman sideband cooling.
-    The Raman transitions has a one photon detuning $\Delta=25GHz$ from the D2 line.
-    We use D1 light with $\sigma^-$ polarization to repump atom out of $|F=2,m_F=-1\rangle$
-    state to minimize heating on the atom in $|F=2,m_F=-2\rangle$ state.
+  \caption{(A) Energy levels and schematic of Raman sideband cooling.
+    The Raman transitions have a one photon detuning $\Delta=25$ GHz from the D2 line.
+    We use D1 light with $\sigma^-$ polarization to repump atoms out of $|F=2,m_F=-1\rangle$
+    state to minimize heating on the atom in $|F=2,m_F=-2\rangle$ state [TALK ABOUT THIS IN THE TEXT].
     (B) Geometry and polarizations of the Raman and optical pumping beams relative to the
     optical tweezer and bias magnetic field.
-    (C) Schematics of the cooling sequence. The tweezer is switching at $3\text{MHz}$ to
-    reduce light shift during optical pumping. Each cooling cycle consists of $8$ pulses.
+    (C) Schematic of the cooling sequence. The tweezer switches at 3 MHz to
+    reduce light shifts during optical pumping. Each cooling cycle consists of $8$ pulses.
     The four axial pulses are addressing two neighboring cooling orders.
@@
     (A) before and (B) after Raman sideband cooling.
-    The data for the second and higher orders of cooling sidebands are taken with $150\mu s$
-    pulse time and the rest are taken with $125\mu s$ pulse time.
+    The data for the second and higher orders of cooling sidebands are taken with 150 $\mu$s
+    pulse time and the rest are taken with 125 $\mu$s pulse time.
     Rabi flopping on axial (C) carrier and (D) first order heating sideband
@@
 it is larger for sodium given the same trap depth due to its low mass and short D line wavelength.
-With $45mW$ of power at the focus of the trap, we measured a trapping frequency of
-$\{\omega_1,\omega_2,\omega_3\}/2\pi = \{69, 430, 590\}\ \text{\text{kHz}}$
+With 45 mW of power in the trap, we measure trapping frequencies of
+$\{\omega_1,\omega_2,\omega_3\}/2\pi = \{69, 430, 590\}\ \text{\text{kHz}}$ [ERROR BARS]
 which corresponds to optical pumping Lamb-Dicke parameters of
-$\{\eta^{OP}_1,\eta^{OP}_2,\eta^{OP}_3\} = \{0.60, 0.24, 0.21\}$.
+$\{\eta^{OP}_1,\eta^{OP}_2,\eta^{OP}_3\} = \{0.60, 0.24, 0.21\}$ [ERROR BARS].
 Moreover, due to the small hyperfine structure in the $3^2P_{3/2}$ manifold,
 the sub-Doppler cooling in sodium is also less efficient and we start the
-Raman sideband cooling with a initial temperature of $70\mu K$. Combined with the high Lamb-Dicke
+Raman sideband cooling with a initial temperature of 70 $\mu$K. Combined with the high Lamb-Dicke
 parameters, this gives us a initial effective optical pumping Lamb-Dicke parameters of
@@
 As a result, there is a very high probability of heating during the optical pumping step
-(figure \ref{f-ld}B) causing a $30\%$ average heating probability during optical pumping
-in the weakly confined axial direction. Fortunately, the high Lamb-Dicke parameters also
-provide us tools to overcome this issue. From our geometry, the Lamb-Dicke parameters for
-Raman transitions are $\{\eta^R_{1},\eta^R_{2},\eta^R_{3}\} = \{0.40, 0.34, 0.29\}$. As shown in
+(figure \ref{f-ld}B) causing an estimated $30\%$ average heating probability during optical pumping
+in the weakly confined axial direction.
+
+Fortunately, the high Lamb-Dicke parameters also
+provide us with tools to overcome this issue. The Lamb-Dicke parameters for the
+Raman transitions in our configuration are $\{\eta^R_{1},\eta^R_{2},\eta^R_{3}\} = \{0.40, 0.34, 0.29\}$. As shown in
 figure \ref{f-ld}A, the high Raman Lamb-Dicke parameters causes a strong coupling to higher orders
 of cooling sidebands, especially for high motional states.
-This enables us to cool atoms in high motional states by driving on high order Raman sidebands,
-removing more motional energy in a single cooling pulse and offsetting the effect of
-strong heating. Since the heating probability is higher for high motional states,
+This enables cooling of atoms in high motional states by driving higher order Raman sidebands,
+removing more motional energy in a single cooling pulse and offsetting the effect of heating. Since the heating probability is higher for high motional states,
 cooling on these high order sidebands can greatly suppress the high heating during
 optical pumping during the initial cooling. Since the coupling strength of different orders
-do not reach their minimums at the same time, using multiple orders of motional sidebands
+do not reach their minimums at the same time [FIG], using multiple orders of motional sidebands
 for cooling also avoids accumulation of population near the coupling minimum of a particular
@@
 
-In additional to improving the cooling efficiency, the large Raman Lamb-Dicke parameters $\eta^R$
-also creates difficulties for measuring the temperature. Traditional sideband thermometry uses
-the ratio of the cooling and heating sidebands to measure $\bar n / (\bar n + 1)$, which relies
-on the coupling strength to be proportional to $\sqrt{n}$. However, since we are not in the
-Lamb-Dicke regime, the coupling strength deviates from this simple scaling rule quickly as already
-shown in figure \ref{f-ld}A, causing the normal sideband thermometry to break down.
-In order to solve this problem, when the atom temperature is still high,
-we measure the heights of multiple sidebands to make sure no population is hidden at the
-minimum of one sideband order. And when the atom is cooled down, we estimate the temperature
-and ground state population under the assumption that only a few states are populated.
-This result is then verified using independent measure of Rabi flopping on the carrier and heating
-sidebands since they provide more information about the distribution of coupling strength.
-
-Another issue caused by the high initial temperature is trap anharmonicity.
-Although the potential near the center of a focused Gaussian beam can be approximated
-by a harmonic trap, when a large number of levels are populated due to high initial temperature
-the anharmonicity of the trap can lead to broadening of the sideband and decrease of
-the sideband signal. In our setup, this effect limits the Rabi frequency of the Raman pulse
-on the radial sidebands to be no lower than tens of kilo-Hertz in order to drive atoms in
-different motional states equally.
-
-Finally, the deep trap that is needed to trap and image single sodium atom also creates
-a very large AC Stark shift in the excited state. For the trap depth we are using, the
-light shift in the center of the trap is as large as $300\text{MHz}$.
-In additional to creating a large and position dependent detuning for the optical pumping light,
-it also mixes the excited state state hyperfine levels,
-affecting the branching ratio and increasing the number of photons needed during optical pumping.
-Similar to our loading and imaging process \cite{Hutzler2016},
-we solve this issue by switching the trapping light at $3\text{MHz}$
-during the whole cooling sequence.
-Due to the large light shift, the optical pumping is effectively off when the trap light is on.
+The high initial temperature also causes additional complications.  First, population in high motional states means that the atoms sample
+the anharmonicity of the trap away from the harmonic center.  This results in sidebands that are broader and of reduced height [FIG], and limits the Rabi frequency of the Raman pulse
+on the radial sidebands to be no lower than tens of kHz in order to drive atoms in
+different motional states equally.  [EXPLAIN THIS A LITTLE MORE].
+Second, the deep trap that is needed to trap and image single sodium atom also creates
+a very large AC Stark shift in the excited state (as large as 300 MHz).
+This creates large, position-dependent detuning for the optical pumping light and mixes the excited state state hyperfine levels,
+which affects the branching ratios and increases the number of photons needed for optical pumping.
+We solve this issue by switching the trapping light at $3\text{MHz}$
+during the whole cooling sequence, similar to our loading and imaging process \cite{Hutzler2017-LightShifts}, but leave on the OP light with constant intensity.
+Due to the large light shift, the OP light is effectively off when the trap light is on.
 Since the atom can only be addressed by the optical pumping light when the trap light is off,
@@
 
-Taking all the features of our system into account, we use a Monte-Carlo simulation to verify
-the validity of our method.
+Taking all these features of our system into account, we use a Monte-Carlo simulation to verify
+the validity of our method [WRITE BRIEF SUMMARY IN APPENDIX?].
 In the simulation, we can observe the high heating rate due to the high Lamb-Dicke parameters
@@
 For the more tightly confined radial directions,
-we starts the cooling with $\{\bar n_2, \bar n_3\}=2.2, 1.9$.
+we begin the cooling with $\{\bar n_2, \bar n_3\}=2.2, 1.9$ [ERROR BARS].
 The radial sideband spectra of the initial distribution is shown in figure \ref{f-radial}A
@@
 second order cooling sidebands.
-After applying about 1000 cooling pulses cooling in all three dimensions
+After applying around 1000 cooling pulses cooling in all three dimensions
 starting with cooling on the radial second order,
-the Raman spectrum with the same parameter is shown in figure \ref{f-radial}B,
+the Raman spectrum with the same parameters is shown in figure \ref{f-radial}B,
 where the first and second order cooling sidebands on both axis are suppressed.
@@
 we can estimate the ground state probability in each direction based on the height of
-the first order cooling and heating sideband to be $89.7(19)\%$ and $93.8(26)\%$.
-Due to the complexity of the sideband structure,
-we measured the Rabi flopping on the carrier and heating sideband before and after cooling
-(\ref{f-radial}C and \ref{f-radial}D)
-as a independent way to obtain the population in different motional states.
-Fitting the Rabi flopping data give a ground state probability of $90\%$ and $92\%$,
+the first order cooling and heating sideband to be $90(2)\%$ and $94(3)\%$.
+
+It is important to note that the large Raman Lamb-Dicke parameters $\eta^R$ mean that we must use caution when measuring the temperature.
+Traditional sideband thermometry uses
+the ratio of the cooling and heating sidebands to measure $\bar n / (\bar n + 1)$, which relies
+on the coupling strength to be proportional to $\sqrt{n}$. However, outside the
+Lamb-Dicke regime, the coupling strength deviates from this simple scaling rule rapidly as
+shown in figure \ref{f-ld}A.
+When the atom temperature is still high,
+we measure the heights of multiple sidebands to make sure no population is hidden at the
+minimum of one sideband order. Once the atom is cooled down, we estimate the temperature
+and ground state population under the assumption that only a few states are populated.
+We can verify the result via an independent measurement of Rabi flopping on the carrier and heating
+sidebands. This data is shown before and after cooling in Figures
+\ref{f-radial}C and \ref{f-radial}D
+and yields $90\%$ and $92\%$ [ERROR BARS],
 showing good agreement between the two methods.
@@
 The axial direction is much less confined and therefore has a much higher initial effective
-Lamb-Dicke parameter of $\eta^{OP}_{eff1}\approx3.97$.
-The line in figure \ref{f-axial}A shows the Raman spectrum in the axial direction
-before applying Raman sideband cooling where we can see clearly resolved Raman cooling sidebands
-up to the eighth order suggesting that we have many motional states populated in this direction.
-Therefore, we starts our cooling sequence by driving Raman transitions on the eighth order axial
+Lamb-Dicke parameter of $\eta^{OP}_{eff1}\approx 3.97$, and is therefore more difficult to cool.
+Figure \ref{f-axial}A shows the Raman spectrum in the axial direction
+before applying Raman sideband cooling; the clearly resolved sidebands
+up to eighth order indicates population in highly-excited motional levels.
+Therefore, we begin our cooling sequence by driving Raman transitions on the eighth order axial
 cooling sideband. After applying the cooling sequence identical to the one we use to cool
 the radial directions, the spectrum is shown in figure \ref{f-axial}B.
-All of the high order ($\geqslant2$) axial cooling sidebands disappeared and the first order
-cooling sideband is also strongly suppressed.
-The ground state probability calculated from this spectrum is $91.6(28)\%$.
-We can also use Rabi flopping on the carrier and heating sideband to verify this result
+All of the high order ($\geqslant2$) axial cooling sidebands disappear, and the first order
+cooling sideband is strongly suppressed.
+The ground state probability calculated from this spectrum is $92(3)\%$.
+We can again use Rabi flopping on the carrier and heating sideband to verify this result
 similar to the radial direction. In this case, we see very good agreement on the carrier
@@
 heating sideband (figure \ref{f-axial}C).
-We believe this decoherence is caused by technical noise in our setup which
-produces the strongest effect on this transition due to its slow Rabi frequency.
-The decoherence time scale agree with the magnetic field fluctuation we measured which produces
+We believe this decoherence is caused by technical noise, which is the most pronounced 
+on this transition due to its slow Rabi frequency.
+The decoherence time scale is consistent with magnetic field fluctuations of XXX mG that we have measured in the lab, which produces
 a Zeeman shift of around $5\text{kHz}$.
@@
 Combining the axial and radial cooling results,
-we have achieved a ground state probability of $77.1(35)\%$.
+we have achieved a 3D ground state probability of $77(4)\%$.
 We believe this is currently limited by off-resonant scattering from the Raman beams
-and the resonance shift caused by magnetic field fluctuation.
-Improvements on these should improve the cooling performance even further.
+and the resonance shift caused by magnetic field fluctuations.
+Improvements on these [HOW?] should improve the cooling performance even further.
 We have shown that despite the difficulty in cooling sodium atoms,

### 2017-06-19 plot_rabi_flop.jl
Update before cooling fit to use different decoherence time for axial carrier and heating sideband

@@ -319,9 +319,10 @@ const τ_a1 = 60.3e-6
 const p_a1 = [0.92, 0.05, 0.02]
 const δΩ_a1 = 15e3
 
-const τ_a1_init = 65e-6
-const nbar_init_a1 = 20.0
-const δΩ_a1_init = 25e3
+const τ_a1_init = 80e-6
+const nbar_init_a1 = 10.0
+const δΩ_a1_init_0 = 25e3
+const δΩ_a1_init_p1 = 50e3
 
 figure()
 ts_a1_0 = linspace(0, 300e-6, 256)
@@ -330,7 +331,7 @@ plot_f1(f_a1, ts_a1_0, 2π / τ_a1 * (meles_a1_0[1:3] * meles_r3_0[1:3]'), p_a1 
 ts_a1_0_init = linspace(0, 150e-6, 256)
 plot_data(data_before_a1_0, 1, fmt="C3o")
 plot_f1_thermal2(f_a1, ts_a1_0_init, 2π / τ_a1_init * meles_a1_0, nbar_init_a1,
-                 meles_r3_0, nbar_init_r3, δΩ_a1_init, color="C3")
+                 meles_r3_0, nbar_init_r3, δΩ_a1_init_0, color="C3")
 ylim([0, 1])
 xlim([ts_a1_0[1] * 1e6, ts_a1_0[end] * 1e6])
 xlabel("Time (\$\\mu s\$)")
@@ -349,7 +350,7 @@ plot_f1(f_a1, ts_a1_p1, 2π / τ_a1 * (meles_a1_p1[1:3] * meles_r3_0[1:3]'),
 ts_a1_p1_init = linspace(0, 400e-6, 256)
 plot_data(data_before_a1_p1, 1, fmt="C3o")
 plot_f1_thermal2(f_a1, ts_a1_p1_init, 2π / τ_a1_init * meles_a1_p1, nbar_init_a1,
-                 meles_r3_0, nbar_init_r3, δΩ_a1_init, color="C3")
+                 meles_r3_0, nbar_init_r3, δΩ_a1_init_p1, color="C3")
 ylim([0, 1])
 xlim([ts_a1_p1[1] * 1e6, ts_a1_p1[end] * 1e6])
 xlabel("Time (\$\\mu s\$)")

### 2017-06-19 paper.tex
Whitespace changes, reference that got deleted
Use fxnote for notes so that they are more searchable in the tex file

@@
 \usepackage[colorlinks=true]{hyperref}
+
+\usepackage[final]{fixme}
+\fxsetup{layout=inline}
 
@@
     We use D1 light with $\sigma^-$ polarization to repump atoms out of $|F=2,m_F=-1\rangle$
-    state to minimize heating on the atom in $|F=2,m_F=-2\rangle$ state [TALK ABOUT THIS IN THE TEXT].
+    state to minimize heating on the atom in $|F=2,m_F=-2\rangle$ state
+    \fxnote{TALK ABOUT THIS IN THE TEXT}.
     (B) Geometry and polarizations of the Raman and optical pumping beams relative to the
@@
 Systems of single neutral atoms trapped in optical tweezers are an exciting platform to study quantum information, quantum chemistry,
-and quantum simulation of many-body systems [REF].
+and quantum simulation of many-body systems \fxnote{REF}.
 This approach provides full single-site resolution and control, and can feature long-range interactions via Rydberg atoms,
-polar molecules, or dipolar atoms [REF].
+polar molecules, or dipolar atoms \fxnote{REF}.
 Polar molecules in particular offer the additional advantages of long-lived internal states and a high degree of tunability,
-including the shape, range, and strength of the interaction [REF].
-Optical tweezers can also be re-arranged in real-time, allowing rapid preparation of atoms in complex geometries with high fidelity [REF].
+including the shape, range, and strength of the interaction \fxnote{REF}.
+Optical tweezers can also be re-arranged in real-time, allowing rapid preparation of atoms in complex geometries with high fidelity \fxnote{REF}.
 
@@
 three dimensional motional ground state in the optical tweezer.
-This has been demonstrated for neutral Rb and Cs [REF] in experiments that had low initial temperature and small Lamb-Dicke parameter.  
+This has been demonstrated for neutral Rb\cite{Thompson2013,Kaufman2012} and Cs \fxnote{REF} in experiments that had low initial temperature and small Lamb-Dicke parameter.
 These features
-may not be easily achievable for other systems, such as directly laser-cooled polar molecules [REF],
-or atoms with challenging sub-Doppler cooling such as Na, K, and Li [REF].
+may not be easily achievable for other systems, such as directly laser-cooled polar molecules \fxnote{REF},
+or atoms with challenging sub-Doppler cooling such as Na, K, and Li \fxnote{REF}.
 In this letter, we cool single sodium atoms
@@
 With 45 mW of power in the trap, we measure trapping frequencies of
-$\{\omega_1,\omega_2,\omega_3\}/2\pi = \{69, 430, 590\}\ \text{\text{kHz}}$ [ERROR BARS]
+$\{\omega_1,\omega_2,\omega_3\}/2\pi = \{69, 430, 590\}\ \text{\text{kHz}}$ \fxnote{ERROR BARS}
 which corresponds to optical pumping Lamb-Dicke parameters of
-$\{\eta^{OP}_1,\eta^{OP}_2,\eta^{OP}_3\} = \{0.60, 0.24, 0.21\}$ [ERROR BARS].
+$\{\eta^{OP}_1,\eta^{OP}_2,\eta^{OP}_3\} = \{0.60, 0.24, 0.21\}$ \fxnote{ERROR BARS}.
 Moreover, due to the small hyperfine structure in the $3^2P_{3/2}$ manifold,
@@
 optical pumping during the initial cooling. Since the coupling strength of different orders
-do not reach their minimums at the same time [FIG], using multiple orders of motional sidebands
+do not reach their minimums at the same time \fxnote{FIG}, using multiple orders of motional sidebands
 for cooling also avoids accumulation of population near the coupling minimum of a particular
@@
 The high initial temperature also causes additional complications.  First, population in high motional states means that the atoms sample
-the anharmonicity of the trap away from the harmonic center.  This results in sidebands that are broader and of reduced height [FIG], and limits the Rabi frequency of the Raman pulse
+the anharmonicity of the trap away from the harmonic center.  This results in sidebands that are broader and of reduced height \fxnote{FIG}, and limits the Rabi frequency of the Raman pulse
 on the radial sidebands to be no lower than tens of kHz in order to drive atoms in
-different motional states equally.  [EXPLAIN THIS A LITTLE MORE].
+different motional states equally. \fxnote{EXPLAIN THIS A LITTLE MORE}.
 Second, the deep trap that is needed to trap and image single sodium atom also creates
@@
 Taking all these features of our system into account, we use a Monte-Carlo simulation to verify
-the validity of our method [WRITE BRIEF SUMMARY IN APPENDIX?].
+the validity of our method \fxnote{WRITE BRIEF SUMMARY IN APPENDIX?}.
 In the simulation, we can observe the high heating rate due to the high Lamb-Dicke parameters
@@
 For the more tightly confined radial directions,
-we begin the cooling with $\{\bar n_2, \bar n_3\}=2.2, 1.9$ [ERROR BARS].
+we begin the cooling with $\{\bar n_2, \bar n_3\}=2.2, 1.9$ \fxnote{ERROR BARS}.
 The radial sideband spectra of the initial distribution is shown in figure \ref{f-radial}A
@@
 \ref{f-radial}C and \ref{f-radial}D
-and yields $90\%$ and $92\%$ [ERROR BARS],
+and yields $90\%$ and $92\%$ \fxnote{ERROR BARS},
 showing good agreement between the two methods.
@@
 and the resonance shift caused by magnetic field fluctuations.
-Improvements on these [HOW?] should improve the cooling performance even further.
+Improvements on these \fxnote{HOW?} should improve the cooling performance even further.
 We have shown that despite the difficulty in cooling sodium atoms,

### 2017-06-21 paper.tex
Figure updates

@@
 and quantum simulation of many-body systems \fxnote{REF}.
-This approach provides full single-site resolution and control, and can feature long-range interactions via Rydberg atoms,
-polar molecules, or dipolar atoms \fxnote{REF}.
-Polar molecules in particular offer the additional advantages of long-lived internal states and a high degree of tunability,
-including the shape, range, and strength of the interaction \fxnote{REF}.
+This approach provides full single-site resolution and control, and can feature long-range interactions via Rydberg atoms, polar molecules, or dipolar atoms \fxnote{REF}.
+Polar molecules in particular offer the additional advantages of long-lived internal states
+and a high degree of tunability, including the shape, range,
+and strength of the interaction \fxnote{REF}.
 Optical tweezers can also be re-arranged in real-time, allowing rapid preparation of atoms in complex geometries with high fidelity \fxnote{REF}.
@@
 on this transition due to its slow Rabi frequency.
-The decoherence time scale is consistent with magnetic field fluctuations of XXX mG that we have measured in the lab, which produces
+The decoherence time scale is consistent with magnetic field fluctuations of $1.5$ mG that we have measured in the lab, which produces
 a Zeeman shift of around $5\text{kHz}$.
@@
 % ?? Blackman pulse vs square pulse
+% ?? Start from highest visible order
+% In the text, more description
+% Detail in appendix
 

### 2017-06-21 plot_rabi_flop.jl

@@ -252,7 +252,7 @@ ylim([0, 1])
 xlim([ts_r3_0[1] * 1e6, ts_r3_0[end] * 1e6])
 xlabel("Time (\$\\mu s\$)")
 ylabel("Survival")
-text(5, 0.9, "(C)")
+text(5, 0.9, "(B)")
 grid()
 maybe_save("$(prefix)_r3_0")
 
@@ -267,7 +267,7 @@ ylim([0, 1])
 xlim([ts_r3_p1[1] * 1e6, ts_r3_p1[end] * 1e6])
 xlabel("Time (\$\\mu s\$)")
 ylabel("Survival")
-text(10, 0.9, "(D)")
+text(10, 0.9, "(C)")
 grid()
 maybe_save("$(prefix)_r3_p1")
 
@@ -293,7 +293,7 @@ ylim([0, 1])
 xlim([ts_r2_0[1] * 1e6, ts_r2_0[end] * 1e6])
 xlabel("Time (\$\\mu s\$)")
 ylabel("Survival")
-text(5, 0.9, "(C)")
+text(5, 0.9, "(B)")
 grid()
 maybe_save("$(prefix)_r2_0")
 
@@ -309,7 +309,7 @@ ylim([0, 1])
 xlim([ts_r2_p1[1] * 1e6, ts_r2_p1[end] * 1e6])
 xlabel("Time (\$\\mu s\$)")
 ylabel("Survival")
-text(10, 0.9, "(D)")
+text(10, 0.9, "(C)")
 grid()
 maybe_save("$(prefix)_r2_p1")
 
@@ -336,7 +336,7 @@ ylim([0, 1])
 xlim([ts_a1_0[1] * 1e6, ts_a1_0[end] * 1e6])
 xlabel("Time (\$\\mu s\$)")
 ylabel("Survival")
-text(10, 0.9, "(C)")
+text(10, 0.9, "(B)")
 grid()
 maybe_save("$(prefix)_a1_0")
 
@@ -355,7 +355,7 @@ ylim([0, 1])
 xlim([ts_a1_p1[1] * 1e6, ts_a1_p1[end] * 1e6])
 xlabel("Time (\$\\mu s\$)")
 ylabel("Survival")
-text(20, 0.9, "(D)")
+text(20, 0.9, "(C)")
 grid()
 maybe_save("$(prefix)_a1_p1")
 

### 2017-06-21 plot_spectrum.jl

@@ -118,80 +118,50 @@ data_cool_a1_hi =  NaCsData.map_params(to_sideband(-18.488), split_c[4])
 fig = figure(figsize=[1.6, 1] * 4.8)
 
 # Without cooling
-# ax1 = subplot(211)
 # Radial 2
-plot_data(data_nocool_r2[1], 1, fmt="C3o-", label="Axis 2")
-plot_data(data_nocool_r2[2], 1, fmt="C3o-")
-plot_data(data_nocool_r2[3], 1, fmt="C3o-")
+plot_data(data_nocool_r2[1], 1, fmt="C3^-", label="Ax 2 before")
+plot_data(data_nocool_r2[2], 1, fmt="C3^-")
+plot_data(data_nocool_r2[3], 1, fmt="C3^-")
 # Radial 3
-plot_data(data_nocool_r3[1], 1, fmt="C1o-", label="Axis 3")
+plot_data(data_nocool_r3[1], 1, fmt="C1o-", label="Ax 3 before")
 plot_data(data_nocool_r3[2], 1, fmt="C1o-")
 plot_data(data_nocool_r3[3], 1, fmt="C1o-")
-# axhline(0.95, linewidth=2, color="b", ls="--", alpha=0.3)
-grid()
-ylim([0, 1])
-xlim([-700, 1400])
-legend()
-text(-660, 0.8, "(A)")
-# setp(ax1[:get_xticklabels](), visible=false)
+text(-660, 0.9, "(A)")
 
 # With cooling
-# ax2 = subplot(212)
-# subplots_adjust(hspace=0)
-# axvline(605, linewidth=4, color="k", ls="--", alpha=0.3, ymin=0.08)
-# axvline(1210, linewidth=4, color="k", ls="--", alpha=0.3, ymin=0.05)
-# axvline(430, linewidth=4, color="r", ls="--", alpha=0.3, ymin=0.1)
-# axvline(860, linewidth=4, color="r", ls="--", alpha=0.3, ymin=0.05)
 # Radial 2
-plot_data(data_cool_r2[1], 1, fmt="C2o-")
-plot_data(data_cool_r2[2], 1, fmt="C2o-")
-plot_data(data_cool_r2[3], 1, fmt="C2o-")
+plot_data(data_cool_r2[1], 1, fmt="C2v-", label="Ax 2 after")
+plot_data(data_cool_r2[2], 1, fmt="C2v-")
[…]

### 2017-06-21 paper.tex
Address some of Nick's comments
* Most of the error bars
* Figure label update
* More explaination of anharmonicity
* More detail about improvements to be made

@@
   \includegraphics[height=4.2cm]{imgs/rabi_flop_r3_p1.pdf}
-  \caption{Radial Raman sideband spectrum of first order heating, first order cooling and
-    second order cooling (A) before and (B) after Raman sideband cooling.
-    Rabi flopping on axis 3 (C) carrier and (D) first order heating sideband
-    after cooling.
-    Solid lines in (C) and (D) are theoretical fit with a ground state probability of $93\%$.
+  \caption{(A) Radial Raman sideband spectrum of first order heating, first order cooling and
+    second order cooling before and after Raman sideband cooling.
+    (B,C) Rabi flopping on axis 3 (B) carrier and (C) first order heating sideband
+    before (red) and after (blue) cooling.
+    Solid lines in (B) and (C) are theoretical calculation of the Rabi flopping.
+    The blue lines corresponds to a ground state probability of $93\%$ after cooling and
+    the red lines corresponds to a thermal distribution of $70$ $\mu$K before cooling.
     \label{f-radial}}
@@
   \includegraphics[height=4.2cm]{imgs/rabi_flop_a1_p1.pdf}
-  \caption{Axial Raman sideband spectrum from first order heating to eighth order cooling
-    (A) before and (B) after Raman sideband cooling.
+  \caption{(A) Axial Raman sideband spectrum from first order heating to eighth order cooling
+    before and after Raman sideband cooling.
     The data for the second and higher orders of cooling sidebands are taken with 150 $\mu$s
     pulse time and the rest are taken with 125 $\mu$s pulse time.
-    Rabi flopping on axial (C) carrier and (D) first order heating sideband
-    after cooling.
-    Solid lines in (C) and (D) are theoretical fit with a ground state probability of $92\%$.
+    (B,C) Rabi flopping on axial (B) carrier and (C) first order heating sideband
+    before (red) and after (blue) cooling.
+    Solid lines in (B) and (C) are theoretical calculation of the Rabi flopping.
+    The blue and green lines corresponds to a ground state probability of $92\%$ after cooling and
+    the red lines corresponds to a thermal distribution of $70$ $\mu$K before cooling.
+    The blue lines does not take into account the effect of decoherence due to resonance
+    fluctuation. By comparing it to the green line in (C), which includes a $3$ kHz fluctuation,
+    we can clearly see that this effect is the strongest for the after cooling data on
+    the axial heating sideband where the Rabi frequency is the lowest.
     \label{f-axial}}
@@
 three dimensional motional ground state in the optical tweezer.
-This has been demonstrated for neutral Rb\cite{Thompson2013,Kaufman2012} and Cs \fxnote{REF} in experiments that had low initial temperature and small Lamb-Dicke parameter.
+This has been demonstrated for neutral Rb\cite{Thompson2013,Kaufman2012} and Cs\cite{Liu2017} in experiments that had low initial temperature and small Lamb-Dicke parameter.
 These features
@@
 Despite having a large Lamb-Dicke parameter and high initial temperature, we are able to achieve a ground state probability of $77(4)\%$
-by utilizing several new cooling techniques and a carefully optimized cooling sequence.  Our approach is quite general, and opens up ground-state cooling for other systems.
+by utilizing several new cooling techniques and a carefully optimized cooling sequence.
+Our approach is quite general, and opens up ground-state cooling for other systems.
 
@@
 With 45 mW of power in the trap, we measure trapping frequencies of
-$\{\omega_1,\omega_2,\omega_3\}/2\pi = \{69, 430, 590\}\ \text{\text{kHz}}$ \fxnote{ERROR BARS}
+$\{\omega_1,\omega_2,\omega_3\}/2\pi = \{69(1), 430(4), 590(5)\}\ \text{\text{kHz}}$
 which corresponds to optical pumping Lamb-Dicke parameters of
-$\{\eta^{OP}_1,\eta^{OP}_2,\eta^{OP}_3\} = \{0.60, 0.24, 0.21\}$ \fxnote{ERROR BARS}.
+$\{\eta^{OP}_1,\eta^{OP}_2,\eta^{OP}_3\} = \{0.602(5), 0.241(2), 0.206(1)\}$
 Moreover, due to the small hyperfine structure in the $3^2P_{3/2}$ manifold,
@@
 parameters, this gives us a initial effective optical pumping Lamb-Dicke parameters of
-$\{\eta^{OP}_{1eff},\eta^{OP}_{2eff},\eta^{OP}_{3eff}\} = \{3.97, 0.67, 0.50\}$
+$\{\eta^{OP}_{1eff},\eta^{OP}_{2eff},\eta^{OP}_{3eff}\} = \{4.0(1), 0.67(2), 0.50(1)\}$
 As a result, there is a very high probability of heating during the optical pumping step
@@
 provide us with tools to overcome this issue. The Lamb-Dicke parameters for the
-Raman transitions in our configuration are $\{\eta^R_{1},\eta^R_{2},\eta^R_{3}\} = \{0.40, 0.34, 0.29\}$. As shown in
+Raman transitions in our configuration are $\{\eta^R_{1},\eta^R_{2},\eta^R_{3}\} = \{0.40(1), 0.341(2), 0.291(1)\}$. As shown in
 figure \ref{f-ld}A, the high Raman Lamb-Dicke parameters causes a strong coupling to higher orders
@@
 optical pumping during the initial cooling. Since the coupling strength of different orders
-do not reach their minimums at the same time \fxnote{FIG}, using multiple orders of motional sidebands
+do not reach their minimums at the same time, using multiple orders of motional sidebands
 for cooling also avoids accumulation of population near the coupling minimum of a particular
@@
 
-The high initial temperature also causes additional complications.  First, population in high motional states means that the atoms sample
-the anharmonicity of the trap away from the harmonic center. This results in sidebands that are broader and of reduced height \fxnote{FIG}, and limits the Rabi frequency of the Raman pulse
-on the radial sidebands to be no lower than tens of kHz in order to drive atoms in
-different motional states equally. \fxnote{EXPLAIN THIS A LITTLE MORE}.
+The high initial temperature also causes additional complications.
+First, population in high motional states means that the atoms sample
+the anharmonicity of the trap away from the harmonic center.
+This effect broadens the sidebands and reduces their heights,
+and therefore the efficiency of cooling, when driven with a single frequency.
+In order to overcome this issue, we power broaden the sidebands by increasing the Rabi frequency
+so that it is larger than the expected sideband frequencies distribution
+which causes all the states to be driven equally.
+This limits the Rabi frequency of the Raman pulse on the radial sidebands to be no lower
+than tens of kHz.
 Second, the deep trap that is needed to trap and image single sodium atom also creates
@@
 For the more tightly confined radial directions,
-we begin the cooling with $\{\bar n_2, \bar n_3\}=2.2, 1.9$ \fxnote{ERROR BARS}.
+we begin the cooling with $\{\bar n_2, \bar n_3\}=3.4(2), 2.5(2)$
 The radial sideband spectra of the initial distribution is shown in figure \ref{f-radial}A
-where we can clearly see the first order heating, first order cooling and
-second order cooling sidebands.
+as orange and red lines, where we can clearly see the first order heating,
+first order cooling and second order cooling sidebands.
 After applying around 1000 cooling pulses cooling in all three dimensions
 starting with cooling on the radial second order,
-the Raman spectrum with the same parameters is shown in figure \ref{f-radial}B,
-where the first and second order cooling sidebands on both axis are suppressed.
+the Raman spectrum with the same parameters is shown in figure \ref{f-radial}A as
+blue and green lines, where the first and second order cooling sidebands
+on both axis are suppressed.
 Given the absence of the second order cooling sideband,
@@
 
-It is important to note that the large Raman Lamb-Dicke parameters $\eta^R$ mean that we must use caution when measuring the temperature.
+It is important to note that the large Raman Lamb-Dicke parameters $\eta^R$ mean that
+we must use caution when measuring the temperature.
 Traditional sideband thermometry uses
@@
 sidebands. This data is shown before and after cooling in Figures
-\ref{f-radial}C and \ref{f-radial}D
-and yields $90\%$ and $92\%$ \fxnote{ERROR BARS},
+\ref{f-radial}B and \ref{f-radial}C and yields $90\%$ and $92\%$ \fxnote{ERROR BARS},
 showing good agreement between the two methods.
@@
 The axial direction is much less confined and therefore has a much higher initial effective
-Lamb-Dicke parameter of $\eta^{OP}_{eff1}\approx 3.97$, and is therefore more difficult to cool.
-Figure \ref{f-axial}A shows the Raman spectrum in the axial direction
+Lamb-Dicke parameter of $\eta^{OP}_{eff1}\approx 4.0$, and is therefore more difficult to cool.
+The red line in figure \ref{f-axial}A shows the Raman spectrum in the axial direction
 before applying Raman sideband cooling; the clearly resolved sidebands
@@
 cooling sideband. After applying the cooling sequence identical to the one we use to cool
-the radial directions, the spectrum is shown in figure \ref{f-axial}B.
+the radial directions, the spectrum is shown in figure \ref{f-axial}A as the blue line.
 All of the high order ($\geqslant2$) axial cooling sidebands disappear, and the first order
@@
 The decoherence time scale is consistent with magnetic field fluctuations of $1.5$ mG that we have measured in the lab, which produces
-a Zeeman shift of around $5\text{kHz}$.
+a Zeeman shift of around $3$ kHz.
 
@@
 and the resonance shift caused by magnetic field fluctuations.
-Improvements on these \fxnote{HOW?} should improve the cooling performance even further.
+We are planing to improve these by increasing the detuning of the Raman beams
+and implementing better control of the magnetic field.
+We expect these changes to improve the cooling performance even further.
 We have shown that despite the difficulty in cooling sodium atoms,

### 2017-06-21 calc_eta_eff.jl

@@ -5,23 +5,24 @@ import NaCsCalc: Trap
 
 # Matrix elements
 const m_Na = 23e-3 / 6.02e23
-const ν_a1 = 68.8e3
-const ν_r2 = 430e3
-const ν_r3 = 589.5e3
-const η_a1_op = Trap.η(m_Na, ν_a1, 2π / 589e-9)
-const η_r2_op = Trap.η(m_Na, ν_r2, 2π / 589e-9)
-const η_r3_op = Trap.η(m_Na, ν_r3, 2π / 589e-9)
-const η_a1 = η_a1_op * 0.67
-const η_r2 = η_r2_op * √(2)
-const η_r3 = η_r3_op * √(2)
+const νs = (69e3, 430e3, 590e3)
+const ηs_op = Trap.η.(m_Na, νs, 2π / 589e-9)
+const ηs_ra = ηs_op .* (0.67, √2, √2)
 
-function calc_η_eff(TμK)
+function calc_nbar(TμK)
     ħ = 1.0545718e-34
     k_B = 1.38064852e-23
     Hz_per_μK = k_B * 1e-6 / ħ / 2π
     THz = TμK * Hz_per_μK
-    nbars = THz ./ (ν_a1, ν_r2, ν_r3)
-    return sqrt.(2 .* nbars .+ 1) .* (η_a1_op, η_r2_op, η_r3_op)
+    return THz ./ νs
 end
 
+function calc_η_eff(TμK)
+    return sqrt.(2 .* calc_nbar(TμK) .+ 1) .* ηs_op
+end
+
+@show ηs_op
+@show ηs_ra
+@show calc_nbar(70)
 @show calc_η_eff(70)
+# @show calc_η_eff(75)

### 2017-06-21 paper.tex
Add back description of the experiment.
Emphasize D1 OP.

@@
     state to minimize heating on the atom in $|F=2,m_F=-2\rangle$ state
-    \fxnote{TALK ABOUT THIS IN THE TEXT}.
     (B) Geometry and polarizations of the Raman and optical pumping beams relative to the
@@
 
-Systems of single neutral atoms trapped in optical tweezers are an exciting platform to study quantum information, quantum chemistry,
-and quantum simulation of many-body systems \fxnote{REF}.
-This approach provides full single-site resolution and control, and can feature long-range interactions via Rydberg atoms, polar molecules, or dipolar atoms \fxnote{REF}.
+Systems of single neutral atoms trapped in optical tweezers are an exciting platform to study
+quantum information, quantum chemistry, and quantum simulation of many-body systems \fxnote{REF}.
+This approach provides full single-site resolution and control,
+and can feature long-range interactions via Rydberg atoms, polar molecules,
+or dipolar atoms \fxnote{REF}.
 Polar molecules in particular offer the additional advantages of long-lived internal states
@@
 and strength of the interaction \fxnote{REF}.
-Optical tweezers can also be re-arranged in real-time, allowing rapid preparation of atoms in complex geometries with high fidelity \fxnote{REF}.
+Optical tweezers can also be re-arranged in real-time,
+allowing rapid preparation of atoms in complex geometries with high fidelity \fxnote{REF}.
 
@@
 three dimensional motional ground state in the optical tweezer.
-This has been demonstrated for neutral Rb\cite{Thompson2013,Kaufman2012} and Cs\cite{Liu2017} in experiments that had low initial temperature and small Lamb-Dicke parameter.
-These features
-may not be easily achievable for other systems, such as directly laser-cooled polar molecules \fxnote{REF},
+This has been demonstrated for neutral Rb\cite{Thompson2013,Kaufman2012} and Cs\cite{Liu2017}
+in experiments that had low initial temperature and small Lamb-Dicke parameter.
+These features may not be easily achievable for other systems,
+such as directly laser-cooled polar molecules \fxnote{REF},
 or atoms with challenging sub-Doppler cooling such as Na, K, and Li \fxnote{REF}.
-In this letter, we cool single sodium atoms
-trapped in optical tweezers to the motional ground state with Raman sideband cooling.
-Despite having a large Lamb-Dicke parameter and high initial temperature, we are able to achieve a ground state probability of $77(4)\%$
+In this letter, we cool single sodium atoms trapped in optical tweezers to
+the motional ground state with Raman sideband cooling.
+Despite having a large Lamb-Dicke parameter and high initial temperature,
+we are able to achieve a ground state probability of $77(4)\%$
 by utilizing several new cooling techniques and a carefully optimized cooling sequence.
@@
 
-As mentioned previously, in order to perform Raman sideband cooling efficiently and
-minimize the heating during the optical pumping, we need to have a low initial temperature and
+The Raman sideband cooling we used to achieve the high ground state preparation fidelity
+consists of multiple cycles of laser pulses to manipulate the internal and
+motional states of the atoms.
+Figure \ref{f-setup}A shows the schematic of the energy levels and the cooling sequence
+in our setup.
+Each cooling cycle starts with the sodium atom in the $|F=2, m_F=-2\rangle$
+ground electronic state and a certain vibration state $n$.
+In the first step, a Raman pulse drives a transition to the motional state $n-\Delta n$
+to reduce the motional energy while also changing the internal state to $|F=1, m_F=-1\rangle$.
+In the second step, which finishes the cooling cycle,
+an optical pumping pulse bring the atom back to the $|F=2, m_F=-2\rangle$ state to take away
+the entropy.
+The second step could also change the motional state of the atoms which could cause heating.
+The possibility for this to happen for an atom in the motional level $n$
+is approximately proportional to the effective Lamb-Dicke parameter
+$\eta^{OP}_{eff}=\sqrt{2n+1}\eta^{OP}$ where $\eta^{OP}=k^{OP}\sqrt{\hbar/2m\omega}$
+is the Lamb-Dicke parameter for optical pumping.
+Additional photon scattering on the atom in the $|F=2, m_F=-2\rangle$
+state will also cause heating.
+In order to reduce this effect, we address the atom in the $F=2$ states during optical pumping
+on the D1 line, so that the $|F=2, m_F=-2\rangle$ state is a dark state for $\sigma^-$
+polarization and does not scatter any photon. We measured a $130(20)$ times reduction in photon
+scattering rate on $|F=2, m_F=-2\rangle$ state compare to using only the D2 line
+with the same optical pumping rate.
+The geometry of the relevant beams and their polarizations is showed in figure \ref{f-setup}B.
+The optical tweezer has one weakly confined axial direction (axis $1$) and
+two more strongly confined radial directions (axis $2$ and $3$).
+Multiple pairs of beams are used to drive the Raman transition during cooling in order to
+isolate and maximize the coupling to different trap axis.
+
+In order to perform Raman sideband cooling efficiently and minimize
+the heating during the optical pumping, we need to have a low initial temperature and
 a small Lamb-Dicke parameter. However, since the Lamb-Dicke parameter $\eta$ is inversely
-proportional to $\sqrt[4]{m}/\lambda$ where $m$ is the mass of the atom and $\lambda$
+proportional to $\sqrt[4]{m}\lambda$ where $m$ is the mass of the atom and $\lambda$
 is the wavelength of the atomic transition,
-it is larger for sodium given the same trap depth due to its low mass and short D line wavelength.
+it is larger for sodium at a given trap depth due to its low mass and short D line wavelength.
 With 45 mW of power in the trap, we measure trapping frequencies of
@@
 The simulation is also used to guide the optimization of the cooling sequence by exploring the
-large parameter space and finding a robust cooling strategy. As shown in figure \ref{f-setup}B,
+large parameter space and finding a robust cooling strategy. As shown in figure \ref{f-setup}C,
 we found that instead of cooling on only one sideband order at a time, it is generally more
@@
 sidebands. This data is shown before and after cooling in Figures
-\ref{f-radial}B and \ref{f-radial}C and yields $90\%$ and $92\%$ \fxnote{ERROR BARS},
+\ref{f-radial}B and \ref{f-radial}C and yields $89(2)\%$ and $92(2)\%$
 showing good agreement between the two methods.

### 2017-06-21 paper.tex
More detail description of sequence construction and optimizations

@@
 We solve this issue by switching the trapping light at $3\text{MHz}$
-during the whole cooling sequence, similar to our loading and imaging process \cite{Hutzler2017-LightShifts}, but leave on the OP light with constant intensity.
+during the whole cooling sequence, similar to our loading and imaging process
+\cite{Hutzler2017-LightShifts}, but leave on the OP light with constant intensity.
 Due to the large light shift, the OP light is effectively off when the trap light is on.
@@
 The simulation is also used to guide the optimization of the cooling sequence by exploring the
-large parameter space and finding a robust cooling strategy. As shown in figure \ref{f-setup}C,
-we found that instead of cooling on only one sideband order at a time, it is generally more
-efficient to alternate the cooling pulse between two neighboring orders (axial) or pulse lengths.
-A cooling sequence like this minimizes the accumulation of atom in a state not addressed by a
-particular Raman pulse parameter.
+large parameter space and finding a robust cooling strategy.
+As shown in figure \ref{f-setup}C, we found that instead of cooling on only one sideband order
+at a time, it is generally more efficient to alternate the cooling pulse between two
+neighboring orders (axial) to minimize the accumulation of atom in a state
+not addressed by a particular order.
+The simulation also shows that the most efficient way of cooling on a high order sideband is
+to perform a $\pi$ pulse corresponding to its maximum matrix element.
+This makes sure we are using each order to cool a range of states that has the strongest
+coupling to this order and let other sidebands to cool other states.
+This strategy is only not as effective during the last stage of cooling in each direction
+where most of the remainly excited population is in the first motional excited state
+while the rest also have the strongest coupling to the first cooling sideband.
+Because of this, we switch to cooling only on the first order sideband as the last cooling
+stage while maintaining the alternating order between different axis to maximize the final
+ground state probability.
+Guided by the simulation result, we construct our initial cooling sequence by first starting
+at the highest two observed cooling sideband and decrease the order after cooling on them
+for 6 to 15 cycles with the optimum pulse lengths.
+This sequence gives good cooling performance which is then experimentally further optimized
+by fine tuning of different parameters.
 

### 2017-06-23 paper.tex
Edits from Nick

@@
 \newcommand{\sddiff}[3][{}]{{\frac{\ud^{#1}}{\ud {#3}{}^{#1}} {#2}}}
+\newcommand{\eff}{ef\! f}
+%Nick redefined fxnote so that the notes could be seen in the PDF since that is what Kang-Kuen is editing
+\renewcommand{\fxnote}[1]{{\textbf{[#1]}}}
 
@@
 \begin{abstract}
-  Single neutral atom trapped in optical tweezer is a promising system for various applications
+  Single neutral atoms trapped in optical tweezers are a promising system for many applications
   in quantum information and simulation.
-  The control of the motional states for such a system is crucial
-  for exploiting its full potential.
+  These applications typically require complete quantum control, including motional states, which requires cooling of the trapped atoms.
   We report Raman sideband cooling of a single sodium atom to its three-dimensional
@@
   large differential AC Stark shift in the excited state,
-  we achieved a ground state preparation fidelity of $77(4)\%$ after a few hundred ms of cooling
-  by using a few new cooling techniques including addressing high order Raman sideband.
-  We demonstrate that Raman sideband cooling to the 3D motional ground state is applicable to
-  systems where tight confinement or low initial cooling is hard to achieve.
+  we achieve a ground state preparation fidelity of $77(4)\%$ after a few hundred ms of cooling
+  by using novel cooling techniques such as addressing high order Raman sidebands.
+  We demonstrate that Raman sideband cooling to the 3D motional ground state is applicable outside the Lamb-Dicke regime, for example in
+  systems where tight confinement and low initial temperature are difficult to realize.
   The is particularly relevant for systems which are challenging to laser-cool,
@@
 
-Systems of single neutral atoms trapped in optical tweezers are an exciting platform to study
+Systems of individual neutral atoms trapped in optical tweezers are an exciting platform to study
 quantum information, quantum chemistry, and quantum simulation of many-body systems \fxnote{REF}.
 This approach provides full single-site resolution and control,
-and can feature long-range interactions via Rydberg atoms, polar molecules,
+and can feature long-range interactions by using Rydberg atoms, polar molecules,
 or dipolar atoms \fxnote{REF}.
@@
 
-The Raman sideband cooling we used to achieve the high ground state preparation fidelity
+The Raman sideband cooling we use to achieve the high ground state preparation fidelity
 consists of multiple cycles of laser pulses to manipulate the internal and
@@
 an optical pumping pulse bring the atom back to the $|F=2, m_F=-2\rangle$ state to take away
-the entropy.
-The second step could also change the motional state of the atoms which could cause heating.
+the entropy via the spontaneously emitted photon.
+The second step could also change the motional state of the atoms and result in heating.
 The possibility for this to happen for an atom in the motional level $n$
-is approximately proportional to the effective Lamb-Dicke parameter
-$\eta^{OP}_{eff}=\sqrt{2n+1}\eta^{OP}$ where $\eta^{OP}=k^{OP}\sqrt{\hbar/2m\omega}$
-is the Lamb-Dicke parameter for optical pumping.
-Additional photon scattering on the atom in the $|F=2, m_F=-2\rangle$
-state will also cause heating.
-In order to reduce this effect, we address the atom in the $F=2$ states during optical pumping
-on the D1 line, so that the $|F=2, m_F=-2\rangle$ state is a dark state for $\sigma^-$
-polarization and does not scatter any photon. We measured a $130(20)$ times reduction in photon
-scattering rate on $|F=2, m_F=-2\rangle$ state compare to using only the D2 line
-with the same optical pumping rate.
-The geometry of the relevant beams and their polarizations is showed in figure \ref{f-setup}B.
+is approximately proportional to the effective Lamb-Dicke (LD) parameter
+$\eta^{OP}_{\eff}=\sqrt{2n+1}\eta^{OP}$ where $\eta^{OP}=k^{OP}\sqrt{\hbar/2m\omega}$
+is the LD parameter for optical pumping, $k^{OP}$ is the wavenumber of the OP light, $m$ is the mass of the atom, and $\hbar$ is the reduced Planck constant.
+
+In order to reduce OP scattering on the $|F=2, m_F=-2\rangle$ state, which would causing heating, we use a $\sigma^-$-polarized laser resonant with the D1 line to address atoms in the $F=2$ state, so that $|F=2, m_F=-2\rangle$ is dark.
+Compared to using a D2 OP beam, we find a reduction in the scattering rate of a factor of $130(20)$.
+
+The geometry of the relevant beams and their polarizations is shown in figure \ref{f-setup}B.
 The optical tweezer has one weakly confined axial direction (axis $1$) and
@@
 the heating during the optical pumping, we need to have a low initial temperature and
-a small Lamb-Dicke parameter. However, since the Lamb-Dicke parameter $\eta$ is inversely
-proportional to $\sqrt[4]{m}\lambda$ where $m$ is the mass of the atom and $\lambda$
+a small LD parameter. However, since the LD parameter $\eta\propto 1/(\sqrt[4]{m}\lambda)$ where $m$ is the mass of the atom and $\lambda$
 is the wavelength of the atomic transition,
@@
 $\{\omega_1,\omega_2,\omega_3\}/2\pi = \{69(1), 430(4), 590(5)\}\ \text{\text{kHz}}$
-which corresponds to optical pumping Lamb-Dicke parameters of
+which corresponds to optical pumping LD parameters of
 $\{\eta^{OP}_1,\eta^{OP}_2,\eta^{OP}_3\} = \{0.602(5), 0.241(2), 0.206(1)\}$
-Moreover, due to the small hyperfine structure in the $3^2P_{3/2}$ manifold,
+Moreover, due to the small hyperfine splitting in the $3^2P_{3/2}$ manifold,
 the sub-Doppler cooling in sodium is also less efficient and we start the
-Raman sideband cooling with a initial temperature of 70 $\mu$K. Combined with the high Lamb-Dicke
-parameters, this gives us a initial effective optical pumping Lamb-Dicke parameters of
-$\{\eta^{OP}_{1eff},\eta^{OP}_{2eff},\eta^{OP}_{3eff}\} = \{4.0(1), 0.67(2), 0.50(1)\}$
+Raman sideband cooling with a initial temperature of 70 $\mu$K. Combined with the high $\eta$, this gives us a initial effective optical pumping LD parameters of
+$\{\eta^{OP}_{1\eff},\eta^{OP}_{2\eff},\eta^{OP}_{3\eff}\} = \{4.0(1), 0.67(2), 0.50(1)\}$
 As a result, there is a very high probability of heating during the optical pumping step
 (figure \ref{f-ld}B) causing an estimated $30\%$ average heating probability during optical pumping
-in the weakly confined axial direction.
+in the weakly confined axial direction \fxnote{So what?  Is 30\% too high?  Can we interpret this in terms of an observable, like best-possible ground state fraction?}.
 
-Fortunately, the high Lamb-Dicke parameters also
-provide us with tools to overcome this issue. The Lamb-Dicke parameters for the
-Raman transitions in our configuration are $\{\eta^R_{1},\eta^R_{2},\eta^R_{3}\} = \{0.40(1), 0.341(2), 0.291(1)\}$. As shown in
-figure \ref{f-ld}A, the high Raman Lamb-Dicke parameters causes a strong coupling to higher orders
+Fortunately, the high LD parameters also
+provide us with tools to overcome this issue. The Raman transitions in our configuration have $\{\eta^R_{1},\eta^R_{2},\eta^R_{3}\} = \{0.40(1), 0.341(2), 0.291(1)\}$. As shown in
+figure \ref{f-ld}A, this results in strong coupling to higher orders
 of cooling sidebands, especially for high motional states.
@@
 
-The high initial temperature also causes additional complications.
+The high initial temperature also causes additional complications beyond large $\eta$.
 First, population in high motional states means that the atoms sample
 the anharmonicity of the trap away from the harmonic center.
-This effect broadens the sidebands and reduces their heights,
+This effect broadens the sidebands and reduces their strengths on resonance,
 and therefore the efficiency of cooling, when driven with a single frequency.
@@
 which affects the branching ratios and increases the number of photons needed for optical pumping.
-We solve this issue by switching the trapping light at $3\text{MHz}$
+We solve this issue by switching the trapping light at 3 MHz
 during the whole cooling sequence, similar to our loading and imaging process
-\cite{Hutzler2017-LightShifts}, but leave on the OP light with constant intensity.
+\cite{Hutzler2017-LightShifts}, but leaving on the OP light with constant intensity.
 Due to the large light shift, the OP light is effectively off when the trap light is on.
@@
 
-Taking all these features of our system into account, we use a Monte-Carlo simulation to verify
+Taking all these features into account, we use a Monte-Carlo simulation to verify
 the validity of our method \fxnote{WRITE BRIEF SUMMARY IN APPENDIX?}.
-In the simulation, we can observe the high heating rate due to the high Lamb-Dicke parameters
+In the simulation, we can observe the high heating rate due to the high LD parameters
 and confirm that by using high order Raman sideband transition in the cooling sequence we can
@@
 not addressed by a particular order.
-The simulation also shows that the most efficient way of cooling on a high order sideband is
-to perform a $\pi$ pulse corresponding to its maximum matrix element.
+The simulation also shows that an efficient way of cooling on a high order sideband is
+to set the Rabi frequency of the Raman transition to perform a $\pi$ pulse for the maximum matrix element of that order over all states (i.e. the maxima in \ref{f-ld}A).
 This makes sure we are using each order to cool a range of states that has the strongest
 coupling to this order and let other sidebands to cool other states.
-This strategy is only not as effective during the last stage of cooling in each direction
-where most of the remainly excited population is in the first motional excited state
-while the rest also have the strongest coupling to the first cooling sideband.
-Because of this, we switch to cooling only on the first order sideband as the last cooling
-stage while maintaining the alternating order between different axis to maximize the final
-ground state probability.
-Guided by the simulation result, we construct our initial cooling sequence by first starting
+
+The efficiency of this approach diminishes during the last stages of cooling as the atom approaches the ground state.
+We therefore finish the sequence by cooling only on the first order sideband while maintaining the alternating order between different axes.
+Guided by the simulation results, we construct our initial cooling sequence by first starting
 at the highest two observed cooling sideband and decrease the order after cooling on them
@@
 For the more tightly confined radial directions,
-we begin the cooling with $\{\bar n_2, \bar n_3\}=3.4(2), 2.5(2)$
+we begin the cooling with $\{\bar n_2, \bar n_3\}=3.4(2), 2.5(2)$.
 The radial sideband spectra of the initial distribution is shown in figure \ref{f-radial}A
@@
 
-It is important to note that the large Raman Lamb-Dicke parameters $\eta^R$ mean that
+It is important to note that the large Raman LD parameters $\eta^R$ mean that
 we must use caution when measuring the temperature.
@@
 on the coupling strength to be proportional to $\sqrt{n}$. However, outside the
-Lamb-Dicke regime, the coupling strength deviates from this simple scaling rule rapidly as
+LD regime, the coupling strength deviates from this simple scaling rule rapidly as
 shown in figure \ref{f-ld}A.
@@
 The axial direction is much less confined and therefore has a much higher initial effective
-Lamb-Dicke parameter of $\eta^{OP}_{eff1}\approx 4.0$, and is therefore more difficult to cool.
+LD parameter of $\eta^{OP}_{eff1}\approx 4.0$, and is therefore more difficult to cool.
 The red line in figure \ref{f-axial}A shows the Raman spectrum in the axial direction

### 2017-06-23 paper.tex
Fixed paper title
Very minor update

@@
 \begin{document}
-\title{Motional Quantum Ground-State Cooing Outside the Lamb-Dicke Regime}
+\title{Motional Quantum Ground-State Cooling Outside the Lamb-Dicke Regime}
 \author{Yichao Yu}
@@
 $\eta^{OP}_{\eff}=\sqrt{2n+1}\eta^{OP}$ where $\eta^{OP}=k^{OP}\sqrt{\hbar/2m\omega}$
-is the LD parameter for optical pumping, $k^{OP}$ is the wavenumber of the OP light, $m$ is the mass of the atom, and $\hbar$ is the reduced Planck constant.
+is the LD parameter for optical pumping (OP), $k^{OP}$ is the wavenumber of the OP light, $m$ is the mass of the atom, and $\hbar$ is the reduced Planck constant.
 

### 2017-06-25 paper.tex
Change how optical pumping heating is explained

@@
   \includegraphics[width=8.5cm]{imgs/fig2_raman_op.pdf}
-  \caption{Matrix elements and heating probabilities as a function of motional state.
-    The range plotted covers $99\%$ of the initial thermal distribution.
+  \caption{Matrix elements and heating as a function of motional state.
+    The range plotted covers $95\%$ of the initial thermal distribution.
     (A) Matrix elements for Raman transition in the axial direction showing deviation from
     $\sqrt{n}$ scaling and multiple minimums for different sideband orders.
-    (B) Heating probability during the optical pumping step for all three axis.
+    (B) Average change in motional state after the optical pumping step for all three axis.
     Due to the large Lamb-Dicke parameter,
-    there is a high probability of heating especially in the axial direction.
+    there is a high probability of $n$ changing especially in the axial direction.
     \label{f-ld}}
@@
 three dimensional motional ground state in the optical tweezer.
-This has been demonstrated for neutral Rb\cite{Thompson2013,Kaufman2012} and Cs\cite{Liu2017}
+This has been demonstrated for neutral Rb\cite{Thompson2013,Kaufman2012}
+and Cs\cite{Li2012,Liu2017}
 in experiments that had low initial temperature and small Lamb-Dicke parameter.
@@
 $\{\eta^{OP}_{1\eff},\eta^{OP}_{2\eff},\eta^{OP}_{3\eff}\} = \{4.0(1), 0.67(2), 0.50(1)\}$
-As a result, there is a very high probability of heating during the optical pumping step
-(figure \ref{f-ld}B) causing an estimated $30\%$ average heating probability during optical pumping
-in the weakly confined axial direction \fxnote{So what?  Is 30\% too high?  Can we interpret this in terms of an observable, like best-possible ground state fraction?}.
+As a result, there is a very high average change of motional state during the optical pumping step
+(figure \ref{f-ld}B). The averaged change in motional states over the initial distribution
+is $2.4$ in the axial direction.
+Compare to $0.89-0.95$ in the axis with the weakest confinement in previous experiments
+\cite{Thompson2013,Kaufman2012,Li2012,Liu2017} this causes greater uncertainty in the motional
+state making it harder to cool.
 

### 2017-06-25 calc_op_heat.jl

@@ -2,20 +2,12 @@
 
 push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
 
-import NaCsCalc.Utils: interactive
 import NaCsCalc: Trap
 using Cubature
-using PyPlot
-
-PyPlot.matplotlib["rcParams"][:update](Dict("font.size" => 20))
-PyPlot.matplotlib[:rc]("xtick", labelsize=15)
-PyPlot.matplotlib[:rc]("ytick", labelsize=15)
 
 const m_Na = 23e-3 / 6.02e23
 const η_ax = Trap.η(m_Na, 67e3, 2π / 589e-9) / √(2)
 const η_ax_op = Trap.η(m_Na, 67e3, 2π / 589e-9)
-const η_ra1 = Trap.η(m_Na, 430e3, 2π / 589e-9)
-const η_ra2 = Trap.η(m_Na, 590e3, 2π / 589e-9)
 
 """
     emission(v, isσ::Bool) -> (sinθ, cosθ)
@@ -105,14 +97,20 @@ function op_heating_all(cb::Function, sz1, sz2, η::T, isσ) where T
     res
 end
 
-const coupling_ax = (op_heating_all(op_heating_ax, 100, 100, Float32(η_ax_op), false) *
-                     op_heating_all(op_heating_ax, 100, 100, Float32(η_ax_op), true))
-const coupling_ra1 = (op_heating_all(op_heating_ra, 30, 30, Float32(η_ra1), false) *
-                      op_heating_all(op_heating_ra, 30, 30, Float32(η_ra1), true))
-const coupling_ra2 = (op_heating_all(op_heating_ra, 30, 30, Float32(η_ra2), false) *
-                      op_heating_all(op_heating_ra, 30, 30, Float32(η_ra2), true))
-
 function p_heat(coupling, sz)
+    T = eltype(coupling)
+    res = Vector{T}(sz)
+    @inbounds for i in 1:sz
+        v = zero(T)
+        for j in (i + 1):size(coupling, 1)
+            v += coupling[j, i]
+        end
+        res[i] = v
+    end
+    return res
+end
+
+function op_unc(coupling, sz)
     T = eltype(coupling)
     res = Vector{T}(sz)
     @inbounds for i in 1:sz
@@ -128,59 +126,48 @@ function p_heat(coupling, sz)
     return res
 end
 
[…]

### 2017-06-25 paper.tex
References

@@
 Systems of individual neutral atoms trapped in optical tweezers are an exciting platform to study
-quantum information, quantum chemistry, and quantum simulation of many-body systems \fxnote{REF}.
+quantum information, quantum chemistry, and quantum simulation of many-body systems\cite{Schlosser2001,DeMille2002,Muller2014Rydberg}.
 This approach provides full single-site resolution and control,
 and can feature long-range interactions by using Rydberg atoms, polar molecules,
-or dipolar atoms \fxnote{REF}.
+or dipolar atoms\cite{Micheli2006,Muller2014Rydberg,Walker2012}.
 Polar molecules in particular offer the additional advantages of long-lived internal states
 and a high degree of tunability, including the shape, range,
-and strength of the interaction \fxnote{REF}.
+and strength of the interaction\cite{Sortais2007,Beugnon2007,Ni2009}.
 Optical tweezers can also be re-arranged in real-time,
-allowing rapid preparation of atoms in complex geometries with high fidelity \fxnote{REF}.
+allowing rapid preparation of atoms in complex geometries with high fidelity
+\cite{Carpentier2013,Weiss2004}.
 
@@
 These features may not be easily achievable for other systems,
-such as directly laser-cooled polar molecules \fxnote{REF},
-or atoms with challenging sub-Doppler cooling such as Na, K, and Li \fxnote{REF}.
+such as directly laser-cooled polar molecules\cite{Shuman2010,Chae2017},
+or atoms with challenging sub-Doppler cooling such as Na, K, and Li\cite{Shahriar1993a,Colzi2016,Salomon2013,Salomon2015}.
 In this letter, we cool single sodium atoms trapped in optical tweezers to

### 2017-06-25 sm.tex
Supplemental material about simulation

\documentclass[aps,twocolumn,secnumarabic,balancelastpage,amsmath,amssymb]{revtex4}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{color}
\usepackage{graphics}
\usepackage[pdftex]{graphicx}
\usepackage[utf8x]{inputenc}
\usepackage[colorlinks=true]{hyperref}

\newcommand{\ud}{\mathrm{d}}
\newcommand{\ue}{\mathrm{e}}
\newcommand{\ui}{\mathrm{i}}
\newcommand{\res}{\mathrm{Res}}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\dsum}{\displaystyle\sum}
\newcommand{\dprod}{\displaystyle\prod}
\newcommand{\dlim}{\dispqlaystyle\lim}
\newcommand{\dint}{\displaystyle\int}
\newcommand{\fsno}[1]{{\!\not\!{#1}}}
\newcommand{\texp}[2]{\ensuremath{{#1}\times10^{#2}}}
\newcommand{\dexp}[2]{\ensuremath{{#1}\cdot10^{#2}}}
\newcommand{\eval}[2]{{\left.{#1}\right|_{#2}}}
\newcommand{\paren}[1]{{\left({#1}\right)}}
\newcommand{\lparen}[1]{{\left({#1}\right.}}
\newcommand{\rparen}[1]{{\left.{#1}\right)}}
\newcommand{\abs}[1]{{\left|{#1}\right|}}
\newcommand{\sqr}[1]{{\left[{#1}\right]}}
\newcommand{\crly}[1]{{\left\{{#1}\right\}}}
\newcommand{\angl}[1]{{\left\langle{#1}\right\rangle}}
\newcommand{\tpdiff}[4][{}]{{\paren{\frac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}_{#4}}}
\newcommand{\tpsdiff}[4][{}]{{\paren{\frac{\partial^{#1}}{\partial {#3}{}^{#1}}{#2}}_{#4}}}
\newcommand{\pdiff}[3][{}]{{\frac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}}
\newcommand{\diff}[3][{}]{{\frac{\ud^{#1} {#2}}{\ud {#3}{}^{#1}}}}
\newcommand{\psdiff}[3][{}]{{\frac{\partial^{#1}}{\partial {#3}{}^{#1}} {#2}}}
\newcommand{\sdiff}[3][{}]{{\frac{\ud^{#1}}{\ud {#3}{}^{#1}} {#2}}}
\newcommand{\tpddiff}[4][{}]{{\left(\dfrac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}\right)_{#4}}}
\newcommand{\tpsddiff}[4][{}]{{\paren{\dfrac{\partial^{#1}}{\partial {#3}{}^{#1}}{#2}}_{#4}}}
\newcommand{\pddiff}[3][{}]{{\dfrac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}}
\newcommand{\ddiff}[3][{}]{{\dfrac{\ud^{#1} {#2}}{\ud {#3}{}^{#1}}}}
\newcommand{\psddiff}[3][{}]{{\frac{\partial^{#1}}{\partial{}^{#1} {#3}} {#2}}}
\newcommand{\sddiff}[3][{}]{{\frac{\ud^{#1}}{\ud {#3}{}^{#1}} {#2}}}
\newcommand{\eff}{ef\! f}

\begin{document}
\title{Motional Quantum Ground-State Cooling Outside the Lamb-Dicke Regime -- Supplemental material}
\author{Yichao Yu}
\author{Nicholas R. Hutzler}
\author{Jessie T. Zhang}
\author{Lee R. Liu}
\author{Kang-Kuen Ni}
\email{ni@chemistry.harvard.edu}
\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts, 02138, USA}
\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts, 02138, USA}
\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts, 02138, USA}

\date{\today}

\maketitle

\section{Simulation of Raman sideband cooling}

\subsection{Overview}

We use a computer simulation to study the importance of different effects
and guide the optimization of cooling. The simulation uses quantum jump method to accurately
calculate the evolution within each laser pulse while different energy eigenstates are assumed
to decohere immediately on spontaneous emission of photon and on pulse boundaries.
Such approxiations are valid for simulation of the cooling and greatly simplifies the computation
at the cost of limiting the applicability of the simulation to processes that requires stronger
coherence such as Ramsey spectroscopy and rapid push-out.

A few other approximations are used in the simulation either because they are proved to have
negligible effect on the experiment or because they'll increase the complexity of the simulation
and can be optimized through other methods in the experiment.
A list of the most important approximations is,

\begin{enumerate}
\item All Raman pulses are assumed to be resonantly driving only one sideband/carrier order.\\
  We tweak the pulse shape, power and length to suppress any deviation
  from this in the experiment. We do still see deviation from this in the experiment
  but the effect is small for the short pulse we use for cooling and is the most pronounced
  for long detection pulses.
\item No heating from other sources including trap switching.\\
  We measured the heating rate and observed that it mainly comes from off-resonance scattering
  of photons from various sources which we already include so additional heating can be
  ignored.
\item Trapping frequency difference between different states are ignored.\\
  This effect is negligible for Na in the ground state due to the small fine structure.
  It is easy to include this effect if the calculation needs to be repeated on a system where
  this is not the case (e.g. directly laser cooled molecules)
\end{enumerate}

Some of the important effects that are included are,
\begin{enumerate}
\item Full 3D simulation.\\
  This includes 3D motional states, accurate 3D wavevector, and different emission pattern
  for different photon polarizations.
\item Off resonant scattering from all beams.\\
  Including Raman, optical pumping and dipole trap.
\item Optical pumping polarization imperfection.
\end{enumerate}

The optical pumping polarization and the off resonant scattering are especially important
for accurate simulation since they are the main heating source that is present
for ground motional dark state atom and therefore are the main limation on cooling performance.

\subsection{Simulation of each pulse}

Each pulse in general has a coherent part from the Raman drive (zero for optical pumping pulse)
and an incoherent part from scattering (optical pumping or off-resonance scattering).
This nicely fits the general formula of the quantum jump method. Due to the large number of
states that we need to take into account ($30-150$ states in each of the three axis and
$8$ hyperfine states, giving a total of $10^6$ states),
the generic wavefunction propagation is very inefficient.
Therefore, this is further simplified by reducing the number of states to be kept track of during
the coherent propagation and apply quantum jump using a set of reduced jump operator that
describes the total jump probability from a certain states (sum over all final states).
The coherent propagation is then accurately solved in order to avoid having to use a time step
much shorter than the scattering rate (up to hundreds of kHz)\footnote{\href{https://github.com/nacs-lab/yyc-data/blob/3b50baae233ba54456cc35260d91208a23021410/notes/precise-quantum-jump.pdf}{note about modification to the quantum jump method}}.

In order to simulate a pulse, we first start with the coherent propagation that includes the
modification from the jump operators as in quantum jump method.
When a jump happens, we pick a final internal state to jump to based on the rates ratio
of different scattering sources and their branching ratios.
This process also determines the polarization and emission pattern of the photon and
a particular wave vector for the emitted photon is then selected as the next step.
The recoil is not fixed so the final motional state of the atom can now be selected.
This process is then repeated on the same pulse until the pulse time is used up before
we start to simulate the next pulse.

\subsection{Measurements}

We apply ``virtual'' measurements on each results of the cooling which we then average to
obtain the expected value of qualities that we are interested in.
Due to the decoherence approximation, the measurement has to commute with the Hamiltonian.
Particularly useful measurements used in our simulation are hyperfine state distribution,
Average motional energy, loss rate (where an atom is assumed to be lost if its motional energy
goes above a certain threshold at any time) probability of being in certain states
(e.g. ground state).

\subsection{Code}

The simulation is written in Julia. All code are available under GPLv3 license at
\footnote{\href{https://github.com/nacs-lab/yyc-data/tree/3b50baae233ba54456cc35260d91208a23021410/lib}{Library code}} and
\footnote{\href{https://github.com/nacs-lab/yyc-data/blob/3b50baae233ba54456cc35260d91208a23021410/calculations/sideband/sideband.jl}{Top level code}}

\end{document}

### 2017-06-28 sm.tex
SM references, use and show shorten url

@@
 
-\section{Simulation of Raman sideband cooling}
+\section{Simulation of 3D Raman sideband cooling}
 
@@
 We use a computer simulation to study the importance of different effects
-and guide the optimization of cooling. The simulation uses quantum jump method to accurately
-calculate the evolution within each laser pulse while different energy eigenstates are assumed
-to decohere immediately on spontaneous emission of photon and on pulse boundaries.
+and guide the optimization of cooling.
+The simulation uses quantum jump method\cite{Chretien2014} (or Monte-Carlo wavefunction method)
+to accurately calculate the evolution within each laser pulse while different energy eigenstates
+are assumed to decohere immediately on spontaneous emission of photon and on pulse boundaries.
 Such approxiations are valid for simulation of the cooling and greatly simplifies the computation
@@
 The coherent propagation is then accurately solved in order to avoid having to use a time step
-much shorter than the scattering rate (up to hundreds of kHz)\footnote{\href{https://github.com/nacs-lab/yyc-data/blob/3b50baae233ba54456cc35260d91208a23021410/notes/precise-quantum-jump.pdf}{note about modification to the quantum jump method}}.
+much shorter than the scattering rate (up to hundreds of kHz)\footnote{\href{https://goo.gl/EZ13wt}{note about modification to the quantum jump method (https://goo.gl/EZ13wt)}}.
 
@@
 The simulation is written in Julia. All code are available under GPLv3 license at
-\footnote{\href{https://github.com/nacs-lab/yyc-data/tree/3b50baae233ba54456cc35260d91208a23021410/lib}{Library code}} and
-\footnote{\href{https://github.com/nacs-lab/yyc-data/blob/3b50baae233ba54456cc35260d91208a23021410/calculations/sideband/sideband.jl}{Top level code}}
+\footnote{\href{https://goo.gl/WLJwJp}{Library code (https://goo.gl/WLJwJp)}} and
+\footnote{\href{https://goo.gl/XXVreq}{Top level code (https://goo.gl/XXVreq)}}
 
+\bibliography{paper}
 \end{document}

### 2017-06-28 sm.tex
[SM] simulation results plots

@@
 
+\subsection{Sample results}
+
+\begin{figure}
+  \includegraphics[width=8.5cm]{imgs/simcool_no_scatter.pdf}
+  \caption{Simulated ground state population as a function of cooling cycles without
+    technical imperfections \label{f-no-scatter}}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=8.5cm]{imgs/simcool_real.pdf}
+  \caption{Simulated ground state population as a function of cooling cycles including effect of
+    off-resonant scattering from all beams and OP misalignment\label{f-real}}
+\end{figure}
+
+When not considering the off-resonant scattering from the Raman beams and the tweezer as well
+as optical pumping polarization misalignment, the simulation shows that there isn't a cooling
+limit despite the large Lamb-Dicke parameter and high initial temperature (Fig \ref{f-no-scatter}).
+However, when these effects are taken into account, the ground state probability can saturate at
+a lower value (Fig \ref{f-real}) and require much more careful tweaking.
+
 \subsection{Code}

### 2017-06-28 sm.tex
[SM] Fix ref in pdf, include numbers in plot

@@
   \caption{Simulated ground state population as a function of cooling cycles without
-    technical imperfections \label{f-no-scatter}}
+    technical imperfections. The ground state probability reaches $>99\%$. \label{f-no-scatter}}
 \end{figure}
@@
   \caption{Simulated ground state population as a function of cooling cycles including effect of
-    off-resonant scattering from all beams and OP misalignment\label{f-real}}
+    off-resonant scattering from all beams and OP misalignment.
+    For this particular sequence, the ground state probability saturates $\approx88\%$.
+    \label{f-real}}
 \end{figure}

### 2017-06-28 paper.tex
Supplemental material about simulation
Rabi flopping reference, heating/loss number

@@
 Taking all these features into account, we use a Monte-Carlo simulation to verify
-the validity of our method \fxnote{WRITE BRIEF SUMMARY IN APPENDIX?}.
+the validity of our method.
 In the simulation, we can observe the high heating rate due to the high LD parameters
@@
 and ground state population under the assumption that only a few states are populated.
-We can verify the result via an independent measurement of Rabi flopping on the carrier and heating
-sidebands. This data is shown before and after cooling in Figures
-\ref{f-radial}B and \ref{f-radial}C and yields $89(2)\%$ and $92(2)\%$
-showing good agreement between the two methods.
+We can verify the result via an independent measurement of Rabi flopping on the carrier and
+heating sidebands\cite{Meekhof1996}. This data is shown before and after cooling in Figures
+\ref{f-radial}B and \ref{f-radial}C.
+The data is fitted using same Monte-Carlo simulation we used to simulate the cooling
+which yields $89(2)\%$ and $92(2)\%$ showing good agreement between the two methods.
 
-The axial direction is much less confined and therefore has a much higher initial effective
-LD parameter of $\eta^{OP}_{eff1}\approx 4.0$, and is therefore more difficult to cool.
+The axial direction is much less confined and therefore has a much higher initial
+$\bar n_1=21(2)$ and effective LD parameter of $\eta^{OP}_{eff1}\approx 4.0(2)$,
+and is therefore more difficult to cool.
 The red line in figure \ref{f-axial}A shows the Raman spectrum in the axial direction
@@
 we have achieved a 3D ground state probability of $77(4)\%$.
-We believe this is currently limited by off-resonant scattering from the Raman beams
+We believe this is currently limited by off-resonant scattering from the Raman beams,
+which are measured to be between $3$ to $15$ kHz for the detuning and power we use,
 and the resonance shift caused by magnetic field fluctuations.
-We are planing to improve these by increasing the detuning of the Raman beams
-and implementing better control of the magnetic field.
+Other imperfections of the current experiement include a $5\%$ loss during the single atom
+imaging and an additional $10\%$ due to the heating from the Raman beams during cooling.
+We are planing to improve these by increasing the detuning of the Raman beams,
+implementing better control of the magnetic field and optimize the temperature during imaging.
 We expect these changes to improve the cooling performance even further.

### 2017-06-28 paper.tex
Add description of the sequence

@@
 
-The Raman sideband cooling we use to achieve the high ground state preparation fidelity
-consists of multiple cycles of laser pulses to manipulate the internal and
-motional states of the atoms.
+The experiment begins by loading the optical tweezer from a magneto-optical trap.
+The tweezer is created by focusing a $700$nm beam through an objective with NA $0.55$.
+With $45$mW of power, we measure a trapping frequencies of
+$\{\omega_1,\omega_2,\omega_3\}/2\pi = \{69(1), 430(4), 590(5)\}\ \text{\text{kHz}}$.
+The successfulness of the loading is detected by taking an image of the single atom for $1.5$ms.
+The same imaging light is optimized for cooling and reduces the temperature of the single atom
+to $70$ $\mu$K which corresponds to an initial motional states of
+$\{\bar n_1, \bar n_2, \bar n_3\}=21(2), 3.4(2), 2.5(2)$.
+
+The Raman sideband cooling we use to further reduce the temperature of the single atom and
+achieve the high ground state preparation fidelity consists of multiple cycles of laser pulses
+to manipulate the internal and motional states of the atoms.
 Figure \ref{f-setup}A shows the schematic of the energy levels and the cooling sequence
@@
 the heating during the optical pumping, we need to have a low initial temperature and
-a small LD parameter. However, since the LD parameter $\eta\propto 1/(\sqrt[4]{m}\lambda)$ where $m$ is the mass of the atom and $\lambda$
-is the wavelength of the atomic transition,
+a small LD parameter. However, since the LD parameter $\eta\propto 1/(\sqrt[4]{m}\lambda)$ where $m$ is the mass of the atom and $\lambda$ is the wavelength of the atomic transition,
 it is larger for sodium at a given trap depth due to its low mass and short D line wavelength.
-With 45 mW of power in the trap, we measure trapping frequencies of
-$\{\omega_1,\omega_2,\omega_3\}/2\pi = \{69(1), 430(4), 590(5)\}\ \text{\text{kHz}}$
-which corresponds to optical pumping LD parameters of
+With $45$ mW of power in the trap, which is what we use during the cooling sequence,
+the optical pumping LD parameters are
 $\{\eta^{OP}_1,\eta^{OP}_2,\eta^{OP}_3\} = \{0.602(5), 0.241(2), 0.206(1)\}$
 Moreover, due to the small hyperfine splitting in the $3^2P_{3/2}$ manifold,
-the sub-Doppler cooling in sodium is also less efficient and we start the
-Raman sideband cooling with a initial temperature of 70 $\mu$K. Combined with the high $\eta$, this gives us a initial effective optical pumping LD parameters of
+the sub-Doppler cooling in sodium is also less efficient and our initial temperature of 70 $\mu$K
+is higher than what is achieved for other atoms in previous experiments
+\cite{Thompson2013,Kaufman2012,Li2012,Liu2017}.
+Combined with the high $\eta$, this gives us a initial effective optical pumping LD parameters of
 $\{\eta^{OP}_{1\eff},\eta^{OP}_{2\eff},\eta^{OP}_{3\eff}\} = \{4.0(1), 0.67(2), 0.50(1)\}$
@@
 
-Fortunately, the high LD parameters also
-provide us with tools to overcome this issue. The Raman transitions in our configuration have $\{\eta^R_{1},\eta^R_{2},\eta^R_{3}\} = \{0.40(1), 0.341(2), 0.291(1)\}$. As shown in
-figure \ref{f-ld}A, this results in strong coupling to higher orders
+Fortunately, the high LD parameters also provide us with tools to overcome this issue.
+The Raman transitions in our configuration have
+$\{\eta^R_{1},\eta^R_{2},\eta^R_{3}\} = \{0.40(1), 0.341(2), 0.291(1)\}$.
+As shown in figure \ref{f-ld}A, this results in strong coupling to higher orders
 of cooling sidebands, especially for high motional states.
@@
 For the more tightly confined radial directions,
-we begin the cooling with $\{\bar n_2, \bar n_3\}=3.4(2), 2.5(2)$.
-The radial sideband spectra of the initial distribution is shown in figure \ref{f-radial}A
+the radial sideband spectra of the initial distribution is shown in figure \ref{f-radial}A
 as orange and red lines, where we can clearly see the first order heating,
@@
 
-The axial direction is much less confined and therefore has a much higher initial
-$\bar n_1=21(2)$ and effective LD parameter of $\eta^{OP}_{eff1}\approx 4.0(2)$,
-and is therefore more difficult to cool.
+The axial direction is much less confined which means a much higher initial
+effective LD parameter of $\eta^{OP}_{eff1}\approx 4.0(2)$ and is therefore more difficult to cool.
 The red line in figure \ref{f-axial}A shows the Raman spectrum in the axial direction
@@
 and the resonance shift caused by magnetic field fluctuations.
-Other imperfections of the current experiement include a $5\%$ loss during the single atom
+Other imperfections of the current experiment include a $5\%$ loss during the single atom
 imaging and an additional $10\%$ due to the heating from the Raman beams during cooling.
@@
 % ?? Blackman pulse vs square pulse
-% ?? Start from highest visible order
-% In the text, more description
-% Detail in appendix
 

### 2017-07-07 paper.tex
Kang-Kuen's edit

--- 2017-06-25 paper.tex
@@
 \newcommand{\eff}{ef\! f}
-%Nick redefined fxnote so that the notes could be seen in the PDF since that is what Kang-Kuen is editing
+% Nick redefined fxnote so that the notes could be seen in the PDF since that is what Kang-Kuen is editing
 \renewcommand{\fxnote}[1]{{\textbf{[#1]}}}
@@
 \begin{document}
-\title{Motional Quantum Ground-State Cooling Outside the Lamb-Dicke Regime}
+\title{Motional Ground-State Cooling Outside the Lamb-Dicke Regime}
 \author{Yichao Yu}
+\email{yichaoyu@g.harvard.edu}
 \author{Nicholas R. Hutzler}
@@
 \begin{abstract}
-  Single neutral atoms trapped in optical tweezers are a promising system for many applications
-  in quantum information and simulation.
-  These applications typically require complete quantum control, including motional states, which requires cooling of the trapped atoms.
   We report Raman sideband cooling of a single sodium atom to its three-dimensional
   motional ground state in an optical tweezer.
-  Despite having a very large Lamb-Dicke parameter, high initial temperature and
-  large differential AC Stark shift in the excited state,
-  we achieve a ground state preparation fidelity of $77(4)\%$ after a few hundred ms of cooling
-  by using novel cooling techniques such as addressing high order Raman sidebands.
-  We demonstrate that Raman sideband cooling to the 3D motional ground state is applicable outside the Lamb-Dicke regime, for example in
+  Despite having a very large Lamb-Dicke parameter, high initial temperature, and
+  large differential AC Stark shifts in the excited state,
+  we achieved a ground-state preparation fidelity of $77(4)\%$ after a few hundred ms of cooling.
+  Our technique includes addressing very high-order sidebands and
+  fast modulating of optical tweezer trap.
+  We demonstrate that Raman sideband cooling to the 3D motional ground state is applicable
+  outside the Lamb-Dicke regime, for example in
   systems where tight confinement and low initial temperature are difficult to realize.
-  The is particularly relevant for systems which are challenging to laser-cool,
-  such as molecules and exotic atoms, and opens up a new approach for further cooling
-  of these systems.
+  This is particularly relevant for systems which are challenging to laser-cool,
+  such as molecules and exotic atoms,
+  and opens up the possibility to gain quantum motional control of these systems.
 \end{abstract}
@@
 
-Systems of individual neutral atoms trapped in optical tweezers are an exciting platform to study
-quantum information, quantum chemistry, and quantum simulation of many-body systems\cite{Schlosser2001,DeMille2002,Muller2014Rydberg}.
-This approach provides full single-site resolution and control,
-and can feature long-range interactions by using Rydberg atoms, polar molecules,
-or dipolar atoms\cite{Micheli2006,Muller2014Rydberg,Walker2012}.
-Polar molecules in particular offer the additional advantages of long-lived internal states
-and a high degree of tunability, including the shape, range,
-and strength of the interaction\cite{Sortais2007,Beugnon2007,Ni2009}.
-Optical tweezers can also be re-arranged in real-time,
-allowing rapid preparation of atoms in complex geometries with high fidelity
-\cite{Carpentier2013,Weiss2004}.
+Bottom-up assemblies of trapped neutral atoms in optical tweezer arrays
+are an exciting platform to study quantum information and quantum simulations~\cite{Schlosser2001,Weiss2004,Isenhower2010,Wilk2010,Kaufman2015,Labuhn2016,Murmann2015}.
+The inherent single-particle detection and control that combines with tunable interactions
+are keys to demonstrate neutral atom based quantum logic gates~\cite{Isenhower2010,Wilk2010},
+novel quantum phases~\cite{Labuhn2016}, and single-photon switches~\cite{Dayan2008,Tiecke2014}.
+Advances of real-time re-arrangement of optical tweezers enable rapid preparation of atoms
+in large and complex geometries with high fidelity~\cite{Barredo2016,Endres2016}.
+Adding quantum motional control of individual
+atoms~\cite{Li2012,Kaufman2012,Thompson2013,qfLiu2017,Robens2017} further allows
+efficient coupling of single atoms to photonic crystal cavity~\cite{Thompson2013a},
+high-fidelity single qubit gates~\cite{Wang2016},
+and laser-cooled bosons to exhibit indistinguishability
+through Hong-Ou-Mandel interference~\cite{Kaufman2014}.
 
-In order to achieve long coherence times and full quantum control of the system,
-it is typically necessary to cool the atom to the
-three dimensional motional ground state in the optical tweezer.
-This has been demonstrated for neutral Rb\cite{Thompson2013,Kaufman2012}
-and Cs\cite{Li2012,Liu2017}
-in experiments that had low initial temperature and small Lamb-Dicke parameter.
-These features may not be easily achievable for other systems,
-such as directly laser-cooled polar molecules\cite{Shuman2010,Chae2017},
-or atoms with challenging sub-Doppler cooling such as Na, K, and Li\cite{Shahriar1993a,Colzi2016,Salomon2013,Salomon2015}.
-In this letter, we cool single sodium atoms trapped in optical tweezers to
-the motional ground state with Raman sideband cooling.
-Despite having a large Lamb-Dicke parameter and high initial temperature,
-we are able to achieve a ground state probability of $77(4)\%$
-by utilizing several new cooling techniques and a carefully optimized cooling sequence.
-Our approach is quite general, and opens up ground-state cooling for other systems.
+Extend such an optical tweezer array to polar molecules could open up a large range of
+new applications that exploits rich molecular long-lived internal states
+and high degrees of tunable interactions~\cite{DeMille2002,Ni2008,Gorshkov2011,Yan2013}.
+Molecules could be assembled from atoms directly inside the optical tweezer~\cite{Liu2017}
+or to be loaded from magneto-optical traps
+(MOTs)~\cite{Barry2014,Truppe2017SubDoppler,Anderegg2017}.
+For either approach, preparing constituent atoms or molecules in the lowest motional
+quantum state is important for high efficient molecular assembly
+and for long coherence times of any realistic quantum applications.
 
-The Raman sideband cooling we use to achieve the high ground state preparation fidelity
-consists of multiple cycles of laser pulses to manipulate the internal and
-motional states of the atoms.
-Figure \ref{f-setup}A shows the schematic of the energy levels and the cooling sequence
-in our setup.
-Each cooling cycle starts with the sodium atom in the $|F=2, m_F=-2\rangle$
-ground electronic state and a certain vibration state $n$.
-In the first step, a Raman pulse drives a transition to the motional state $n-\Delta n$
-to reduce the motional energy while also changing the internal state to $|F=1, m_F=-1\rangle$.
-In the second step, which finishes the cooling cycle,
-an optical pumping pulse bring the atom back to the $|F=2, m_F=-2\rangle$ state to take away
-the entropy via the spontaneously emitted photon.
-The second step could also change the motional state of the atoms and result in heating.
-The possibility for this to happen for an atom in the motional level $n$
-is approximately proportional to the effective Lamb-Dicke (LD) parameter
-$\eta^{OP}_{\eff}=\sqrt{2n+1}\eta^{OP}$ where $\eta^{OP}=k^{OP}\sqrt{\hbar/2m\omega}$
-is the LD parameter for optical pumping (OP), $k^{OP}$ is the wavenumber of the OP light, $m$ is the mass of the atom, and $\hbar$ is the reduced Planck constant.
+Prepare quantum ground-state for a variety of systems including
+single atoms in optical tweezers~\cite{Kaufman2012,Thompson2013,Liu2017,Robens2017}
+has been successful using Raman sideband cooling (RSC)~\cite{Monroe1995,Kerman2000,Han2000}.
+However, RSC in these systems has all been applied in the Lamb-Dicke regime \fxnote{define}.
+A challenging goal is to apply ground-state cooling to system such as atoms with light masses
+or laser-cooled polar molecules, that are often outside of the Lamb-Dicke regime.
+In this letter, we overcome this challenge and demonstrate cooling of single sodium atoms
+that are trapped in optical tweezers to the motional ground state.
+We achieve a single atom ground-state probability of $P_0=77(4)\%$ by utilizing cooling of
+very high-order sidebands in a carefully optimized cooling sequence.
+Our approach is  general and opens up ground-state cooling for other systems.
 
-In order to reduce OP scattering on the $|F=2, m_F=-2\rangle$ state, which would causing heating, we use a $\sigma^-$-polarized laser resonant with the D1 line to address atoms in the $F=2$ state, so that $|F=2, m_F=-2\rangle$ is dark.
-Compared to using a D2 OP beam, we find a reduction in the scattering rate of a factor of $130(20)$.
+Our experiment begins by loading a single sodium atom into an optical tweezer from a MOT
+for \fxnote{??} ms~\cite{Hutzler2017-LightShifts} and repeats at 2Hz\fxnote{?}.
+The tweezer is created by focusing a $700$nm laser beam through an NA=$0.55$ objective to
+a beam waist of 0.7 $\mu$m\fxnote{?}.
+With $45$mW of tweezer power, the trapping frequencies are
+$\{\omega_1,\omega_2,\omega_3\}/2\pi = \{69(1), 430(4), 590(5)\}\ \text{\text{kHz}}$.
+Upon loading, an image is taken for $1.5$ms to determine its success.
+The same imaging light is used for polarization gradient cooling (PGC) and
+reduces the temperature of the single atom to $70$ $\mu$K,
+which corresponds to an initial motional state along the three different axes of
+$\{\bar n_1, \bar n_2, \bar n_3\}=\{21(2),\, 3.4(2),\, 2.5(2)\}$ (initial $P_0=0.3\%$) in the trap.
 
-The geometry of the relevant beams and their polarizations is shown in figure \ref{f-setup}B.
-The optical tweezer has one weakly confined axial direction (axis $1$) and
-two more strongly confined radial directions (axis $2$ and $3$).
-Multiple pairs of beams are used to drive the Raman transition during cooling in order to
-isolate and maximize the coupling to different trap axis.
+To further reduce the temperature of the single atom and
+to achieve high ground-state preparation fidelity, we apply Raman sideband cooling.
+The relevant energy levels, the cooling sequence, and the Raman beam geometries our system
+is shown in Figure \ref{f-setup}. Overall, the RSC consists of two steps:
+a step to drive a coherent Raman transition while removing motional quanta and
+a step to reset the atom internal state via optical pumping (OP).
+RSC is applied repeatedly until motional ground state is achieved.
 
-In order to perform Raman sideband cooling efficiently and minimize
-the heating during the optical pumping, we need to have a low initial temperature and
-a small LD parameter. However, since the LD parameter $\eta\propto 1/(\sqrt[4]{m}\lambda)$ where $m$ is the mass of the atom and $\lambda$
-is the wavelength of the atomic transition,
-it is larger for sodium at a given trap depth due to its low mass and short D line wavelength.
-With 45 mW of power in the trap, we measure trapping frequencies of
-$\{\omega_1,\omega_2,\omega_3\}/2\pi = \{69(1), 430(4), 590(5)\}\ \text{\text{kHz}}$
-which corresponds to optical pumping LD parameters of
-$\{\eta^{OP}_1,\eta^{OP}_2,\eta^{OP}_3\} = \{0.602(5), 0.241(2), 0.206(1)\}$
-Moreover, due to the small hyperfine splitting in the $3^2P_{3/2}$ manifold,
-the sub-Doppler cooling in sodium is also less efficient and we start the
-Raman sideband cooling with a initial temperature of 70 $\mu$K. Combined with the high $\eta$, this gives us a initial effective optical pumping LD parameters of
-$\{\eta^{OP}_{1\eff},\eta^{OP}_{2\eff},\eta^{OP}_{3\eff}\} = \{4.0(1), 0.67(2), 0.50(1)\}$
-As a result, there is a very high average change of motional state during the optical pumping step
-(figure \ref{f-ld}B). The averaged change in motional states over the initial distribution
-is $2.4$ in the axial direction.
-Compare to $0.89-0.95$ in the axis with the weakest confinement in previous experiments
-\cite{Thompson2013,Kaufman2012,Li2012,Liu2017} this causes greater uncertainty in the motional
-state making it harder to cool.
+Specifically, Raman transitions are driven in Na between the hyperfine states
+$|F=2, m_F=-2\rangle$ and  $|F=1, m_F=-1\rangle$ in the presence of a $8.8$ G magnetic field.
+Subsequently, an OP/repump pulse brings the atom back to $|F=2, m_F=-2\rangle$
+via spontaneous emissions.
+Because any photon scattering is a heating source,
+we use a $\sigma^-$-polarized laser resonant with the D1 line for repump,
+which is dark to $|F=2, m_F=-2\rangle$ \fxnote{cite ion and K39}.
+Compared to using a D2 repump beam, we find a reduction in the $|F=2, m_F=-2\rangle$
+scattering rate of a factor of $130(20)$.
 
-Fortunately, the high LD parameters also
-provide us with tools to overcome this issue. The Raman transitions in our configuration have $\{\eta^R_{1},\eta^R_{2},\eta^R_{3}\} = \{0.40(1), 0.341(2), 0.291(1)\}$. As shown in
-figure \ref{f-ld}A, this results in strong coupling to higher orders
-of cooling sidebands, especially for high motional states.
-This enables cooling of atoms in high motional states by driving higher order Raman sidebands,
-removing more motional energy in a single cooling pulse and offsetting the effect of heating. Since the heating probability is higher for high motional states,
-cooling on these high order sidebands can greatly suppress the high heating during
-optical pumping during the initial cooling. Since the coupling strength of different orders
-do not reach their minimums at the same time, using multiple orders of motional sidebands
-for cooling also avoids accumulation of population near the coupling minimum of a particular
-order, which improves the overall efficiency of the cooling process.
+For an atom in the motional level $n$, the OP could result in motional-state redistribution
+as shown in Fig.~\ref{f-ld}\fxnote{A or B?}. The state redistribution probability,
+and hence overall heating, is approximately proportional to the effective Lamb-Dicke parameter
+$\eta^{OP}_{\eff}=\sqrt{2n+1}\eta^{OP}$, where $\eta^{OP}=k z_0=k \sqrt{\hbar/2m\omega}$,
+$k$ is the optical pumping wavenumber, $z_0$ is the zero-point wavefunction spread,
+$m$ is the mass of the atom, and $\hbar$ is the reduced Planck constant.
+Such heating presents a major challenge for efficient cooling of single Na atoms
+which feature a light mass and short D-line wavelengths.
+For our trap frequencies and beam geometry,
+$\{\eta^{OP}_1,\eta^{OP}_2,\eta^{OP}_3\} = \{0.602(5), 0.241(2), 0.206(1)\}$.
+Combined with a relatively large PGC temperature gives initial
+$\{\eta^{OP}_{1\eff},\eta^{OP}_{2\eff},\eta^{OP}_{3\eff}\} = \{4.0(1), 0.67(2), 0.50(1)\}$.
+For the weak axial direction, $(\eta^{OP}_{1\eff})^2>1$ is far outside of the Lamb-Dicke regime.
+As a result, the average change of motional state per OP step is large,
+which creates a large uncertainty on the motional state at the end of a full RSC step.
+Scenarios of runaway OP heating from RSC cycles are possible.
+As a comparison, the averaged change in motional states over the initial distribution
+is $2.4$ in the axial direction, which is significantly greater than $0.89-0.95$
+in previous experiments of RSC of Rb and Cs~\cite{Li2012,Kaufman2012,Thompson2013,Liu2017}.
 
-The high initial temperature also causes additional complications beyond large $\eta$.
-First, population in high motional states means that the atoms sample
-the anharmonicity of the trap away from the harmonic center.
-This effect broadens the sidebands and reduces their strengths on resonance,
-and therefore the efficiency of cooling, when driven with a single frequency.
-In order to overcome this issue, we power broaden the sidebands by increasing the Rabi frequency
-so that it is larger than the expected sideband frequencies distribution
-which causes all the states to be driven equally.
-This limits the Rabi frequency of the Raman pulse on the radial sidebands to be no lower
-than tens of kHz.
-Second, the deep trap that is needed to trap and image single sodium atom also creates
-a very large AC Stark shift in the excited state (as large as 300 MHz).
-This creates large, position-dependent detuning for the optical pumping light and mixes the excited state state hyperfine levels,
-which affects the branching ratios and increases the number of photons needed for optical pumping.
-We solve this issue by switching the trapping light at 3 MHz
-during the whole cooling sequence, similar to our loading and imaging process
-\cite{Hutzler2017-LightShifts}, but leaving on the OP light with constant intensity.
-Due to the large light shift, the OP light is effectively off when the trap light is on.
+Fortunately, the large Lamb-Dicke parameters also provide a way to overcome OP heating.
+The Raman transitions in our configuration have
+$\{\eta^R_{1},\eta^R_{2},\eta^R_{3}\} = \{0.40(1), 0.341(2), 0.291(1)\}$,
+which allow strong coupling to higher order sidebands for atoms in large motional states
+as calculated in Figure~\ref{f-ld}\fxnote{A or B?}.x
+To offset heating from OP initially, higher-order Raman cooling sidebands can be utilized
+to remove more motional quanta in a single cooling pulse.
+Since the coupling strengths of different orders do not reach minima for the same pulse duration,
+using multiple orders of cooling sidebands would avoid accumulations of population
+near the coupling minima.
+
+Taking the large motional-state changing heating and cooling sources into account,
+it was not immediately clear that efficient cooling can be achieved.
+We therefore use a Monte-Carlo simulation to guide our search and
+to find a robust cooling sequence \fxnote{cite sm}.
+In the simulation, we indeed observe a high heating rate due to the large Lamb-Dicke parameters
+and confirm that cooling with higher-order Raman sidebands can suppress heating.
+In particular, we find that instead of cooling on only one sideband order repeatedly,
+it is more efficient to alternate the cooling pulses (Fig.~\ref{f-setup}C) between two
+neighboring orders for the axial direction and 2nd- and 1st-orders for the radial directions
+to minimize the accumulation of the atom in motional states that have zero Raman coupling.
+The simulation also indicates setting the coupling strength of each cooling sideband
+to drive a Rabi $\pi$ pulse corresponding to the maximum matrix element motional state
+(i.e. the maxima in \ref{f-ld}\fxnote{A or B?}).
+Such choice insures each order cools a range of states that have the strongest
+couplings and leaves other sidebands to cool the rest.
+The efficiency of cooling on higher-order sidebands diminishes
+as the atom approaches the ground state.
+Therefore, the final cooling cycles utilize only the first-order sideband
+while alternating between different axes.
+
+Guided by the promising simulation results,
+we construct our axial part of cooling sequence by starting at the highest
+two observed cooling sidebands (8th- and 7th-orders)
+and decreasing the orders after 6 to 15 cycles.
+This sequence gives good initial cooling performance which is further optimized experimentally
+by fine tuning of different parameters. \fxnote{which parameters? Elaborate more about the sequence including starting with the second-order radial to remove the most amount of energy initially.}
+
+Two additional challenges of cooling single sodium atoms are
+further identified and addressed experimentally.
+First, the high initial temperature causes population in high motional states
+means that the atoms sample anharmonicity of the trap away from the center.
+In order to address trap anharmonicity, we drive sidebands with a large Rabi frequency
+and short pulses to Fourier broaden spectrum coverage.
+For the higher trap frequency radial directions, anharmonicity is calculated to be 1kHz/n,
+Rabi frequency exceeds tens of kHz is needed to couple to \fxnote{??\%} population up to
+\fxnote{n=?(we should calculate this)}.
+Second, the  tweezer trap  causes a large AC Stark shift (as large as $300$ MHz)
+in the excited state. This creates  a large, position-dependent OP detuning
+and mixes the excited-state hyperfine levels, and therefore reduces the optical pumping fidelity.
+We solve this issue by switching the trapping light at 3 MHz during the whole cooling sequence,
+similar to our loading and imaging process~\cite{Hutzler2017-LightShifts},
+while leaving OP on with constant intensity.
+Due to the large light shift, the optical pumping is effectively off when the trap light is on.
 Since the atom can only be addressed by the optical pumping light when the trap light is off,
@@
 
-Taking all these features into account, we use a Monte-Carlo simulation to verify
-the validity of our method \fxnote{WRITE BRIEF SUMMARY IN APPENDIX?}.
-In the simulation, we can observe the high heating rate due to the high LD parameters
-and confirm that by using high order Raman sideband transition in the cooling sequence we can
-suppress this effect and reduces the motional energy of the atom faster.
-The simulation is also used to guide the optimization of the cooling sequence by exploring the
-large parameter space and finding a robust cooling strategy.
-As shown in figure \ref{f-setup}C, we found that instead of cooling on only one sideband order
-at a time, it is generally more efficient to alternate the cooling pulse between two
-neighboring orders (axial) to minimize the accumulation of atom in a state
-not addressed by a particular order.
-The simulation also shows that an efficient way of cooling on a high order sideband is
-to set the Rabi frequency of the Raman transition to perform a $\pi$ pulse for the maximum matrix element of that order over all states (i.e. the maxima in \ref{f-ld}A).
-This makes sure we are using each order to cool a range of states that has the strongest
-coupling to this order and let other sidebands to cool other states.
+Our final cooling results are shown in Fig.~\ref{f-radial} and \ref{f-axial}.
+In total, 1000 cooling pulses (for \fxnote{??} ms) are applied along three axes with
+cooling begins on the radial second order to remove most energy initially.
+To characterize the single atom thermal occupation before and after cooling,
+we perform Raman sideband thermometry before and after cooling\fxnote{add citation?}.
+\fxnote{How is the thermometry done? pulse duration etc.}
+For the more tightly confined radial directions (non-degenerate),
+we observe clear first-order heating, first-order cooling,
+and second-order cooling sidebands before RSC as is shown in red in Figure \ref{f-radial}A.
+After cooling, the first and second order cooling sidebands on both radial axes are suppressed.
+Given the absence of the second order cooling sideband, we perform sideband thermometry
+by taking the ratio of the peaks of first-order cooling and heating sidebands to measure $\bar n / (\bar n + 1)$ \fxnote{cite}.
+We found $\{\bar n =,\bar n =\}$, which corresponds to a ground state population of $90(2)\%$
+and $94(3)\%$ along the two radial directions.
+It is important to note that the simple sideband thermometry formula assumes the coupling strength
+to be proportional to $\sqrt{n}$. Outside of the Lamb-Dickes regime,
+the coupling strength deviates from this simple scaling rule rapidly
+as shown in figure \ref{f-ld}A. Since the Raman spectroscopy is performed
+with a relatively large Raman Lamb-Dickes parameters $\eta^R$,
+we therefore use an independent measurement of Rabi flopping on the carrier (Fig. \ref{f-radial}B)
+and first-order heating(Fig. \ref{f-radial}C) sidebands
+to verify the ground-state population~\cite{Meekhof1996}.
+The data is fitted using the same Monte-Carlo simulation we used to simulate the cooling which yields $89(2)\%$ and $92(2)\%$ and show good agreement with the population extracted from the sideband thermometry.
+We also extracted the initial temperature before cooling from the motional-state decohered Rabi flopping and obtained \fxnote{70(?)} $\mu$K.
 
-The efficiency of this approach diminishes during the last stages of cooling as the atom approaches the ground state.
-We therefore finish the sequence by cooling only on the first order sideband while maintaining the alternating order between different axes.
-Guided by the simulation results, we construct our initial cooling sequence by first starting
-at the highest two observed cooling sideband and decrease the order after cooling on them
-for 6 to 15 cycles with the optimum pulse lengths.
-This sequence gives good cooling performance which is then experimentally further optimized
-by fine tuning of different parameters.
-
-For the more tightly confined radial directions,
-we begin the cooling with $\{\bar n_2, \bar n_3\}=3.4(2), 2.5(2)$.
-The radial sideband spectra of the initial distribution is shown in figure \ref{f-radial}A
-as orange and red lines, where we can clearly see the first order heating,
-first order cooling and second order cooling sidebands.
-After applying around 1000 cooling pulses cooling in all three dimensions
-starting with cooling on the radial second order,
-the Raman spectrum with the same parameters is shown in figure \ref{f-radial}A as
-blue and green lines, where the first and second order cooling sidebands
-on both axis are suppressed.
-Given the absence of the second order cooling sideband,
-we can estimate the ground state probability in each direction based on the height of
-the first order cooling and heating sideband to be $90(2)\%$ and $94(3)\%$.
-
-It is important to note that the large Raman LD parameters $\eta^R$ mean that
-we must use caution when measuring the temperature.
-Traditional sideband thermometry uses
-the ratio of the cooling and heating sidebands to measure $\bar n / (\bar n + 1)$, which relies
-on the coupling strength to be proportional to $\sqrt{n}$. However, outside the
-LD regime, the coupling strength deviates from this simple scaling rule rapidly as
-shown in figure \ref{f-ld}A.
-When the atom temperature is still high,
-we measure the heights of multiple sidebands to make sure no population is hidden at the
-minimum of one sideband order. Once the atom is cooled down, we estimate the temperature
-and ground state population under the assumption that only a few states are populated.
-We can verify the result via an independent measurement of Rabi flopping on the carrier and heating
-sidebands. This data is shown before and after cooling in Figures
-\ref{f-radial}B and \ref{f-radial}C and yields $89(2)\%$ and $92(2)\%$
-showing good agreement between the two methods.
-
-The axial direction is much less confined and therefore has a much higher initial effective
-LD parameter of $\eta^{OP}_{eff1}\approx 4.0$, and is therefore more difficult to cool.
-The red line in figure \ref{f-axial}A shows the Raman spectrum in the axial direction
-before applying Raman sideband cooling; the clearly resolved sidebands
-up to eighth order indicates population in highly-excited motional levels.
-Therefore, we begin our cooling sequence by driving Raman transitions on the eighth order axial
-cooling sideband. After applying the cooling sequence identical to the one we use to cool
-the radial directions, the spectrum is shown in figure \ref{f-axial}A as the blue line.
-All of the high order ($\geqslant2$) axial cooling sidebands disappear, and the first order
-cooling sideband is strongly suppressed.
-The ground state probability calculated from this spectrum is $92(3)\%$.
-We can again use Rabi flopping on the carrier and heating sideband to verify this result
-similar to the radial direction. In this case, we see very good agreement on the carrier
-(figure \ref{f-axial}B) but there is additional decoherence on the axial first order
-heating sideband (figure \ref{f-axial}C).
-We believe this decoherence is caused by technical noise, which is the most pronounced
-on this transition due to its slow Rabi frequency.
-The decoherence time scale is consistent with magnetic field fluctuations of $1.5$ mG that we have measured in the lab, which produces
-a Zeeman shift of around $3$ kHz.
+For the weaker axial direction, cooling is much more challenging
+due to the large $\eta^{OP}_{eff1}\approx 4.0(2)$.
+In the Raman sideband thermometry, we observe up to 8th-order cooling sidebands initially,
+which indicates population in highly-excited motional states.
+Nevertheless, our cooling sequence works efficiently as all the cooling sidebands are suppressed
+after RSC (Fig.~\ref{f-axial}).
+The ground-state probability calculated using the ratio of first-order sideband heights yields
+$92(3)\%$. We also perform Rabi flopping on the carrier(Figure~\ref{f-axial}B)
+and extracted a ground-state population of \fxnote{??}\%, in agreement with the other method.
+For the first-order heating sideband Rabi flopping (Figure~\ref{f-axial}C),
+we observed additional decoherence that is more produced due to the slower Rabi frequency.
+The decoherence time scale is consistent with magnetic field fluctuations of $1.5$ mG
+that we measure independently in the lab, which produces a Zeeman shift of $\sim 3$ kHz.
 
 Combining the axial and radial cooling results,
-we have achieved a 3D ground state probability of $77(4)\%$.
-We believe this is currently limited by off-resonant scattering from the Raman beams
+we have prepared a single Na atom with 3D ground state probability of $77(4)\%$.
+We measuring a heating rate of the single atoms in the tweezer to be \fxnote{??}\%
+due to trapping light scattering.\fxnote{ciet Grimm}
+The ground-state preparation fidelity is currently limited by off-resonant scattering
+from the Raman beams,
+which are measured to be between $3$ to $15$ kHz for the detuning and power we use,
 and the resonance shift caused by magnetic field fluctuations.
-We are planing to improve these by increasing the detuning of the Raman beams
-and implementing better control of the magnetic field.
-We expect these changes to improve the cooling performance even further.
-We have shown that despite the difficulty in cooling sodium atoms,
-it is possible to achieve reliable three dimensional cooling with significant ground state
-probability using new cooling techniques and a optimized cooling sequence.
-This opens up the possibility of cooling a large variety of systems to their motional ground
-state using Raman sideband cooling that is challenging to laser cool
-including molecules and exotic atoms.
+In addition, there are $15$\% population loss during the experiment,
+including $5\%$ from single atom imaging and  $10\%$ very high-lying initial motional states
+that are not efficiently cooled by RSC, but off-resonantly heat by the Raman beams.
+We are planing to improve these by increasing the detuning of the Raman beams,
+addressing wider range of anharmonicity by frequency sweep...,
+implementing better control of the magnetic field and optimize the temperature during imaging.
+We expect these changes to improve the cooling performance further.
+Another improvement could be to implement grey molasses cooling to achieve
+a lower starting temperature before RSC. \fxnote{cite}
+
+We have shown that despite the difficulty in achieving a low optical cooling temperature
+of light mass sodium atoms, reliable three dimensional cooling
+with significant ground-state population can be achieved by using high-order Raman sidebands
+in an optimized cooling sequence in the presence of temporal switching tweezer trap.
+These techniques are well-suited for a large variety of systems
+and open up a route to ground-state cooling to other species including molecules and exotic atoms.
+
+We thank T. Rosenband and J. Hood for discussion.
+This work is supported by the NSF through the Harvard-MIT CUA,
+the AFOSR Young Investigator Program, the Arnold and Mabel Beckman Foundation,
+and the Alfred P. Sloan Foundation.
 

### 2017-07-07 paper.tex
Fix all citations

@@
 \usepackage[colorlinks=true]{hyperref}
-
-\usepackage[final]{fixme}
-\fxsetup{layout=inline}
 
@@
 \newcommand{\eff}{ef\! f}
-% Nick redefined fxnote so that the notes could be seen in the PDF since that is what Kang-Kuen is editing
-\renewcommand{\fxnote}[1]{{\textbf{[#1]}}}
+\newcommand{\fxnote}[1]{{\textbf{[#1]}}}
 
@@
 Adding quantum motional control of individual
-atoms~\cite{Li2012,Kaufman2012,Thompson2013,qfLiu2017,Robens2017} further allows
+atoms~\cite{Li2012,Kaufman2012,Thompson2013,Liu2017,Robens2017} further allows
 efficient coupling of single atoms to photonic crystal cavity~\cite{Thompson2013a},
@@
 to verify the ground-state population~\cite{Meekhof1996}.
-The data is fitted using the same Monte-Carlo simulation we used to simulate the cooling which yields $89(2)\%$ and $92(2)\%$ and show good agreement with the population extracted from the sideband thermometry.
-We also extracted the initial temperature before cooling from the motional-state decohered Rabi flopping and obtained \fxnote{70(?)} $\mu$K.
+The data is fitted using the same Monte-Carlo simulation we used to simulate the cooling
+which yields $89(2)\%$ and $92(2)\%$ and show good agreement with
+the population extracted from the sideband thermometry.
+We also extracted the initial temperature before cooling
+from the motional-state decohered Rabi flopping and obtained \fxnote{70(?)} $\mu$K.
 

### 2017-07-09 paper.tex
Correct number

@@
   large differential AC Stark shifts in the excited state,
-  we achieved a ground-state preparation fidelity of $77(4)\%$ after a few hundred ms of cooling.
+  we achieved a ground-state preparation fidelity of $77(4)\%$ after $100$ ms of cooling.
   Our technique includes addressing very high-order sidebands and
@@
 Our final cooling results are shown in Fig.~\ref{f-radial} and \ref{f-axial}.
-In total, 1000 cooling pulses (for \fxnote{??} ms) are applied along three axes with
+In total, $1000$ cooling pulses (for $100$ ms) are applied along three axes with
 cooling begins on the radial second order to remove most energy initially.

### 2017-07-09 plot_spectrum.jl
Radial plot color and line style

@@ -123,20 +123,20 @@ plot_data(data_nocool_r2[1], 1, fmt="C3^-", label="Ax 2 before")
 plot_data(data_nocool_r2[2], 1, fmt="C3^-")
 plot_data(data_nocool_r2[3], 1, fmt="C3^-")
 # Radial 3
-plot_data(data_nocool_r3[1], 1, fmt="C1o-", label="Ax 3 before")
-plot_data(data_nocool_r3[2], 1, fmt="C1o-")
-plot_data(data_nocool_r3[3], 1, fmt="C1o-")
+plot_data(data_nocool_r3[1], 1, fmt="C3o--", label="Ax 3 before")
+plot_data(data_nocool_r3[2], 1, fmt="C3o--")
+plot_data(data_nocool_r3[3], 1, fmt="C3o--")
 text(-660, 0.9, "(A)")
 
 # With cooling
 # Radial 2
-plot_data(data_cool_r2[1], 1, fmt="C2v-", label="Ax 2 after")
-plot_data(data_cool_r2[2], 1, fmt="C2v-")
-plot_data(data_cool_r2[3], 1, fmt="C2v-")
+plot_data(data_cool_r2[1], 1, fmt="C0v-", label="Ax 2 after")
+plot_data(data_cool_r2[2], 1, fmt="C0v-")
+plot_data(data_cool_r2[3], 1, fmt="C0v-")
 # Radial 3
-plot_data(data_cool_r3[1], 1, fmt="C0s-", label="Ax 3 after")
-plot_data(data_cool_r3[2], 1, fmt="C0s-")
-plot_data(data_cool_r3[3], 1, fmt="C0s-")
+plot_data(data_cool_r3[1], 1, fmt="C0s--", label="Ax 3 after")
+plot_data(data_cool_r3[2], 1, fmt="C0s--")
+plot_data(data_cool_r3[3], 1, fmt="C0s--")
 grid()
 ylim([0, 1])
 xlim([-700, 1500])

### 2017-07-09 paper.tex
More numbers corrections and explaination of experimental correction on top of simulation

@@
 Our experiment begins by loading a single sodium atom into an optical tweezer from a MOT
-for \fxnote{??} ms~\cite{Hutzler2017-LightShifts} and repeats at 2Hz\fxnote{?}.
+for $250$ ms~\cite{Hutzler2017-LightShifts} and repeats at $2.5$ Hz.
 The tweezer is created by focusing a $700$nm laser beam through an NA=$0.55$ objective to
-a beam waist of 0.7 $\mu$m\fxnote{?}.
+a beam waist of $0.7$ $\mu$m\fxnote{?}.
 With $45$mW of tweezer power, the trapping frequencies are
@@
 We therefore use a Monte-Carlo simulation to guide our search and
-to find a robust cooling sequence \fxnote{cite sm}.
+to find a robust cooling sequence\footnote{See supplemental material}.
 In the simulation, we indeed observe a high heating rate due to the large Lamb-Dicke parameters
@@
 Guided by the promising simulation results,
-we construct our axial part of cooling sequence by starting at the highest
+we construct our axial cooling sequence by starting at the highest
 two observed cooling sidebands (8th- and 7th-orders)
-and decreasing the orders after 6 to 15 cycles.
-This sequence gives good initial cooling performance which is further optimized experimentally
-by fine tuning of different parameters. \fxnote{which parameters? Elaborate more about the sequence including starting with the second-order radial to remove the most amount of energy initially.}
+and decreasing the orders after $6$ to $15$ cycles.
+This process is repeated until we reach the first order cooling sideband where most of the
+population are in the first few excited state at which point we switch to only cooling on the
+first order sideband with two different pulse lengths in order to efficiently cool atoms in the
+few remaining motional states.
+The radial cooling is done similarly to the axial cooling with the initial cooling orders being
+the 2nd and 1st order and switching to first order only after $20$ to $30$ pulses.
+This sequence gives good initial cooling performance which is used to measure experimental
+parameters, including the Rabi rates of the Raman beams and optical pumping rates,
+in order to optimize the sequence further.
 

### 2017-07-09 paper.tex
Anharmonicity number

@@
 For the higher trap frequency radial directions, anharmonicity is calculated to be 1kHz/n,
-Rabi frequency exceeds tens of kHz is needed to couple to \fxnote{??\%} population up to
-\fxnote{n=?(we should calculate this)}.
+Rabi frequency of at least $15$ kHz is needed to couple to $99$\% population up to $n=15$.
 Second, the  tweezer trap  causes a large AC Stark shift (as large as $300$ MHz)

### 2017-07-09 paper.tex
State detection note

@@
 $\{\bar n_1, \bar n_2, \bar n_3\}=\{21(2),\, 3.4(2),\, 2.5(2)\}$ (initial $P_0=0.3\%$) in the trap.
+A beam with $\sigma^-$-polarization is used to optical pump the atom into
+the $|F=2, m_F=-2\rangle$ stretch state.
+The hyperfine state detection is done by pushing out atoms in the stretch state with a strong
+beam on resonance with the $|F=2, m_F=-2\rangle$ to $|F'=3, m_{F'}=-3\rangle$ transition before
+taking the second image.
+The state preparation and detection have a combined fidelity of larger than $99$\%.
 

### 2017-07-10 paper.tex
Axis explained

@@
     $\sqrt{n}$ scaling and multiple minimums for different sideband orders.
+    ($k$ is the difference in wave vector of the Raman beams,
+    $r$ is the coordinate in axial direction).
     (B) Average change in motional state after the optical pumping step for all three axis.
@@
 we perform Raman sideband thermometry before and after cooling\fxnote{add citation?}.
-\fxnote{How is the thermometry done? pulse duration etc.}
 For the more tightly confined radial directions (non-degenerate),
@@
 and second-order cooling sidebands before RSC as is shown in red in Figure \ref{f-radial}A.
+
 After cooling, the first and second order cooling sidebands on both radial axes are suppressed.
-Given the absence of the second order cooling sideband, we perform sideband thermometry
+It is important to note that the simple sideband thermometry formula,
+which predicts the ratio of the cooling and heating sideband heights to be $\bar n / (\bar n + 1)$,
+assumes that the coupling strength for different motional states to be proportional to $\sqrt{n}$.
+Outside of the Lamb-Dickes regime, however,
+the coupling strength deviates from this simple scaling rule rapidly
+as shown in figure \ref{f-ld}A and since the Raman spectroscopy is performed
+with a relatively large Raman Lamb-Dickes parameters $\eta^R$, we cannot use this formula to
+measure $\bar n$. Instead, given the absence of the second order cooling sideband,
+we assume that the atoms are colder than
+
+\fxnote{How is the thermometry done? pulse duration etc.}
+, we perform sideband thermometry
 by taking the ratio of the peaks of first-order cooling and heating sidebands to measure $\bar n / (\bar n + 1)$ \fxnote{cite}.
@@
 and $94(3)\%$ along the two radial directions.
-It is important to note that the simple sideband thermometry formula assumes the coupling strength
-to be proportional to $\sqrt{n}$. Outside of the Lamb-Dickes regime,
-the coupling strength deviates from this simple scaling rule rapidly
-as shown in figure \ref{f-ld}A. Since the Raman spectroscopy is performed
-with a relatively large Raman Lamb-Dickes parameters $\eta^R$,
+
 we therefore use an independent measurement of Rabi flopping on the carrier (Fig. \ref{f-radial}B)

### 2017-07-12 paper.tex
Clarify Lamb-Dicke regime

@@
 has been successful using Raman sideband cooling (RSC)~\cite{Monroe1995,Kerman2000,Han2000}.
-However, RSC in these systems has all been applied in the Lamb-Dicke regime \fxnote{define}.
+However, RSC in these systems has all been applied in the Lamb-Dicke regime where
+the size of the wavefunction is much smaller than the wavelengths of
+the Raman and optical pumping light.
 A challenging goal is to apply ground-state cooling to system such as atoms with light masses
@@
 which allow strong coupling to higher order sidebands for atoms in large motional states
-as calculated in Figure~\ref{f-ld}\fxnote{A or B?}.x
+as calculated in Figure~\ref{f-ld}\fxnote{A or B?}.
 To offset heating from OP initially, higher-order Raman cooling sidebands can be utilized
@@
 measure $\bar n$. Instead, given the absence of the second order cooling sideband,
-we assume that the atoms are colder than
+we assume that the atoms are cold enough to have stronger coupling to the first order cooling
+sideband than the second order, in which case the
 
@@
 We also extracted the initial temperature before cooling
-from the motional-state decohered Rabi flopping and obtained \fxnote{70(?)} $\mu$K.
+from the motional-state decohered Rabi flopping and obtained $70 \mu$K.
 
@@
 We measuring a heating rate of the single atoms in the tweezer to be \fxnote{??}\%
-due to trapping light scattering.\fxnote{ciet Grimm}
+due to trapping light scattering.\fxnote{cite Grimm}
 The ground-state preparation fidelity is currently limited by off-resonant scattering

### 2017-07-12 paper.tex
Verify beam waist
Format citation update

@@
   large differential AC Stark shifts in the excited state,
-  we achieved a ground-state preparation fidelity of $77(4)\%$ after $100$ ms of cooling.
+  we achieved a ground-state preparation fidelity of $77(4)$\% after $100$ ms of cooling.
   Our technique includes addressing very high-order sidebands and
@@
   \caption{Matrix elements and heating as a function of motional state.
-    The range plotted covers $95\%$ of the initial thermal distribution.
+    The range plotted covers $95$\% of the initial thermal distribution.
     (A) Matrix elements for Raman transition in the axial direction showing deviation from
@@
     Solid lines in (B) and (C) are theoretical calculation of the Rabi flopping.
-    The blue lines corresponds to a ground state probability of $93\%$ after cooling and
+    The blue lines corresponds to a ground state probability of $93$\% after cooling and
     the red lines corresponds to a thermal distribution of $70$ $\mu$K before cooling.
@@
     Solid lines in (B) and (C) are theoretical calculation of the Rabi flopping.
-    The blue and green lines corresponds to a ground state probability of $92\%$ after cooling and
+    The blue and green lines corresponds to a ground state probability of $92$\% after cooling and
     the red lines corresponds to a thermal distribution of $70$ $\mu$K before cooling.
@@
 that are trapped in optical tweezers to the motional ground state.
-We achieve a single atom ground-state probability of $P_0=77(4)\%$ by utilizing cooling of
+We achieve a single atom ground-state probability of $P_0=77(4)$\% by utilizing cooling of
 very high-order sidebands in a carefully optimized cooling sequence.
@@
 The tweezer is created by focusing a $700$nm laser beam through an NA=$0.55$ objective to
-a beam waist of $0.7$ $\mu$m\fxnote{?}.
+a beam waist of $0.7 \mu$m.
 With $45$mW of tweezer power, the trapping frequencies are
@@
 which corresponds to an initial motional state along the three different axes of
-$\{\bar n_1, \bar n_2, \bar n_3\}=\{21(2),\, 3.4(2),\, 2.5(2)\}$ (initial $P_0=0.3\%$) in the trap.
-A beam with $\sigma^-$-polarization is used to optical pump the atom into
+$\{\bar n_1, \bar n_2, \bar n_3\}=\{21(2),\, 3.4(2),\, 2.5(2)\}$ (initial $P_0=0.3$\%) in the trap.
+A beam with $\sigma^-$-polarization is used to initialize the atom into
 the $|F=2, m_F=-2\rangle$ stretch state.
@@
 For an atom in the motional level $n$, the OP could result in motional-state redistribution
-as shown in Fig.~\ref{f-ld}\fxnote{A or B?}. The state redistribution probability,
-and hence overall heating, is approximately proportional to the effective Lamb-Dicke parameter
+as shown in Fig.~\ref{f-ld}A. The state redistribution probability
+is approximately proportional to the effective Lamb-Dicke parameter
 $\eta^{OP}_{\eff}=\sqrt{2n+1}\eta^{OP}$, where $\eta^{OP}=k z_0=k \sqrt{\hbar/2m\omega}$,
@@
 which allow strong coupling to higher order sidebands for atoms in large motional states
-as calculated in Figure~\ref{f-ld}\fxnote{A or B?}.
+as calculated in Figure~\ref{f-ld}B.
 To offset heating from OP initially, higher-order Raman cooling sidebands can be utilized
@@
 to drive a Rabi $\pi$ pulse corresponding to the maximum matrix element motional state
-(i.e. the maxima in \ref{f-ld}\fxnote{A or B?}).
+(i.e. the maxima in \ref{f-ld}B).
 Such choice insures each order cools a range of states that have the strongest
@@
 
+%% TODO
+
 Our final cooling results are shown in Fig.~\ref{f-radial} and \ref{f-axial}.
@@
 by taking the ratio of the peaks of first-order cooling and heating sidebands to measure $\bar n / (\bar n + 1)$ \fxnote{cite}.
-We found $\{\bar n =,\bar n =\}$, which corresponds to a ground state population of $90(2)\%$
-and $94(3)\%$ along the two radial directions.
+We found $\{\bar n =,\bar n =\}$, which corresponds to a ground state population of $90(2)$\%
+and $94(3)$\% along the two radial directions.
 
@@
 The data is fitted using the same Monte-Carlo simulation we used to simulate the cooling
-which yields $89(2)\%$ and $92(2)\%$ and show good agreement with
+which yields $89(2)$\% and $92(2)$\% and show good agreement with
 the population extracted from the sideband thermometry.
@@
 from the motional-state decohered Rabi flopping and obtained $70 \mu$K.
+
+%% End of TODO
 
@@
 The ground-state probability calculated using the ratio of first-order sideband heights yields
-$92(3)\%$. We also perform Rabi flopping on the carrier(Figure~\ref{f-axial}B)
-and extracted a ground-state population of \fxnote{??}\%, in agreement with the other method.
+$92(3)$\%. We also perform Rabi flopping on the carrier(Figure~\ref{f-axial}B)
+and extracted a ground-state population of $91(2)$\%, in agreement with the other method.
 For the first-order heating sideband Rabi flopping (Figure~\ref{f-axial}C),
@@
 Combining the axial and radial cooling results,
-we have prepared a single Na atom with 3D ground state probability of $77(4)\%$.
-We measuring a heating rate of the single atoms in the tweezer to be \fxnote{??}\%
-due to trapping light scattering.\fxnote{cite Grimm}
+we have prepared a single Na atom with 3D ground state probability of $77(4)$\%.
+We measuring a heating rate of the single atoms in the tweezer to be $0.9$\%/s
+due to trapping light scattering\cite{Grimm2000}.
 The ground-state preparation fidelity is currently limited by off-resonant scattering
@@
 and the resonance shift caused by magnetic field fluctuations.
-In addition, there are $15$\% population loss during the experiment,
-including $5\%$ from single atom imaging and  $10\%$ very high-lying initial motional states
+In addition, there are $15$\% population loss during the experiment which gives us a $66(3)$\%
+probability of ground state atom after each successful loading event.
+The loss includes $5$\% from single atom imaging and
+$10$\% very high-lying initial motional states
 that are not efficiently cooled by RSC, but off-resonantly heat by the Raman beams.
 We are planing to improve these by increasing the detuning of the Raman beams,
-addressing wider range of anharmonicity by frequency sweep...,
+addressing wider range of anharmonicity by frequency sweep,
 implementing better control of the magnetic field and optimize the temperature during imaging.
@@
 Another improvement could be to implement grey molasses cooling to achieve
-a lower starting temperature before RSC. \fxnote{cite}
+a lower starting temperature before RSC\cite{Colzi2016}.
 

### 2017-07-13 paper.tex
Cooling fitting

@@
 
-%% TODO
-
 Our final cooling results are shown in Fig.~\ref{f-radial} and \ref{f-axial}.
@@
 To characterize the single atom thermal occupation before and after cooling,
-we perform Raman sideband thermometry before and after cooling\fxnote{add citation?}.
+we perform Raman sideband thermometry before and after cooling.
 For the more tightly confined radial directions (non-degenerate),
@@
 and second-order cooling sidebands before RSC as is shown in red in Figure \ref{f-radial}A.
-
 After cooling, the first and second order cooling sidebands on both radial axes are suppressed.
 It is important to note that the simple sideband thermometry formula,
-which predicts the ratio of the cooling and heating sideband heights to be $\bar n / (\bar n + 1)$,
+which predicts the ratio of the cooling and heating sideband heights
+to be $\bar n / (\bar n + 1)$~\cite{Monroe1995},
 assumes that the coupling strength for different motional states to be proportional to $\sqrt{n}$.
@@
 with a relatively large Raman Lamb-Dickes parameters $\eta^R$, we cannot use this formula to
-measure $\bar n$. Instead, given the absence of the second order cooling sideband,
+measure $\bar n$.
+Instead, given the absence of the second order cooling sideband,
 we assume that the atoms are cold enough to have stronger coupling to the first order cooling
-sideband than the second order, in which case the
-
-\fxnote{How is the thermometry done? pulse duration etc.}
-, we perform sideband thermometry
-by taking the ratio of the peaks of first-order cooling and heating sidebands to measure $\bar n / (\bar n + 1)$ \fxnote{cite}.
-We found $\{\bar n =,\bar n =\}$, which corresponds to a ground state population of $90(2)$\%
+sideband than the second order, in which case the lower bound of the ground state population
+can be computed from the heights of the sidebands by assuming all of the excitation are in the
+$n=1$ state. In doing this, we found a ground state population of $90(2)$\%
 and $94(3)$\% along the two radial directions.
-
-we therefore use an independent measurement of Rabi flopping on the carrier (Fig. \ref{f-radial}B)
+We also use an independent measurement of Rabi flopping on the carrier (Fig. \ref{f-radial}B)
 and first-order heating(Fig. \ref{f-radial}C) sidebands
@@
 from the motional-state decohered Rabi flopping and obtained $70 \mu$K.
-
-%% End of TODO
 

### 2017-07-13 paper.tex
Update raman and op coupling plot

@@
   \includegraphics[width=8.5cm]{imgs/fig2_raman_op.pdf}
-  \caption{Matrix elements and heating as a function of motional state.
+  \caption{Optical pumping state changing probability and Raman matrix element for axial direction.
     The range plotted covers $95$\% of the initial thermal distribution.
-    (A) Matrix elements for Raman transition in the axial direction showing deviation from
-    $\sqrt{n}$ scaling and multiple minimums for different sideband orders.
+    (A) Axial motional state distribution after one optical pumping cycle
+    for different initial $n$. Due to the large Lamb-Dicke parameter,
+    there is a high probability of $n$ changing.
+    (B) Matrix elements for Raman transition in the axial direction showing deviation from
+    $\sqrt{n}$ scaling and multiple minima for different sideband orders.
     ($k$ is the difference in wave vector of the Raman beams,
     $r$ is the coordinate in axial direction).
-    (B) Average change in motional state after the optical pumping step for all three axis.
-    Due to the large Lamb-Dicke parameter,
-    there is a high probability of $n$ changing especially in the axial direction.
     \label{f-ld}}

### 2017-07-13 plot_raman_op.jl

@@ -112,20 +112,11 @@ const coupling_ra1 = (op_heating_all(op_heating_ra, 30, 30, Float32(η_ra1), fal
 const coupling_ra2 = (op_heating_all(op_heating_ra, 30, 30, Float32(η_ra2), false) *
                       op_heating_all(op_heating_ra, 30, 30, Float32(η_ra2), true))
 
-function p_heat(coupling, sz)
-    T = eltype(coupling)
-    res = Vector{T}(sz)
-    @inbounds for i in 1:sz
-        sump = zero(T)
-        avgΔn = zero(T)
-        @simd for j in 1:size(coupling, 1)
-            p = coupling[j, i]
-            sump += p
-            avgΔn += abs(j - i) * p
-        end
-        res[i] = avgΔn / sump
+function plot_op_sidebands(n1s, n2s, coupling)
+    for i in 1:length(n2s)
+        n2 = n2s[i]
+        plot(n1s, coupling[n2 + 1, n1s + 1], ".-")
     end
-    return res
 end
 
 function maybe_save(name)
@@ -155,30 +146,35 @@ end
 figure(figsize=[1.5, 1.1] * 4.8)
 
 ax1 = subplot(211)
-plot_sidebands(0:nmax, -1:-1:-5, η_ax)
-xlim([0, nmax])
-ylim([0, 0.75])
+plot_op_sidebands(0:nmax, [0, 1, 2, 5, 10, 20, 35, 55], coupling_ax)
+text(0.5, 0.8, "\$n_{init}\\!\\!=\\!\\!0\$", color="C0")
+text(1, 0.63, "\$n_{init}\\!\\!=\\!\\!1\$", color="C1")
+text(2, 0.47, "\$n_{init}\\!\\!=\\!\\!2\$", color="C2")
+text(3, 0.33, "\$n_{init}\\!\\!=\\!\\!5\$", color="C3")
+text(7, 0.21, "\$n_{init}\\!\\!=\\!\\!10\$", color="C4")
+text(19.5, 0.14, "\$n_{init}\\!\\!=\\!\\!20\$", color="C5")
+text(33, 0.12, "\$n_{init}\\!\\!=\\!\\!35\$", color="C6")
+text(49, 0.11, "\$n_{init}\\!\\!=\\!\\!55\$", color="C7")
[…]

### 2017-07-13 paper.tex
Mention and cite Blackman pulse

@@
     towards then end of the cooling sequence.
+    All of the Raman pulses use Blackman pulse envelopes to reduce the off resonance
+    coupling to carrier and heating sidebands.
     \label{f-setup}}
@@
 In order to address trap anharmonicity, we drive sidebands with a large Rabi frequency
-and short pulses to Fourier broaden spectrum coverage.
+and short pulses to Fourier broaden spectrum coverage and we use Blackman pulse envelops
+to avoid unwanted coupling to the carrier and heating sidebands~\cite{Kasevich1992}.
 For the higher trap frequency radial directions, anharmonicity is calculated to be 1kHz/n,
@@
 
-% Missing:
-% ?? Blackman pulse vs square pulse
-
 \bibliography{paper}

### 2017-07-14 paper.tex
Nick's updates

@@
 \begin{document}
-\title{Motional Ground-State Cooling Outside the Lamb-Dicke Regime}
+\title{Motional ground state Cooling Outside the Lamb-Dicke Regime}
 \author{Yichao Yu}
@@
 \author{Nicholas R. Hutzler}
+\altaffiliation{Present address: California Institute of Technology, Division of Physics, Mathematics, and Astronomy.  Pasadena, CA, 91125}
 \author{Jessie T. Zhang}
@@
   large differential AC Stark shifts in the excited state,
-  we achieved a ground-state preparation fidelity of $77(4)$\% after $100$ ms of cooling.
+  we achieve a ground state preparation fidelity of $77(4)$\% after $100$ ms of cooling.
   Our technique includes addressing very high-order sidebands and
-  fast modulating of optical tweezer trap.
+  fast modulation of the optical tweezer trap.
   We demonstrate that Raman sideband cooling to the 3D motional ground state is applicable
@@
 
-Bottom-up assemblies of trapped neutral atoms in optical tweezer arrays
+Systems of trapped neutral atoms assembled from the bottom-up in optical tweezer arrays
 are an exciting platform to study quantum information and quantum simulations~\cite{Schlosser2001,Weiss2004,Isenhower2010,Wilk2010,Kaufman2015,Labuhn2016,Murmann2015}.
-The inherent single-particle detection and control that combines with tunable interactions
-are keys to demonstrate neutral atom based quantum logic gates~\cite{Isenhower2010,Wilk2010},
+The inherent single-particle detection and control combined with tunable interactions
+are key to implementing neutral atom based quantum logic gates~\cite{Isenhower2010,Wilk2010},
 novel quantum phases~\cite{Labuhn2016}, and single-photon switches~\cite{Dayan2008,Tiecke2014}.
-Advances of real-time re-arrangement of optical tweezers enable rapid preparation of atoms
+Advances in real-time re-arrangement of optical tweezers enable rapid preparation of atoms
 in large and complex geometries with high fidelity~\cite{Barredo2016,Endres2016}.
 Adding quantum motional control of individual
-atoms~\cite{Li2012,Kaufman2012,Thompson2013,Liu2017,Robens2017} further allows
-efficient coupling of single atoms to photonic crystal cavity~\cite{Thompson2013a},
+atoms~\cite{Li2012,Kaufman2012,Thompson2013,Liu2017,Robens2017} enables
+efficient coupling of single atoms to photonic crystal cavities~\cite{Thompson2013a},
 high-fidelity single qubit gates~\cite{Wang2016},
-and laser-cooled bosons to exhibit indistinguishability
-through Hong-Ou-Mandel interference~\cite{Kaufman2014}.
+and studies of the atomic Hong-Ou-Mandel effect~\cite{Kaufman2014}.
 
-Extend such an optical tweezer array to polar molecules could open up a large range of
-new applications that exploits rich molecular long-lived internal states
-and high degrees of tunable interactions~\cite{DeMille2002,Ni2008,Gorshkov2011,Yan2013}.
-Molecules could be assembled from atoms directly inside the optical tweezer~\cite{Liu2017}
-or to be loaded from magneto-optical traps
+Extending optical tweezer array techniques to include polar molecules will open up a large range of
+new applications that exploit their many long-lived internal states
+and highly tunable interactions~\cite{DeMille2002,Ni2008,Gorshkov2011,Yan2013}.
+Molecules could be assembled from atom pairs in the optical tweezer~\cite{Liu2017},
+or directly loaded from magneto-optical traps
 (MOTs)~\cite{Barry2014,Truppe2017SubDoppler,Anderegg2017}.
-For either approach, preparing constituent atoms or molecules in the lowest motional
-quantum state is important for high efficient molecular assembly
-and for long coherence times of any realistic quantum applications.
+For either approach, preparing the constituent atoms or molecules in the lowest motional
+quantum state is important for realizing long coherence times in quantum applications.
 
-Prepare quantum ground-state for a variety of systems including
-single atoms in optical tweezers~\cite{Kaufman2012,Thompson2013,Liu2017,Robens2017}
-has been successful using Raman sideband cooling (RSC)~\cite{Monroe1995,Kerman2000,Han2000}.
-However, RSC in these systems has all been applied in the Lamb-Dicke regime where
-the size of the wavefunction is much smaller than the wavelengths of
-the Raman and optical pumping light.
-A challenging goal is to apply ground-state cooling to system such as atoms with light masses
-or laser-cooled polar molecules, that are often outside of the Lamb-Dicke regime.
-In this letter, we overcome this challenge and demonstrate cooling of single sodium atoms
-that are trapped in optical tweezers to the motional ground state.
-We achieve a single atom ground-state probability of $P_0=77(4)$\% by utilizing cooling of
+Preparation of single atoms in the motional ground state has been achieved in optical tweezers~\cite{Kaufman2012,Thompson2013,Liu2017,Robens2017}
+ using Raman sideband cooling (RSC)~\cite{Monroe1995,Kerman2000,Han2000}.
+However, RSC in these systems has been applied in the Lamb-Dicke (LD) regime, where
+the size of the atomic wavefunction is much smaller than the wavelength of light used to address them.
+Extending ground state cooling to systems outside the LD regime, such as light atoms or polar molecules, is challenging.
+In this letter we demonstrate cooling of single sodium atoms in optical tweezers, initially outside of the LD regime, to the motional ground state.
+We achieve a ground state probability of $P_0=77(4)$\% by utilizing cooling of
 very high-order sidebands in a carefully optimized cooling sequence.
-Our approach is general and opens up ground-state cooling for other systems.
+Our approach is general and opens up ground state cooling for other systems.
 
 Our experiment begins by loading a single sodium atom into an optical tweezer from a MOT
-for $250$ ms~\cite{Hutzler2017-LightShifts} and repeats at $2.5$ Hz.
-The tweezer is created by focusing a $700$nm laser beam through an NA=$0.55$ objective to
-a beam waist of $0.7 \mu$m.
-With $45$mW of tweezer power, the trapping frequencies are
+for $250$ ms~\cite{Hutzler2017-LightShifts}, and has an overall repetition rate of $2.5$ Hz.
+The tweezer is created by focusing a $700$ nm laser beam through an NA=$0.55$ objective to
+create a focused beam with waist $0.7 \mu$m.
+With $45$ mW of tweezer power, the trapping frequencies are
 $\{\omega_1,\omega_2,\omega_3\}/2\pi = \{69(1), 430(4), 590(5)\}\ \text{\text{kHz}}$.
-Upon loading, an image is taken for $1.5$ms to determine its success.
-The same imaging light is used for polarization gradient cooling (PGC) and
+After attempting to load an atom from the MOT, an image is taken with $1.5$ ms exposure time to determine if it was a success.
+The same imaging light is used for polarization gradient cooling (PGC), which
 reduces the temperature of the single atom to $70$ $\mu$K,
-which corresponds to an initial motional state along the three different axes of
-$\{\bar n_1, \bar n_2, \bar n_3\}=\{21(2),\, 3.4(2),\, 2.5(2)\}$ (initial $P_0=0.3$\%) in the trap.
+corresponding to an initial mean motional state along the three different axes of
+$\{\bar n_1, \bar n_2, \bar n_3\}=\{21(2),\, 3.4(2),\, 2.5(2)\}$, and therefore initial 3D ground state probability of $P_0=0.3$\%.
 A beam with $\sigma^-$-polarization is used to initialize the atom into
-the $|F=2, m_F=-2\rangle$ stretch state.
-The hyperfine state detection is done by pushing out atoms in the stretch state with a strong
+the $|F=2, m_F=-2\rangle$ stretched state via optical pumping.
+The hyperfine state detection is performed by pushing out atoms in the stretched state with a strong
 beam on resonance with the $|F=2, m_F=-2\rangle$ to $|F'=3, m_{F'}=-3\rangle$ transition before
-taking the second image.
+taking the second image to determine if the atom was pushed out.
 The state preparation and detection have a combined fidelity of larger than $99$\%.
@@
 To further reduce the temperature of the single atom and
-to achieve high ground-state preparation fidelity, we apply Raman sideband cooling.
-The relevant energy levels, the cooling sequence, and the Raman beam geometries our system
-is shown in Figure \ref{f-setup}. Overall, the RSC consists of two steps:
-a step to drive a coherent Raman transition while removing motional quanta and
-a step to reset the atom internal state via optical pumping (OP).
-RSC is applied repeatedly until motional ground state is achieved.
+to achieve high ground state preparation fidelity, we apply Raman sideband cooling (RSC).
+The relevant energy levels, cooling sequence, and Raman beam geometries for our system
+are shown in Figure \ref{f-setup}. Briefly, the RSC consists of two steps:
+driving a coherent Raman transition while removing motional quanta, followed by resetting the atom's internal state via optical pumping (OP).
+RSC is applied repeatedly until the motional ground state is populated with high probability.
 
 Specifically, Raman transitions are driven in Na between the hyperfine states
-$|F=2, m_F=-2\rangle$ and  $|F=1, m_F=-1\rangle$ in the presence of a $8.8$ G magnetic field.
+$|F=2, m_F=-2\rangle$ and  $|F=1, m_F=-1\rangle$ in the presence of a $8.8$ G magnetic field to suppress vector light shifts~\cite{Kaufman2012,Thompson2013}.
 Subsequently, an OP/repump pulse brings the atom back to $|F=2, m_F=-2\rangle$
-via spontaneous emissions.
-Because any photon scattering is a heating source,
-we use a $\sigma^-$-polarized laser resonant with the D1 line for repump,
-which is dark to $|F=2, m_F=-2\rangle$ \fxnote{cite ion and K39}.
-Compared to using a D2 repump beam, we find a reduction in the $|F=2, m_F=-2\rangle$
-scattering rate of a factor of $130(20)$.
+via spontaneous emission.
 
-For an atom in the motional level $n$, the OP could result in motional-state redistribution
+It is important that the re-pumping step scatter as few photons as possible to minimize heating.
+Therefore, we use a $\sigma^-$-polarized laser resonant with the D1 line since the $|F=2, m_F=-2\rangle$ is a dark state in this case \fxnote{cite ion and K39}.
+Compared to using a D2 repump beam, from which the $|F=2, m_F=-2\rangle$ state could always scatter a photon via the excited $|F=r, m_F=-3\rangle$ state, we find a reduction in the scattering rate of a factor of $130(20)$.
+
+For an atom in motional level $n$, the OP could result in motional-state redistribution
 as shown in Fig.~\ref{f-ld}A. The state redistribution probability
-is approximately proportional to the effective Lamb-Dicke parameter
+is approximately proportional to the effective LD parameter
 $\eta^{OP}_{\eff}=\sqrt{2n+1}\eta^{OP}$, where $\eta^{OP}=k z_0=k \sqrt{\hbar/2m\omega}$,
-$k$ is the optical pumping wavenumber, $z_0$ is the zero-point wavefunction spread,
+$k$ is the wavenumber of the optical pumping beam, $z_0$ is the zero-point wavefunction spread,
 $m$ is the mass of the atom, and $\hbar$ is the reduced Planck constant.
@@
 $\{\eta^{OP}_{1\eff},\eta^{OP}_{2\eff},\eta^{OP}_{3\eff}\} = \{4.0(1), 0.67(2), 0.50(1)\}$.
-For the weak axial direction, $(\eta^{OP}_{1\eff})^2>1$ is far outside of the Lamb-Dicke regime.
+For the weak axial direction, $(\eta^{OP}_{1\eff})^2>1$ is far outside of the LD regime.
 As a result, the average change of motional state per OP step is large,
-which creates a large uncertainty on the motional state at the end of a full RSC step.
-Scenarios of runaway OP heating from RSC cycles are possible.
-As a comparison, the averaged change in motional states over the initial distribution
+which creates a large uncertainty on the motional state at the end of a full RSC step, and possibly leading to runaway heating.
+For example, the average change in motional states over the initial distribution
 is $2.4$ in the axial direction, which is significantly greater than $0.89-0.95$
@@
 
-Fortunately, the large Lamb-Dicke parameters also provide a way to overcome OP heating.
+Fortunately, the large LD parameters also provide opportunities to overcome OP heating.
 The Raman transitions in our configuration have
@@
 Since the coupling strengths of different orders do not reach minima for the same pulse duration,
-using multiple orders of cooling sidebands would avoid accumulations of population
+using multiple orders of cooling sidebands avoids accumulations of population
 near the coupling minima.
@@
 Taking the large motional-state changing heating and cooling sources into account,
-it was not immediately clear that efficient cooling can be achieved.
+it is not immediately clear that efficient cooling can be achieved.
 We therefore use a Monte-Carlo simulation to guide our search and
 to find a robust cooling sequence\footnote{See supplemental material}.
-In the simulation, we indeed observe a high heating rate due to the large Lamb-Dicke parameters
+In the simulation, we indeed observe a high heating rate due to the large LD parameters
 and confirm that cooling with higher-order Raman sidebands can suppress heating.
@@
 to minimize the accumulation of the atom in motional states that have zero Raman coupling.
-The simulation also indicates setting the coupling strength of each cooling sideband
+The simulation also indicates that setting the coupling strength of each cooling sideband
 to drive a Rabi $\pi$ pulse corresponding to the maximum matrix element motional state
-(i.e. the maxima in \ref{f-ld}B).
-Such choice insures each order cools a range of states that have the strongest
-couplings and leaves other sidebands to cool the rest.
+(i.e. the maxima in \ref{f-ld}B) can yield efficient cooling.
 The efficiency of cooling on higher-order sidebands diminishes
-as the atom approaches the ground state.
-Therefore, the final cooling cycles utilize only the first-order sideband
-while alternating between different axes.
+as the atom approaches the ground state, so the final cooling cycles utilize only the first-order sideband while alternating between the three different axes.
 
-Guided by the promising simulation results,
-we construct our axial cooling sequence by starting at the highest
-two observed cooling sidebands (8th- and 7th-orders)
+Guided by the simulation results,
+we construct our axial cooling sequence by starting at the two highest
+observed cooling sidebands (8th- and 7th-orders)
 and decreasing the orders after $6$ to $15$ cycles.
-This process is repeated until we reach the first order cooling sideband where most of the
-population are in the first few excited state at which point we switch to only cooling on the
+This process is repeated until we reach the first order cooling sideband, and most of the
+population is in the first few excited states.  We then switch to cooling only on the
 first order sideband with two different pulse lengths in order to efficiently cool atoms in the
 few remaining motional states.
-The radial cooling is done similarly to the axial cooling with the initial cooling orders being
+The radial cooling is performed similarly to the axial cooling with the initial cooling orders being
 the 2nd and 1st order and switching to first order only after $20$ to $30$ pulses.
-This sequence gives good initial cooling performance which is used to measure experimental
+This sequence gives good initial cooling performance, which can then be used to measure experimental
 parameters, including the Rabi rates of the Raman beams and optical pumping rates,
@@
 
-Two additional challenges of cooling single sodium atoms are
-further identified and addressed experimentally.
-First, the high initial temperature causes population in high motional states
-means that the atoms sample anharmonicity of the trap away from the center.
-In order to address trap anharmonicity, we drive sidebands with a large Rabi frequency
-and short pulses to Fourier broaden spectrum coverage and we use Blackman pulse envelops
+There are two additional important challenges in cooling single sodium atoms.
+First, the high initial temperature populates high motional states,
+meaning that the atoms sample the anharmonicity of the trap away from the center.
+In order to address this, we drive the sidebands with a large Rabi frequency
+and short pulses to Fourier broaden the spectrum coverage, and use Blackman pulse envelopes
 to avoid unwanted coupling to the carrier and heating sidebands~\cite{Kasevich1992}.
-For the higher trap frequency radial directions, anharmonicity is calculated to be 1kHz/n,
+The anharmonicity in the radial directions is calculated to be 1kHz/n, meaning that a
 Rabi frequency of at least $15$ kHz is needed to couple to $99$\% population up to $n=15$.
@@
 in the excited state. This creates a large, position-dependent OP detuning
-and mixes the excited-state hyperfine levels, and therefore reduces the optical pumping fidelity.
-We solve this issue by switching the trapping light at 3 MHz during the whole cooling sequence,
+and mixes the excited-state hyperfine levels, which reduces the optical pumping fidelity.
+We address this by switching the trapping light at 3 MHz during the whole cooling sequence,
 similar to our loading and imaging process~\cite{Hutzler2017-LightShifts},
@@
 Our final cooling results are shown in Fig.~\ref{f-radial} and \ref{f-axial}.
-In total, $1000$ cooling pulses (for $100$ ms) are applied along three axes with
-cooling begins on the radial second order to remove most energy initially.
+In total, $1000$ cooling pulses (with a total duration of $100$ ms) are applied along three axes with
+cooling beginning on the radial second order.
 To characterize the single atom thermal occupation before and after cooling,
-we perform Raman sideband thermometry before and after cooling.
-For the more tightly confined radial directions (non-degenerate),
+we perform Raman sideband thermometry.
+For the more tightly confined (non-degenerate) radial directions,
 we observe clear first-order heating, first-order cooling,
@@
 assumes that the coupling strength for different motional states to be proportional to $\sqrt{n}$.
-Outside of the Lamb-Dickes regime, however,
-the coupling strength deviates from this simple scaling rule rapidly
-as shown in figure \ref{f-ld}A and since the Raman spectroscopy is performed
-with a relatively large Raman Lamb-Dickes parameters $\eta^R$, we cannot use this formula to
+However, outside of the LD regime, the coupling strength deviates from this simple scaling rule rapidly,
+as shown in figure \ref{f-ld}A.  Since the Raman spectroscopy is performed
+with relatively large Raman LD parameters $\eta^R$, we cannot use this formula to
 measure $\bar n$.
 Instead, given the absence of the second order cooling sideband,
-we assume that the atoms are cold enough to have stronger coupling to the first order cooling
+we assume \fxnote{[What is the cutoff for the validity of this assumption, and are we below that cutoff?]} that the atoms are cold enough to have stronger coupling to the first order cooling
 sideband than the second order, in which case the lower bound of the ground state population
@@
 and first-order heating(Fig. \ref{f-radial}C) sidebands
-to verify the ground-state population~\cite{Meekhof1996}.
+to verify the ground state population~\cite{Meekhof1996}.
 The data is fitted using the same Monte-Carlo simulation we used to simulate the cooling
@@
 We also extracted the initial temperature before cooling
-from the motional-state decohered Rabi flopping and obtained $70 \mu$K.
+from the motional-state decohered Rabi flopping to obtain the initial temperature of $70 \mu$K.
 
@@
 due to the large $\eta^{OP}_{eff1}\approx 4.0(2)$.
-In the Raman sideband thermometry, we observe up to 8th-order cooling sidebands initially,
+We observe up to 8th-order Raman cooling sidebands initially,
 which indicates population in highly-excited motional states.
@@
 after RSC (Fig.~\ref{f-axial}).
-The ground-state probability calculated using the ratio of first-order sideband heights yields
+The ground state probability calculated using the ratio of first-order sideband heights yields
 $92(3)$\%. We also perform Rabi flopping on the carrier(Figure~\ref{f-axial}B)
-and extracted a ground-state population of $91(2)$\%, in agreement with the other method.
+and extracted a ground state population of $91(2)$\%, in agreement with the other method.
 For the first-order heating sideband Rabi flopping (Figure~\ref{f-axial}C),
@@
 We measuring a heating rate of the single atoms in the tweezer to be $0.9$\%/s
-due to trapping light scattering\cite{Grimm2000}.
-The ground-state preparation fidelity is currently limited by off-resonant scattering
+due to off-resonant scattering of the trapping light\cite{Grimm2000}.
+The ground state preparation fidelity is currently limited by off-resonant scattering
 from the Raman beams,
@@
 and the resonance shift caused by magnetic field fluctuations.
-In addition, there are $15$\% population loss during the experiment which gives us a $66(3)$\%
-probability of ground state atom after each successful loading event.
-The loss includes $5$\% from single atom imaging and
-$10$\% very high-lying initial motional states
-that are not efficiently cooled by RSC, but off-resonantly heat by the Raman beams.
-We are planing to improve these by increasing the detuning of the Raman beams,
-addressing wider range of anharmonicity by frequency sweep,
-implementing better control of the magnetic field and optimize the temperature during imaging.
-We expect these changes to improve the cooling performance further.
+
+There is an additional $5$\% loss from finite imaging fidelity and $10$\% loss from very high-lying initial motional states
+that are not efficiently cooled by RSC, but off-resonantly heated by the Raman beams.  These give us a $66(3)$\% probability of ground state atom after each successful loading event.
+We are planning to improve these by increasing the detuning of the Raman beams,
+addressing wider range of trap anharmonicity by frequency sweeps,
+implementing better control of the magnetic field, and optimizing the temperature during imaging.
 Another improvement could be to implement grey molasses cooling to achieve
@@
 
+\fxnote{[The distinction between 77 and 66 percent is confusing, we should discuss it]}
+
 We have shown that despite the difficulty in achieving a low optical cooling temperature
 of light mass sodium atoms, reliable three dimensional cooling
-with significant ground-state population can be achieved by using high-order Raman sidebands
-in an optimized cooling sequence in the presence of temporal switching tweezer trap.
+with significant ground state population can be achieved by using high-order Raman sidebands
+in an optimized cooling sequence.
 These techniques are well-suited for a large variety of systems
-and open up a route to ground-state cooling to other species including molecules and exotic atoms.
+and open up a route to ground state cooling to other species, including molecules and exotic atoms.
 
-We thank T. Rosenband and J. Hood for discussion.
+We thank T. Rosenband and J. Hood for valuable discussions.
 This work is supported by the NSF through the Harvard-MIT CUA,

### 2017-07-17 paper.tex
More Nick Updates
Minor updates to main text, updates to SM.

@@
 \begin{document}
-\title{Motional ground state Cooling Outside the Lamb-Dicke Regime}
+\title{Motional Ground State Cooling Outside the Lamb-Dicke Regime}
 \author{Yichao Yu}
@@
     We use D1 light with $\sigma^-$ polarization to repump atoms out of $|F=2,m_F=-1\rangle$
-    state to minimize heating on the atom in $|F=2,m_F=-2\rangle$ state
+    state to minimize heating on the atom in the $|F=2,m_F=-2\rangle$ state
     (B) Geometry and polarizations of the Raman and optical pumping beams relative to the
@@
     the red lines corresponds to a thermal distribution of $70$ $\mu$K before cooling.
-    The blue lines does not take into account the effect of decoherence due to resonance
+    The blue lines do not take into account the effect of decoherence due to resonance
     fluctuation. By comparing it to the green line in (C), which includes a $3$ kHz fluctuation,

### 2017-07-17 sm.tex
Typo...
Cite julia paper
More Nick Updates
Minor updates to main text, updates to SM.

@@
-\documentclass[aps,twocolumn,secnumarabic,balancelastpage,amsmath,amssymb]{revtex4}
+\documentclass[aps,twocolumn,secnumarabic,amsmath,amssymb]{revtex4}
 \usepackage{amsmath}
@@
 
-\subsection{Overview}
+%\subsection{Overview}
 
 We use a computer simulation to study the importance of different effects
-and guide the optimization of cooling.
-The simulation uses quantum jump method\cite{Chretien2014} (or Monte-Carlo wavefunction method)
-to accurately calculate the evolution within each laser pulse while different energy eigenstates
-are assumed to decohere immediately on spontaneous emission of photon and on pulse boundaries.
-Such approxiations are valid for simulation of the cooling and greatly simplifies the computation
+and guide the optimization of Raman sideband cooling.
+The simulation uses the quantum jump (or Monte-Carlo wavefunction) method~\cite{Chretien2014} 
+to accurately calculate the evolution within each laser pulse where different energy eigenstates
+are assumed to decohere immediately upon spontaneous emission and on pulse boundaries.
+Such approximations are valid and greatly simplifies the computation
 at the cost of limiting the applicability of the simulation to processes that requires stronger
-coherence such as Ramsey spectroscopy and rapid push-out.
+coherence, such as Ramsey spectroscopy or rapid push-out of the atoms from the trap.
 
-A few other approximations are used in the simulation either because they are proved to have
-negligible effect on the experiment or because they'll increase the complexity of the simulation
-and can be optimized through other methods in the experiment.
-A list of the most important approximations is,
+A number of other simplifying approximations, listed below, are also used in the simulation.
+These either have a demonstrably negligible effect on the experiment, or result in a significant reduction of complexity for an effect that can be optimized more easily in the experiment.
 
 \begin{enumerate}
-\item All Raman pulses are assumed to be resonantly driving only one sideband/carrier order.\\
-  We tweak the pulse shape, power and length to suppress any deviation
-  from this in the experiment. We do still see deviation from this in the experiment
-  but the effect is small for the short pulse we use for cooling and is the most pronounced
-  for long detection pulses.
-\item No heating from other sources including trap switching.\\
-  We measured the heating rate and observed that it mainly comes from off-resonance scattering
-  of photons from various sources which we already include so additional heating can be
-  ignored.
-\item Trapping frequency difference between different states are ignored.\\
-  This effect is negligible for Na in the ground state due to the small fine structure.
+\item \emph{All Raman pulses resonantly drive only one sideband/carrier order.}  We tweak the pulse shape, power and length as discussed in the text, for example by using Blackman pulses, to reduce coupling to other orders.
+We do see deviation from this approximation in the experiment, though mostly in the long detection pulses, and it is less of a concern for the short cooling pulses.
+\item \emph{No heating from other sources.}\\
+  We measured the heating rate and found that it results mainly from off-resonant scattering
+  of photons, which is included in the simulation.  In particular, we can ignore heating from the switching trap.
+\item \emph{Same trapping frequency for all states.}\\
+  This effect is negligible for Na in the ground state due to the small fine structure splitting in the excited state.
   It is easy to include this effect if the calculation needs to be repeated on a system where
@@
 
-Some of the important effects that are included are,
-\begin{enumerate}
-\item Full 3D simulation.\\
-  This includes 3D motional states, accurate 3D wavevector, and different emission pattern
-  for different photon polarizations.
-\item Off resonant scattering from all beams.\\
-  Including Raman, optical pumping and dipole trap.
-\item Optical pumping polarization imperfection.
-\end{enumerate}
+Some effects that are important to include are all three dimensions (3D motional states, accurate 3D wavevector, and different emission pattern for different photon polarizations), off-resonant scattering from all laser beams, and optical pumping polarization imperfection.
+The optical pumping polarization and off-resonant scattering are especially important
+for accurate simulation since they are the main limitation on cooling performance.
 
-The optical pumping polarization and the off resonant scattering are especially important
-for accurate simulation since they are the main heating source that is present
-for ground motional dark state atom and therefore are the main limation on cooling performance.
+%\subsection{Simulation of each pulse}
 
-\subsection{Simulation of each pulse}
-
-Each pulse in general has a coherent part from the Raman drive (zero for optical pumping pulse)
-and an incoherent part from scattering (optical pumping or off-resonance scattering).
-This nicely fits the general formula of the quantum jump method. Due to the large number of
-states that we need to take into account ($30-150$ states in each of the three axis and
-$8$ hyperfine states, giving a total of $10^6$ states),
-the generic wavefunction propagation is very inefficient.
-Therefore, this is further simplified by reducing the number of states to be kept track of during
-the coherent propagation and apply quantum jump using a set of reduced jump operator that
-describes the total jump probability from a certain states (sum over all final states).
+In general, each pulse has a coherent part from the Raman drive (which is absent for the optical pumping pulses)
+and an incoherent part from scattering (optical pumping or off-resonant).
+This nicely fits the general approach of the quantum jump method. Due to the large number of
+states that we need to take into account ($30-150$ motional per axis and
+$8$ hyperfine, giving a total of $10^6$),
+ generic wavefunction propagation is very inefficient.
+Therefore, we further simplify by reducing the number of states tracked during
+the coherent propagation and apply quantum jumps using a set of reduced jump operator that
+describes the total jump probability from a certain states (summed over all final states).
 The coherent propagation is then accurately solved in order to avoid having to use a time step
@@
 modification from the jump operators as in quantum jump method.
-When a jump happens, we pick a final internal state to jump to based on the rates ratio
+When a jump happens, we pick a final internal state to jump to based on the relative rates
 of different scattering sources and their branching ratios.
@@
 a particular wave vector for the emitted photon is then selected as the next step.
-The recoil is not fixed so the final motional state of the atom can now be selected.
+The recoil is now fixed so the final motional state of the atom can now be selected.
 This process is then repeated on the same pulse until the pulse time is used up before
@@
 
-\subsection{Measurements}
+%\subsection{Measurements}
 
-We apply ``virtual'' measurements on each results of the cooling which we then average to
-obtain the expected value of qualities that we are interested in.
+We apply ``virtual'' measurements on the results of each simulated cooling sequence which we then average to
+obtain the expected value of experimental quantities.
 Due to the decoherence approximation, the measurement has to commute with the Hamiltonian.
 Particularly useful measurements used in our simulation are hyperfine state distribution,
-Average motional energy, loss rate (where an atom is assumed to be lost if its motional energy
+average motional energy, loss rate (where an atom is assumed to be lost if its motional energy
 goes above a certain threshold at any time) probability of being in certain states
@@
 
-\subsection{Sample results}
-
-\begin{figure}
+\begin{figure}[t]
   \includegraphics[width=8.5cm]{imgs/simcool_no_scatter.pdf}
@@
 \end{figure}
-
-\begin{figure}
+\begin{figure}[t]
   \includegraphics[width=8.5cm]{imgs/simcool_real.pdf}
@@
     off-resonant scattering from all beams and OP misalignment.
-    For this particular sequence, the ground state probability saturates $\approx88\%$.
+    For this particular sequence, the ground state probability saturates to $\approx88\%$.
     \label{f-real}}
@@
 
-When not considering the off-resonant scattering from the Raman beams and the tweezer as well
-as optical pumping polarization misalignment, the simulation shows that there isn't a cooling
+If off-resonant scattering and optical pumping polarization misalignment are ignored, the simulation shows that there isn't a cooling
 limit despite the large Lamb-Dicke parameter and high initial temperature (Fig \ref{f-no-scatter}).
@@
 
-\subsection{Code}
+%\subsection{Code}
 
-The simulation is written in Julia. All code are available under GPLv3 license at
+The simulation is written in Julia\cite{Bezanson2017}.
+All code is available under the GPLv3 license at
 \footnote{\href{https://goo.gl/WLJwJp}{Library code (https://goo.gl/WLJwJp)}} and

### 2017-07-19 paper.tex
Jessie and Lee's comments

@@
     The four axial pulses are addressing two neighboring cooling orders.
-    The two pulses in each radial directions are either addressing two neighboring cooling orders
+    The two pulses in each radial direction are either addressing two neighboring cooling orders
     or having different length on the first order when most of the population are below $n=3$
-    towards then end of the cooling sequence.
-    All of the Raman pulses use Blackman pulse envelopes to reduce the off resonance
+    towards the end of the cooling sequence.
+    All of the Raman pulses use Blackman pulse envelopes to reduce the off-resonant
     coupling to carrier and heating sidebands.
@@
     Solid lines in (B) and (C) are theoretical calculation of the Rabi flopping.
-    The blue lines corresponds to a ground state probability of $93$\% after cooling and
-    the red lines corresponds to a thermal distribution of $70$ $\mu$K before cooling.
+    The blue lines correspond to a ground state probability of $93$\% after cooling and
+    the red lines correspond to a thermal distribution of $70$ $\mu$K before cooling.
     \label{f-radial}}
@@
     fluctuation. By comparing it to the green line in (C), which includes a $3$ kHz fluctuation,
-    we can clearly see that this effect is the strongest for the after cooling data on
+    we can clearly see that this effect is the strongest for the post-cooling data on
     the axial heating sideband where the Rabi frequency is the lowest.
@@
 Therefore, we use a $\sigma^-$-polarized laser resonant with the D1 line since the $|F=2, m_F=-2\rangle$ is a dark state in this case \fxnote{cite ion and K39}.
-Compared to using a D2 repump beam, from which the $|F=2, m_F=-2\rangle$ state could always scatter a photon via the excited $|F=r, m_F=-3\rangle$ state, we find a reduction in the scattering rate of a factor of $130(20)$.
+Compared to using a D2 repump beam, from which the $|F=2, m_F=-2\rangle$ state could always scatter a photon via the excited $|F=3, m_F=-3\rangle$ state, we find a reduction in the scattering rate of a factor of $130(20)$.
 
@@
 is approximately proportional to the effective LD parameter
-$\eta^{OP}_{\eff}=\sqrt{2n+1}\eta^{OP}$, where $\eta^{OP}=k z_0=k \sqrt{\hbar/2m\omega}$,
+$\eta^{OP}_{eff}=\sqrt{2n+1}\eta^{OP}$, where $\eta^{OP}=k z_0=k \sqrt{\hbar/2m\omega}$,
 $k$ is the wavenumber of the optical pumping beam, $z_0$ is the zero-point wavefunction spread,
@@
 As a result, the average change of motional state per OP step is large,
-which creates a large uncertainty on the motional state at the end of a full RSC step, and possibly leading to runaway heating.
+which creates a large uncertainty on the motional state at the end of a full RSC step, possibly leading to runaway heating.
 For example, the average change in motional states over the initial distribution
@@
 $\{\eta^R_{1},\eta^R_{2},\eta^R_{3}\} = \{0.40(1), 0.341(2), 0.291(1)\}$,
-which allow strong coupling to higher order sidebands for atoms in large motional states
+which allow strong coupling to higher order sidebands for atoms in higher motional states
 as calculated in Figure~\ref{f-ld}B.
@@
 while leaving OP on with constant intensity.
-Due to the large light shift, the optical pumping is effectively off when the trap light is on.
+Due to the large light shift, the OP is effectively off whenever the trap light switches back on.
 Since the atom can only be addressed by the optical pumping light when the trap light is off,
-the effect of light shift on optical pumping fidelity is suppressed.
+the effect of light shifts on OP fidelity is suppressed.
 
@@
 assumes that the coupling strength for different motional states to be proportional to $\sqrt{n}$.
-However, outside of the LD regime, the coupling strength deviates from this simple scaling rule rapidly,
+However, outside of the LD regime,
+the coupling strength rapidly deviates from this simple scaling rule,
 as shown in figure \ref{f-ld}A.  Since the Raman spectroscopy is performed
@@
 sideband than the second order, in which case the lower bound of the ground state population
-can be computed from the heights of the sidebands by assuming all of the excitation are in the
+can be computed from the heights of the sidebands by assuming all of the excitations are in the
 $n=1$ state. In doing this, we found a ground state population of $90(2)$\%
@@
 For the weaker axial direction, cooling is much more challenging
-due to the large $\eta^{OP}_{eff1}\approx 4.0(2)$.
+due to the large $\eta^{OP}_{1eff}\approx 4.0(2)$.
 We observe up to 8th-order Raman cooling sidebands initially,
@@
 after RSC (Fig.~\ref{f-axial}).
-The ground state probability calculated using the ratio of first-order sideband heights yields
+The ground state population calculated using the ratio of first-order sideband heights yields
 $92(3)$\%. We also perform Rabi flopping on the carrier(Figure~\ref{f-axial}B)
@@
 For the first-order heating sideband Rabi flopping (Figure~\ref{f-axial}C),
-we observed additional decoherence that is more produced due to the slower Rabi frequency.
+we observed additional decoherence that is more pronounced due to the slower Rabi frequency.
 The decoherence time scale is consistent with magnetic field fluctuations of $1.5$ mG
@@
 
-There is an additional $5$\% loss from finite imaging fidelity and $10$\% loss from very high-lying initial motional states
-that are not efficiently cooled by RSC, but off-resonantly heated by the Raman beams.  These give us a $66(3)$\% probability of ground state atom after each successful loading event.
+There is an additional $5$\% loss from finite imaging fidelity and $10$\% loss
+from very high-lying initial motional states that are not efficiently cooled by RSC,
+but instead off-resonantly heated by the Raman beams.
+These give us a $66(3)$\% probability of ground state atom after each successful loading event.
 We are planning to improve these by increasing the detuning of the Raman beams,
-addressing wider range of trap anharmonicity by frequency sweeps,
+addressing a wider range of trap anharmonicity by frequency sweeps,
 implementing better control of the magnetic field, and optimizing the temperature during imaging.
@@
 
+% Define \eta_R
+% Lamb-Dicke parameter square explain
+% why not just molecules instead of polar molecules
+% entropy
+% use different line shape for rabi flopping
+% mention axis definitions
+% heating from trap -> decrease of ground state procetage (maybe add temprature too)
+% Differetial AC starck shift **between excited states and ground states**?
+% at the same time, the atom is cooled via PGC instead of "the same imaging light is used to"
+% 1 sentence to explain why anisotropy?
+% is strobed at 3MHz instead of is switching at...
+% Cite Na loading paper in caption?
+% Make sure the caption for the before cooling axial rabi flopping mentions decoherence
+% Mention after cooling is non-thermal?
+% Make it clear that we cool for 6-15 cycles each time before going to the next set of orders in axial
+
+% sm:
+% mention the simulation results are 3d
+% effect of changing groups.
+% mention effects that are included first.
+
 \bibliography{paper}

### 2017-07-19 sm.tex
Jessie and Lee's comments

@@
 
-%\subsection{Overview}
-
 We use a computer simulation to study the importance of different effects
@@
 are assumed to decohere immediately upon spontaneous emission and on pulse boundaries.
-Such approximations are valid and greatly simplifies the computation
-at the cost of limiting the applicability of the simulation to processes that requires stronger
-coherence, such as Ramsey spectroscopy or rapid push-out of the atoms from the trap.
+Such approximations are valid and greatly simplify the computation
+at the cost of limiting the applicability of the simulation to processes that require stronger
+coherence, such as Ramsey spectroscopy or rapid push-out of the atoms from the trap
+(faster than a trap oscillation period).
 
 A number of other simplifying approximations, listed below, are also used in the simulation.
-These either have a demonstrably negligible effect on the experiment, or result in a significant reduction of complexity for an effect that can be optimized more easily in the experiment.
+These either have a demonstrably negligible effect on the experiment,
+or result in a significant reduction of complexity for an effect
+that can be optimized more easily in the experiment.
 
@@
 
-Some effects that are important to include are all three dimensions (3D motional states, accurate 3D wavevector, and different emission pattern for different photon polarizations), off-resonant scattering from all laser beams, and optical pumping polarization imperfection.
+Some effects that are important to include are all three dimensions (3D motional states,
+accurate 3D wavevector, and different emission pattern for different photon polarizations),
+off-resonant scattering from all laser beams, and optical pumping polarization imperfection.
 The optical pumping polarization and off-resonant scattering are especially important
@@
 
-%\subsection{Simulation of each pulse}
-
-In general, each pulse has a coherent part from the Raman drive (which is absent for the optical pumping pulses)
+In general, each pulse has a coherent part from the Raman drive
+(which is absent for the optical pumping pulses)
 and an incoherent part from scattering (optical pumping or off-resonant).
-This nicely fits the general approach of the quantum jump method. Due to the large number of
-states that we need to take into account ($30-150$ motional per axis and
-$8$ hyperfine, giving a total of $10^6$),
+This nicely fits the general approach of the quantum jump method.
+Due to the large number of states that we need to take into account
+($30-150$ motional per axis and $8$ hyperfine, giving a total of $10^6$),
 generic wavefunction propagation is very inefficient.
 Therefore, we further simplify by reducing the number of states tracked during
-the coherent propagation and apply quantum jumps using a set of reduced jump operator that
-describes the total jump probability from a certain states (summed over all final states).
+the coherent propagation and applying quantum jumps using a set of reduced jump operators that
+describe the total jump probability from a certain state (summed over all final states).
 The coherent propagation is then accurately solved in order to avoid having to use a time step
-much shorter than the scattering rate (up to hundreds of kHz)\footnote{\href{https://goo.gl/EZ13wt}{note about modification to the quantum jump method (https://goo.gl/EZ13wt)}}.
+much shorter than the inverse of scattering rate (up to hundreds of kHz)\footnote{\href{https://goo.gl/EZ13wt}{note about modification to the quantum jump method (https://goo.gl/EZ13wt)}}.
 
 In order to simulate a pulse, we first start with the coherent propagation that includes the
-modification from the jump operators as in quantum jump method.
+modification from the jump operators as in the quantum jump method.
 When a jump happens, we pick a final internal state to jump to based on the relative rates
 of different scattering sources and their branching ratios.
-This process also determines the polarization and emission pattern of the photon and
-a particular wave vector for the emitted photon is then selected as the next step.
-The recoil is now fixed so the final motional state of the atom can now be selected.
-This process is then repeated on the same pulse until the pulse time is used up before
-we start to simulate the next pulse.
+This process determines the polarization and emission pattern of the emitted photon,
+from which we randomly sample a particular wave vector.
+The photon recoil being defined, we can then assign a final motional state to the atom.
+This process is then repeated as long as the pulse is on,
+before we start to simulate the next pulse.
 
-%\subsection{Measurements}
-
-We apply ``virtual'' measurements on the results of each simulated cooling sequence which we then average to
-obtain the expected value of experimental quantities.
+We apply ``virtual'' measurements on the results of each simulated cooling sequence
+which we then average to obtain the expected value of experimental quantities.
 Due to the decoherence approximation, the measurement has to commute with the Hamiltonian.
@@
 
-If off-resonant scattering and optical pumping polarization misalignment are ignored, the simulation shows that there isn't a cooling
-limit despite the large Lamb-Dicke parameter and high initial temperature (Fig \ref{f-no-scatter}).
+If off-resonant scattering and optical pumping polarization misalignment are ignored,
+the simulation shows that there isn't a cooling limit
+despite the large Lamb-Dicke parameter and high initial temperature (Fig \ref{f-no-scatter}).
 However, when these effects are taken into account, the ground state probability can saturate at
 a lower value (Fig \ref{f-real}) and require much more careful tweaking.
-
-%\subsection{Code}
 

### 2017-07-20 paper.tex
Implement more suggestions

@@
   Despite having a very large Lamb-Dicke parameter, high initial temperature, and
-  large differential AC Stark shifts in the excited state,
+  large differential AC Stark shifts between the excited state and the ground state,
   we achieve a ground state preparation fidelity of $77(4)$\% after $100$ ms of cooling.
@@
     optical tweezer and bias magnetic field.
-    (C) Schematic of the cooling sequence. The tweezer switches at 3 MHz to
-    reduce light shifts during optical pumping. Each cooling cycle consists of $8$ pulses.
+    (C) Schematic of the cooling sequence. The tweezer is strobed at 3 MHz to
+    reduce light shifts during optical pumping~\cite{Hutzler2017-LightShifts}.
+    Each cooling cycle consists of $8$ pulses.
     The four axial pulses are addressing two neighboring cooling orders.
@@
 Fortunately, the large LD parameters also provide opportunities to overcome OP heating.
-The Raman transitions in our configuration have
+The Raman transitions in our configuration have LD parameters of
 $\{\eta^R_{1},\eta^R_{2},\eta^R_{3}\} = \{0.40(1), 0.341(2), 0.291(1)\}$,
@@
 as calculated in Figure~\ref{f-ld}B.
+The LD parameter for Raman transitions is defined as $\eta^R\equiv\Delta k z_0$ similar to OP
+where $\Delta k$ being the wave vector difference
+between the two beams that drives the Raman transition.
 To offset heating from OP initially, higher-order Raman cooling sidebands can be utilized
@@
 and mixes the excited-state hyperfine levels, which reduces the optical pumping fidelity.
-We address this by switching the trapping light at 3 MHz during the whole cooling sequence,
+We address this by strobing the trapping light at 3 MHz during the whole cooling sequence,
 similar to our loading and imaging process~\cite{Hutzler2017-LightShifts},
@@
 Our final cooling results are shown in Fig.~\ref{f-radial} and \ref{f-axial}.
-In total, $1000$ cooling pulses (with a total duration of $100$ ms) are applied along three axes with
-cooling beginning on the radial second order.
+In total, $1000$ cooling pulses (with a total duration of $100$ ms) are applied
+along three axes with cooling beginning on the radial second order.
 To characterize the single atom thermal occupation before and after cooling,
@@
 
-% Define \eta_R
 % Lamb-Dicke parameter square explain
@@
 % heating from trap -> decrease of ground state procetage (maybe add temprature too)
-% Differetial AC starck shift **between excited states and ground states**?
 % at the same time, the atom is cooled via PGC instead of "the same imaging light is used to"
 % 1 sentence to explain why anisotropy?
-% is strobed at 3MHz instead of is switching at...
-% Cite Na loading paper in caption?
 % Make sure the caption for the before cooling axial rabi flopping mentions decoherence

### 2017-07-20 plot_rabi_flop.jl

@@ -242,7 +242,7 @@ const δΩ_r3_init = 15e3
 
 figure()
 ts_r3_0 = linspace(0, 80e-6, 256)
-plot_data(data_after_r3_0, 1, fmt="C0o")
+plot_data(data_after_r3_0, 1, fmt="C0s")
 plot_f1(f_r3, ts_r3_0, 2π / τ_r3 * meles_r3_0[1:3], p_r3, color="C0")
 ts_r3_0_init = linspace(0, 30e-6, 256)
 plot_data(data_before_r3_0, 1, fmt="C3o")
@@ -258,7 +258,7 @@ maybe_save("$(prefix)_r3_0")
 
 figure()
 ts_r3_p1 = linspace(0, 180e-6, 256)
-plot_data(data_after_r3_p1, 1, fmt="C0o")
+plot_data(data_after_r3_p1, 1, fmt="C0s")
 plot_f1(f_r3, ts_r3_p1, 2π / τ_r3 * meles_r3_p1[1:3], p_r3, color="C0")
 ts_r3_p1_init = linspace(0, 160e-6, 256)
 plot_data(data_before_r3_p1, 1, fmt="C3o")
@@ -283,7 +283,7 @@ const δΩ_r2_init = 15e3
 
 figure()
 ts_r2_0 = linspace(0, 80e-6, 256)
-plot_data(data_after_r2_0, 1, fmt="C0o")
+plot_data(data_after_r2_0, 1, fmt="C0s")
 plot_f1(f_r2, ts_r2_0, 2π / τ_r2 * meles_r2_0[1:3], p_r2, color="C0")
 ts_r2_0_init = linspace(0, 30e-6, 256)
 plot_data(data_before_r2_0, 1, fmt="C3o")
@@ -299,7 +299,7 @@ maybe_save("$(prefix)_r2_0")
 
 figure()
 ts_r2_p1 = linspace(0, 180e-6, 256)
-plot_data(data_after_r2_p1, 1, fmt="C0o")
+plot_data(data_after_r2_p1, 1, fmt="C0s")
 plot_f1(f_r2, ts_r2_p1, 2π / τ_r2 * meles_r2_p1[1:3], p_r2, color="C0")
 ts_r2_p1_init = linspace(0, 140e-6, 256)
 plot_data(data_before_r2_p1, 1, fmt="C3o")
@@ -326,7 +326,7 @@ const δΩ_a1_init_p1 = 50e3
 
[…]

### 2017-07-20 paper.tex
Implement all obvious suggestions from Lee and Jessie

@@
     the axial heating sideband where the Rabi frequency is the lowest.
+    The asymptotic values for the red lines are low also because of resonance fluctuation.
     \label{f-axial}}
@@
 create a focused beam with waist $0.7 \mu$m.
-With $45$ mW of tweezer power, the trapping frequencies are
-$\{\omega_1,\omega_2,\omega_3\}/2\pi = \{69(1), 430(4), 590(5)\}\ \text{\text{kHz}}$.
+With $45$ mW of tweezer power, the trapping frequencies along the three axes are
+$\{\omega_1,\omega_2,\omega_3\}/2\pi = \{69(1), 430(4), 590(5)\}\ \text{\text{kHz}}$
+where axis 1 is along the weakly confined axial direction and axis 2 and 3 are along the
+tightly confined radial directions.
 After attempting to load an atom from the MOT, an image is taken with $1.5$ ms exposure time to determine if it was a success.
-The same imaging light is used for polarization gradient cooling (PGC), which
-reduces the temperature of the single atom to $70$ $\mu$K,
+At the same time, the atom is cooled via polarization gradient cooling (PGC),
+which reduces the temperature of the single atom to $70$ $\mu$K,
 corresponding to an initial mean motional state along the three different axes of
@@
 It is important that the re-pumping step scatter as few photons as possible to minimize heating.
-Therefore, we use a $\sigma^-$-polarized laser resonant with the D1 line since the $|F=2, m_F=-2\rangle$ is a dark state in this case \fxnote{cite ion and K39}.
-Compared to using a D2 repump beam, from which the $|F=2, m_F=-2\rangle$ state could always scatter a photon via the excited $|F=3, m_F=-3\rangle$ state, we find a reduction in the scattering rate of a factor of $130(20)$.
+Therefore, we use a $\sigma^-$-polarized laser resonant with the D1 line
+since $|F=2, m_F=-2\rangle$ is a dark state in this case \fxnote{cite ion and K39}.
+Compared to using a D2 repump beam, from which the $|F=2, m_F=-2\rangle$ state
+could always scatter a photon via the excited $|F=3, m_F=-3\rangle$ state,
+we find a reduction in the scattering rate of a factor of $130(20)$.
 
@@
 observed cooling sidebands (8th- and 7th-orders)
-and decreasing the orders after $6$ to $15$ cycles.
+and decreasing the orders to the next pair after every $6$ to $15$ cycles.
 This process is repeated until we reach the first order cooling sideband, and most of the
@@
 and first-order heating(Fig. \ref{f-radial}C) sidebands
-to verify the ground state population~\cite{Meekhof1996}.
+to verify our assumption about the distribution and the ground state population~\cite{Meekhof1996}.
 The data is fitted using the same Monte-Carlo simulation we used to simulate the cooling
@@
 we have prepared a single Na atom with 3D ground state probability of $77(4)$\%.
-We measuring a heating rate of the single atoms in the tweezer to be $0.9$\%/s
-due to off-resonant scattering of the trapping light\cite{Grimm2000}.
+We measured a heating rate of the single atoms in the tweezer to be $67$nK/ms
+due to off-resonant scattering of the trapping light, which
+corresponds to $0.9$\%/ms decrease in ground state population\cite{Grimm2000}.
 The ground state preparation fidelity is currently limited by off-resonant scattering
@@
 % why not just molecules instead of polar molecules
-% entropy
-% use different line shape for rabi flopping
-% mention axis definitions
-% heating from trap -> decrease of ground state procetage (maybe add temprature too)
-% at the same time, the atom is cooled via PGC instead of "the same imaging light is used to"
+% use entropy to describe the effect of large \eta_{eff}
 % 1 sentence to explain why anisotropy?
-% Make sure the caption for the before cooling axial rabi flopping mentions decoherence
 % Mention after cooling is non-thermal?
-% Make it clear that we cool for 6-15 cycles each time before going to the next set of orders in axial
-
-% sm:
-% mention the simulation results are 3d
-% effect of changing groups.
-% mention effects that are included first.
 

### 2017-07-20 sm.tex
Implement all obvious suggestions from Lee and Jessie

@@
   This effect is negligible for Na in the ground state due to the small fine structure splitting in the excited state.
-  It is easy to include this effect if the calculation needs to be repeated on a system where
-  this is not the case (e.g. directly laser cooled molecules)
+  It is straightforward to include this effect if the calculation needs to be repeated
+  on a system where this is not the case (e.g. directly laser cooled molecules).
 \end{enumerate}
@@
   \includegraphics[width=8.5cm]{imgs/simcool_no_scatter.pdf}
-  \caption{Simulated ground state population as a function of cooling cycles without
+  \caption{Simulated 3D ground state population as a function of cooling cycles without
     technical imperfections. The ground state probability reaches $>99\%$. \label{f-no-scatter}}
@@
   \includegraphics[width=8.5cm]{imgs/simcool_real.pdf}
-  \caption{Simulated ground state population as a function of cooling cycles including effect of
+  \caption{Simulated 3D ground state population as a function of cooling cycles including effect of
     off-resonant scattering from all beams and OP misalignment.
@@
 If off-resonant scattering and optical pumping polarization misalignment are ignored,
-the simulation shows that there isn't a cooling limit
+the simulation shows that there is not a cooling limit
 despite the large Lamb-Dicke parameter and high initial temperature (Fig \ref{f-no-scatter}).
@@
 a lower value (Fig \ref{f-real}) and require much more careful tweaking.
+The change of slop in these plots corresponds to changing the sideband orders used for cooling.
 
@@
 
+% mention effects that are included first?
+
 \bibliography{paper}

### 2017-07-24 sm.tex
[sm] update email, include original mcwf paper

@@
 \author{Yichao Yu}
+\email{yichaoyu@g.harvard.edu}
 \author{Nicholas R. Hutzler}
@@
 and guide the optimization of Raman sideband cooling.
-The simulation uses the quantum jump (or Monte-Carlo wavefunction) method~\cite{Chretien2014}
+The simulation uses the quantum jump (or Monte-Carlo wavefunction) method~\cite{Dalibard1992,Chretien2014}
 to accurately calculate the evolution within each laser pulse where different energy eigenstates

### 2017-07-24 paper.tex
Add K39 reference, slightly clarify cutoff

@@
 Therefore, we use a $\sigma^-$-polarized laser resonant with the D1 line
-since $|F=2, m_F=-2\rangle$ is a dark state in this case \fxnote{cite ion and K39}.
+since $|F=2, m_F=-2\rangle$ is a dark state in this case~\cite{Grobner2017}\fxnote{cite ion}.
 Compared to using a D2 repump beam, from which the $|F=2, m_F=-2\rangle$ state
@@
 Instead, given the absence of the second order cooling sideband,
-we assume \fxnote{[What is the cutoff for the validity of this assumption, and are we below that cutoff?]} that the atoms are cold enough to have stronger coupling to the first order cooling
-sideband than the second order, in which case the lower bound of the ground state population
+we assume that the atoms are cold enough to have stronger coupling to the first order cooling
+sideband than the second order, i.e. below where the matrix element for the two orders cross,
+in which case the lower bound of the ground state population
 can be computed from the heights of the sidebands by assuming all of the excitations are in the

### 2017-07-25 sequence.tex
Start renaming axis

\documentclass[border=0pt]{standalone}
\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing,
  fadings
}
\tikzfading[name=fade img right,left color=transparent!100, right color=transparent!0]
\tikzfading[name=fade img left,right color=transparent!100, left color=transparent!0]
\usepackage{graphicx}
\begin{document}
\begin{tikzpicture}
  % 0.0 - 1.6 axial (1.6)
  % 1.6 - 1.9 OP (0.3)
  % 1.9 - 2.5 radial 2 (0.6)
  % 2.5 - 2.8 OP (0.3)
  % 2.8 - 4.4 axial (1.6)
  % 4.4 - 4.7 OP (0.3)
  % 4.7 - 5.3 radial 3 (0.6)
  % 5.3 - 5.6 OP (0.3)
  % 5.6 - 7.2 axial (1.6)
  % 7.2 - 7.5 OP (0.3)
  % 7.5 - 8.1 radial 2 (0.6)
  % 8.1 - 8.4 OP (0.3)
  % 8.4 - 10.0 axial (1.6)
  % 10.0 - 10.3 OP (0.3)
  % 10.3 - 10.9 radial 3 (0.6)
  % 10.9 - 11.2 OP (0.3)

  \begin{scope}
    \clip (4.6, -2.1) rectangle (17.8, 3.5);
    %% Pulse mark
    \foreach \i in {0,...,7} {
      \draw[gray!20, line width=2] (2.8*\i, 1.5) -- (2.8*\i, -2.0);
      \draw[gray!20, line width=2] (2.8*\i+1.9, 1.5) -- (2.8*\i+1.9, -2.0);
    }

    %% Tweezer
    \draw[line width=1.5,purple] (0, 2.4) -- (22.4, 2.4);
    \foreach \i in {0,...,99} {
      \filldraw[line width=1,purple] (\i*22.4/100, 2.4) rectangle (\i*22.4/100+0.06, 3.5);
    }

    %% Axial
    \foreach \i in {0,...,7} {
      \fill[blue!30]
      plot[draw,samples=200,domain={2.8*\i}:{2.8*\i+1.6},variable=\x] ({\x}, {sin((\x-2.8*\i) * 112.5)^4})
      -- cycle;
      \draw[line width=1,blue] plot[domain={2.8*\i}:{2.8*\i+1.6},variable=\x]
      ({\x}, {sin((\x-2.8*\i) * 112.5)^4}) -- (2.8*\i + 2.8, 0);
    }
    \path[blue] (2.8*2+0.8, 1) node[above,align=center] {\textit{Axial $z$}};
    \foreach \i in {0,...,3} {
      \path (5.6*\i + 0.8, -0.15) node[below,blue,align=center] {\textbf{$n$-th}\\\textbf{order}};
      \path (5.6*\i + 3.6, -0.15) node[below,blue,align=center] {\textbf{$(\!n-1\!)$-th}\\\textbf{order}};
    }

    %% Radial 2
    \foreach \i in {0,...,3} {
      \fill[red!30]
      plot[draw,samples=200,domain={5.6*\i+1.9}:{5.6*\i+2.5},variable=\x] ({\x}, {1.5*sin((\x-5.6*\i-1.9) * 300)^4})
      -- cycle;
      \draw[line width=1,red] (5.6*\i, 0) -- plot[domain={5.6*\i+1.9}:{5.6*\i+2.5},variable=\x]
      ({\x}, {1.5*sin((\x-5.6*\i-1.9) * 300)^4}) -- (5.6*\i+5.6, 0);
    }
    \path[red] (5.6*1+2.2, 1.5) node[above,align=center] {\textit{Radial $x$}};
    \path[red] (5.6*1+2.1, 0.05) node[below,align=center] {\textbf{pulse $1$}};
    \path[red] (5.6*2+2.1, 0.05) node[below,align=center] {\textbf{pulse $2$}};

    %% Radial 3
    \foreach \i in {0,...,3} {
      \fill[black!30]
      plot[draw,samples=200,domain={5.6*\i+4.7}:{5.6*\i+5.3},variable=\x] ({\x}, {1.5*sin((\x-5.6*\i-4.7) * 300)^4})
      -- cycle;
      \draw[line width=1,black] (5.6*\i, 0) -- plot[domain={5.6*\i+4.7}:{5.6*\i+5.3},variable=\x]
      ({\x}, {1.5*sin((\x-5.6*\i-4.7) * 300)^4}) -- (5.6*\i+5.6, 0);
    }
    \path[black] (5.6*1+5.0, 1.5) node[above,align=center] {\textit{Radial $y$}};
    \path[black] (5.6*1+5.2, 0.05) node[below,align=center] {\textbf{pulse $1$}};
    \path[black] (5.6*2+5.2, 0.05) node[below,align=center] {\textbf{pulse $2$}};

    %% OP
    \foreach \i in {0,...,7} {
      \filldraw[fill=orange!30,draw=orange,line width=1.2]
      (2.8*\i+1.58, -2) rectangle (2.8*\i+1.91, -1);
      \filldraw[fill=orange!30,draw=orange,line width=1.2]
      (2.8*\i+2.48, -2) rectangle (2.8*\i+2.81, -1);
    }
    \draw[line width=2,orange] (0,-2) -- (22.4,-2);
  \end{scope}

  \fill[white,path fading=fade img right] (16.8, -2.2) rectangle (17.81, 3.51);
  \fill[white,path fading=fade img right] (16.8, -2.2) rectangle (17.81, 3.51);
  \fill[white,path fading=fade img right] (16.8, -2.2) rectangle (17.81, 3.51);

  \fill[white,path fading=fade img left] (5.6, -2.2) rectangle (4.59, 3.51);
  \fill[white,path fading=fade img left] (5.6, -2.2) rectangle (4.59, 3.51);
  \fill[white,path fading=fade img left] (5.6, -2.2) rectangle (4.59, 3.51);

  \path (5.0, 2.3) node[left,purple,align=center] {\textbf{Tweezer}};
  \path (4.8, 0.5) node[left,align=center] {\textbf{Raman}};
  \path (5.15, -1.5) node[left,orange,align=center] {\textbf{Optical}\\\textbf{pumping}};
  \draw[line width=2,orange,->] (5.6,-2) -- (17.8,-2) node[right, below] {\scalebox{2}{$t$}};

  %% Cycle mark
  \draw[decoration={brace,mirror,raise=3pt, amplitude=10pt},decorate,line width=2]
  (5.6,-2) -- node[below=15pt] {\scalebox{1.5}{One cooling cycle}} (16.8,-2);

  %% Sub figure label
  \path (3.8,2.5) node[above=8pt] {\scalebox{1.2}{(C)}};
\end{tikzpicture}
\end{document}

### 2017-07-25 paper.tex
More axis renaming

@@
 With $45$ mW of tweezer power, the trapping frequencies along the three axes are
-$\{\omega_1,\omega_2,\omega_3\}/2\pi = \{69(1), 430(4), 590(5)\}\ \text{\text{kHz}}$
-where axis 1 is along the weakly confined axial direction and axis 2 and 3 are along the
+$\{\omega_x,\omega_y,\omega_z\}/2\pi = \{430(4), 590(5), 69(1)\}\ \text{\text{kHz}}$
+where axis z is along the weakly confined axial direction and axis x and y are along the
 tightly confined radial directions.
@@
 corresponding to an initial mean motional state along the three different axes of
-$\{\bar n_1, \bar n_2, \bar n_3\}=\{21(2),\, 3.4(2),\, 2.5(2)\}$, and therefore initial 3D ground state probability of $P_0=0.3$\%.
+$\{\bar n_x, \bar n_y, \bar n_z\}=\{3.4(2),\, 2.5(2),\, 21(2)\}$, and therefore initial 3D ground state probability of $P_0=0.3$\%.
 A beam with $\sigma^-$-polarization is used to initialize the atom into
@@
 is approximately proportional to the effective LD parameter
-$\eta^{OP}_{eff}=\sqrt{2n+1}\eta^{OP}$, where $\eta^{OP}=k z_0=k \sqrt{\hbar/2m\omega}$,
+$\eta^{\textrm{OP}}_{\textrm{eff}}=\sqrt{2n+1}\eta^{\textrm{OP}}$, where $\eta^{\textrm{OP}}=k z_0=k \sqrt{\hbar/2m\omega}$,
 $k$ is the wavenumber of the optical pumping beam, $z_0$ is the zero-point wavefunction spread,
@@
 For our trap frequencies and beam geometry,
-$\{\eta^{OP}_1,\eta^{OP}_2,\eta^{OP}_3\} = \{0.602(5), 0.241(2), 0.206(1)\}$.
+$\{\eta^{\textrm{OP}}_x,\eta^{\textrm{OP}}_y,\eta^{\textrm{OP}}_z\} = \{0.241(2), 0.206(1), 0.602(5)\}$.
 Combined with a relatively large PGC temperature gives initial
-$\{\eta^{OP}_{1\eff},\eta^{OP}_{2\eff},\eta^{OP}_{3\eff}\} = \{4.0(1), 0.67(2), 0.50(1)\}$.
-For the weak axial direction, $(\eta^{OP}_{1\eff})^2>1$ is far outside of the LD regime.
+$\{\eta^{\textrm{OP}}_{x,\textrm{eff}},\eta^{\textrm{OP}}_{y,\textrm{eff}},\eta^{\textrm{OP}}_{z,\textrm{eff}}\} = \{0.67(2), 0.50(1), 4.0(1)\}$.
+For the weak axial direction, $(\eta^{\textrm{OP}}_{z,\textrm{eff}})^2>1$ is far outside of the LD regime.
 As a result, the average change of motional state per OP step is large,
@@
 The Raman transitions in our configuration have LD parameters of
-$\{\eta^R_{1},\eta^R_{2},\eta^R_{3}\} = \{0.40(1), 0.341(2), 0.291(1)\}$,
+$\{\eta^R_x,\eta^R_y,\eta^R_z\} = \{0.341(2), 0.291(1), 0.40(1)\}$,
 which allow strong coupling to higher order sidebands for atoms in higher motional states
@@
 For the weaker axial direction, cooling is much more challenging
-due to the large $\eta^{OP}_{1eff}\approx 4.0(2)$.
+due to the large $\eta^{\textrm{OP}}_{z,\textrm{eff}}\approx 4.0(2)$.
 We observe up to 8th-order Raman cooling sidebands initially,
@@
 
-\fxnote{[The distinction between 77 and 66 percent is confusing, we should discuss it]}
+\fxnote{The distinction between 77 and 66 percent is confusing, we should discuss it}
 

### 2017-07-25 plot_spectrum.jl
Axis renaming

@@ -119,22 +119,22 @@ fig = figure(figsize=[1.6, 1] * 4.8)
 
 # Without cooling
 # Radial 2
-plot_data(data_nocool_r2[1], 1, fmt="C3^-", label="Ax 2 before")
+plot_data(data_nocool_r2[1], 1, fmt="C3^-", label="\$x\$ initial")
 plot_data(data_nocool_r2[2], 1, fmt="C3^-")
 plot_data(data_nocool_r2[3], 1, fmt="C3^-")
 # Radial 3
-plot_data(data_nocool_r3[1], 1, fmt="C3o--", label="Ax 3 before")
+plot_data(data_nocool_r3[1], 1, fmt="C3o--", label="\$y\$ initial")
 plot_data(data_nocool_r3[2], 1, fmt="C3o--")
 plot_data(data_nocool_r3[3], 1, fmt="C3o--")
 text(-660, 0.9, "(A)")
 
 # With cooling
 # Radial 2
-plot_data(data_cool_r2[1], 1, fmt="C0v-", label="Ax 2 after")
+plot_data(data_cool_r2[1], 1, fmt="C0v-", label="\$x\$ cooled")
 plot_data(data_cool_r2[2], 1, fmt="C0v-")
 plot_data(data_cool_r2[3], 1, fmt="C0v-")
 # Radial 3
-plot_data(data_cool_r3[1], 1, fmt="C0s--", label="Ax 3 after")
+plot_data(data_cool_r3[1], 1, fmt="C0s--", label="\$y\$ cooled")
 plot_data(data_cool_r3[2], 1, fmt="C0s--")
 plot_data(data_cool_r3[3], 1, fmt="C0s--")
 grid()
@@ -148,13 +148,13 @@ maybe_save("$(prefix)_r")
 
 fig = figure(figsize=[1.6, 1] * 4.8)
 # Without cooling
-plot_data(data_nocool_a1[1], 1, fmt="C3o-", label="Ax 1 before")
+plot_data(data_nocool_a1[1], 1, fmt="C3o-", label="\$z\$ initial")
 plot_data(data_nocool_a1[2], 1, fmt="C3o-")
 plot_data(data_nocool_a1_0, 1, fmt="C3o-")
 plot_data(data_nocool_a1_hi, 1, fmt="C3o-")
 
 # With cooling
-plot_data(data_cool_a1[1], 1, fmt="C0s-", label="Ax 1 after")
[…]

### 2017-07-25 paper.tex
Axis renaming
Overall survival line

@@
     second order cooling before and after Raman sideband cooling.
-    (B,C) Rabi flopping on axis 3 (B) carrier and (C) first order heating sideband
+    (B,C) Rabi flopping on axis $y$ (B) carrier and (C) first order heating sideband
     before (red) and after (blue) cooling.
@@
     the red lines correspond to a thermal distribution of $70$ $\mu$K before cooling.
+    The horizontal dashed line shows the overall survival after cooling and imaging.
     \label{f-radial}}
@@
     The asymptotic values for the red lines are low also because of resonance fluctuation.
+    Similar to the radial plot,
+    the horizontal dashed line shows the overall survival after cooling and imaging.
     \label{f-axial}}

### 2017-07-25 plot_rabi_flop.jl

@@ -248,6 +248,7 @@ ts_r3_0_init = linspace(0, 30e-6, 256)
 plot_data(data_before_r3_0, 1, fmt="C3o")
 plot_f1_thermal(f_r3, ts_r3_0_init, 2π / τ_r3_init * meles_r3_0, nbar_init_r3, δΩ_r3_init,
                 color="C3")
+axhline(0.85, c="C0", ls="-.")
 ylim([0, 1])
 xlim([ts_r3_0[1] * 1e6, ts_r3_0[end] * 1e6])
 xlabel("Time (\$\\mu s\$)")
@@ -263,6 +264,7 @@ plot_f1(f_r3, ts_r3_p1, 2π / τ_r3 * meles_r3_p1[1:3], p_r3, color="C0")
 ts_r3_p1_init = linspace(0, 160e-6, 256)
 plot_data(data_before_r3_p1, 1, fmt="C3o")
 plot_f1_thermal(f_r3, ts_r3_p1_init, 2π / τ_r3_init * meles_r3_p1, nbar_init_r3, δΩ_r3_init, color="C3")
+axhline(0.85, c="C0", ls="-.")
 ylim([0, 1])
 xlim([ts_r3_p1[1] * 1e6, ts_r3_p1[end] * 1e6])
 xlabel("Time (\$\\mu s\$)")
@@ -289,6 +291,7 @@ ts_r2_0_init = linspace(0, 30e-6, 256)
 plot_data(data_before_r2_0, 1, fmt="C3o")
 plot_f1_thermal(f_r2, ts_r2_0_init, 2π / τ_r2_init * meles_r2_0, nbar_init_r2,
                 δΩ_r2_init, color="C3")
+axhline(0.85, c="C0", ls="-.")
 ylim([0, 1])
 xlim([ts_r2_0[1] * 1e6, ts_r2_0[end] * 1e6])
 xlabel("Time (\$\\mu s\$)")
@@ -305,6 +308,7 @@ ts_r2_p1_init = linspace(0, 140e-6, 256)
 plot_data(data_before_r2_p1, 1, fmt="C3o")
 plot_f1_thermal(f_r2, ts_r2_p1_init, 2π / τ_r2_init * meles_r2_p1, nbar_init_r2,
                 δΩ_r2_init, color="C3")
+axhline(0.85, c="C0", ls="-.")
 ylim([0, 1])
[…]

### 2017-07-25 plot_raman_op.jl

@@ -161,9 +161,10 @@ ylim([0, 0.9])
 xlim([0, nmax])
 ylabel("Probability")
 setp(ax1[:get_xticklabels](), visible=false)
+ax1[:tick_params](axis="x", length=0)
 
 ax2 = subplot(212)
-subplots_adjust(hspace=0)
+subplots_adjust(hspace=0.08)
 plot_sidebands(0:nmax, -1:-1:-5, η_ax)
 xlim([0, nmax])
 ylim([0, 0.75])

### 2017-07-26 paper.tex
Jon's comments

@@
   Our technique includes addressing very high-order sidebands and
-  fast modulation of the optical tweezer trap.
-  We demonstrate that Raman sideband cooling to the 3D motional ground state is applicable
+  fast modulation of the optical tweezer.
+  We demonstrate that Raman sideband cooling to the 3D motional ground state is possible
   outside the Lamb-Dicke regime, for example in
@@
 atoms~\cite{Li2012,Kaufman2012,Thompson2013,Liu2017,Robens2017} enables
-efficient coupling of single atoms to photonic crystal cavities~\cite{Thompson2013a},
+studies of the atomic Hong-Ou-Mandel effect~\cite{Kaufman2014},
 high-fidelity single qubit gates~\cite{Wang2016},
-and studies of the atomic Hong-Ou-Mandel effect~\cite{Kaufman2014}.
+and efficient coupling of single atoms to photonic crystal cavities~\cite{Thompson2013a}.
 
@@
 new applications that exploit their many long-lived internal states
-and highly tunable interactions~\cite{DeMille2002,Ni2008,Gorshkov2011,Yan2013}.
+and highly tunable long range interactions~\cite{DeMille2002,Ni2008,Gorshkov2011,Yan2013}.
 Molecules could be assembled from atom pairs in the optical tweezer~\cite{Liu2017},
@@
 However, RSC in these systems has been applied in the Lamb-Dicke (LD) regime, where
-the size of the atomic wavefunction is much smaller than the wavelength of light used to address them.
-Extending ground state cooling to systems outside the LD regime, such as light atoms or polar molecules, is challenging.
-In this letter we demonstrate cooling of single sodium atoms in optical tweezers, initially outside of the LD regime, to the motional ground state.
+the size of the wavefunction is much smaller than the wavelength of light used to address them.
+Systems with a large wavefunction size, either due to small mass or high initial temperature,
+fall outside of the LD regieme and result in strong heating during RSC.
+Extending RSC outside of the LD regime opens up the possibility
+for ground state cooling of light atoms or systems with poor cooling such as polar molecules.
+In this letter we demonstrate cooling of single sodium atoms in an optical tweezer,
+initially outside of the LD regime, to the motional ground state.
 We achieve a ground state probability of $P_0=77(4)$\% by utilizing cooling of
@@
 
-Our experiment begins by loading a single sodium atom into an optical tweezer from a MOT
-for $250$ ms~\cite{Hutzler2017-LightShifts}, and has an overall repetition rate of $2.5$ Hz.
-The tweezer is created by focusing a $700$ nm laser beam through an NA=$0.55$ objective to
-create a focused beam with waist $0.7 \mu$m.
+Our experiment has an overall repetition rate of $2.5$ Hz and
+begins by loading a single sodium atom into an optical tweezer from a MOT
+for $250$ ms~\cite{Hutzler2017-LightShifts}.
+The tweezer is created by sending a $700$ nm laser beam through an NA=$0.55$ objective to
+focus the light down to a waist of $0.7 \mu$m.
 With $45$ mW of tweezer power, the trapping frequencies along the three axes are
-$\{\omega_x,\omega_y,\omega_z\}/2\pi = \{430(4), 590(5), 69(1)\}\ \text{\text{kHz}}$
-where axis z is along the weakly confined axial direction and axis x and y are along the
-tightly confined radial directions.
-After attempting to load an atom from the MOT, an image is taken with $1.5$ ms exposure time to determine if it was a success.
-At the same time, the atom is cooled via polarization gradient cooling (PGC),
+$\{\omega_x,\omega_y,\omega_z\}/2\pi = \{430(4), 590(5), 69(1)\}\ \text{\text{kHz}}$,
+where axis z is along the weakly confined axial direction,
+and axis x and y are along the tightly confined radial directions.
+After attempting to load an atom from the MOT, an image is taken with a $1.5$ ms exposure time
+to determine if it was a success.
+During the imaging, the atom is cooled via polarization gradient cooling (PGC),
 which reduces the temperature of the single atom to $70$ $\mu$K,
@@
 $\{\bar n_x, \bar n_y, \bar n_z\}=\{3.4(2),\, 2.5(2),\, 21(2)\}$, and therefore initial 3D ground state probability of $P_0=0.3$\%.
-A beam with $\sigma^-$-polarization is used to initialize the atom into
+Light with $\sigma^-$-polarization is used to initialize the atom into
 the $|F=2, m_F=-2\rangle$ stretched state via optical pumping.
@@
 Specifically, Raman transitions are driven in Na between the hyperfine states
-$|F=2, m_F=-2\rangle$ and $|F=1, m_F=-1\rangle$ in the presence of a $8.8$ G magnetic field to suppress vector light shifts~\cite{Kaufman2012,Thompson2013}.
+$|F=2, m_F=-2\rangle$ and $|F=1, m_F=-1\rangle$ in the presence of a $8.8$ G magnetic field
+orthogonal to the effective magnetic field from the tweezer
+in order to suppress the vector light shifts~\cite{Kaufman2012,Thompson2013}.
 Subsequently, an OP/repump pulse brings the atom back to $|F=2, m_F=-2\rangle$
@@
 since $|F=2, m_F=-2\rangle$ is a dark state in this case~\cite{Grobner2017}\fxnote{cite ion}.
-Compared to using a D2 repump beam, from which the $|F=2, m_F=-2\rangle$ state
-could always scatter a photon via the excited $|F=3, m_F=-3\rangle$ state,
-we find a reduction in the scattering rate of a factor of $130(20)$.
+We find a reduction in the scattering rate by a factor of $130(20)$,
+as compared to using a D2 repump, from which the $|F=2, m_F=-2\rangle$ state
+could always scatter a photon via the excited $|F=3, m_F=-3\rangle$ state.
 
-For an atom in motional level $n$, the OP could result in motional-state redistribution
-as shown in Fig.~\ref{f-ld}A. The state redistribution probability
-is approximately proportional to the effective LD parameter
-$\eta^{\textrm{OP}}_{\textrm{eff}}=\sqrt{2n+1}\eta^{\textrm{OP}}$, where $\eta^{\textrm{OP}}=k z_0=k \sqrt{\hbar/2m\omega}$,
-$k$ is the wavenumber of the optical pumping beam, $z_0$ is the zero-point wavefunction spread,
-$m$ is the mass of the atom, and $\hbar$ is the reduced Planck constant.
+For an atomm starting in motional level $n_{\textrm{init}}$ the OP sequence results in
+a motional-state redistribution, as shown in Fig.~\ref{f-ld}A.
+The state redistribution probability is approximately proportional to the effective LD parameter
+$\eta^{\textrm{OP}}_{\textrm{eff}}=\sqrt{2n+1}\eta^{\textrm{OP}}$,
+where the optical pumping LD parameter $\eta^{\textrm{OP}} = kz_0$ is the wavenumber $k$
+multiplied by the zero-point wavefunction spread $z_0 = \sqrt{\hbar/2m\omega}$.
+Here, $m$ is the mass of the atom, $\omega$ is the trap frequency,
+and $\hbar$ is the reduced Planck constant.
 Such heating presents a major challenge for efficient cooling of single Na atoms
 which feature a light mass and short D-line wavelengths.
-For our trap frequencies and beam geometry,
+For our trap frequencies and beam geometry, the LD parameters are
 $\{\eta^{\textrm{OP}}_x,\eta^{\textrm{OP}}_y,\eta^{\textrm{OP}}_z\} = \{0.241(2), 0.206(1), 0.602(5)\}$.
-Combined with a relatively large PGC temperature gives initial
+The relatively large PGC temperature results in initial effective LD parameters of
 $\{\eta^{\textrm{OP}}_{x,\textrm{eff}},\eta^{\textrm{OP}}_{y,\textrm{eff}},\eta^{\textrm{OP}}_{z,\textrm{eff}}\} = \{0.67(2), 0.50(1), 4.0(1)\}$.
@@
 which creates a large uncertainty on the motional state at the end of a full RSC step, possibly leading to runaway heating.
-For example, the average change in motional states over the initial distribution
+For example, the average change in the motional states for the initial distribution
 is $2.4$ in the axial direction, which is significantly greater than $0.89-0.95$
@@
 Fortunately, the large LD parameters also provide opportunities to overcome OP heating.
+The LD parameter for Raman transitions is defined as $\eta^R\equiv\Delta k z_0$,
+where the wave vector is replaced by the wave vector difference $\Delta k$
+between the two beams that drive the Raman transition.
 The Raman transitions in our configuration have LD parameters of
@@
 as calculated in Figure~\ref{f-ld}B.
-The LD parameter for Raman transitions is defined as $\eta^R\equiv\Delta k z_0$ similar to OP
-where $\Delta k$ being the wave vector difference
-between the two beams that drives the Raman transition.
 To offset heating from OP initially, higher-order Raman cooling sidebands can be utilized
@@
 
-Taking the large motional-state changing heating and cooling sources into account,
+Taking the large motional-state changing heating and cooling sources
+during optical pumping into account,
 it is not immediately clear that efficient cooling can be achieved.
-We therefore use a Monte-Carlo simulation to guide our search and
-to find a robust cooling sequence\footnote{See supplemental material}.
-In the simulation, we indeed observe a high heating rate due to the large LD parameters
-and confirm that cooling with higher-order Raman sidebands can suppress heating.
+We use a Monte-Carlo simulation to guide our search and
+to find a robust cooling sequence~\footnote{See supplemental material}.
+In the simulation, we indeed observe a high heating rate due to the large LD parameters,
+and we confirm that the heating can be supressed by cooling with higher order Raman sidebands.
 In particular, we find that instead of cooling on only one sideband order repeatedly,
@@
 Rabi frequency of at least $15$ kHz is needed to couple to $99$\% population up to $n=15$.
-Second, the tweezer trap causes a large AC Stark shift (as large as $300$ MHz)
+Second, the tweezer causes a large AC Stark shift (as large as $300$ MHz)
 in the excited state. This creates a large, position-dependent OP detuning

### 2017-07-26 plot_raman_op.jl

@@ -162,6 +162,7 @@ xlim([0, nmax])
 ylabel("Probability")
 setp(ax1[:get_xticklabels](), visible=false)
 ax1[:tick_params](axis="x", length=0)
+ax1[:get_yaxis]()[:set_label_coords](-0.105, 0.5)
 
 ax2 = subplot(212)
 subplots_adjust(hspace=0.08)
@@ -176,7 +177,8 @@ text(21, 0.47, "\$\\Delta n\\!\\!=\\!\\!3\$", color="C2")
 text(36, 0.44, "\$\\Delta n\\!\\!=\\!4\$", color="C3")
 text(53, 0.42, "\$\\Delta n\\!\\!=\\!5\$", color="C4")
 text(60, 0.632, "(B)")
-xlabel("Motional state")
+ax2[:get_yaxis]()[:set_label_coords](-0.105, 0.5)
+xlabel("Motional state \$n\$")
 
 maybe_save(joinpath(@__DIR__, "imgs/fig2_raman_op"))
 

### 2017-08-01 CoolingSequence.m
Include code in SM, update schematic

@@ -1,0 +1,129 @@
+%% Raman Cooling
+state = NaRamanState(s);
+% The following Pulsed cooling no-op
+state.PulseOPF1 = 0.32;
+state.TPulseOP = 40e-6;
+
+% NaPulsedCool(T, Det, F1Vert, F2Counter, RamanF1, RamanF2, OPF2)
+% NCoolCycles = 20;
+NaAxial0 = -18.506e6;
+NaAxialF = 67.5e3;
+
+NaAxial8 = NaAxial0 + NaAxialF * 8;
+NaAxial7 = NaAxial0 + NaAxialF * 7;
+NaAxial6 = NaAxial0 + NaAxialF * 6;
+NaAxial5 = NaAxial0 + NaAxialF * 5;
+NaAxial4 = NaAxial0 + NaAxialF * 4;
+NaAxial3 = NaAxial0 + NaAxialF * 3;
+NaAxial2 = NaAxial0 + NaAxialF * 2;
+NaAxial1 = NaAxial0 + NaAxialF;
+NaAxial1_2 = NaAxial0 + 77e3;
+
+NaCools1 = {NaPulsedCool(25e-6, -17.6375e6, 1, 1, 0.0, 0.05, 0.21, 1.0, 0.0), ...
+            NaPulsedCool(25e-6, -18.03e6, 1, 1, 0.0, 0.05, 0.23, 1.0, 0.0), ...
+            NaPulsedCool(25e-6, -17.2825e6, 0, 1, 0.0, 0.05, 0.21, 0.22, 0.0), ...
+            NaPulsedCool(21e-6, -17.875e6, 0, 1, 0.0, 0.05, 0.23, 0.22, 0.0)};
+NaCools1 = repmat(NaCools1, 1, 5);
+% Axial 8+7, Radial2 2+1, Radial3 2+1
+NaCools2 = {NaPulsedCool(80e-6, NaAxial8, 1, 0, 0.4, 0.14, 0.21), ...
+            NaPulsedCool(80e-6, NaAxial7, 1, 0, 0.4, 0.14, 0.21), ...
+            NaPulsedCool(25e-6, -17.6375e6, 1, 1, 0.0, 0.05, 0.21, 1.0, 0.0), ...
+            NaPulsedCool(25e-6, -18.03e6, 1, 1, 0.0, 0.05, 0.21, 1.0, 0.0), ...
+            NaPulsedCool(80e-6, NaAxial8, 1, 0, 0.4, 0.14, 0.21), ...
[…]

### 2017-08-01 calc_trap_waist.jl
Script to calculate trap waists

@@ -1,0 +1,12 @@
+#
+
+
+k_B = 1.38064852e-23
+I0 = k_B * 3e-3
+m_Na = 23e-3 / 6.02e23
+ω2 = 420e3 * 2π
+ω3 = 580e3 * 2π
+w2 = sqrt(4 * I0 / m_Na / ω2^2)
+w3 = sqrt(4 * I0 / m_Na / ω3^2)
+@show w2 * 1e6
+@show w3 * 1e6

### 2017-08-01 calc_ground.jl
Naive way to calculate ground state probability

@@ -1,0 +1,29 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
+import NaCsCalc.Format: Unc
+
+const a1m1 = [0.0410, 0.0182]
+const a1p1 = [0.476, 0.411]
+
+const r2m1 = [0.0656, 0.0366]
+const r2p1 = [0.656, 0.593]
+
+const r3m1 = [0.0310, 0.0121]
+const r3p1 = [0.459, 0.395]
+
+function naive_ground(m1, p1)
+    avg_m1 = (m1[1] + m1[2]) / 2
+    std_m1 = abs(m1[1] - m1[2]) / 2
+    avg_p1 = (p1[1] + p1[2]) / 2
+    std_p1 = abs(p1[1] - p1[2]) / 2
+
+    avg_r = avg_m1 / avg_p1
+    std_r = avg_r * sqrt((std_p1 / avg_p1)^2 + (std_m1 / avg_m1)^2)
+
+    return Unc(1 - avg_r, std_r)
+end
+
+@show naive_ground(a1m1, a1p1)
+@show naive_ground(r2m1, r2p1)
+@show naive_ground(r3m1, r3p1)

### 2017-08-01 calc_trap_waist.jl

@@ -1,5 +1,4 @@
-#
-
+#!/usr/bin/julia
 
 k_B = 1.38064852e-23
 I0 = k_B * 3e-3

### 2017-08-02 calc_ground.jl
Include before cooling and better printing

@@ -12,6 +12,15 @@ const r2p1 = [0.656, 0.593]
 const r3m1 = [0.0310, 0.0121]
 const r3p1 = [0.459, 0.395]
 
+const a1m10 = [0.419, 0.317]
+const a1p10 = [0.497, 0.396]
+
+const r2m10 = [0.599, 0.500]
+const r2p10 = [0.820, 0.740]
+
+const r3m10 = [0.455, 0.355]
+const r3p10 = [0.664, 0.574]
+
 function naive_ground(m1, p1)
     avg_m1 = (m1[1] + m1[2]) / 2
     std_m1 = abs(m1[1] - m1[2]) / 2
@@ -21,9 +30,26 @@ function naive_ground(m1, p1)
     avg_r = avg_m1 / avg_p1
     std_r = avg_r * sqrt((std_p1 / avg_p1)^2 + (std_m1 / avg_m1)^2)
 
-    return Unc(1 - avg_r, std_r)
+    avg_g = 1 - avg_r
+    std_g = std_r
+
+    avg_n = 1 / avg_g - 1
+    std_n = std_g / avg_g^2
+
+    return Unc(avg_g, std_g), Unc(avg_n, std_n)
 end
 
-@show naive_ground(a1m1, a1p1)
-@show naive_ground(r2m1, r2p1)
-@show naive_ground(r3m1, r3p1)
+function show_ground(m1, p1, name)
+    println(name)
+    g, n = naive_ground(m1, p1)
+    println("  P_0: ", g)
+    println("  nbar: ", n)
+end
+
+show_ground(a1m1, a1p1, "Axial (z) cooled")
+show_ground(r2m1, r2p1, "Radial (x) cooled")
+show_ground(r3m1, r3p1, "Radial (y) cooled")
+
+show_ground(a1m10, a1p10, "Axial (z) initial")
+show_ground(r2m10, r2p10, "Radial (x) initial")
+show_ground(r3m10, r3p10, "Radial (y) initial")

### 2017-08-03 sequence.tex
Figure tweaks

@@
     \foreach \i in {0,...,3} {
-      \path (5.6*\i + 0.8, -0.15) node[below,blue,align=center] {\textbf{$n$-th}\\\textbf{order}};
-      \path (5.6*\i + 3.6, -0.15) node[below,blue,align=center] {\textbf{$(\!n-1\!)$-th}\\\textbf{order}};
+      \path (5.6*\i + 0.8, -0.15) node[below,blue,align=center] {\textbf{$m$-th}\\\textbf{order}};
+      \path (5.6*\i + 3.6, -0.15) node[below,blue,align=center] {\textbf{$(\!m-1\!)$-th}\\\textbf{order}};
     }

### 2017-08-03 plot_raman_op.jl

@@ -170,12 +170,12 @@ plot_sidebands(0:nmax, -1:-1:-5, η_ax)
 xlim([0, nmax])
 ylim([0, 0.75])
 grid()
-ylabel("\$|\\langle n |e^{ikr}| n - \\Delta n \\rangle|\$")
-text(0, 0.65, "\$\\Delta n\\!\\!=\\!\\!1\$", color="C0")
-text(9, 0.55, "\$\\Delta n\\!\\!=\\!\\!2\$", color="C1")
-text(21, 0.47, "\$\\Delta n\\!\\!=\\!\\!3\$", color="C2")
-text(36, 0.44, "\$\\Delta n\\!\\!=\\!4\$", color="C3")
-text(53, 0.42, "\$\\Delta n\\!\\!=\\!5\$", color="C4")
+ylabel("\$|\\langle n |e^{ikr}| n + \\Delta n \\rangle|\$")
+text(0, 0.65, "\$\\Delta n\\!\\!=\\!\\!\\!-\\!1\$", color="C0")
+text(9, 0.55, "\$\\Delta n\\!\\!=\\!\\!\\!-\\!2\$", color="C1")
+text(21, 0.47, "\$\\Delta n\\!\\!=\\!\\!\\!-\\!3\$", color="C2")
+text(36, 0.44, "\$\\Delta n\\!\\!=\\!\\!\\!-\\!4\$", color="C3")
+text(53, 0.42, "\$\\Delta n\\!\\!=\\!\\!\\!-\\!5\$", color="C4")
 text(60, 0.632, "(B)")
 ax2[:get_yaxis]()[:set_label_coords](-0.105, 0.5)
 xlabel("Motional state \$n\$")

### 2017-08-08 plot_spectrum.jl
Figure update

@@ -141,7 +141,7 @@ grid()
 ylim([0, 1])
 xlim([-700, 1500])
 legend()
-xlabel("Detuning from carrier (kHz)")
+xlabel("\$\\delta\$, Detuning from carrier (kHz)")
 ylabel("Survival")
 
 maybe_save("$(prefix)_r")
@@ -162,7 +162,7 @@ ylim([0, 0.6])
 xlim([-100, 620])
 legend()
 text(-86, 0.54, "(A)")
-xlabel("Detuning from carrier (kHz)")
+xlabel("\$\\delta\$, Detuning from carrier (kHz)")
 ylabel("Survival")
 maybe_save("$(prefix)_a1")
 

### 2017-08-09 geometry.tex
Try drawing the tweezer

\documentclass[border=0pt]{standalone}
\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing,
  arrows,
  calc,
  decorations.pathmorphing,
  decorations.pathreplacing,
  decorations.markings,
  fadings,
  positioning,
  shapes,
  3d
}
\tikzfading[name=fade img right,left color=transparent!100, right color=transparent!0]
\tikzfading[name=fade img left,right color=transparent!100, left color=transparent!0]
\tikzstyle{snakearrow} = [decorate, decoration={pre length=0.1cm,
  post length=0.1cm, snake, amplitude=.4mm,
  segment length=4mm},thick, ->]
\usepackage{graphicx}
\begin{document}
\newcommand*{\arrowthreeD}[5]{%
  \fill[left color=#1!50!black,right color=#1!50!black,middle color=#1!43,
  shift = {#2},
  opacity=0.9,
  rotate=#3,shading=axis,shading angle=90+#3]
  (0,0) -- (83:#4) arc (83:97:#4) -- cycle;
  \fill[left color=#1!50!black,right color=#1!50!black,middle color=#1!43,
  shift = {#2},
  opacity=0.9,
  rotate=#3,shading=axis,shading angle=90+#3]
  (87:#4) -- ++(0, #5) -- ++(-{2 * #4 * sin(3)}, 0) -- (93:#4) -- cycle;
}
\begin{tikzpicture}
  \pgfmathsetmacro{\radiush}{0.8}
  \pgfmathsetmacro{\theight}{2}
  \pgfmathsetmacro{\radiusv}{.7 * \radiush}
  \pgfmathsetmacro{\waist}{.15}
  \pgfmathsetmacro{\xscale}{\radiush / sqrt(1 + (\waist)^2)}

  \fill[left color=red!50!black,right color=red!50!black,middle color=red!43,
  shading=axis,rotate=-50,shading angle=32]
  plot[domain={-1}:{1}, smooth, variable=\y] ({sqrt((\y)^2 + (\waist)^2) * \xscale}, \y * \theight)
  arc (0:180:\radiush cm and \radiusv cm)
  -- plot[domain={-1}:{1}, smooth, variable=\y] ({-sqrt((\y)^2 + (\waist)^2) * \xscale}, -\y * \theight)
  arc (180:360:\radiush cm and \radiusv cm);

  \arrowthreeD{orange}{(0.3, 0)}{-90}{0.3}{1.2};

  \def\tiltratio{0.4}
  \fill[blue!50!black,opacity=0.15] (-1.4, 1.2 + \tiltratio) -- (1.4, 1.2 - \tiltratio)
  -- (1.4, -1.2 - \tiltratio) -- (-1.4, -1.2 + \tiltratio) -- cycle;
  \draw[blue!50!black, densely dotted] (-1.4, 1.2 + \tiltratio) -- (1.4, 1.2 - \tiltratio)
  -- (1.4, -1.2 - \tiltratio) -- (-1.4, -1.2 + \tiltratio) -- cycle;

  \arrowthreeD{red}{(0, -0.2)}{180}{0.3}{0.55};
  \arrowthreeD{orange}{(-0.2, 0.2 * \tiltratio / 1.4)}{90-16}{0.3}{0.7};

  \fill[left color=red!50!black,right color=red!50!black,middle color=red!43,
  shading=axis,rotate=-50,shading angle=40]
  plot[domain={-1}:{0}, smooth, variable=\y] ({sqrt((\y)^2 + (\waist)^2) * \xscale}, \y * \theight)
  arc (0:180:{(\radiush)*(\waist)} and {(\radiusv)*(\waist)})
  -- plot[domain={0}:{1}, smooth, variable=\y] ({-sqrt((\y)^2 + (\waist)^2) * \xscale}, -\y * \theight)
  arc (180:360:\radiush cm and \radiusv cm);
  \fill[red!50!gray,rotate=-50]
  ({-sqrt(1 + (\waist)^2) * \xscale}, -\theight*1.05)
  arc (180:{360+180}:\radiush cm and \radiusv cm);

  \arrowthreeD{blue}{(0.2, -0.2 * \tiltratio / 1.4)}{-90-16}{0.3}{0.7};
  \arrowthreeD{red}{(0, 0.2)}{0}{0.3}{0.55};
\end{tikzpicture}

\end{document}

### 2017-08-09 geometry.tex
Correct transformation of shade
Tweak geometry again...

@@
   rotate=#3,shading=axis,shading angle=90+#3]
-  (0,0) -- (83:#4) arc (83:97:#4) -- cycle;
+  (0,0) -- (80:#4) arc (80:100:#4) -- cycle;
   \fill[left color=#1!50!black,right color=#1!50!black,middle color=#1!43,
@@
 \begin{tikzpicture}
-  \pgfmathsetmacro{\radiush}{0.8}
-  \pgfmathsetmacro{\theight}{2}
+  \pgfmathsetmacro{\radiush}{1.6}
+  \pgfmathsetmacro{\theight}{4}
   \pgfmathsetmacro{\radiusv}{.7 * \radiush}
@@
 
-  \arrowthreeD{orange}{(0.3, 0)}{-90}{0.3}{1.2};
+  \arrowthreeD{orange}{(0.6, 0)}{-90}{0.4}{3.2};
+  \path (3.4, 0) node[above,orange!80!black] {Raman F2};
+  \path (3, 0) node[below,orange!80!black] {\textbf{R3}};
 
-  \def\tiltratio{0.4}
-  \fill[blue!50!black,opacity=0.15] (-1.4, 1.2 + \tiltratio) -- (1.4, 1.2 - \tiltratio)
-  -- (1.4, -1.2 - \tiltratio) -- (-1.4, -1.2 + \tiltratio) -- cycle;
-  \draw[blue!50!black, densely dotted] (-1.4, 1.2 + \tiltratio) -- (1.4, 1.2 - \tiltratio)
-  -- (1.4, -1.2 - \tiltratio) -- (-1.4, -1.2 + \tiltratio) -- cycle;
+  \draw[orange!50!black, <->, densely dotted, >=stealth, line width=0.8]
+  (-1:3.4) arc (-2:-29:3.4 and 1.65);
+  \path (-10:3.3) node[orange!50!black, right] {$42^\circ$};
 
-  \arrowthreeD{red}{(0, -0.2)}{180}{0.3}{0.55};
-  \arrowthreeD{orange}{(-0.2, 0.2 * \tiltratio / 1.4)}{90-16}{0.3}{0.7};
+  \begin{scope}[transform canvas={cm={1,-0.28,0,1,(0, 0)}}]
+    \draw[blue, dotted, line width=0.5] (-4.0, 0) -- (4.0, 0);
+
+    \fill[blue!50!black,opacity=0.1] (-2.5, 2.7) -- (2.5, 2.7)
+    -- (2.5, -2.7) -- (-2.5, -2.7) -- cycle;
+    \draw[blue!50!black, densely dotted,line width=0.6] (-2.5, 2.7) -- (2.5, 2.7)
+    -- (2.5, -2.7) -- (-2.5, -2.7) -- cycle;
+    \arrowthreeD{red}{(0, -0.4)}{180}{0.4}{1.4};
+    \arrowthreeD{orange}{(-0.4, 0)}{90}{0.4}{1.4};
+    \arrowthreeD{blue}{(0.4, 0)}{-90}{0.4}{1.4};
+    \arrowthreeD{red}{(0, 0.4)}{0}{0.4}{1.4};
+    \path (1.6, 0) node[below,blue!80!black] {OP};
+    \path (-1.6, 0) node[above,orange!80!black] {Raman F2};
+    \path (-1.6, 0) node[below,orange!80!black] {\textbf{R1}};
+
+    \path (0, 1.7) node[left,red!80!black] {Raman F1};
+    \path (0, 1.7) node[right,red!80!black] {\textbf{R2}};
+
+    \path (0, -1.7) node[left,red!80!black] {\textbf{R4}};
+    \path (0, -1.7) node[right,red!80!black] {Raman F1};
+
+    \draw[white,opacity=0.5,->,>=stealth,line width=1.5] (2.21, 2.39) -- (0.81, 2.39);
+    \draw[->,>=stealth,line width=1.5] (2.2, 2.4) -- (0.8, 2.4);
+    \path (1.51, 2.39) node[below,white,opacity=0.5] {B field};
+    \path (1.5, 2.4) node[below] {B field};
+  \end{scope}
 
@@
 
-  \arrowthreeD{blue}{(0.2, -0.2 * \tiltratio / 1.4)}{-90-16}{0.3}{0.7};
-  \arrowthreeD{red}{(0, 0.2)}{0}{0.3}{0.55};
+  \path (-140:\theight) node[white] {\textbf{Tweezer}};
 \end{tikzpicture}

### 2017-08-09 geometry.tex
Fix arrow transformation

@@
   \fill[left color=#1!50!black,right color=#1!50!black,middle color=#1!43,
-  shift = {#2},
   opacity=0.9,
-  rotate=#3,shading=axis,shading angle=90+#3]
+  transform canvas={shift={#2}, rotate=#3},shading=axis,shading angle=90]
   (0,0) -- (80:#4) arc (80:100:#4) -- cycle;
   \fill[left color=#1!50!black,right color=#1!50!black,middle color=#1!43,
-  shift = {#2},
   opacity=0.9,
-  rotate=#3,shading=axis,shading angle=90+#3]
+  transform canvas={shift={#2}, rotate=#3},shading=axis,shading angle=90]
   (87:#4) -- ++(0, #5) -- ++(-{2 * #4 * sin(3)}, 0) -- (93:#4) -- cycle;
@@
 \begin{tikzpicture}
-  \pgfmathsetmacro{\radiush}{1.6}
+  \pgfmathsetmacro{\radiush}{1.5}
   \pgfmathsetmacro{\theight}{4}
@@
 
+  \begin{scope}[transform canvas={rotate={4}}]
     \arrowthreeD{orange}{(0.6, 0)}{-90}{0.4}{3.2};
@@
     \path (3, 0) node[below,orange!80!black] {\textbf{R3}};
+  \end{scope}
 
   \draw[orange!50!black, <->, densely dotted, >=stealth, line width=0.8]
-  (-1:3.4) arc (-2:-29:3.4 and 1.65);
-  \path (-10:3.3) node[orange!50!black, right] {$42^\circ$};
+  (3:3.4) arc (3:-32:3.4 and 1.65);
+  \path (-6:3.3) node[orange!50!black, right] {$42^\circ$};
 

### 2017-08-09 sm.tex
Include code in SM, update schematic
WIP: pulse sequence
Pulse sequence description in SM

@@
-\documentclass[aps,twocolumn,secnumarabic,amsmath,amssymb]{revtex4}
+\documentclass[aps,secnumarabic,amsmath,amssymb]{revtex4}
 \usepackage{amsmath}
@@
 \usepackage[colorlinks=true]{hyperref}
+\usepackage{listings}
 
@@
 
-% mention effects that are included first?
+\section{Cooling sequence}
+
+\subsection{Optical pumping parameters}
+All optical pumping pulses has the same length of $40\mu$s
+with a $|F=1,m_F=-1\rangle$ scattering rate of $0.14$ MHz
+and a $|F=2,m_F=-1\rangle$ scattering rate of $0.39$ MHz.
+
+\subsection{Raman pulse parameters}
+Each of the Raman pulse in the cooling sequence is followed immediately by an optical pumping
+pulse with the parameters given above.
+The parameters for the Raman pulses are different between different groups and are listed below.
+The full Rabi frequency is the two-photon Rabi frequency $\Omega$ excluding the matrix element
+from wavefunction overlap.
+For a Raman pulse with a power ramp,
+the full Rabi frequency gives the arithmetics mean over the duration of the pulse.
+The power ramp field gives, if any,
+the beam (in terms of their corresponding $F$ number)
+that ramps with a Blackman profile during the pulse.
+\subsubsection{Group 1}
+This group is repeated 5 times.
+\begin{center}
+  \begin{tabular}{|c|c|c|c|c|}
+    \hline
+    Axis&Order&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
+    $x$&-2&25&$2\pi\times34$&F1\\\hline
+    $y$&-2&25&$2\pi\times34$&F1\\\hline
+    $x$&-1&25&$2\pi\times34$&F1\\\hline
+    $y$&-1&21&$2\pi\times34$&F1\\\hline
+  \end{tabular}
+\end{center}
+\subsubsection{Group 2}
+This group is repeated 5 times.
+\begin{center}
+  \begin{tabular}{|c|c|c|c|c|}
+    \hline
+    Axis&Order&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
+    $z$&-8&80&$2\pi\times14$&\\\hline
+    $x$&-2&25&$2\pi\times34$&F1\\\hline
+    $z$&-7&80&$2\pi\times14$&\\\hline
+    $y$&-2&25&$2\pi\times34$&F1\\\hline
+    $z$&-8&80&$2\pi\times14$&\\\hline
+    $x$&-1&25&$2\pi\times34$&F1\\\hline
+    $z$&-7&80&$2\pi\times14$&\\\hline
+    $y$&-1&21&$2\pi\times34$&F1\\\hline
+  \end{tabular}
+\end{center}
+\subsubsection{Group 3}
+This group is repeated 6 times.
+\begin{center}
+  \begin{tabular}{|c|c|c|c|c|}
+    \hline
+    Axis&Order&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
+    $z$&-7&80&$2\pi\times14$&\\\hline
+    $x$&-2&25&$2\pi\times34$&F1\\\hline
+    $z$&-6&80&$2\pi\times14$&\\\hline
+    $y$&-2&25&$2\pi\times34$&F1\\\hline
+    $z$&-7&80&$2\pi\times14$&\\\hline
+    $x$&-1&25&$2\pi\times34$&F1\\\hline
+    $z$&-6&80&$2\pi\times14$&\\\hline
+    $y$&-1&21&$2\pi\times34$&F1\\\hline
+  \end{tabular}
+\end{center}
+\subsubsection{Group 4}
+This group is repeated 7 times.
+\begin{center}
+  \begin{tabular}{|c|c|c|c|c|}
+    \hline
+    Axis&Order&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
+    $z$&-6&80&$2\pi\times14$&\\\hline
+    $x$&-2&25&$2\pi\times34$&F1\\\hline
+    $z$&-5&60&$2\pi\times14$&\\\hline
+    $y$&-2&25&$2\pi\times34$&F1\\\hline
+    $z$&-6&80&$2\pi\times14$&\\\hline
+    $x$&-1&25&$2\pi\times34$&F1\\\hline
+    $z$&-5&60&$2\pi\times14$&\\\hline
+    $y$&-1&21&$2\pi\times34$&F1\\\hline
+  \end{tabular}
+\end{center}
+\subsubsection{Group 5}
+This group is repeated 7 times.
+\begin{center}
+  \begin{tabular}{|c|c|c|c|c|}
+    \hline
+    Axis&Order&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
+    $z$&-5&90&$2\pi\times17$&F2\\\hline
+    $x$&-1&38&$2\pi\times34$&F1\\\hline
+    $z$&-4&75&$2\pi\times17$&F2\\\hline
+    $y$&-1&25&$2\pi\times34$&F1\\\hline
+    $z$&-5&90&$2\pi\times17$&F2\\\hline
+    $x$&-1&43&$2\pi\times34$&F1\\\hline
+    $z$&-4&75&$2\pi\times17$&F2\\\hline
+    $y$&-1&28&$2\pi\times34$&F1\\\hline
+  \end{tabular}
+\end{center}
+\subsubsection{Group 6}
+This group is repeated 8 times.
+\begin{center}
+  \begin{tabular}{|c|c|c|c|c|}
+    \hline
+    Axis&Order&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
+    $z$&-4&75&$2\pi\times17$&F2\\\hline
+    $x$&-1&38&$2\pi\times34$&F1\\\hline
+    $z$&-3&60&$2\pi\times17$&F2\\\hline
+    $y$&-1&25&$2\pi\times34$&F1\\\hline
+    $z$&-4&75&$2\pi\times17$&F2\\\hline
+    $x$&-1&43&$2\pi\times34$&F1\\\hline
+    $z$&-3&60&$2\pi\times17$&F2\\\hline
+    $y$&-1&28&$2\pi\times34$&F1\\\hline
+  \end{tabular}
+\end{center}
+\subsubsection{Group 7}
+This group is repeated 10 times.
+\begin{center}
+  \begin{tabular}{|c|c|c|c|c|}
+    \hline
+    Axis&Order&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
+    $z$&-3&60&$2\pi\times17$&F2\\\hline
+    $x$&-1&38&$2\pi\times34$&F1\\\hline
+    $z$&-2&60&$2\pi\times17$&F2\\\hline
+    $y$&-1&25&$2\pi\times34$&F1\\\hline
+    $z$&-3&60&$2\pi\times17$&F2\\\hline
+    $x$&-1&43&$2\pi\times34$&F1\\\hline
+    $z$&-2&60&$2\pi\times17$&F2\\\hline
+    $y$&-1&28&$2\pi\times34$&F1\\\hline
+  \end{tabular}
+\end{center}
+\subsubsection{Group 8}
+This group is repeated 10 times.
+\begin{center}
+  \begin{tabular}{|c|c|c|c|c|}
+    \hline
+    Axis&Order&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
+    $z$&-2&60&$2\pi\times17$&F2\\\hline
+    $x$&-1&38&$2\pi\times34$&F1\\\hline
+    $z$&-1&60&$2\pi\times17$&F2\\\hline
+    $y$&-1&25&$2\pi\times34$&F1\\\hline
+    $z$&-2&60&$2\pi\times17$&F2\\\hline
+    $x$&-1&43&$2\pi\times34$&F1\\\hline
+    $z$&-1&60&$2\pi\times17$&F2\\\hline
+    $y$&-1&28&$2\pi\times34$&F1\\\hline
+  \end{tabular}
+\end{center}
+\subsubsection{Group 9}
+This group is repeated 40 times.
+\begin{center}
+  \begin{tabular}{|c|c|c|c|c|}
+    \hline
+    Axis&Order&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
+    $z$&-1&70&$2\pi\times9$&F2\\\hline
+    $z$&-1&100&$2\pi\times9$&F2\\\hline
+    $x$&-1&38&$2\pi\times34$&F1\\\hline
+    $z$&-1&70&$2\pi\times9$&F2\\\hline
+    $z$&-1&100&$2\pi\times9$&F2\\\hline
+    $y$&-1&25&$2\pi\times34$&F1\\\hline
+    $z$&-1&70&$2\pi\times9$&F2\\\hline
+    $z$&-1&100&$2\pi\times9$&F2\\\hline
+    $x$&-1&43&$2\pi\times34$&F1\\\hline
+    $z$&-1&70&$2\pi\times9$&F2\\\hline
+    $z$&-1&100&$2\pi\times9$&F2\\\hline
+    $y$&-1&28&$2\pi\times34$&F1\\\hline
+  \end{tabular}
+\end{center}
 

### 2017-08-09 CoolingSequence.m

@@ -1,129 +1,0 @@
-%% Raman Cooling
-state = NaRamanState(s);
-% The following Pulsed cooling no-op
-state.PulseOPF1 = 0.32;
-state.TPulseOP = 40e-6;
-
-% NaPulsedCool(T, Det, F1Vert, F2Counter, RamanF1, RamanF2, OPF2)
-% NCoolCycles = 20;
-NaAxial0 = -18.506e6;
-NaAxialF = 67.5e3;
-
-NaAxial8 = NaAxial0 + NaAxialF * 8;
-NaAxial7 = NaAxial0 + NaAxialF * 7;
-NaAxial6 = NaAxial0 + NaAxialF * 6;
-NaAxial5 = NaAxial0 + NaAxialF * 5;
-NaAxial4 = NaAxial0 + NaAxialF * 4;
-NaAxial3 = NaAxial0 + NaAxialF * 3;
-NaAxial2 = NaAxial0 + NaAxialF * 2;
-NaAxial1 = NaAxial0 + NaAxialF;
-NaAxial1_2 = NaAxial0 + 77e3;
-
-NaCools1 = {NaPulsedCool(25e-6, -17.6375e6, 1, 1, 0.0, 0.05, 0.21, 1.0, 0.0), ...
-            NaPulsedCool(25e-6, -18.03e6, 1, 1, 0.0, 0.05, 0.23, 1.0, 0.0), ...
-            NaPulsedCool(25e-6, -17.2825e6, 0, 1, 0.0, 0.05, 0.21, 0.22, 0.0), ...
-            NaPulsedCool(21e-6, -17.875e6, 0, 1, 0.0, 0.05, 0.23, 0.22, 0.0)};
-NaCools1 = repmat(NaCools1, 1, 5);
-% Axial 8+7, Radial2 2+1, Radial3 2+1
-NaCools2 = {NaPulsedCool(80e-6, NaAxial8, 1, 0, 0.4, 0.14, 0.21), ...
-            NaPulsedCool(80e-6, NaAxial7, 1, 0, 0.4, 0.14, 0.21), ...
-            NaPulsedCool(25e-6, -17.6375e6, 1, 1, 0.0, 0.05, 0.21, 1.0, 0.0), ...
-            NaPulsedCool(25e-6, -18.03e6, 1, 1, 0.0, 0.05, 0.21, 1.0, 0.0), ...
-            NaPulsedCool(80e-6, NaAxial8, 1, 0, 0.4, 0.14, 0.21), ...
[…]

### 2017-08-09 paper.tex
Kang-Kuen's edit

--- 2017-07-25 paper.tex
@@
 \title{Motional Ground State Cooling Outside the Lamb-Dicke Regime}
-\author{Yichao Yu}
+\author{Y. Yu}
 \email{yichaoyu@g.harvard.edu}
-\author{Nicholas R. Hutzler}
+\author{N. R. Hutzler}
 \altaffiliation{Present address: California Institute of Technology, Division of Physics, Mathematics, and Astronomy. Pasadena, CA, 91125}
-\author{Jessie T. Zhang}
-\author{Lee R. Liu}
-\author{Kang-Kuen Ni}
+\author{J. T. Zhang}
+\author{L. R. Liu}
+\author{T. Rosenband}
+\author{K.-K. Ni}
 \email{ni@chemistry.harvard.edu}
@@
   motional ground state in an optical tweezer.
-  Despite having a very large Lamb-Dicke parameter, high initial temperature, and
-  large differential AC Stark shifts between the excited state and the ground state,
-  we achieve a ground state preparation fidelity of $77(4)$\% after $100$ ms of cooling.
-  Our technique includes addressing very high-order sidebands and
-  fast modulation of the optical tweezer trap.
-  We demonstrate that Raman sideband cooling to the 3D motional ground state is applicable
-  outside the Lamb-Dicke regime, for example in
-  systems where tight confinement and low initial temperature are difficult to realize.
-  This is particularly relevant for systems which are challenging to laser-cool,
-  such as molecules and exotic atoms,
-  and opens up the possibility to gain quantum motional control of these systems.
+  Despite  a  large Lamb-Dicke parameter, high initial temperature, and
+  large differential light shifts between the excited state and the ground state,
+  we achieve a ground state population of $81(4)$\% after $100$ ms of cooling. In addition, $10\,\%$ of initial atom population escapes the trap during cooling.
+  Our technique includes addressing  high-order sidebands, , where several motional quanta are removed by a single laser pulse,  and
+  fast modulation of the optical tweezer intensity.
+  We demonstrate that Raman sideband cooling to the 3D motional ground state is possible %outside the Lamb-Dicke regime, 
+  where tight confinement and low initial temperature are difficult to realize.
+%  This is particularly relevant for systems which are challenging to laser-cool, such as molecules and exotic atoms, and opens up the possibility to gain quantum motional control of these systems.
 \end{abstract}
@@
 
+%Systems of trapped neutral atoms assembled from the bottom-up in an array of optical tweezers are a promising  platform to study quantum information and quantum simulations~
+Trapped neutral atoms, assembled  in an array of optical tweezers, are a promising  platform to study quantum information and quantum simulations~
+\cite{Schlosser2001,Weiss2004,Isenhower2010,Wilk2010,Kaufman2015,Labuhn2016,Murmann2015}.
+The inherent single-particle detection and control, combined with tunable interactions,
+allow implementations of neutral-atom-based quantum logic gates~\cite{Isenhower2010,Wilk2010},
+novel quantum phases~\cite{Labuhn2016}, and single-photon switches~\cite{Dayan2008,Tiecke2014}.
+Advances in real-time re-arrangement of optical tweezers enable rapid preparation of atoms
+in large and complex geometries~\cite{Barredo2016,Endres2016}.
+Quantum motional control of individual
+atoms~\cite{Li2012,Kaufman2012,Thompson2013,Liu2017,Robens2017} enable
+studies of the atomic Hong-Ou-Mandel effect~\cite{Kaufman2014},
+high-fidelity single qubit gates~\cite{Wang2016},
+and efficient coupling of single atoms to photonic crystal cavities~\cite{Thompson2013a}.
+
+Extending optical tweezer arrays  to include polar molecules will open up a  range of
+new applications that exploit  long-lived molecular internal states
+and  tunable long range interactions~\cite{DeMille2002,Gorshkov2011,Yan2013}.
+Molecules could be assembled from atom pairs in  optical tweezers~\cite{Liu2017},
+or directly loaded from magneto-optical traps
+(MOTs)~\cite{Barry2014,Truppe2017SubDoppler,Anderegg2017}.
+For either approach, preparing the constituent atoms or molecules in the lowest motional
+quantum state is important to realize long coherence times in quantum applications.
+
+Preparation of single atoms in the motional ground state has been achieved in optical tweezers~\cite{Kaufman2012,Thompson2013,Liu2017,Robens2017}
+ using Raman sideband cooling (RSC)~\cite{Monroe1995,Kerman2000,Han2000}.
+However, RSC in these systems take place in the Lamb-Dicke (LD) regime, where
+the spread of the initial wavefunctions is much smaller than the wavelength of light used to address them.
+Systems with a large wavefunction, either due to small mass or high initial temperature,
+fall outside of the LD regime and undergo strong recoil heating during RSC.
+Extending RSC beyond the LD regime opens  the possibility
+for ground state cooling of systems such as light atoms and %systems with poor cooling such as 
+molecules that can be laser-cooled.
+In this letter we demonstrate cooling of single sodium atoms in optical tweezers,
+initially outside of the LD regime, to the motional ground state.
+We achieve a 3D ground state population of $P_0=81(4)$\% by  cooling via
+ high-order sidebands in a carefully optimized cooling sequence.
+Our approach is general and applicable to %opens up ground state cooling for 
+other systems.
+
+Our experiment has an overall repetition rate of $2.5$ Hz and
+begins by loading a single sodium atom into optical tweezers from a MOT~\cite{Hutzler2017-LightShifts}.
+%for $250$ ms~\cite{Hutzler2017-LightShifts}.
+The tweezers are created by focussing a $700$ nm wavelength laser beam through an NA=$0.55$ objective to an elliptical waist with radii $\{w_{0,x},w_{0,y}\}\approx \{0.79,0.57\}\,\mu$m.
+For $45$ mW of optical power, the trapping frequencies along the three axes are
+$\{\omega_x,\omega_y,\omega_z\}/2\pi = \{430(4), 590(5), 69(1)\}\ \text{\text{kHz}}$,
+where  $z$ is the weakly confined axial direction,
+and  $x$ and $y$ are the tightly confined radial directions.
+After each single atom loading attempt, an image is taken with a $1.5$ ms exposure time
+to determine success.
+During  imaging, the atom is cooled via polarization gradient cooling (PGC),
+which reduces the temperature of the single atom to $70$ $\mu$K,
+corresponding to mean motional states along the three trap axes of
+$\{\bar n_x, \bar n_y, \bar n_z\}=\{3.4(2),\, 2.5(2),\, 21(2)\}$, and therefore initial 3D ground state probability of $P_0=0.3$\%.
+The atom is then initialized  into
+the $|F=2, m_F=-2\rangle$ stretched state via optical pumping (OP).
+Each experimental cycle ends with a second imaging sequence that measures the hyperfine state of the atom as $|F=2\rangle$ or $|F=1\rangle$~\footnote{The final hyperfine state sensitive detection employs a strong beam that is resonant with the $F=2$ to $F'=3$ cycling transition, to heat the $F=2$ population out of the trap.
+Therefore, any atoms which survive this heat out procedure are interpreted as having been in the $F=1$ state.}.%a repetition of the experiment that was initially bright and remained bright after the pulse sequence is interpreted as a final F=1 atomic state.}.
+
+%\footnote{We were able to load into larger tweezers with waist $> 1$ micron with an unmodulated tweezer and MOT beams, though the loading was only a few percent efficient.}
+%, while a bright image that turned dark is interpreted as F=2.   
+%The hyperfine state detection is performed by pushing out atoms in the stretched state with a strong beam on resonance with the $|F=2, m_F=-2\rangle$ to $|F'=3, m_{F'}=-3\rangle$ transition before taking the second image to determine if the atom was pushed out.
+The state preparation and detection have a combined fidelity of larger than $99$\%.
+
+To  reduce the temperature of the single atom and
+ achieve high ground state population, we apply Raman sideband cooling~\cite{Monroe1995, Kaufman2012}.
+The  energy levels, cooling sequence, and Raman beam geometries 
+are shown in Fig.~\ref{f-setup}. RSC consists of two steps:
+driving a coherent Raman transition  to remove motional quanta, followed by resetting the atom's internal state via OP.
+These  steps are  repeated, until the motional ground state is populated with high probability.
+
 \begin{figure*}
@@
   \includegraphics[height=4.5cm]{sequence.pdf}
-  \caption{(A) Energy levels and schematic of Raman sideband cooling.
-    The Raman transitions have a one photon detuning $\Delta=25$ GHz from the D2 line.
-    We use D1 light with $\sigma^-$ polarization to repump atoms out of $|F=2,m_F=-1\rangle$
-    state to minimize heating on the atom in the $|F=2,m_F=-2\rangle$ state
+  \caption{Single Na atom Raman sideband cooling scheme and sequence. (A)
+    The Raman transitions between $|2,-2;n\rangle$ and $|1,-1;n+\Delta n\rangle$ have a one-photon detuning $\Delta=25$ GHz below the $3^2S_{1/2}$ to $3^2P_{3/2}$ transition.
+Two-photon detuning, $\delta$, is defined relative to the $\Delta n=0$ carrier transition.
+For optical pumping, we use two $\sigma^-$ polarized transitions, one   to  pump the atom state out of $|1,-1\rangle$ via $3^2P_{3/2}$ and one  to pump atoms out of $|2,-1\rangle$ via $3^2P_{1/2}$
+     to minimize heating on the atom in the $|2,-2\rangle$ state.
     (B) Geometry and polarizations of the Raman and optical pumping beams relative to the
-    optical tweezer and bias magnetic field.
-    (C) Schematic of the cooling sequence. The tweezer is strobed at 3 MHz to
+    optical tweezers and bias magnetic field.
+Raman beams 1 and 4 address the radial $x$ mode.
+Raman beams 1 and 2 address the radial $y$ mode.
+Raman beams 3 and 4 address the axial $z$ mode, which also couples to the radial $y$ mode.
+    (C) Schematic of the cooling pulse sequence. The tweezer is strobed at 3 MHz to
     reduce light shifts during optical pumping~\cite{Hutzler2017-LightShifts}.
-    Each cooling cycle consists of $8$ pulses.
-    The four axial pulses are addressing two neighboring cooling orders.
-    The two pulses in each radial direction are either addressing two neighboring cooling orders
-    or having different length on the first order when most of the population are below $n=3$
-    towards the end of the cooling sequence.
-    All of the Raman pulses use Blackman pulse envelopes to reduce the off-resonant
-    coupling to carrier and heating sidebands.
+    Each cooling cycle consists of $8$ sideband pulses.
+    The four axial pulses address two sideband orders.
+    The two pulses in each radial direction  either address $\Delta n=-2$ and $\Delta n=-1$
+    or have different durations to drive $\Delta n=-1$, when most of the population is below $n=3$
+    at the end of the cooling sequence.
+    The Raman cooling and spectroscopy pulses have Blackman  envelopes to reduce  off-resonant
+    coupling, while the measurement Rabi pulses in Fig.~\ref{f-radial}(B,C) and \ref{f-axial}(B,C) have square envelopes to simplify analysis.
     \label{f-setup}}
 \end{figure*}
+
+Specifically, Raman transitions are driven in Na between the hyperfine states
+$|2, -2\rangle$ and $|1, -1\rangle$ in the presence of an $8.8$ G magnetic field. The external field is
+orthogonal to the effective magnetic field of the tweezer, to reduce  vector light shifts~\cite{Kaufman2012,Thompson2013}.
+Subsequently, an OP pulse, which consists of two frequencies  both with $\sigma^-$-polarization, is applied  to bring the atom out of the $F=1$ manifold and back to  $|2, -2\rangle$ via spontaneous emission (Fig.~\ref{f-setup}A).
+%brings the atom back to $|F=2, m_F=-2\rangle$ via spontaneous emission.
+%, which consists of two frequencies with $\sigma^-$-polarization for the  to bring the atom out of $F=1$ manifold and back to  $|F=2, m_F=-2\rangle$ via spontaneous emission.
+It is important that the optical pumping step scatter as few photons as possible to minimize recoil heating.
+%The OP consists of driving a $|F=1, m_F=-1\rangle$ into the $F=2$ manifold via the transition of $3P_{3/2} D2 line$
+Therefore, to optically pump atoms from $|2,-1\rangle$ into $|2, -2\rangle$, we apply light resonant with  $3^2P_{1/2}$~\footnote{We find a reduction in the scattering rate by a factor of $130(20)$, as compared to using an OP resonant with $3^2P_{3/2}$, from which the $|2, -2>$ state could always scatter a photon via the excited $|F'=3, m_F'=-3>$ state.} because $|2, -2\rangle$ is a dark state to $\sigma^-$-polarized light~\cite{Monroe1995, Grobner2017}.
+%~\footnote{We find a reduction in the scattering rate by a factor of $130(20)$, as compared to using an OP resonant with $3P_{3/2}$, from which the $|2, -2 \rangle$}
+
 \begin{figure}[b]
   \includegraphics[width=8.5cm]{imgs/fig2_raman_op.pdf}
-  \caption{Optical pumping state changing probability and Raman matrix element for axial direction.
+  \caption{Optical pumping motional-state redistribution and  Raman coupling for large  Lamb-Dicke parameters for the axial direction ($z$).
 The range plotted covers $95$\% of the initial thermal distribution.
-    (A) Axial motional state distribution after one optical pumping cycle
-    for different initial $n$. Due to the large Lamb-Dicke parameter,
-    there is a high probability of $n$ changing.
-    (B) Matrix elements for Raman transition in the axial direction showing deviation from
-    $\sqrt{n}$ scaling and multiple minima for different sideband orders.
+   % The range plotted covers $95$\% of the initial thermal distribution.
+    (A) Motional state distribution after one optical pumping cycle
+    for different initial n, $n_{\textrm{init}}$. Due to photon-recoil and the large Lamb-Dicke parameter, $\eta^{OP}_z=0.6$,
+    there is a high  $n$ changing probability.         (B) Matrix elements for Raman transition deviate from
+    $\sqrt{n}$ scaling with multiple minima. During cooling, we utilize the fact that higher motional states couple most effectively to sidebands with large $|\Delta n|$.
     ($k$ is the difference in wave vector of the Raman beams,
-    $r$ is the coordinate in axial direction).
+    $r$ is the coordinate in the axial direction).
     \label{f-ld}}
 \end{figure}
+
+For an atom starting in motional level $n_{\textrm{init}}$, the probability of recoil during the OP sequence results in
+a motional-state redistribution  is shown in Fig.~\ref{f-ld}A.
+The  probability is approximately proportional to the square of effective LD parameter
+$\eta^{\textrm{OP}}_{\textrm{eff}}=\sqrt{2n+1}\eta^{\textrm{OP}}$~\cite{Kaufman2012},
+where the optical pumping LD parameter $\eta^{\textrm{OP}} = z_0\frac{2\pi}{\lambda}$ is the ratio of the zero-point wavefunction spread $z_0 = \sqrt{\hbar/2m\omega}$ to the reduced wavelength $\lambda$.
+Here, $m$ is the mass of the atom, $\omega$ is the trap frequency,
+and $\hbar$ is the reduced Planck constant.
+Such heating presents a major challenge for efficient cooling of single Na atoms
+which feature a low mass (23 amu) and short wavelengths.
+For our configuration, 
+$\{\eta^{\textrm{OP}}_x,\eta^{\textrm{OP}}_y,\eta^{\textrm{OP}}_z\} = \{0.241(2), 0.206(1), 0.602(5)\}$.
+A relatively large PGC temperature results in initial $\{\eta^{\textrm{OP}}_{x,\textrm{eff}},\eta^{\textrm{OP}}_{y,\textrm{eff}},\eta^{\textrm{OP}}_{z,\textrm{eff}}\} = \{0.67(2), 0.50(1), 4.0(1)\}$.
+The weak axial direction %, $(\eta^{\textrm{OP}}_{z,\textrm{eff}})^2>1$ 
+is far outside of the LD regime ($\eta^2\ll 1$), and the probability of recoil heating per OP step is large.
+%~\footnote{For example, the average change in the motional states for the initial distribution is $2.4$ in the axial direction, which is significantly greater than $0.89-0.95$in previous experiments of RSC of Rb and Cs~\cite{Li2012,Kaufman2012,Thompson2013,Liu2017}.},
+This creates a large uncertainty on the motional state at the end of a full RSC step, possibly leading to runaway heating.
+
+Fortunately, the large LD parameters also provide opportunities to overcome OP heating.
+The LD parameter for Raman transitions is defined as $\eta^R\equiv\Delta k z_0$,
+where the wave vector is replaced by the wave vector difference $\Delta k$
+between the two beams that drive the Raman transition.
+The Raman transitions in our configuration have LD parameters of
+$\{\eta^R_x,\eta^R_y,\eta^R_z\} = \{0.341(2), 0.291(1), 0.40(1)\}$.
+To offset heating from OP initially, higher-order Raman  sidebands ($\Delta n <-1$)  can be utilized
+to remove several motional quanta in a single cooling pulse (see Fig.~\ref{f-ld}B).
+Because the coupling strengths of different orders do not reach minima for the same state of motion $n$,
+using multiple orders of sidebands avoids accumulations of population
+near the coupling minima.
+
+Taking the large motional-state changing heating and cooling sources
+ into account,
+it is not immediately clear that efficient cooling can be achieved.
+We therefore use a Monte-Carlo simulation to guide our search~\cite{Dalibard1992}. 
+%and to find a robust cooling sequence~\footnote{See supplemental material}.
+In particular, we find that alternating the cooling pulses (Fig.~\ref{f-setup}C) between two
+neighboring orders for the axial direction and $\Delta n=-2$ and $\Delta n=-1$ for the radial directions
+eliminates the accumulation of population in motional states that have zero Raman coupling, which would halt the cooling process.
+The simulation also indicates that setting the coupling strength of each  sideband
+to drive a Rabi $\pi$-pulse corresponding to the maximum matrix element motional state
+(i.e. the maxima in Fig.~\ref{f-ld}B)  yields efficient cooling, initially.
+The efficiency of cooling on higher-order sidebands diminishes
+as the atom approaches the ground state, so the final  cycles utilize only the $\Delta n=-1$ sideband while alternating between the three  axes.
+
+Guided by the simulation results,
+we construct our axial cooling sequence by starting at the two highest
+observed  sideband orders ($\Delta n=-8$ and $\Delta n=-7$)
+and decreasing the orders to the next pair after every $6$ to $15$ cycles.
+This process is repeated until we reach $\Delta n=-1$, and most of the
+population is in the first few excited states. We then switch to cooling only on $\Delta n=-1$ with two different pulse lengths in order to efficiently cool atoms in the
+few remaining motional states.
+Radial cooling is performed similarly to the axial cooling with the initial cooling of $\Delta n=-2$ and $\Delta n=-1$ and switching to $\Delta n=-1$ only after $20$ to $30$ pulses.
+This sequence gives good initial cooling performance, which can then be used to measure experimental
+parameters, including the Rabi rates of the Raman beams and optical pumping rates,
+in order to optimize the sequence further.
+
+There are two additional important challenges in cooling single sodium atoms.
+First, the high initial temperature populates high motional states,
+causing the atoms to sample the anharmonicity of the trap away from the center.
+Anharmonicity may be defined as $A_{i,n}=(E_{i,n+1}-E_{i,n})/h - \omega_i/(2\pi)$ for each trap axis $i$, and calculated from the quartic term of the optical tweezers via perturbation theory.
+We find $A_{i,n}=\frac{3n \hbar}{4 \pi m d_i^2}$  where $d_i=w_{0,x},w_{0,y}$ for the radial directions and $d_z=\pi w_{0,x}w_{0,y}/\lambda$.
+Numerically, $\{A_{x,n},A_{y,n},A_{z,n}\}=\{1.1, 2.0, 0.16\}n$~kHz.
+For mixed states, this  broadens high-order sidebands due to the $n$-dependence of the transitions.
+In order to mitigate this, we drive the sidebands with a large  Rabi frequency
+and short pulses to Fourier broaden the spectrum. %, and use Blackman pulse envelopes to avoid unwanted coupling to the carrier and heating sidebands~\cite{Kasevich1992}. 
+However, anharmonicity  may still shift high-$n$ states out of resonance and prevent effective cooling.
+%Anharmonicity may be defined as $A_{i,n}=(E_{i,n+1}-E_{i,n})/h - \omega_i/(2\pi)$ for each trap axis $i$, and calculated from the quartic term of the optical tweezers via perturbation theory.
+We find $A_{i,n}=\frac{3n \hbar}{2 m d_i^2}$  where $d_i=w_0$ for the radial directions and $d_z=\pi w_0^2/\lambda$  Numerically, $\{A_{x,n},A_{y,n},A_{z,n}\}=\{1.3, 1.2, 0.2\}n$~kHz.
+Anharmonicity broadens the high-order axial transitions and may shift high-$n$ states out of resonance to prevent effective cooling.
+
+%The anharmonicity in the radial directions is calculated to be 1kHz/n, meaning that a Rabi frequency of at least $15$ kHz is needed to couple to $99$\% population up to $n=15$.
+
 \begin{figure*}
@@
   \includegraphics[height=4.2cm]{imgs/rabi_flop_r3_p1.pdf}
-  \caption{(A) Radial Raman sideband spectrum of first order heating, first order cooling and
-    second order cooling before and after Raman sideband cooling.
-    (B,C) Rabi flopping on axis 3 (B) carrier and (C) first order heating sideband
-    before (red) and after (blue) cooling.
-    Solid lines in (B) and (C) are theoretical calculation of the Rabi flopping.
-    The blue lines correspond to a ground state probability of $93$\% after cooling and
+  \caption{(A) Left to right: Radial Raman sideband spectrum of $\Delta n_y=1,\,\Delta n_x=1,\,\Delta n_x=-1,\,\Delta n_y=-1,\,\Delta n_x=-2,\,\Delta n_y=-2$  before and after Raman sideband cooling.
+    (B,C) Rabi flopping on axis $y$ (B) carrier and (C) $\Delta n_y=1$  sideband
+    before (red circle) and after (blue square) cooling.
+    Solid lines in (B) and (C) are 
+    fits to a Rabi-flopping that includes a thermal distribution of motional states~\cite{Meekhof1996}  as well as off-resonant scattering from the Raman beams.
+The curves reach a maximum contrast of 85\% (horizontal dashed line) because 5\% of atoms are lost from one imaging step to the next, and 10\% of atoms are additionally lost during Raman cooling.
+    The blue lines correspond to a 1D ground state probability of $93$\% after cooling (not including loss) and
     the red lines correspond to a thermal distribution of $70$ $\mu$K before cooling.
+    %The horizontal dashed line shows the overall survival after cooling and imaging.
     \label{f-radial}}
@@
   \includegraphics[height=4.2cm]{imgs/rabi_flop_a1_p1.pdf}
-  \caption{(A) Axial Raman sideband spectrum from first order heating to eighth order cooling
-    before and after Raman sideband cooling.
-    The data for the second and higher orders of cooling sidebands are taken with 150 $\mu$s
-    pulse time and the rest are taken with 125 $\mu$s pulse time.
-    (B,C) Rabi flopping on axial (B) carrier and (C) first order heating sideband
-    before (red) and after (blue) cooling.
-    Solid lines in (B) and (C) are theoretical calculation of the Rabi flopping.
-    The blue and green lines corresponds to a ground state probability of $92$\% after cooling and
-    the red lines corresponds to a thermal distribution of $70$ $\mu$K before cooling.
-    The blue lines do not take into account the effect of decoherence due to resonance
-    fluctuation. By comparing it to the green line in (C), which includes a $3$ kHz fluctuation,
-    we can clearly see that this effect is the strongest for the post-cooling data on
-    the axial heating sideband where the Rabi frequency is the lowest.
-    The asymptotic values for the red lines are low also because of resonance fluctuation.
+  \caption{(A) Left to right: Axial Raman sideband spectrum from $\Delta n_z=1,0,-1,\ldots,-8$    before and after Raman sideband cooling.
+    %The data for the 2nd- and higher-orders of cooling sidebands are taken with 150 $\mu$s pulse duration and the rest are taken with 125 $\mu$s pulse duration.
+    (B,C) Rabi flopping on axial (B) carrier $\Delta n_z=0$  and (C) $\Delta n_z=1$ sideband
+    before (red circle) and after (blue square) cooling.
+    Solid blue lines in (B) and (C), similar to Fig.~\ref{f-radial}B and C, are fits to  the Rabi flopping and yield  a ground state probability of $92$\% after cooling (not including the 15\% population loss) and
+    the red lines correspond to a thermal distribution of $70$ $\mu$K before cooling.
+    %The blue lines do not take into account the effect of decoherence due to resonance fluctuation. 
+    %By comparing it to 
+    The green line in (C), includes the additional decoherence due to a fluctuation of the hyperfine splitting of magnitude 3kHz. %a $3$ kHz fluctuation of the hyperfine splitting. 
+    We see that the decoherence effect is  strongest for the post-cooling data on
+    the $\Delta n_z=1$ sideband where the Rabi frequency is the lowest.
+    %The asymptotic values for the red lines are low also because of resonance fluctuation.
+    %Similar to the Figure~\ref{f-radial},
+    The horizontal dashed line shows the overall survival after cooling and imaging.
     \label{f-axial}}
@@
 
-Systems of trapped neutral atoms assembled from the bottom-up in optical tweezer arrays
-are an exciting platform to study quantum information and quantum simulations~\cite{Schlosser2001,Weiss2004,Isenhower2010,Wilk2010,Kaufman2015,Labuhn2016,Murmann2015}.
-The inherent single-particle detection and control combined with tunable interactions
-are key to implementing neutral atom based quantum logic gates~\cite{Isenhower2010,Wilk2010},
-novel quantum phases~\cite{Labuhn2016}, and single-photon switches~\cite{Dayan2008,Tiecke2014}.
-Advances in real-time re-arrangement of optical tweezers enable rapid preparation of atoms
-in large and complex geometries with high fidelity~\cite{Barredo2016,Endres2016}.
-Adding quantum motional control of individual
-atoms~\cite{Li2012,Kaufman2012,Thompson2013,Liu2017,Robens2017} enables
-efficient coupling of single atoms to photonic crystal cavities~\cite{Thompson2013a},
-high-fidelity single qubit gates~\cite{Wang2016},
-and studies of the atomic Hong-Ou-Mandel effect~\cite{Kaufman2014}.
-
-Extending optical tweezer array techniques to include polar molecules will open up a large range of
-new applications that exploit their many long-lived internal states
-and highly tunable interactions~\cite{DeMille2002,Ni2008,Gorshkov2011,Yan2013}.
-Molecules could be assembled from atom pairs in the optical tweezer~\cite{Liu2017},
-or directly loaded from magneto-optical traps
-(MOTs)~\cite{Barry2014,Truppe2017SubDoppler,Anderegg2017}.
-For either approach, preparing the constituent atoms or molecules in the lowest motional
-quantum state is important for realizing long coherence times in quantum applications.
-
-Preparation of single atoms in the motional ground state has been achieved in optical tweezers~\cite{Kaufman2012,Thompson2013,Liu2017,Robens2017}
- using Raman sideband cooling (RSC)~\cite{Monroe1995,Kerman2000,Han2000}.
-However, RSC in these systems has been applied in the Lamb-Dicke (LD) regime, where
-the size of the atomic wavefunction is much smaller than the wavelength of light used to address them.
-Extending ground state cooling to systems outside the LD regime, such as light atoms or polar molecules, is challenging.
-In this letter we demonstrate cooling of single sodium atoms in optical tweezers, initially outside of the LD regime, to the motional ground state.
-We achieve a ground state probability of $P_0=77(4)$\% by utilizing cooling of
-very high-order sidebands in a carefully optimized cooling sequence.
-Our approach is general and opens up ground state cooling for other systems.
-
-Our experiment begins by loading a single sodium atom into an optical tweezer from a MOT
-for $250$ ms~\cite{Hutzler2017-LightShifts}, and has an overall repetition rate of $2.5$ Hz.
-The tweezer is created by focusing a $700$ nm laser beam through an NA=$0.55$ objective to
-create a focused beam with waist $0.7 \mu$m.
-With $45$ mW of tweezer power, the trapping frequencies along the three axes are
-$\{\omega_x,\omega_y,\omega_z\}/2\pi = \{430(4), 590(5), 69(1)\}\ \text{\text{kHz}}$
-where axis z is along the weakly confined axial direction and axis x and y are along the
-tightly confined radial directions.
-After attempting to load an atom from the MOT, an image is taken with $1.5$ ms exposure time to determine if it was a success.
-At the same time, the atom is cooled via polarization gradient cooling (PGC),
-which reduces the temperature of the single atom to $70$ $\mu$K,
-corresponding to an initial mean motional state along the three different axes of
-$\{\bar n_x, \bar n_y, \bar n_z\}=\{3.4(2),\, 2.5(2),\, 21(2)\}$, and therefore initial 3D ground state probability of $P_0=0.3$\%.
-A beam with $\sigma^-$-polarization is used to initialize the atom into
-the $|F=2, m_F=-2\rangle$ stretched state via optical pumping.
-The hyperfine state detection is performed by pushing out atoms in the stretched state with a strong
-beam on resonance with the $|F=2, m_F=-2\rangle$ to $|F'=3, m_{F'}=-3\rangle$ transition before
-taking the second image to determine if the atom was pushed out.
-The state preparation and detection have a combined fidelity of larger than $99$\%.
-
-To further reduce the temperature of the single atom and
-to achieve high ground state preparation fidelity, we apply Raman sideband cooling (RSC).
-The relevant energy levels, cooling sequence, and Raman beam geometries for our system
-are shown in Figure \ref{f-setup}. Briefly, the RSC consists of two steps:
-driving a coherent Raman transition while removing motional quanta, followed by resetting the atom's internal state via optical pumping (OP).
-RSC is applied repeatedly until the motional ground state is populated with high probability.
-
-Specifically, Raman transitions are driven in Na between the hyperfine states
-$|F=2, m_F=-2\rangle$ and $|F=1, m_F=-1\rangle$ in the presence of a $8.8$ G magnetic field to suppress vector light shifts~\cite{Kaufman2012,Thompson2013}.
-Subsequently, an OP/repump pulse brings the atom back to $|F=2, m_F=-2\rangle$
-via spontaneous emission.
-
-It is important that the re-pumping step scatter as few photons as possible to minimize heating.
-Therefore, we use a $\sigma^-$-polarized laser resonant with the D1 line
-since $|F=2, m_F=-2\rangle$ is a dark state in this case~\cite{Grobner2017}\fxnote{cite ion}.
-Compared to using a D2 repump beam, from which the $|F=2, m_F=-2\rangle$ state
-could always scatter a photon via the excited $|F=3, m_F=-3\rangle$ state,
-we find a reduction in the scattering rate of a factor of $130(20)$.
-
-For an atom in motional level $n$, the OP could result in motional-state redistribution
-as shown in Fig.~\ref{f-ld}A. The state redistribution probability
-is approximately proportional to the effective LD parameter
-$\eta^{\textrm{OP}}_{\textrm{eff}}=\sqrt{2n+1}\eta^{\textrm{OP}}$, where $\eta^{\textrm{OP}}=k z_0=k \sqrt{\hbar/2m\omega}$,
-$k$ is the wavenumber of the optical pumping beam, $z_0$ is the zero-point wavefunction spread,
-$m$ is the mass of the atom, and $\hbar$ is the reduced Planck constant.
-Such heating presents a major challenge for efficient cooling of single Na atoms
-which feature a light mass and short D-line wavelengths.
-For our trap frequencies and beam geometry,
-$\{\eta^{\textrm{OP}}_x,\eta^{\textrm{OP}}_y,\eta^{\textrm{OP}}_z\} = \{0.241(2), 0.206(1), 0.602(5)\}$.
-Combined with a relatively large PGC temperature gives initial
-$\{\eta^{\textrm{OP}}_{x,\textrm{eff}},\eta^{\textrm{OP}}_{y,\textrm{eff}},\eta^{\textrm{OP}}_{z,\textrm{eff}}\} = \{0.67(2), 0.50(1), 4.0(1)\}$.
-For the weak axial direction, $(\eta^{\textrm{OP}}_{z,\textrm{eff}})^2>1$ is far outside of the LD regime.
-As a result, the average change of motional state per OP step is large,
-which creates a large uncertainty on the motional state at the end of a full RSC step, possibly leading to runaway heating.
-For example, the average change in motional states over the initial distribution
-is $2.4$ in the axial direction, which is significantly greater than $0.89-0.95$
-in previous experiments of RSC of Rb and Cs~\cite{Li2012,Kaufman2012,Thompson2013,Liu2017}.
-
-Fortunately, the large LD parameters also provide opportunities to overcome OP heating.
-The Raman transitions in our configuration have LD parameters of
-$\{\eta^R_x,\eta^R_y,\eta^R_z\} = \{0.341(2), 0.291(1), 0.40(1)\}$,
-which allow strong coupling to higher order sidebands for atoms in higher motional states
-as calculated in Figure~\ref{f-ld}B.
-The LD parameter for Raman transitions is defined as $\eta^R\equiv\Delta k z_0$ similar to OP
-where $\Delta k$ being the wave vector difference
-between the two beams that drives the Raman transition.
-To offset heating from OP initially, higher-order Raman cooling sidebands can be utilized
-to remove more motional quanta in a single cooling pulse.
-Since the coupling strengths of different orders do not reach minima for the same pulse duration,
-using multiple orders of cooling sidebands avoids accumulations of population
-near the coupling minima.
-
-Taking the large motional-state changing heating and cooling sources into account,
-it is not immediately clear that efficient cooling can be achieved.
-We therefore use a Monte-Carlo simulation to guide our search and
-to find a robust cooling sequence\footnote{See supplemental material}.
-In the simulation, we indeed observe a high heating rate due to the large LD parameters
-and confirm that cooling with higher-order Raman sidebands can suppress heating.
-In particular, we find that instead of cooling on only one sideband order repeatedly,
-it is more efficient to alternate the cooling pulses (Fig.~\ref{f-setup}C) between two
-neighboring orders for the axial direction and 2nd- and 1st-orders for the radial directions
-to minimize the accumulation of the atom in motional states that have zero Raman coupling.
-The simulation also indicates that setting the coupling strength of each cooling sideband
-to drive a Rabi $\pi$ pulse corresponding to the maximum matrix element motional state
-(i.e. the maxima in \ref{f-ld}B) can yield efficient cooling.
-The efficiency of cooling on higher-order sidebands diminishes
-as the atom approaches the ground state, so the final cooling cycles utilize only the first-order sideband while alternating between the three different axes.
-
-Guided by the simulation results,
-we construct our axial cooling sequence by starting at the two highest
-observed cooling sidebands (8th- and 7th-orders)
-and decreasing the orders to the next pair after every $6$ to $15$ cycles.
-This process is repeated until we reach the first order cooling sideband, and most of the
-population is in the first few excited states. We then switch to cooling only on the
-first order sideband with two different pulse lengths in order to efficiently cool atoms in the
-few remaining motional states.
-The radial cooling is performed similarly to the axial cooling with the initial cooling orders being
-the 2nd and 1st order and switching to first order only after $20$ to $30$ pulses.
-This sequence gives good initial cooling performance, which can then be used to measure experimental
-parameters, including the Rabi rates of the Raman beams and optical pumping rates,
-in order to optimize the sequence further.
-
-There are two additional important challenges in cooling single sodium atoms.
-First, the high initial temperature populates high motional states,
-meaning that the atoms sample the anharmonicity of the trap away from the center.
-In order to address this, we drive the sidebands with a large Rabi frequency
-and short pulses to Fourier broaden the spectrum coverage, and use Blackman pulse envelopes
-to avoid unwanted coupling to the carrier and heating sidebands~\cite{Kasevich1992}.
-The anharmonicity in the radial directions is calculated to be 1kHz/n, meaning that a
-Rabi frequency of at least $15$ kHz is needed to couple to $99$\% population up to $n=15$.
-Second, the tweezer trap causes a large AC Stark shift (as large as $300$ MHz)
-in the excited state. This creates a large, position-dependent OP detuning
-and mixes the excited-state hyperfine levels, which reduces the optical pumping fidelity.
-We address this by strobing the trapping light at 3 MHz during the whole cooling sequence,
+Second, the tweezers cause a large light shift (as large as $300$ MHz)
+in the excited state. %This causes position-dependent OP detuning
+%and mixes the excited-state hyperfine levels,  reducing optical pumping fidelity. 
+We address this by strobing the trapping light at a rate of 3 MHz during the whole cooling sequence,
 similar to our loading and imaging process~\cite{Hutzler2017-LightShifts},
@@
 Due to the large light shift, the OP is effectively off whenever the trap light switches back on.
-Since the atom can only be addressed by the optical pumping light when the trap light is off,
-the effect of light shifts on OP fidelity is suppressed.
+Since the atom is primarily addressed by  optical pumping light when the trap light is off, OP remains effective.
+%  However, the selection rules that make the state |2,-2> dark to OP light are only approximately true when the tweezer light is on, and turning off the OP light during this period is expected to reduce spontaneous emission.
 
 Our final cooling results are shown in Fig.~\ref{f-radial} and \ref{f-axial}.
-In total, $1000$ cooling pulses (with a total duration of $100$ ms) are applied
-along three axes with cooling beginning on the radial second order.
-To characterize the single atom thermal occupation before and after cooling,
-we perform Raman sideband thermometry.
+In total, $1000$ cooling pulses (total duration $100$ ms) are applied
+along three axes with cooling beginning on the radial second order and axial eighth order.
+To characterize the single atom thermal state before and after cooling,
+we perform Raman sideband thermometry~\cite{Monroe1995, Meekhof1996}.
 For the more tightly confined (non-degenerate) radial directions,
-we observe clear first-order heating, first-order cooling,
-and second-order cooling sidebands before RSC as is shown in red in Figure \ref{f-radial}A.
-After cooling, the first and second order cooling sidebands on both radial axes are suppressed.
-It is important to note that the simple sideband thermometry formula,
-which predicts the ratio of the cooling and heating sideband heights
-to be $\bar n / (\bar n + 1)$~\cite{Monroe1995},
-assumes that the coupling strength for different motional states to be proportional to $\sqrt{n}$.
-However, outside of the LD regime,
-the coupling strength rapidly deviates from this simple scaling rule,
-as shown in figure \ref{f-ld}A. Since the Raman spectroscopy is performed
-with relatively large Raman LD parameters $\eta^R$, we cannot use this formula to
-measure $\bar n$.
-Instead, given the absence of the second order cooling sideband,
-we assume that the atoms are cold enough to have stronger coupling to the first order cooling
-sideband than the second order, i.e. below where the matrix element for the two orders cross,
-in which case the lower bound of the ground state population
-can be computed from the heights of the sidebands by assuming all of the excitations are in the
-$n=1$ state. In doing this, we found a ground state population of $90(2)$\%
-and $94(3)$\% along the two radial directions.
-We also use an independent measurement of Rabi flopping on the carrier (Fig. \ref{f-radial}B)
-and first-order heating(Fig. \ref{f-radial}C) sidebands
-to verify our assumption about the distribution and the ground state population~\cite{Meekhof1996}.
-The data is fitted using the same Monte-Carlo simulation we used to simulate the cooling
-which yields $89(2)$\% and $92(2)$\% and show good agreement with
-the population extracted from the sideband thermometry.
-We also extracted the initial temperature before cooling
-from the motional-state decohered Rabi flopping to obtain the initial temperature of $70 \mu$K.
+we observe clear $\Delta n=1$, $\Delta n=-1$, and $\Delta n=-2$ sidebands before RSC, as is shown in Fig.~\ref{f-radial}A.
+After cooling, the $\Delta n=-1$ and $\Delta n=-2$ sidebands on both radial axes are strongly reduced.
+%It is important to note that the simple sideband thermometry formula, which predicts the ratio of the cooling and heating sideband heights to be $\bar n / (\bar n + 1)$~\cite{Monroe1995}, assumes that the coupling strength for different motional states is proportional to $\sqrt{n}$.
+However, outside of the LD regime, the coupling strength rapidly deviates from this simple scaling rule, as shown in Figure \ref{f-ld}A.
+Since the Raman spectroscopy is performed with relatively large Raman LD parameters $\eta^R$, we cannot use this formula to measure $\bar n$.
+The formula that equates the ratio of $\Delta n=-1$ and $\Delta n=1$ sideband heights to $\bar{n}/(\bar{n}+1)$ ($\bar{n}$ is the mean motional quantum number of the assumed thermal state) was  derived in the LD regime~\cite{Monroe1995}.
+However, it is also valid outside the LD regime.
+The resulting $\bar{n}_x=0.09(3)$ and $\bar{n}_y=0.05(2)$ correspond to ground-state fractions of 92(2)\% and 95(2)\%,  in agreement with fitted values of 89(2)\% and 92(2)\% from the Rabi flopping curves~ \cite{Meekhof1996} in Fig.~\ref{f-radial}B and \ref{f-radial}C.
+%Instead, given the absence of the second order cooling sideband, we assume that the atoms are cold enough to have stronger coupling to the first order cooling sideband than the second order, i.e.
+below where the matrix element for the two orders cross, in which case the lower bound of the ground state population can be computed from the heights of the sidebands by assuming all of the excitations are in the $n=1$ state.
+In doing this, we found a ground state population of $90(2)$\% and $94(3)$\% along the two radial directions.
+We also use measurements of Rabi flopping on the carrier (Fig.
+\ref{f-radial}B) and first-order heating(Fig.
+\ref{f-radial}C) sidebands to verify our assumption about the distribution and the ground state population~\cite{Meekhof1996}.
+The data is fitted using the same Monte-Carlo simulation we used to simulate the cooling which yields $89(2)$\% and $92(2)$\% and show good agreement with the population extracted from the sideband thermometry.
+The initial temperature of $70\,\mu$K before cooling is obtained 
+from the motional-state decohered Rabi flopping.
 
-For the weaker axial direction, cooling is much more challenging
+For the weak axial direction, cooling is challenging
 due to the large $\eta^{\textrm{OP}}_{z,\textrm{eff}}\approx 4.0(2)$.
@@
 which indicates population in highly-excited motional states.
-Nevertheless, our cooling sequence works efficiently as all the cooling sidebands are suppressed
+Nevertheless, our cooling sequence works efficiently as all the cooling sidebands are reduced
 after RSC (Fig.~\ref{f-axial}).
-The ground state population calculated using the ratio of first-order sideband heights yields
-$92(3)$\%. We also perform Rabi flopping on the carrier(Figure~\ref{f-axial}B)
-and extracted a ground state population of $91(2)$\%, in agreement with the other method.
-For the first-order heating sideband Rabi flopping (Figure~\ref{f-axial}C),
-we observed additional decoherence that is more pronounced due to the slower Rabi frequency.
-The decoherence time scale is consistent with magnetic field fluctuations of $1.5$ mG
-that we measure independently in the lab, which produces a Zeeman shift of $\sim 3$ kHz.
+Using the ratio of first-order sideband heights, we obtain $\bar{n}_z=0.07(3)$, which corresponds to the ground state population of 
+93(3)\%, in agreement with a ground state population of 91(2)\% extracted from  Rabi flopping 
+when $\Delta n=0$ (Fig.~\ref{f-axial}B).
+For the $\Delta n=1$ sideband Rabi flopping (Fig.~\ref{f-axial}C),
+we observe additional decoherence that is more pronounced due to the slower Rabi frequency.
+The decoherence rate is consistent with magnetic field fluctuations of $1.5$ mG measured independently in the lab, which would produce a Zeeman shift of $\sim 3$ kHz.
 
 Combining the axial and radial cooling results,
-we have prepared a single Na atom with 3D ground state probability of $77(4)$\%.
-We measured a heating rate of the single atoms in the tweezer to be $67$nK/ms
-due to off-resonant scattering of the trapping light, which
-corresponds to $0.9$\%/ms decrease in ground state population\cite{Grimm2000}.
-The ground state preparation fidelity is currently limited by off-resonant scattering
-from the Raman beams,
-which are measured to be between $3$ to $15$ kHz for the detuning and power we use,
-and the resonance shift caused by magnetic field fluctuations.
+ a single Na atom is in  the 3D ground state  with a probability of 81(4)\% after RSC. 
+ We note that there is an additional 5\% population loss from  imaging  and 10\% loss
+from  high-lying initial motional states that are not efficiently cooled by RSC,
+but instead heated out of the trap by off-resonant scattering from the Raman beams.
+The cooling efficiency is limited by spontaneous scattering rate (3-15 kHz) from the Raman beams, as well as spectral broadening from magnetic field fluctuations and trap anharmonicity.
 
-There is an additional $5$\% loss from finite imaging fidelity and $10$\% loss
-from very high-lying initial motional states that are not efficiently cooled by RSC,
-but instead off-resonantly heated by the Raman beams.
-These give us a $66(3)$\% probability of ground state atom after each successful loading event.
-We are planning to improve these by increasing the detuning of the Raman beams,
-addressing a wider range of trap anharmonicity by frequency sweeps,
-implementing better control of the magnetic field, and optimizing the temperature during imaging.
+We measure a heating rate that corresponds to  decreasing of 3D ground state population of single atoms in the tweezers  of  $\sim0.9$\%/ms. 
+The  rate is consistent with off-resonant scattering of the trapping light~\cite{Grimm2000}, and is predominantly in the axial direction where the trapping beam propagates. 
+%The ground state probability achieved is currently limited by off-resonant scattering from the Raman beams, which are measured to be between $3$ to $15$ kHz for the detuning and power we use, and the resonance shift caused by magnetic field fluctuations.
+
+%Taking into account the population loss, from each successful single atom loading event, we can currently prepared a single \textit{Na} atom in the 3D ground-state with an overall  $66(3)$\% fidelity.
+We expect to reduce atom losses and enhance the ground state probability after RSC
+by increasing the detuning of the Raman beams,
+addressing a wider range of axial trap anharmonicity, % by frequency sweeps,
+implementing better control of the magnetic field, and optimizing imaging.
 Another improvement could be to implement grey molasses cooling to achieve
-a lower starting temperature before RSC\cite{Colzi2016}.
+a lower starting temperature before RSC~\cite{Colzi2016}.
 
-\fxnote{The distinction between 77 and 66 percent is confusing, we should discuss it}
+%\fxnote{The distinction between 77 and 66 percent is confusing, we should discuss it}
 
 We have shown that despite the difficulty in achieving a low optical cooling temperature
-of light mass sodium atoms, reliable three dimensional cooling
+of low mass sodium atoms,  three dimensional cooling
 with significant ground state population can be achieved by using high-order Raman sidebands
@@
 These techniques are well-suited for a large variety of systems
-and open up a route to ground state cooling to other species, including molecules and exotic atoms.
+and open up a route to ground state cooling for other species, including molecules and exotic atoms.
 
-We thank T. Rosenband and J. Hood for valuable discussions.
-This work is supported by the NSF through the Harvard-MIT CUA,
-the AFOSR Young Investigator Program, the Arnold and Mabel Beckman Foundation,
+We thank  J. D. Hood for  discussions.
+This work is supported by the Arnold and Mabel Beckman Foundation, the AFOSR Young Investigator Program, the NSF through the CUA,
 and the Alfred P. Sloan Foundation.

### 2017-08-09 geometry.tex
Polarizations

@@
   \begin{scope}[transform canvas={rotate={4}}]
-    \arrowthreeD{orange}{(0.6, 0)}{-90}{0.4}{3.2};
-    \path (3.4, 0) node[above,orange!80!black] {Raman F2};
-    \path (3, 0) node[below,orange!80!black] {\textbf{R3}};
+    \arrowthreeD{orange}{(0.6, 0)}{-90}{0.4}{3.4};
+    \path (3.33, 0) node[above,orange!80!black] {Raman F2};
+    \path (2.9, 0) node[below,orange!80!black] {\textbf{(R3)}};
   \end{scope}
+  \draw[->,>=stealth,line width=0.8,color=black!60] (4:4.4) -- ++ (90-30:0.3);
+  \draw[->,>=stealth,line width=0.8,color=black!60] (4:4.4) -- ++ (90-30:-0.3);
 
-  \draw[orange!50!black, <->, densely dotted, >=stealth, line width=0.8]
+  \draw[orange!50!black, <->, densely dotted, >=stealth, line width=0.4]
   (3:3.4) arc (3:-32:3.4 and 1.65);
@@
 
+  \draw[line width=0.8,color=black!60] (2.2, -0.25-2.2*0.28) arc (-90:60:0.13 and 0.25);
+  \draw[->,>=stealth,line width=0.8,color=black!60]
+  (-2.24, -0.25+2.24*0.28) arc (-90:40:0.13 and 0.25);
+
   \begin{scope}[transform canvas={cm={1,-0.28,0,1,(0, 0)}}]
+    \draw[->,>=stealth,line width=0.8,color=black!60] (-0.23, 2.2) arc (180:35:0.23 and 0.13);
+    \draw[line width=0.8,color=black!60] (-0.23, -2.2) arc (180:35:0.23 and 0.13);
+
     \draw[blue, dotted, line width=0.5] (-4.0, 0) -- (4.0, 0);
@@
     -- (2.5, -2.7) -- (-2.5, -2.7) -- cycle;
-    \arrowthreeD{red}{(0, -0.4)}{180}{0.4}{1.4};
-    \arrowthreeD{orange}{(-0.4, 0)}{90}{0.4}{1.4};
-    \arrowthreeD{blue}{(0.4, 0)}{-90}{0.4}{1.4};
-    \arrowthreeD{red}{(0, 0.4)}{0}{0.4}{1.4};
-    \path (1.6, 0) node[below,blue!80!black] {OP};
-    \path (-1.6, 0) node[above,orange!80!black] {Raman F2};
-    \path (-1.6, 0) node[below,orange!80!black] {\textbf{R1}};
+    \arrowthreeD{red}{(0, -0.4)}{180}{0.4}{1.6};
+    \arrowthreeD{orange}{(-0.4, 0)}{90}{0.4}{1.6};
+    \arrowthreeD{cyan!40!blue}{(0.4, 0)}{-90}{0.4}{1.6};
+    \arrowthreeD{red}{(0, 0.4)}{0}{0.4}{1.6};
+    \path (1.6, 0) node[below,cyan!20!blue!80!black] {OP};
+    \path (-1.25, 0) node[above,orange!80!black] {Raman F2};
+    \path (-1.6, 0) node[below,orange!80!black] {\textbf{(R1)}};
 
-    \path (0, 1.7) node[left,red!80!black] {Raman F1};
-    \path (0, 1.7) node[right,red!80!black] {\textbf{R2}};
+    \path (0, 1.5) node[left,red!80!black,align=center] {Raman F1\\\textbf{(R2)}};
 
-    \path (0, -1.7) node[left,red!80!black] {\textbf{R4}};
-    \path (0, -1.7) node[right,red!80!black] {Raman F1};
+    \path (0, -1.7) node[right,red!80!black,align=center] {Raman F1\\\textbf{(R4)}};
 
@@
     \path (1.5, 2.4) node[below] {B field};
+
+    \draw[line width=0.8,color=black!60] (-0.23, 2.2) arc (180:330:0.23 and 0.13);
+    \draw[->,>=stealth,line width=0.8,color=black!60] (-0.23, -2.2) arc (180:330:0.23 and 0.13);
   \end{scope}
+
+  \draw[->,>=stealth,line width=0.8,color=black!60]
+  (2.2, -0.25-2.2*0.28) arc (-90:-250:0.13 and 0.25);
+  \draw[line width=0.8,color=black!60]
+  (-2.24, -0.25+2.24*0.28) arc (-90:-240:0.13 and 0.25);
 

### 2017-08-09 geometry.tex
Shorter axis
geometry figure: bigger text

@@
     \arrowthreeD{orange}{(0.6, 0)}{-90}{0.4}{3.4};
-    \path (3.33, 0) node[above,orange!80!black] {Raman F2};
+    \path (3.46, 0) node[above,orange!80!black] {\large Raman F2};
     \path (2.9, 0) node[below,orange!80!black] {\textbf{(R3)}};
@@
 
-    \draw[blue, dotted, line width=0.5] (-4.0, 0) -- (4.0, 0);
+    \draw[blue, dotted, line width=0.5] (-3.0, 0) -- (3.5, 0);
 
@@
     \arrowthreeD{red}{(0, 0.4)}{0}{0.4}{1.6};
-    \path (1.6, 0) node[below,cyan!20!blue!80!black] {OP};
-    \path (-1.25, 0) node[above,orange!80!black] {Raman F2};
+    \path (1.6, 0) node[below,cyan!20!blue!80!black] {\large OP};
+    \path (-1.2, 0) node[above,orange!80!black] {\large Raman F2};
     \path (-1.6, 0) node[below,orange!80!black] {\textbf{(R1)}};
 
-    \path (0, 1.5) node[left,red!80!black,align=center] {Raman F1\\\textbf{(R2)}};
+    \path (0, 1.5) node[left,red!80!black,align=center] {{\large Raman F1}\\\textbf{(R2)}};
 
-    \path (0, -1.7) node[right,red!80!black,align=center] {Raman F1\\\textbf{(R4)}};
+    \path (0, -1.7) node[right,red!80!black,align=center] {{\large Raman F1}\\\textbf{(R4)}};
 
@@
     \draw[->,>=stealth,line width=1.5] (2.2, 2.4) -- (0.8, 2.4);
-    \path (1.51, 2.39) node[below,white,opacity=0.5] {B field};
-    \path (1.5, 2.4) node[below] {B field};
+    \path (1.51, 2.39) node[below,white,opacity=0.5] {\large B field};
+    \path (1.5, 2.4) node[below] {\large B field};
 
@@
 
-  \path (-140:\theight) node[white] {\textbf{Tweezer}};
+  \path (-140:\theight) node[white] {\Large \textbf{Tweezer}};
 \end{tikzpicture}

### 2017-08-09 geometry.tex
New figure 1 version 2 =)

@@
   \fill[left color=red!50!black,right color=red!50!black,middle color=red!43,
-  shading=axis,rotate=-50,shading angle=32]
+  shading=axis,rotate=-45,shading angle=32]
   plot[domain={-1}:{1}, smooth, variable=\y] ({sqrt((\y)^2 + (\waist)^2) * \xscale}, \y * \theight)
@@
   \fill[left color=red!50!black,right color=red!50!black,middle color=red!43,
-  shading=axis,rotate=-50,shading angle=40]
+  shading=axis,rotate=-45,shading angle=40]
   plot[domain={-1}:{0}, smooth, variable=\y] ({sqrt((\y)^2 + (\waist)^2) * \xscale}, \y * \theight)
@@
   arc (180:360:\radiush cm and \radiusv cm);
-  \fill[red!50!gray,rotate=-50]
+  \fill[red!50!gray,rotate=-45]
   ({-sqrt(1 + (\waist)^2) * \xscale}, -\theight*1.05)
@@
 
-  \path (-140:\theight) node[white] {\Large \textbf{Tweezer}};
+  \path (-135:\theight) -- ++(-0.2, 0) node[white] {\Large \textbf{Tweezer}};
 \end{tikzpicture}

### 2017-08-09 plot_rabi_flop.jl
Rabi flop survival -> F1 population

@@ -252,7 +252,7 @@ axhline(0.85, c="C0", ls="-.")
 ylim([0, 1])
 xlim([ts_r3_0[1] * 1e6, ts_r3_0[end] * 1e6])
 xlabel("Time (\$\\mu s\$)")
-ylabel("Survival")
+ylabel("F=1 population")
 text(5, 0.9, "(B)")
 grid()
 maybe_save("$(prefix)_r3_0")
@@ -268,7 +268,7 @@ axhline(0.85, c="C0", ls="-.")
 ylim([0, 1])
 xlim([ts_r3_p1[1] * 1e6, ts_r3_p1[end] * 1e6])
 xlabel("Time (\$\\mu s\$)")
-ylabel("Survival")
+ylabel("F=1 population")
 text(10, 0.9, "(C)")
 grid()
 maybe_save("$(prefix)_r3_p1")
@@ -295,7 +295,7 @@ axhline(0.85, c="C0", ls="-.")
 ylim([0, 1])
 xlim([ts_r2_0[1] * 1e6, ts_r2_0[end] * 1e6])
 xlabel("Time (\$\\mu s\$)")
-ylabel("Survival")
+ylabel("F=1 population")
 text(5, 0.9, "(B)")
 grid()
 maybe_save("$(prefix)_r2_0")
@@ -312,7 +312,7 @@ axhline(0.85, c="C0", ls="-.")
 ylim([0, 1])
 xlim([ts_r2_p1[1] * 1e6, ts_r2_p1[end] * 1e6])
 xlabel("Time (\$\\mu s\$)")
-ylabel("Survival")
+ylabel("F=1 population")
 text(10, 0.9, "(C)")
 grid()
 maybe_save("$(prefix)_r2_p1")
@@ -340,7 +340,7 @@ axhline(0.85, c="C0", ls="-.")
 ylim([0, 1])
 xlim([ts_a1_0[1] * 1e6, ts_a1_0[end] * 1e6])
 xlabel("Time (\$\\mu s\$)")
-ylabel("Survival")
+ylabel("F=1 population")
 text(10, 0.9, "(B)")
 grid()
 maybe_save("$(prefix)_a1_0")
@@ -360,7 +360,7 @@ axhline(0.85, c="C0", ls="-.")
 ylim([0, 1])
 xlim([ts_a1_p1[1] * 1e6, ts_a1_p1[end] * 1e6])
 xlabel("Time (\$\\mu s\$)")
[…]

### 2017-08-09 plot_spectrum.jl
Spectrum survival -> F1 population

@@ -142,7 +142,7 @@ ylim([0, 1])
 xlim([-700, 1500])
 legend()
 xlabel("\$\\delta\$, Detuning from carrier (kHz)")
-ylabel("Survival")
+ylabel("F=1 population")
 
 maybe_save("$(prefix)_r")
 
@@ -163,7 +163,7 @@ xlim([-100, 620])
 legend()
 text(-86, 0.54, "(A)")
 xlabel("\$\\delta\$, Detuning from carrier (kHz)")
-ylabel("Survival")
+ylabel("F=1 population")
 maybe_save("$(prefix)_a1")
 
 maybe_show()

### 2017-08-09 geometry.tex
Bigger font sizes in figure one

@@
   transform canvas={shift={#2}, rotate=#3},shading=axis,shading angle=90]
-  (0,0) -- (80:#4) arc (80:100:#4) -- cycle;
+  (0,0) -- (75:#4) arc (75:105:#4) -- cycle;
   \fill[left color=#1!50!black,right color=#1!50!black,middle color=#1!43,
@@
   transform canvas={shift={#2}, rotate=#3},shading=axis,shading angle=90]
-  (87:#4) -- ++(0, #5) -- ++(-{2 * #4 * sin(3)}, 0) -- (93:#4) -- cycle;
+  (84:#4) -- ++(0, #5) -- ++(-{2 * #4 * sin(6)}, 0) -- (96:#4) -- cycle;
 }
@@
     \arrowthreeD{orange}{(0.6, 0)}{-90}{0.4}{3.4};
-    \path (3.46, 0) node[above,orange!80!black] {\large Raman F2};
-    \path (2.9, 0) node[below,orange!80!black] {\textbf{(R3)}};
+    \path (2.9, 0) node[above,orange!80!black] {\LARGE \textbf{Raman F2}};
+    \path (3.9, 0.45) node[above,orange!80!black] {\LARGE \textbf{(R3)}};
   \end{scope}
-  \draw[->,>=stealth,line width=0.8,color=black!60] (4:4.4) -- ++ (90-30:0.3);
-  \draw[->,>=stealth,line width=0.8,color=black!60] (4:4.4) -- ++ (90-30:-0.3);
+  \draw[->,>=stealth,line width=1.5,color=black!60] (4:4.4) -- ++ (90-30:0.45);
+  \draw[->,>=stealth,line width=1.5,color=black!60] (4:4.4) -- ++ (90-30:-0.5);
 
   \draw[orange!50!black, <->, densely dotted, >=stealth, line width=0.4]
-  (3:3.4) arc (3:-32:3.4 and 1.65);
-  \path (-6:3.3) node[orange!50!black, right] {$42^\circ$};
+  (3:3.8) arc (3:-32:3.8 and 1.85);
+  \path (-8:3.6) node[orange!50!black, right] {\LARGE $42^\circ$};
 
-  \draw[line width=0.8,color=black!60] (2.2, -0.25-2.2*0.28) arc (-90:60:0.13 and 0.25);
-  \draw[->,>=stealth,line width=0.8,color=black!60]
-  (-2.24, -0.25+2.24*0.28) arc (-90:40:0.13 and 0.25);
+  \draw[line width=1.5,color=black!60] (2.6, -0.40-2.6*0.28) arc (-90:60:0.20 and 0.40);
+  \draw[->,>=stealth,line width=1.5,color=black!60]
+  (-3.14, -0.40+3.14*0.28) arc (-90:40:0.20 and 0.40);
 
   \begin{scope}[transform canvas={cm={1,-0.28,0,1,(0, 0)}}]
-    \draw[->,>=stealth,line width=0.8,color=black!60] (-0.23, 2.2) arc (180:35:0.23 and 0.13);
-    \draw[line width=0.8,color=black!60] (-0.23, -2.2) arc (180:35:0.23 and 0.13);
+    \draw[->,>=stealth,line width=1.5,color=black!60] (-0.38, 2.1) arc (180:35:0.38 and 0.20);
+    \draw[line width=1.5,color=black!60] (-0.38, -2.1) arc (180:35:0.38 and 0.20);
 
-    \draw[blue, dotted, line width=0.5] (-3.0, 0) -- (3.5, 0);
+    \draw[blue, dotted, line width=0.5] (0, 0) -- (3.5, 0);
 
-    \fill[blue!50!black,opacity=0.1] (-2.5, 2.7) -- (2.5, 2.7)
-    -- (2.5, -2.7) -- (-2.5, -2.7) -- cycle;
-    \draw[blue!50!black, densely dotted,line width=0.6] (-2.5, 2.7) -- (2.5, 2.7)
-    -- (2.5, -2.7) -- (-2.5, -2.7) -- cycle;
+    \fill[blue!50!black,opacity=0.1] (-3.5, 3.3) -- (3.2, 3.3)
+    -- (3.2, -2.7) -- (-3.5, -2.7) -- cycle;
+    \draw[blue!50!black, densely dotted,line width=0.6] (-3.5, 3.3) -- (3.2, 3.3)
+    -- (3.2, -2.7) -- (-3.5, -2.7) -- cycle;
     \arrowthreeD{red}{(0, -0.4)}{180}{0.4}{1.6};
-    \arrowthreeD{orange}{(-0.4, 0)}{90}{0.4}{1.6};
-    \arrowthreeD{cyan!40!blue}{(0.4, 0)}{-90}{0.4}{1.6};
+    \arrowthreeD{orange}{(-0.4, 0)}{90}{0.4}{2.65};
+    \arrowthreeD{cyan!40!blue}{(0.4, 0)}{-90}{0.4}{2.2};
     \arrowthreeD{red}{(0, 0.4)}{0}{0.4}{1.6};
-    \path (1.6, 0) node[below,cyan!20!blue!80!black] {\large OP};
-    \path (-1.2, 0) node[above,orange!80!black] {\large Raman F2};
-    \path (-1.6, 0) node[below,orange!80!black] {\textbf{(R1)}};
+    \path (1.6, 0) node[below,cyan!20!blue!80!black] {\LARGE \textbf{OP}};
+    \path (-1.8, 0.1) node[above,orange!80!black] {\LARGE \textbf{Raman F2}};
+    \path (-1.8, 0) node[below,orange!80!black] {\LARGE \textbf{(R1)}};
 
-    \path (0, 1.5) node[left,red!80!black,align=center] {{\large Raman F1}\\\textbf{(R2)}};
+    \path (0.2, 2.3)
+    node[left,red!80!black,align=center] {\LARGE \textbf{Raman F1}\\\LARGE \textbf{(R2)}};
+    \path (-0.05, -1.7)
+    node[right,red!80!black,align=center] {\LARGE \textbf{Raman F1}\\\LARGE \textbf{(R4)}};
 
-    \path (0, -1.7) node[right,red!80!black,align=center] {{\large Raman F1}\\\textbf{(R4)}};
+    \draw[white,opacity=0.5,->,>=stealth,line width=2] (2.61, 2.99) -- (0.21, 2.99);
+    \draw[->,>=stealth,line width=2] (2.6, 3.0) -- (0.2, 3.0);
+    \path (1.51, 2.99) node[below,white,opacity=0.5] {\LARGE \textbf{B field}};
+    \path (1.5, 3.0) node[below] {\LARGE \textbf{B field}};
 
-    \draw[white,opacity=0.5,->,>=stealth,line width=1.5] (2.21, 2.39) -- (0.81, 2.39);
-    \draw[->,>=stealth,line width=1.5] (2.2, 2.4) -- (0.8, 2.4);
-    \path (1.51, 2.39) node[below,white,opacity=0.5] {\large B field};
-    \path (1.5, 2.4) node[below] {\large B field};
-
-    \draw[line width=0.8,color=black!60] (-0.23, 2.2) arc (180:330:0.23 and 0.13);
-    \draw[->,>=stealth,line width=0.8,color=black!60] (-0.23, -2.2) arc (180:330:0.23 and 0.13);
+    \draw[line width=1.5,color=black!60] (-0.38, 2.1) arc (180:330:0.38 and 0.20);
+    \draw[->,>=stealth,line width=1.5,color=black!60] (-0.38, -2.1) arc (180:330:0.38 and 0.20);
   \end{scope}
 
-  \draw[->,>=stealth,line width=0.8,color=black!60]
-  (2.2, -0.25-2.2*0.28) arc (-90:-250:0.13 and 0.25);
-  \draw[line width=0.8,color=black!60]
-  (-2.24, -0.25+2.24*0.28) arc (-90:-240:0.13 and 0.25);
+  \draw[->,>=stealth,line width=1.5,color=black!60]
+  (2.6, -0.40-2.6*0.28) arc (-90:-250:0.20 and 0.40);
+  \draw[line width=1.5,color=black!60]
+  (-3.14, -0.40+3.14*0.28) arc (-90:-240:0.20 and 0.40);
 
@@
 
-  \path (-135:\theight) -- ++(-0.2, 0) node[white] {\Large \textbf{Tweezer}};
+  \path (-135:\theight) -- ++(-0.2, 0) node[white,rotate=-5] {\LARGE \textbf{Tweezer}};
 \end{tikzpicture}

### 2017-08-09 plot_raman_op.jl
Use vector form in matrix element plot y label

@@ -170,7 +170,7 @@ plot_sidebands(0:nmax, -1:-1:-5, η_ax)
 xlim([0, nmax])
 ylim([0, 0.75])
 grid()
-ylabel("\$|\\langle n |e^{ikr}| n + \\Delta n \\rangle|\$")
+ylabel("\$|\\langle n |e^{i\\Delta\\vec k\\cdot\\vec z}| n + \\Delta n \\rangle|\$")
 text(0, 0.65, "\$\\Delta n\\!\\!=\\!\\!\\!-\\!1\$", color="C0")
 text(9, 0.55, "\$\\Delta n\\!\\!=\\!\\!\\!-\\!2\$", color="C1")
 text(21, 0.47, "\$\\Delta n\\!\\!=\\!\\!\\!-\\!3\$", color="C2")

### 2017-08-10 paper.tex
New figure 1
New figure 1 version 2 =)
More edits from Kang-Kuen

@@
   large differential light shifts between the excited state and the ground state,
-  we achieve a ground state population of $81(4)$\% after $100$ ms of cooling. In addition, $10\,\%$ of initial atom population escapes the trap during cooling.
-  Our technique includes addressing  high-order sidebands, , where several motional quanta are removed by a single laser pulse,  and
+  we achieve a ground state population of $81(4)$\% after $100$ ms of cooling, for the 85\% of atoms that survive cooling and re-imaging.
+  Our technique includes addressing  high-order sidebands, where several motional quanta are removed by a single laser pulse,  and
   fast modulation of the optical tweezer intensity.
-  We demonstrate that Raman sideband cooling to the 3D motional ground state is possible %outside the Lamb-Dicke regime, 
-  where tight confinement and low initial temperature are difficult to realize.
+  We demonstrate that Raman sideband cooling to the 3D motional ground state is possible, even without  tight confinement and low initial temperature.
 %  This is particularly relevant for systems which are challenging to laser-cool, such as molecules and exotic atoms, and opens up the possibility to gain quantum motional control of these systems.
@@
 
-Extending optical tweezer arrays  to include polar molecules will open up a  range of
+Extending optical tweezer arrays  to include polar molecules will open  a  range of
 new applications that exploit  long-lived molecular internal states
@@
  using Raman sideband cooling (RSC)~\cite{Monroe1995,Kerman2000,Han2000}.
-However, RSC in these systems take place in the Lamb-Dicke (LD) regime, where
-the spread of the initial wavefunctions is much smaller than the wavelength of light used to address them.
-Systems with a large wavefunction, either due to small mass or high initial temperature,
+However, RSC in these systems takes place in the Lamb-Dicke (LD) regime, where
+the spread of the initial wavefunctions is  smaller than the reduced wavelength of light ($\lambdabar$)
+used to address them.
+Systems with a large RMS position spread ($z_{rms}$), either due to small mass or high initial temperature,
 fall outside of the LD regime and undergo strong recoil heating during RSC.
-Extending RSC beyond the LD regime opens  the possibility
-for ground state cooling of systems such as light atoms and %systems with poor cooling such as 
-molecules that can be laser-cooled.
 In this letter we demonstrate cooling of single sodium atoms in optical tweezers,
-initially outside of the LD regime, to the motional ground state.
+initially outside  the LD regime ($z_{rms}/\lambdabar=4.0$), to the motional ground state.
 We achieve a 3D ground state population of $P_0=81(4)$\% by  cooling via
@@
 Our approach is general and applicable to %opens up ground state cooling for
-other systems.
+other systems.  Extending RSC beyond the LD regime opens  the possibility
+for ground state cooling of systems such as light atoms and %systems with poor cooling such as
+molecules that can be laser-cooled.
 
 Our experiment has an overall repetition rate of $2.5$ Hz and
-begins by loading a single sodium atom into optical tweezers from a MOT~\cite{Hutzler2017-LightShifts}.
+begins by loading a single sodium atom into an optical tweezer from a MOT~\cite{Hutzler2017-LightShifts}.
 %for $250$ ms~\cite{Hutzler2017-LightShifts}.
-The tweezers are created by focussing a $700$ nm wavelength laser beam through an NA=$0.55$ objective to an elliptical waist with radii $\{w_{0,x},w_{0,y}\}\approx \{0.79,0.57\}\,\mu$m.
+The tweezer is created by focussing a $700$ nm wavelength laser beam through an NA=$0.55$ objective to an elliptical waist with radii $\{w_{0,x},w_{0,y}\}\approx \{0.79,0.57\}\,\mu$m.
 For $45$ mW of optical power, the trapping frequencies along the three axes are
@@
 and  $x$ and $y$ are the tightly confined radial directions.
-After each single atom loading attempt, an image is taken with a $1.5$ ms exposure time
-to determine success.
+After each single atom loading attempt, a first image is taken with a $1.5$ ms exposure time
+to determine success, which occurs about 50\% of the time due to the loading mechanism~\cite{Schlosser2001}.
+%After attempting to load a single atom from the MOT, an image with 1.5 ms exposure time is taken to determine if the attempt was successful, which occurs about 50% of the time due to the loading mechanism [ref].
 During  imaging, the atom is cooled via polarization gradient cooling (PGC),
@@
 Each experimental cycle ends with a second imaging sequence that measures the hyperfine state of the atom as $|F=2\rangle$ or $|F=1\rangle$~\footnote{The final hyperfine state sensitive detection employs a strong beam that is resonant with the $F=2$ to $F'=3$ cycling transition, to heat the $F=2$ population out of the trap.
-Therefore, any atoms which survive this heat out procedure are interpreted as having been in the $F=1$ state.}.%a repetition of the experiment that was initially bright and remained bright after the pulse sequence is interpreted as a final F=1 atomic state.}.
+Therefore, any atoms which survive this heat out procedure are interpreted as having been in the $F=1$ state.}.
+The data analysis includes only those experiments where the first image  reveals successful atom loading.
+%a repetition of the experiment that was initially bright and remained bright after the pulse sequence is interpreted as a final F=1 atomic state.}.
 
@@
 \begin{figure*}
-  \includegraphics[height=5.2cm]{imgs/Na_RSC_schematic.pdf}
-  \includegraphics[height=4.5cm]{sequence.pdf}
+  \includegraphics[height=4.5cm]{fig1_combined.pdf}
   \caption{Single Na atom Raman sideband cooling scheme and sequence. (A)
@@
 For optical pumping, we use two $\sigma^-$ polarized transitions, one   to  pump the atom state out of $|1,-1\rangle$ via $3^2P_{3/2}$ and one  to pump atoms out of $|2,-1\rangle$ via $3^2P_{1/2}$
-     to minimize heating on the atom in the $|2,-2\rangle$ state.
+     to minimize heating of the $|2,-2\rangle$ state.
     (B) Geometry and polarizations of the Raman and optical pumping beams relative to the
-    optical tweezers and bias magnetic field.
-Raman beams 1 and 4 address the radial $x$ mode.
-Raman beams 1 and 2 address the radial $y$ mode.
-Raman beams 3 and 4 address the axial $z$ mode, which also couples to the radial $y$ mode.
+    optical tweezer and bias magnetic field.
+Raman beams R1 and R4 address the radial $x$-mode.
+R1 and R2 address the radial $y$-mode.
+R3 and R4 address the axial $z$-mode, where the beams also couple to radial motion, but this coupling can be neglected when the atoms is cooled to the ground state of motion.
+%, which also couples to the radial $y$ mode.
+The radial $x$-mode is addressed by turning on beams R1 and R4, $y$ is addressed by R1 and R2, and $z$ is addressed by R3 and R4.
+In this geometry, the radial mode directions coincide with the respective $k$-vector differences.
+The ``axial'' Raman beams also couple to radial motion, but this coupling can be neglected when the atoms is cooled to the ground state of motion.
     (C) Schematic of the cooling pulse sequence. The tweezer is strobed at 3 MHz to
@@
     The two pulses in each radial direction  either address $\Delta n=-2$ and $\Delta n=-1$
-    or have different durations to drive $\Delta n=-1$, when most of the population is below $n=3$
-    at the end of the cooling sequence.
+    or have different durations to drive $\Delta n=-1$, at the end of the cooling sequence when most of the population is below $n=3$.
     The Raman cooling and spectroscopy pulses have Blackman  envelopes to reduce  off-resonant
@@
 
-Specifically, Raman transitions are driven in Na between the hyperfine states
+Specifically, Raman transitions are driven in $^{23}$Na between the hyperfine states
 $|2, -2\rangle$ and $|1, -1\rangle$ in the presence of an $8.8$ G magnetic field. The external field is
@@
 %The OP consists of driving a $|F=1, m_F=-1\rangle$ into the $F=2$ manifold via the transition of $3P_{3/2} D2 line$
-Therefore, to optically pump atoms from $|2,-1\rangle$ into $|2, -2\rangle$, we apply light resonant with  $3^2P_{1/2}$~\footnote{We find a reduction in the scattering rate by a factor of $130(20)$, as compared to using an OP resonant with $3^2P_{3/2}$, from which the $|2, -2>$ state could always scatter a photon via the excited $|F'=3, m_F'=-3>$ state.} because $|2, -2\rangle$ is a dark state to $\sigma^-$-polarized light~\cite{Monroe1995, Grobner2017}.
+Therefore, to optically pump atoms from $|2,-1\rangle$ into $|2, -2\rangle$ while keeping the target state dark, we apply light resonant with  $3^2P_{1/2}$~\cite{Monroe1995, Grobner2017}~\footnote{We find a reduction in the scattering rate by a factor of $130(20)$, as compared to using an OP resonant with $3^2P_{3/2}$, from which the $|2, -2>$ state could always scatter a photon via the excited $|F'=3, m_F'=-3>$ state.}.
 %~\footnote{We find a reduction in the scattering rate by a factor of $130(20)$, as compared to using an OP resonant with $3P_{3/2}$, from which the $|2, -2 \rangle$}
@@
   \includegraphics[width=8.5cm]{imgs/fig2_raman_op.pdf}
-  \caption{Optical pumping motional-state redistribution and  Raman coupling for large  Lamb-Dicke parameters for the axial direction ($z$).
+  \caption{Optical pumping motional-state redistribution and  Raman coupling for large  LD parameters for the axial direction ($z$).
 The range plotted covers $95$\% of the initial thermal distribution.
    % The range plotted covers $95$\% of the initial thermal distribution.
-    (A) Motional state distribution after one optical pumping cycle
-    for different initial n, $n_{\textrm{init}}$. Due to photon-recoil and the large Lamb-Dicke parameter, $\eta^{OP}_z=0.6$,
-    there is a high  $n$ changing probability.         (B) Matrix elements for Raman transition deviate from
-    $\sqrt{n}$ scaling with multiple minima. During cooling, we utilize the fact that higher motional states couple most effectively to sidebands with large $|\Delta n|$.
-    ($k$ is the difference in wave vector of the Raman beams,
-    $r$ is the coordinate in the axial direction).
+    (A) Motional state distribution %averaged over photon emission pattern
+    after one OP cycle
+    for different initial states motion, $n_{\textrm{init}}$. Due to photon-recoil and the large LD parameter, $\eta^{OP}_z=0.6$,
+    there is a high  probability of $n$ changing.         (B) Matrix elements for Raman transition deviate from
+    $\sqrt{n}$ scaling with multiple minima. During cooling, we utilize the fact that high motional states couple most effectively to sidebands with large $|\Delta n|$.
     \label{f-ld}}
@@
 
-For an atom starting in motional level $n_{\textrm{init}}$, the probability of recoil during the OP sequence results in
-a motional-state redistribution  is shown in Fig.~\ref{f-ld}A.
-The  probability is approximately proportional to the square of effective LD parameter
-$\eta^{\textrm{OP}}_{\textrm{eff}}=\sqrt{2n+1}\eta^{\textrm{OP}}$~\cite{Kaufman2012},
-where the optical pumping LD parameter $\eta^{\textrm{OP}} = z_0\frac{2\pi}{\lambda}$ is the ratio of the zero-point wavefunction spread $z_0 = \sqrt{\hbar/2m\omega}$ to the reduced wavelength $\lambda$.
-Here, $m$ is the mass of the atom, $\omega$ is the trap frequency,
-and $\hbar$ is the reduced Planck constant.
-Such heating presents a major challenge for efficient cooling of single Na atoms
-which feature a low mass (23 amu) and short wavelengths.
-For our configuration, 
-$\{\eta^{\textrm{OP}}_x,\eta^{\textrm{OP}}_y,\eta^{\textrm{OP}}_z\} = \{0.241(2), 0.206(1), 0.602(5)\}$.
-A relatively large PGC temperature results in initial $\{\eta^{\textrm{OP}}_{x,\textrm{eff}},\eta^{\textrm{OP}}_{y,\textrm{eff}},\eta^{\textrm{OP}}_{z,\textrm{eff}}\} = \{0.67(2), 0.50(1), 4.0(1)\}$.
-The weak axial direction %, $(\eta^{\textrm{OP}}_{z,\textrm{eff}})^2>1$ 
-is far outside of the LD regime ($\eta^2\ll 1$), and the probability of recoil heating per OP step is large.
-%~\footnote{For example, the average change in the motional states for the initial distribution is $2.4$ in the axial direction, which is significantly greater than $0.89-0.95$in previous experiments of RSC of Rb and Cs~\cite{Li2012,Kaufman2012,Thompson2013,Liu2017}.},
-This creates a large uncertainty on the motional state at the end of a full RSC step, possibly leading to runaway heating.
+%During optical pumping, for an atom starting in motional level $n_{\textrm{init}}$, the probability of recoil to another state $n$ is determined by the squared matrix element $|\langle n_{\textrm{init}}|e^{i \Delta k z}| n\rangle|^2$ and causes motional-state redistribution as shown in Fig.~\ref{f-ld}A.
+Here $\Delta k$ is the wave vector difference between absorbed and emitted photons.
+The LD parameters for OP are $\{\eta^{\textrm{OP}}_x,\eta^{\textrm{OP}}_y,\eta^{\textrm{OP}}_z\} = \{0.241(2), 0.206(1), 0.602(5)\}$.
+As noted already, prior to RSC, the weak axial direction %, $(\eta^{\textrm{OP}}_{z,\textrm{eff}})^2>1$ is far outside of the LD regime, and the probability of recoil per OP step is large, possibly leading to runaway heating.
 
-Fortunately, the large LD parameters also provide opportunities to overcome OP heating.
+%Fortunately, the large LD parameters also provide opportunities to overcome OP heating.
+%The LD parameter for Raman transitions is defined as $\eta^R\equiv\Delta k z_0$,
+%where the wave vector is replaced by the wave vector difference $\Delta k$
+%between the two beams that drive the Raman transition.
+%The Raman transitions in our configuration have LD parameters of
+%$\{\eta^R_x,\eta^R_y,\eta^R_z\} = \{0.341(2), 0.291(1), 0.40(1)\}$.
+%To offset heating from OP initially when $n$ is large, higher-order Raman  sidebands ($\Delta n <-1$)   remove several motional quanta in a single cooling pulse (see Fig.~\ref{f-ld}B).
+%Because the coupling strengths of different orders do not reach minima for the same state of motion $n$,
+%using multiple orders of sidebands avoids accumulations of population
+%near the coupling minima.
+
+During optical pumping, photon recoil can lead to significant heating, especially along the weakly-confined axial direction ($z$).
+For an atom starting in an axial motional level $n_{\textrm{init}}$, the probability to end in another axial state $n$ after absorbing and re-emitting one photon is determined by an angular integral of the squared matrix element $|\langle n_{\textrm{init}}|e^{i \Delta k_{OP} z}| n\rangle|^2$ \cite{ItanoWineland1979}.
+Here $\Delta k_{OP}$ is the wave vector difference between absorbed and emitted photons, projected onto the $z$-axis.
+As shown in Fig.~\ref{f-ld}A, the probability of gaining motional energy during OP grows with $n_{\textrm{init}}$, and is an important effect for sideband-cooling outside the Lamb-Dicke regime.
+
+Fortunately, the large LD parameters in our system also provide opportunities to overcome OP heating.
 The LD parameter for Raman transitions is defined as $\eta^R\equiv\Delta k z_0$,
-where the wave vector is replaced by the wave vector difference $\Delta k$
-between the two beams that drive the Raman transition.
+where $\Delta k$ is the wave vector difference
+between the two beams that drive the Raman transition.  Here $z_0=\sqrt{\hbar/(2 m \omega)}$ is the ground state wavefunction spread ($m$ is the atomic mass).
 The Raman transitions in our configuration have LD parameters of
 $\{\eta^R_x,\eta^R_y,\eta^R_z\} = \{0.341(2), 0.291(1), 0.40(1)\}$.
-To offset heating from OP initially, higher-order Raman  sidebands ($\Delta n <-1$)  can be utilized
-to remove several motional quanta in a single cooling pulse (see Fig.~\ref{f-ld}B).
+To offset heating from OP initially when $n$ is large, higher-order Raman  sidebands ($|\Delta n| > 1$)   remove several motional quanta in a single cooling pulse (see Fig.~\ref{f-ld}B).
 Because the coupling strengths of different orders do not reach minima for the same state of motion $n$,
@@
  into account,
-it is not immediately clear that efficient cooling can be achieved.
+it is not immediately clear that ground-state cooling can be achieved.
 We therefore use a Monte-Carlo simulation to guide our search~\cite{Dalibard1992}.
@@
 and decreasing the orders to the next pair after every $6$ to $15$ cycles.
-This process is repeated until we reach $\Delta n=-1$, and most of the
+This process is repeated until  $\Delta n=-1$, and most of the
 population is in the first few excited states. We then switch to cooling only on $\Delta n=-1$ with two different pulse lengths in order to efficiently cool atoms in the
 few remaining motional states.
-Radial cooling is performed similarly to the axial cooling with the initial cooling of $\Delta n=-2$ and $\Delta n=-1$ and switching to $\Delta n=-1$ only after $20$ to $30$ pulses.
-This sequence gives good initial cooling performance, which can then be used to measure experimental
-parameters, including the Rabi rates of the Raman beams and optical pumping rates,
-in order to optimize the sequence further.
+Radial cooling is performed similarly to  axial cooling with the initial cooling of $\Delta n=-2$ and $\Delta n=-1$ and switching to $\Delta n=-1$ only after $20$ to $30$ pulses.
+This sequence gives good initial cooling performance, which is then used to calibrate experimental
+parameters, including the Rabi rates of the Raman beams and optical pumping rates.
 
 There are two additional important challenges in cooling single sodium atoms.
-First, the high initial temperature populates high motional states,
+First, the  initial temperature populates high motional states,
 causing the atoms to sample the anharmonicity of the trap away from the center.
 Anharmonicity may be defined as $A_{i,n}=(E_{i,n+1}-E_{i,n})/h - \omega_i/(2\pi)$ for each trap axis $i$, and calculated from the quartic term of the optical tweezers via perturbation theory.
-We find $A_{i,n}=\frac{3n \hbar}{4 \pi m d_i^2}$  where $d_i=w_{0,x},w_{0,y}$ for the radial directions and $d_z=\pi w_{0,x}w_{0,y}/\lambda$.
-Numerically, $\{A_{x,n},A_{y,n},A_{z,n}\}=\{1.1, 2.0, 0.16\}n$~kHz.
-For mixed states, this  broadens high-order sidebands due to the $n$-dependence of the transitions.
+In the paraxial approximation, we find $A_{i,n}=\frac{-3n\hbar}{4\pi m d_i^2}$, where $d_i$ equals the beam radius for the radial directions and $d_z\approx\pi w_{0,x}w_{0,y}/\lambda_{\textrm{trap}}$.
+%We find $A_{i,n}=\frac{3n \hbar}{4 \pi m d_i^2}$  where $d_i=w_{0,x},w_{0,y}$ for the radial directions and $d_z\approx \pi w_{0,x}w_{0,y}/\lambda$ for the axial direction.
+Numerically, $\{A_{x,n},A_{y,n},A_{z,n}\}=\{-1.1, -2.0, -0.16\}n$~kHz. For mixed states, this  broadens high-order sidebands due to the $n$-dependence of the transitions.
 In order to mitigate this, we drive the sidebands with a large  Rabi frequency
@@
     (B,C) Rabi flopping on axis $y$ (B) carrier and (C) $\Delta n_y=1$  sideband
-    before (red circle) and after (blue square) cooling.
+    before (red circle) and after (blue square) RSC.
     Solid lines in (B) and (C) are
@@
     The blue lines correspond to a 1D ground state probability of $93$\% after cooling (not including loss) and
-    the red lines correspond to a thermal distribution of $70$ $\mu$K before cooling.
+    the red lines correspond to a thermal distribution of $70$ $\mu$K before RSC.
     %The horizontal dashed line shows the overall survival after cooling and imaging.
@@
     (B,C) Rabi flopping on axial (B) carrier $\Delta n_z=0$  and (C) $\Delta n_z=1$ sideband
-    before (red circle) and after (blue square) cooling.
+    before (red circle) and after (blue square) RSC.
     Solid blue lines in (B) and (C), similar to Fig.~\ref{f-radial}B and C, are fits to  the Rabi flopping and yield  a ground state probability of $92$\% after cooling (not including the 15\% population loss) and
-    the red lines correspond to a thermal distribution of $70$ $\mu$K before cooling.
+    the red lines correspond to a thermal distribution of $70$ $\mu$K before RSC.
     %The blue lines do not take into account the effect of decoherence due to resonance fluctuation.
@@
 while leaving OP on with constant intensity.
-Due to the large light shift, the OP is effectively off whenever the trap light switches back on.
-Since the atom is primarily addressed by  optical pumping light when the trap light is off, OP remains effective.
+Due to the large light shift, the OP is effectively off whenever the trap light is on.
+Since the atom is still addressed by  optical pumping light when the trap light is off, OP remains effective.
 %  However, the selection rules that make the state |2,-2> dark to OP light are only approximately true when the tweezer light is on, and turning off the OP light during this period is expected to reduce spontaneous emission.
@@
 we observe clear $\Delta n=1$, $\Delta n=-1$, and $\Delta n=-2$ sidebands before RSC, as is shown in Fig.~\ref{f-radial}A.
-After cooling, the $\Delta n=-1$ and $\Delta n=-2$ sidebands on both radial axes are strongly reduced.
+After RSC, the $\Delta n=-1$ and $\Delta n=-2$ sidebands on both radial axes are strongly reduced.
 %It is important to note that the simple sideband thermometry formula, which predicts the ratio of the cooling and heating sideband heights to be $\bar n / (\bar n + 1)$~\cite{Monroe1995}, assumes that the coupling strength for different motional states is proportional to $\sqrt{n}$.
@@
 The data is fitted using the same Monte-Carlo simulation we used to simulate the cooling which yields $89(2)$\% and $92(2)$\% and show good agreement with the population extracted from the sideband thermometry.
-The initial temperature of $70\,\mu$K before cooling is obtained 
-from the motional-state decohered Rabi flopping.
+The initial temperature of $70\,\mu$K before RSC is obtained
+from similar fits. %the motional-state decohered Rabi flopping.
 
-For the weak axial direction, cooling is challenging
-due to the large $\eta^{\textrm{OP}}_{z,\textrm{eff}}\approx 4.0(2)$.
+For the weak axial direction, cooling is challenging because the atom starts outside the LD regime.
 We observe up to 8th-order Raman cooling sidebands initially,
 which indicates population in highly-excited motional states.
-Nevertheless, our cooling sequence works efficiently as all the cooling sidebands are reduced
-after RSC (Fig.~\ref{f-axial}).
-Using the ratio of first-order sideband heights, we obtain $\bar{n}_z=0.07(3)$, which corresponds to the ground state population of 
+Nevertheless, our cooling sequence works efficiently as all the $\Delta n<0$ sidebands are reduced
+after RSC (Fig.~\ref{f-axial}A).
+Using the ratio of first-order sideband heights, we obtain $\bar{n}_z=0.07(3)$, which corresponds to a ground state population of
 93(3)\%, in agreement with a ground state population of 91(2)\% extracted from  Rabi flopping
 when $\Delta n=0$ (Fig.~\ref{f-axial}B).
-For the $\Delta n=1$ sideband Rabi flopping (Fig.~\ref{f-axial}C),
+For the $\Delta n=1$ sideband (Fig.~\ref{f-axial}C),
 we observe additional decoherence that is more pronounced due to the slower Rabi frequency.
@@
 
-We measure a heating rate that corresponds to  decreasing of 3D ground state population of single atoms in the tweezers  of  $\sim0.9$\%/ms. 
+We measure a heating rate that corresponds to  decreasing  3D ground state population at a rate  of  $\sim0.9$\%/ms.
 The  rate is consistent with off-resonant scattering of the trapping light~\cite{Grimm2000}, and is predominantly in the axial direction where the trapping beam propagates.

### 2017-08-14 sm.tex
[sm] add frequencies

@@
 that ramps with a Blackman profile during the pulse.
+$\delta'$ is the two photon detuning relative to the zero field HF splitting
+of $1.7716261288(10)$GHz.
+All of the relative detunings are negetive indicating that the frequency difference is smaller
+than the zero field HF splitting.
+A more negative number corresponds to lower order cooling sidebands
+and a more negative number corresponds to higher order ones.
+$\delta'_0$ the relative detuning for the carrier with the specific powers in the Raman beams.
 \subsubsection{Group 1}
@@
 \begin{center}
-  \begin{tabular}{|c|c|c|c|c|}
+  \begin{tabular}{|c|c|c|c|c|c|c|}
     \hline
-    Axis&Order&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
-    $x$&-2&25&$2\pi\times34$&F1\\\hline
-    $y$&-2&25&$2\pi\times34$&F1\\\hline
-    $x$&-1&25&$2\pi\times34$&F1\\\hline
-    $y$&-1&21&$2\pi\times34$&F1\\\hline
+    Axis&Order&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
+    $x$&-2&$-17.6375$&$-18.42$&25&$2\pi\times34$&F1\\\hline
+    $y$&-2&$-17.2825$&$-18.47$&25&$2\pi\times34$&F1\\\hline
+    $x$&-1&$-18.03$&$-18.42$&25&$2\pi\times34$&F1\\\hline
+    $y$&-1&$-17.875$&$-18.47$&21&$2\pi\times34$&F1\\\hline
   \end{tabular}
@@
 \begin{center}
-  \begin{tabular}{|c|c|c|c|c|}
+  \begin{tabular}{|c|c|c|c|c|c|c|}
     \hline
-    Axis&Order&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
-    $z$&-8&80&$2\pi\times14$&\\\hline
-    $x$&-2&25&$2\pi\times34$&F1\\\hline
-    $z$&-7&80&$2\pi\times14$&\\\hline
-    $y$&-2&25&$2\pi\times34$&F1\\\hline
-    $z$&-8&80&$2\pi\times14$&\\\hline
-    $x$&-1&25&$2\pi\times34$&F1\\\hline
-    $z$&-7&80&$2\pi\times14$&\\\hline
-    $y$&-1&21&$2\pi\times34$&F1\\\hline
+    Axis&Order&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
+    $z$&-8&$-17.966$&$-18.506$&80&$2\pi\times14$&\\\hline
+    $x$&-2&$-17.6375$&$-18.42$&25&$2\pi\times34$&F1\\\hline
+    $z$&-7&$-18.0335$&$-18.506$&80&$2\pi\times14$&\\\hline
+    $y$&-2&$-17.2825$&$-18.47$&25&$2\pi\times34$&F1\\\hline
+    $z$&-8&$-17.966$&$-18.506$&80&$2\pi\times14$&\\\hline
+    $x$&-1&$-18.03$&$-18.42$&25&$2\pi\times34$&F1\\\hline
+    $z$&-7&$-18.0335$&$-18.506$&80&$2\pi\times14$&\\\hline
+    $y$&-1&$-17.875$&$-18.47$&21&$2\pi\times34$&F1\\\hline
   \end{tabular}
@@
 \begin{center}
-  \begin{tabular}{|c|c|c|c|c|}
+  \begin{tabular}{|c|c|c|c|c|c|c|}
     \hline
-    Axis&Order&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
-    $z$&-7&80&$2\pi\times14$&\\\hline
-    $x$&-2&25&$2\pi\times34$&F1\\\hline
-    $z$&-6&80&$2\pi\times14$&\\\hline
-    $y$&-2&25&$2\pi\times34$&F1\\\hline
-    $z$&-7&80&$2\pi\times14$&\\\hline
-    $x$&-1&25&$2\pi\times34$&F1\\\hline
-    $z$&-6&80&$2\pi\times14$&\\\hline
-    $y$&-1&21&$2\pi\times34$&F1\\\hline
+    Axis&Order&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
+    $z$&-7&$-18.0335$&$-18.506$&80&$2\pi\times14$&\\\hline
+    $x$&-2&$-17.6375$&$-18.42$&25&$2\pi\times34$&F1\\\hline
+    $z$&-6&$-18.101$&$-18.506$&80&$2\pi\times14$&\\\hline
+    $y$&-2&$-17.2825$&$-18.47$&25&$2\pi\times34$&F1\\\hline
+    $z$&-7&$-18.0335$&$-18.506$&80&$2\pi\times14$&\\\hline
+    $x$&-1&$-18.03$&$-18.42$&25&$2\pi\times34$&F1\\\hline
+    $z$&-6&$-18.101$&$-18.506$&80&$2\pi\times14$&\\\hline
+    $y$&-1&$-17.875$&$-18.47$&21&$2\pi\times34$&F1\\\hline
   \end{tabular}
@@
 \begin{center}
-  \begin{tabular}{|c|c|c|c|c|}
+  \begin{tabular}{|c|c|c|c|c|c|c|}
     \hline
-    Axis&Order&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
-    $z$&-6&80&$2\pi\times14$&\\\hline
-    $x$&-2&25&$2\pi\times34$&F1\\\hline
-    $z$&-5&60&$2\pi\times14$&\\\hline
-    $y$&-2&25&$2\pi\times34$&F1\\\hline
-    $z$&-6&80&$2\pi\times14$&\\\hline
-    $x$&-1&25&$2\pi\times34$&F1\\\hline
-    $z$&-5&60&$2\pi\times14$&\\\hline
-    $y$&-1&21&$2\pi\times34$&F1\\\hline
+    Axis&Order&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
+    $z$&-6&$-18.101$&$-18.506$&80&$2\pi\times14$&\\\hline
+    $x$&-2&$-17.6375$&$-18.42$&25&$2\pi\times34$&F1\\\hline
+    $z$&-5&$-18.1685$&$-18.506$&60&$2\pi\times14$&\\\hline
+    $y$&-2&$-17.2825$&$-18.47$&25&$2\pi\times34$&F1\\\hline
+    $z$&-6&$-18.101$&$-18.506$&80&$2\pi\times14$&\\\hline
+    $x$&-1&$-18.03$&$-18.42$&25&$2\pi\times34$&F1\\\hline
+    $z$&-5&$-18.1685$&$-18.506$&60&$2\pi\times14$&\\\hline
+    $y$&-1&$-17.875$&$-18.47$&21&$2\pi\times34$&F1\\\hline
   \end{tabular}
@@
 \begin{center}
-  \begin{tabular}{|c|c|c|c|c|}
+  \begin{tabular}{|c|c|c|c|c|c|c|}
     \hline
-    Axis&Order&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
-    $z$&-5&90&$2\pi\times17$&F2\\\hline
-    $x$&-1&38&$2\pi\times34$&F1\\\hline
-    $z$&-4&75&$2\pi\times17$&F2\\\hline
-    $y$&-1&25&$2\pi\times34$&F1\\\hline
-    $z$&-5&90&$2\pi\times17$&F2\\\hline
-    $x$&-1&43&$2\pi\times34$&F1\\\hline
-    $z$&-4&75&$2\pi\times17$&F2\\\hline
-    $y$&-1&28&$2\pi\times34$&F1\\\hline
+    Axis&Order&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
+    $z$&-5&$-18.1685$&$-18.506$&90&$2\pi\times17$&F2\\\hline
+    $x$&-1&$-18.03$&$-18.42$&38&$2\pi\times34$&F1\\\hline
+    $z$&-4&$-18.236$&$-18.506$&75&$2\pi\times17$&F2\\\hline
+    $y$&-1&$-17.875$&$-18.47$&25&$2\pi\times34$&F1\\\hline
+    $z$&-5&$-18.1685$&$-18.506$&90&$2\pi\times17$&F2\\\hline
+    $x$&-1&$-18.03$&$-18.42$&43&$2\pi\times34$&F1\\\hline
+    $z$&-4&$-18.236$&$-18.506$&75&$2\pi\times17$&F2\\\hline
+    $y$&-1&$-17.875$&$-18.47$&28&$2\pi\times34$&F1\\\hline
   \end{tabular}
@@
 \begin{center}
-  \begin{tabular}{|c|c|c|c|c|}
+  \begin{tabular}{|c|c|c|c|c|c|c|}
     \hline
-    Axis&Order&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
-    $z$&-4&75&$2\pi\times17$&F2\\\hline
-    $x$&-1&38&$2\pi\times34$&F1\\\hline
-    $z$&-3&60&$2\pi\times17$&F2\\\hline
-    $y$&-1&25&$2\pi\times34$&F1\\\hline
-    $z$&-4&75&$2\pi\times17$&F2\\\hline
-    $x$&-1&43&$2\pi\times34$&F1\\\hline
-    $z$&-3&60&$2\pi\times17$&F2\\\hline
-    $y$&-1&28&$2\pi\times34$&F1\\\hline
+    Axis&Order&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
+    $z$&-4&$-18.236$&$-18.506$&75&$2\pi\times17$&F2\\\hline
+    $x$&-1&$-18.03$&$-18.42$&38&$2\pi\times34$&F1\\\hline
+    $z$&-3&$-18.3035$&$-18.506$&60&$2\pi\times17$&F2\\\hline
+    $y$&-1&$-17.875$&$-18.47$&25&$2\pi\times34$&F1\\\hline
+    $z$&-4&$-18.236$&$-18.506$&75&$2\pi\times17$&F2\\\hline
+    $x$&-1&$-18.03$&$-18.42$&43&$2\pi\times34$&F1\\\hline
+    $z$&-3&$-18.3035$&$-18.506$&60&$2\pi\times17$&F2\\\hline
+    $y$&-1&$-17.875$&$-18.47$&28&$2\pi\times34$&F1\\\hline
   \end{tabular}
@@
 \begin{center}
-  \begin{tabular}{|c|c|c|c|c|}
+  \begin{tabular}{|c|c|c|c|c|c|c|}
     \hline
-    Axis&Order&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
-    $z$&-3&60&$2\pi\times17$&F2\\\hline
-    $x$&-1&38&$2\pi\times34$&F1\\\hline
-    $z$&-2&60&$2\pi\times17$&F2\\\hline
-    $y$&-1&25&$2\pi\times34$&F1\\\hline
-    $z$&-3&60&$2\pi\times17$&F2\\\hline
-    $x$&-1&43&$2\pi\times34$&F1\\\hline
-    $z$&-2&60&$2\pi\times17$&F2\\\hline
-    $y$&-1&28&$2\pi\times34$&F1\\\hline
+    Axis&Order&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
+    $z$&-3&$-18.3035$&$-18.506$&60&$2\pi\times17$&F2\\\hline
+    $x$&-1&$-18.03$&$-18.42$&38&$2\pi\times34$&F1\\\hline
+    $z$&-2&$-18.371$&$-18.506$&60&$2\pi\times17$&F2\\\hline
+    $y$&-1&$-17.875$&$-18.47$&25&$2\pi\times34$&F1\\\hline
+    $z$&-3&$-18.3035$&$-18.506$&60&$2\pi\times17$&F2\\\hline
+    $x$&-1&$-18.03$&$-18.42$&43&$2\pi\times34$&F1\\\hline
+    $z$&-2&$-18.371$&$-18.506$&60&$2\pi\times17$&F2\\\hline
+    $y$&-1&$-17.875$&$-18.47$&28&$2\pi\times34$&F1\\\hline
   \end{tabular}
@@
 \begin{center}
-  \begin{tabular}{|c|c|c|c|c|}
+  \begin{tabular}{|c|c|c|c|c|c|c|}
     \hline
-    Axis&Order&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
-    $z$&-2&60&$2\pi\times17$&F2\\\hline
-    $x$&-1&38&$2\pi\times34$&F1\\\hline
-    $z$&-1&60&$2\pi\times17$&F2\\\hline
-    $y$&-1&25&$2\pi\times34$&F1\\\hline
-    $z$&-2&60&$2\pi\times17$&F2\\\hline
-    $x$&-1&43&$2\pi\times34$&F1\\\hline
-    $z$&-1&60&$2\pi\times17$&F2\\\hline
-    $y$&-1&28&$2\pi\times34$&F1\\\hline
+    Axis&Order&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
+    $z$&-2&$-18.371$&$-18.506$&60&$2\pi\times17$&F2\\\hline
+    $x$&-1&$-18.03$&$-18.42$&38&$2\pi\times34$&F1\\\hline
+    $z$&-1&$-18.4385$&$-18.506$&60&$2\pi\times17$&F2\\\hline
+    $y$&-1&$-17.875$&$-18.47$&25&$2\pi\times34$&F1\\\hline
+    $z$&-2&$-18.371$&$-18.506$&60&$2\pi\times17$&F2\\\hline
+    $x$&-1&$-18.03$&$-18.42$&43&$2\pi\times34$&F1\\\hline
+    $z$&-1&$-18.4385$&$-18.506$&60&$2\pi\times17$&F2\\\hline
+    $y$&-1&$-17.875$&$-18.47$&28&$2\pi\times34$&F1\\\hline
   \end{tabular}
@@
 \begin{center}
-  \begin{tabular}{|c|c|c|c|c|}
+  \begin{tabular}{|c|c|c|c|c|c|c|}
     \hline
-    Axis&Order&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
-    $z$&-1&70&$2\pi\times9$&F2\\\hline
-    $z$&-1&100&$2\pi\times9$&F2\\\hline
-    $x$&-1&38&$2\pi\times34$&F1\\\hline
-    $z$&-1&70&$2\pi\times9$&F2\\\hline
-    $z$&-1&100&$2\pi\times9$&F2\\\hline
-    $y$&-1&25&$2\pi\times34$&F1\\\hline
-    $z$&-1&70&$2\pi\times9$&F2\\\hline
-    $z$&-1&100&$2\pi\times9$&F2\\\hline
-    $x$&-1&43&$2\pi\times34$&F1\\\hline
-    $z$&-1&70&$2\pi\times9$&F2\\\hline
-    $z$&-1&100&$2\pi\times9$&F2\\\hline
-    $y$&-1&28&$2\pi\times34$&F1\\\hline
+    Axis&Order&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
+    $z$&-1&$-18.3615$&$-18.429$&70&$2\pi\times9$&F2\\\hline
+    $z$&-1&$-18.3615$&$-18.429$&100&$2\pi\times9$&F2\\\hline
+    $x$&-1&$-18.03$&$-18.42$&38&$2\pi\times34$&F1\\\hline
+    $z$&-1&$-18.3615$&$-18.429$&70&$2\pi\times9$&F2\\\hline
+    $z$&-1&$-18.3615$&$-18.429$&100&$2\pi\times9$&F2\\\hline
+    $y$&-1&$-17.875$&$-18.47$&25&$2\pi\times34$&F1\\\hline
+    $z$&-1&$-18.3615$&$-18.429$&70&$2\pi\times9$&F2\\\hline
+    $z$&-1&$-18.3615$&$-18.429$&100&$2\pi\times9$&F2\\\hline
+    $x$&-1&$-18.03$&$-18.42$&43&$2\pi\times34$&F1\\\hline
+    $z$&-1&$-18.3615$&$-18.429$&70&$2\pi\times9$&F2\\\hline
+    $z$&-1&$-18.3615$&$-18.429$&100&$2\pi\times9$&F2\\\hline
+    $y$&-1&$-17.875$&$-18.47$&28&$2\pi\times34$&F1\\\hline
   \end{tabular}

### 2017-08-14 paper.tex
Kang-Kuen's edit and white space fix

@@
 
-%Systems of trapped neutral atoms assembled from the bottom-up in an array of optical tweezers are a promising  platform to study quantum information and quantum simulations~
+% Systems of trapped neutral atoms assembled from the bottom-up in an array of optical tweezers are a promising platform to study quantum information and quantum simulations~
 Trapped neutral atoms, assembled in an array of optical tweezers, are a promising platform to study quantum information and quantum simulations~
@@
 used to address them.
-Systems with a large RMS position spread ($z_{rms}$), either due to small mass or high initial temperature,
+Systems with a large position spread ($z_{rms}$), either due to small mass or high initial temperature,
 fall outside of the LD regime and undergo strong recoil heating during RSC.
@@
   \includegraphics[width=8.5cm]{imgs/fig2_raman_op.pdf}
-  \caption{Optical pumping motional-state redistribution and  Raman coupling for large  LD parameters for the axial direction ($z$).
-The range plotted covers $95$\% of the initial thermal distribution.
+  \caption{Optical pumping motional-state redistribution and Raman coupling for large LD parameters for the axial direction ($z$). The range plotted covers $95$\% of the initial thermal distribution.
    % The range plotted covers $95$\% of the initial thermal distribution.
@@
 During optical pumping, photon recoil can lead to significant heating, especially along the weakly-confined axial direction ($z$).
-For an atom starting in an axial motional level $n_{\textrm{init}}$, the probability to end in another axial state $n$ after absorbing and re-emitting one photon is determined by an angular integral of the squared matrix element $|\langle n_{\textrm{init}}|e^{i \Delta k_{OP} z}| n\rangle|^2$ \cite{ItanoWineland1979}.
+For an atom starting in an axial motional level $n_{\textrm{init}}$, the probability to end in another axial state $n$ after absorbing and re-emitting one photon is approximated by an angular integral of the squared matrix element $|\langle n_{\textrm{init}}|e^{i \Delta k_{OP} z}| n\rangle|^2$ \cite{ItanoWineland1979}.
 Here $\Delta k_{OP}$ is the wave vector difference between absorbed and emitted photons, projected onto the $z$-axis.
@@
 but instead heated out of the trap by off-resonant scattering from the Raman beams.
-The cooling efficiency is limited by spontaneous scattering rate (3-15 kHz) from the Raman beams, as well as spectral broadening from magnetic field fluctuations and trap anharmonicity.
+The cooling efficiency is limited by spontaneous scattering rate (0.5-1 kHz) from the Raman beams, as well as spectral broadening from magnetic field fluctuations and trap anharmonicity.
 

### 2017-08-14 paper.tex
SM update and other fixup

@@
     or have different durations to drive $\Delta n=-1$, at the end of the cooling sequence when most of the population is below $n=3$.
-    The Raman cooling and spectroscopy pulses have Blackman envelopes to reduce off-resonant
-    coupling, while the measurement Rabi pulses in Fig.~\ref{f-radial}(B,C) and \ref{f-axial}(B,C) have square envelopes to simplify analysis.
+    The Raman cooling and spectroscopy pulses have Blackman envelopes~\cite{Kasevich1992}
+    to reduce off-resonant coupling,
+    while the measurement Rabi pulses in Fig.~\ref{f-radial}(B,C) and \ref{f-axial}(B,C)
+    have square envelopes to simplify analysis.
     \label{f-setup}}
@@
 %The OP consists of driving a $|F=1, m_F=-1\rangle$ into the $F=2$ manifold via the transition of $3P_{3/2} D2 line$
-Therefore, to optically pump atoms from $|2,-1\rangle$ into $|2, -2\rangle$ while keeping the target state dark, we apply light resonant with $3^2P_{1/2}$~\cite{Monroe1995, Grobner2017}~\footnote{We find a reduction in the scattering rate by a factor of $130(20)$, as compared to using an OP resonant with $3^2P_{3/2}$, from which the $|2, -2>$ state could always scatter a photon via the excited $|F'=3, m_F'=-3>$ state.}.
+Therefore, to optically pump atoms from $|2,-1\rangle$ into $|2, -2\rangle$ while keeping the target state dark, we apply light resonant with $3^2P_{1/2}$~\cite{Monroe1995, Grobner2017}~\footnote{We find a reduction in the scattering rate by a factor of $130(20)$, as compared to using an OP resonant with $3^2P_{3/2}$, from which the $|2, -2>$ state could always scatter a photon via the excited $|F'=3, m_{F'}=-3>$ state.}.
 %~\footnote{We find a reduction in the scattering rate by a factor of $130(20)$, as compared to using an OP resonant with $3P_{3/2}$, from which the $|2, -2 \rangle$}

### 2017-08-14 sm.tex
[sm] Update author list
Kang-Kuen's edit and white space fix
SM update and other fixup

@@
 \begin{document}
-\title{Motional Quantum Ground-State Cooling Outside the Lamb-Dicke Regime -- Supplemental material}
-\author{Yichao Yu}
+\title{Motional Ground-State Cooling Outside the Lamb-Dicke Regime -- Supplemental material}
+\author{Y. Yu}
 \email{yichaoyu@g.harvard.edu}
-\author{Nicholas R. Hutzler}
+\author{N. R. Hutzler}
 \altaffiliation{Present address: California Institute of Technology, Division of Physics, Mathematics, and Astronomy. Pasadena, CA, 91125}
-\author{Jessie T. Zhang}
-\author{Lee R. Liu}
-\author{Kang-Kuen Ni}
+\author{J. T. Zhang}
+\author{L. R. Liu}
+\author{T. Rosenband}
+\author{K.-K. Ni}
 \email{ni@chemistry.harvard.edu}
@@
 
-\section{Simulation of 3D Raman sideband cooling}
-
-We use a computer simulation to study the importance of different effects
-and guide the optimization of Raman sideband cooling.
-The simulation uses the quantum jump (or Monte-Carlo wavefunction) method~\cite{Dalibard1992,Chretien2014}
-to accurately calculate the evolution within each laser pulse where different energy eigenstates
-are assumed to decohere immediately upon spontaneous emission and on pulse boundaries.
-Such approximations are valid and greatly simplify the computation
-at the cost of limiting the applicability of the simulation to processes that require stronger
-coherence, such as Ramsey spectroscopy or rapid push-out of the atoms from the trap
-(faster than a trap oscillation period).
-
-A number of other simplifying approximations, listed below, are also used in the simulation.
-These either have a demonstrably negligible effect on the experiment,
-or result in a significant reduction of complexity for an effect
-that can be optimized more easily in the experiment.
-
-\begin{enumerate}
-\item \emph{All Raman pulses resonantly drive only one sideband/carrier order.}  We tweak the pulse shape, power and length as discussed in the text, for example by using Blackman pulses, to reduce coupling to other orders.
-We do see deviation from this approximation in the experiment, though mostly in the long detection pulses, and it is less of a concern for the short cooling pulses.
-\item \emph{No heating from other sources.}\\
-  We measured the heating rate and found that it results mainly from off-resonant scattering
-  of photons, which is included in the simulation.  In particular, we can ignore heating from the switching trap.
-\item \emph{Same trapping frequency for all states.}\\
-  This effect is negligible for Na in the ground state due to the small fine structure splitting in the excited state.
-  It is straightforward to include this effect if the calculation needs to be repeated
-  on a system where this is not the case (e.g. directly laser cooled molecules).
-\end{enumerate}
-
-Some effects that are important to include are all three dimensions (3D motional states,
-accurate 3D wavevector, and different emission pattern for different photon polarizations),
-off-resonant scattering from all laser beams, and optical pumping polarization imperfection.
-The optical pumping polarization and off-resonant scattering are especially important
-for accurate simulation since they are the main limitation on cooling performance.
-
-In general, each pulse has a coherent part from the Raman drive
-(which is absent for the optical pumping pulses)
-and an incoherent part from scattering (optical pumping or off-resonant).
-This nicely fits the general approach of the quantum jump method.
-Due to the large number of states that we need to take into account
-($30-150$ motional per axis and $8$ hyperfine, giving a total of $10^6$),
-generic wavefunction propagation is very inefficient.
-Therefore, we further simplify by reducing the number of states tracked during
-the coherent propagation and applying quantum jumps using a set of reduced jump operators that
-describe the total jump probability from a certain state (summed over all final states).
-The coherent propagation is then accurately solved in order to avoid having to use a time step
-much shorter than the inverse of scattering rate (up to hundreds of kHz)\footnote{\href{https://goo.gl/EZ13wt}{note about modification to the quantum jump method (https://goo.gl/EZ13wt)}}.
-
-In order to simulate a pulse, we first start with the coherent propagation that includes the
-modification from the jump operators as in the quantum jump method.
-When a jump happens, we pick a final internal state to jump to based on the relative rates
-of different scattering sources and their branching ratios.
-This process determines the polarization and emission pattern of the emitted photon,
-from which we randomly sample a particular wave vector.
-The photon recoil being defined, we can then assign a final motional state to the atom.
-This process is then repeated as long as the pulse is on,
-before we start to simulate the next pulse.
-
-We apply ``virtual'' measurements on the results of each simulated cooling sequence
-which we then average to obtain the expected value of experimental quantities.
-Due to the decoherence approximation, the measurement has to commute with the Hamiltonian.
-Particularly useful measurements used in our simulation are hyperfine state distribution,
-average motional energy, loss rate (where an atom is assumed to be lost if its motional energy
-goes above a certain threshold at any time) probability of being in certain states
-(e.g. ground state).
-
-\begin{figure}[t]
-  \includegraphics[width=8.5cm]{imgs/simcool_no_scatter.pdf}
-  \caption{Simulated 3D ground state population as a function of cooling cycles without
-    technical imperfections. The ground state probability reaches $>99\%$. \label{f-no-scatter}}
-\end{figure}
-\begin{figure}[t]
-  \includegraphics[width=8.5cm]{imgs/simcool_real.pdf}
-  \caption{Simulated 3D ground state population as a function of cooling cycles including effect of
-    off-resonant scattering from all beams and OP misalignment.
-    For this particular sequence, the ground state probability saturates to $\approx88\%$.
-    \label{f-real}}
-\end{figure}
-
-If off-resonant scattering and optical pumping polarization misalignment are ignored,
-the simulation shows that there is not a cooling limit
-despite the large Lamb-Dicke parameter and high initial temperature (Fig \ref{f-no-scatter}).
-However, when these effects are taken into account, the ground state probability can saturate at
-a lower value (Fig \ref{f-real}) and require much more careful tweaking.
-The change of slop in these plots corresponds to changing the sideband orders used for cooling.
-
-The simulation is written in Julia\cite{Bezanson2017}.
-All code is available under the GPLv3 license at
-\footnote{\href{https://goo.gl/WLJwJp}{Library code (https://goo.gl/WLJwJp)}} and
-\footnote{\href{https://goo.gl/XXVreq}{Top level code (https://goo.gl/XXVreq)}}
-
-\section{Cooling sequence}
+\section{Raman Sideband Cooling Pulse Sequence}
 
 \subsection{Optical pumping parameters}
-All optical pumping pulses has the same length of $40\mu$s
+The optical pumping is done with a $\sigma^-$ polarized beam aligned with the bias magnetic field.
+There are two frequencies in the beam that are on resonance with
+the $|F=2,m_F=-1\rangle$ to $|F'=2,m_{F'}=-2\rangle$ D1 transition
+and the $|F=1,m_F=-1\rangle$ to $|F'=2,m_{F'}=-2\rangle$ D2 transition respectively.
+All optical pumping pulses have the same length of $40\mu$s
 with a $|F=1,m_F=-1\rangle$ scattering rate of $0.14$ MHz
@@
 the beam (in terms of their corresponding $F$ number)
-that ramps with a Blackman profile during the pulse.
-$\delta'$ is the two photon detuning relative to the zero field HF splitting
+that ramps with a Blackman profile during the pulse~\cite{Kasevich1992}.
+$\delta'$ is the two photon detuning relative to the zero field hyperfine splitting
 of $1.7716261288(10)$GHz.
 All of the relative detunings are negetive indicating that the frequency difference is smaller
-than the zero field HF splitting.
+than the zero field hyperfine splitting.
 A more negative number corresponds to lower order cooling sidebands

### 2017-08-14 sm.tex
SM update

@@
 
-\section{Raman Sideband Cooling Pulse Sequence}
+\section{Raman Sideband Cooling Pulse Parameters and Sequence}
+Here, we list the full Raman sideband cooling (RSC) pulse  parameters and  sequence used to obtain the result in [our paper].
+A step of RSC contains a Raman pulse and an optical pumping pulse.
+The full RSC sequence includes about 1000 pulses in 100 ms.
 
 \subsection{Optical pumping parameters}
-The optical pumping is done with a $\sigma^-$ polarized beam aligned with the bias magnetic field.
-There are two frequencies in the beam that are on resonance with
-the $|F=2,m_F=-1\rangle$ to $|F'=2,m_{F'}=-2\rangle$ D1 transition
-and the $|F=1,m_F=-1\rangle$ to $|F'=2,m_{F'}=-2\rangle$ D2 transition respectively.
-All optical pumping pulses have the same length of $40\mu$s
-with a $|F=1,m_F=-1\rangle$ scattering rate of $0.14$ MHz
-and a $|F=2,m_F=-1\rangle$ scattering rate of $0.39$ MHz.
+The optical pumping is performed with a $\sigma^-$-polarized beam aligned with an 8.8 G bias magnetic field.
+There are two frequencies in the beam: one is on resonance with
+the $|F=2,m_F=-1\rangle$ of $3^2S_{1/2}$ to $|F'=2,m_{F'}=-2\rangle$ of $3^2P_{1/2}$ D1 transition
+and the other is on resonance with the $|F=1,m_F=-1\rangle$ of $3^2S_{1/2}$ to $|F'=2,m_{F'}=-2\rangle$ of $3^2P_{3/2}$ D2 transition.
+All optical pumping pulses have the  length of $40\,\mu$s
+with a  scattering rate of $0.14$ MHz for atoms in $|F=1,m_F=-1\rangle$
+and a  scattering rate of $0.39$ MHz for atoms in $|F=2,m_F=-1\rangle$.
 
 \subsection{Raman pulse parameters}
-Each of the Raman pulse in the cooling sequence is followed immediately by an optical pumping
-pulse with the parameters given above.
-The parameters for the Raman pulses are different between different groups and are listed below.
-The full Rabi frequency is the two-photon Rabi frequency $\Omega$ excluding the matrix element
-from wavefunction overlap.
+Each Raman pulse in the cooling sequence is followed immediately by an optical pumping
+pulse.
+The full parameters  for the Raman pulses, including the cooling ``axis'', the sideband ``order ($\Delta n$)'', the cooling frequency ``$\delta '$", the carrier ($\Delta n=0$) frequency ``$\delta_0'$'', the pulse ``duration'', the pulse strength in ``full Rabi frequency'', and the beam of which a non-uniform ``power ramp'' is applied,   are  listed in 9 groups below.
+The applied cooling frequency, $\delta'$,  is the two-photon detuning given relative to the zero-field $F=1$ and $F=2$ hyperfine splitting
+of $1.7716261288(10)$GHz[cite].
+%All of the relative detunings are negative indicating that the frequency difference is smaller than the zero-field hyperfine splitting. Higher-order sidebands for cooling
+%A more negative number corresponds to lower order cooling sidebands
+%and a more negative number corresponds to higher order ones.
+Due to the Stark shifts of the Raman beams, the carrier  transition, $\delta'_0$, varies with the power of the Raman beams. $\delta'_0$ is given also relative to the zero-field  hyperfine splitting.
+The strength of the pulses given in ``Full Rabi frequency'' is the measured two-photon Rabi frequency $\Omega$ divided by the wave function overlap for each order of cooling.
+The difference between $\delta'$ and $\delta'_0$ gives the motional sideband frequency, $\delta$.
+%The full Rabi frequency is given as the two-photon Rabi frequency $\Omega$ including only electronic dipole matrix element excluding the matrix element
+%from wavefunction overlap.
+Many Raman pulses include a ``power ramp'' with a Blackman envelope~\cite{Kasevich1992} to minimize off-resonant excitations.
+Because each Raman pulse is a product of two spatial- and temporal-overlapped laser beams, the ``power ramp'' is applied only to one of the beams for simplicity (we label the beam by the corresponding $F$ number) while the other beam has  a square-pulse shape.
 For a Raman pulse with a power ramp,
 the full Rabi frequency gives the arithmetics mean over the duration of the pulse.
-The power ramp field gives, if any,
-the beam (in terms of their corresponding $F$ number)
-that ramps with a Blackman profile during the pulse~\cite{Kasevich1992}.
-$\delta'$ is the two photon detuning relative to the zero field hyperfine splitting
-of $1.7716261288(10)$GHz.
-All of the relative detunings are negetive indicating that the frequency difference is smaller
-than the zero field hyperfine splitting.
-A more negative number corresponds to lower order cooling sidebands
-and a more negative number corresponds to higher order ones.
-$\delta'_0$ the relative detuning for the carrier with the specific powers in the Raman beams.
+
+%The power ramp field gives, if any,
+%the beam (in terms of their corresponding $F$ number)
+%that ramps with a Blackman profile during the pulse~\cite{Kasevich1992}.
+\newpage
+
 \subsubsection{Group 1}
@@
     \hline
-    Axis&Order&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
+    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
     $x$&-2&$-17.6375$&$-18.42$&25&$2\pi\times34$&F1\\\hline
@@
     \hline
-    Axis&Order&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
+    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
     $z$&-8&$-17.966$&$-18.506$&80&$2\pi\times14$&\\\hline
@@
     \hline
-    Axis&Order&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
+    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
     $z$&-7&$-18.0335$&$-18.506$&80&$2\pi\times14$&\\\hline
@@
 \end{center}
+
+\newpage
 \subsubsection{Group 4}
@@
     \hline
-    Axis&Order&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
+    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
     $z$&-6&$-18.101$&$-18.506$&80&$2\pi\times14$&\\\hline
@@
     \hline
-    Axis&Order&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
+    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
     $z$&-5&$-18.1685$&$-18.506$&90&$2\pi\times17$&F2\\\hline
@@
     \hline
-    Axis&Order&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
+    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
     $z$&-4&$-18.236$&$-18.506$&75&$2\pi\times17$&F2\\\hline
@@
 \end{center}
+
+\newpage
 \subsubsection{Group 7}
@@
     \hline
-    Axis&Order&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
+    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
     $z$&-3&$-18.3035$&$-18.506$&60&$2\pi\times17$&F2\\\hline
@@
     \hline
-    Axis&Order&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
+    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
     $z$&-2&$-18.371$&$-18.506$&60&$2\pi\times17$&F2\\\hline
@@
     \hline
-    Axis&Order&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
+    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
     $z$&-1&$-18.3615$&$-18.429$&70&$2\pi\times9$&F2\\\hline

### 2017-08-14 sm.tex
Cite steck

@@
 \section{Raman Sideband Cooling Pulse Parameters and Sequence}
-Here, we list the full Raman sideband cooling (RSC) pulse  parameters and  sequence used to obtain the result in [our paper].
+Here, we list the full Raman sideband cooling (RSC) pulse parameters and sequence used to obtain the result in our paper.
 A step of RSC contains a Raman pulse and an optical pumping pulse.
@@
 The applied cooling frequency, $\delta'$,  is the two-photon detuning given relative to the zero-field $F=1$ and $F=2$ hyperfine splitting
-of $1.7716261288(10)$GHz[cite].
+of $1.7716261288(10)$GHz\cite{SteckNa}.
 %All of the relative detunings are negative indicating that the frequency difference is smaller than the zero-field hyperfine splitting. Higher-order sidebands for cooling

### 2017-08-15 paper.tex
Changes from Kang-Kuen

@@
     or have different durations to drive $\Delta n=-1$, at the end of the cooling sequence when most of the population is below $n=3$.
-    The Raman cooling and spectroscopy pulses have Blackman envelopes~\cite{Kasevich1992}
+    The Raman cooling and spectroscopy pulses (excluding $\Delta n=-8$ to $-5$ pulses) have Blackman envelopes~\cite{Kasevich1992}
     to reduce off-resonant coupling,
@@
 along three axes with cooling beginning on the radial second order and axial eighth order.
+The full RSC pulse sequence is given in~\footnote{See supplemental material}.
 To characterize the single atom thermal state before and after cooling,

### 2017-08-15 sm.tex
Changes from Kang-Kuen

--- 2017-08-14 sm.tex
@@
 
-\section{Raman Sideband Cooling Pulse Sequence}
+\section{Raman Sideband Cooling Pulse Parameters and Sequence}
+Here, we list the full Raman sideband cooling (RSC) pulse parameters and sequence used to obtain the result in the manuscript.
+A step of RSC contains a Raman pulse and an optical pumping pulse.
+The full RSC sequence includes about 1000 pulses in 100 ms.
 
 \subsection{Optical pumping parameters}
-The optical pumping is done with a $\sigma^-$ polarized beam aligned with the bias magnetic field.
-There are two frequencies in the beam that are on resonance with
-the $|F=2,m_F=-1\rangle$ to $|F'=2,m_{F'}=-2\rangle$ D1 transition
-and the $|F=1,m_F=-1\rangle$ to $|F'=2,m_{F'}=-2\rangle$ D2 transition respectively.
-All optical pumping pulses have the same length of $40\mu$s
-with a $|F=1,m_F=-1\rangle$ scattering rate of $0.14$ MHz
-and a $|F=2,m_F=-1\rangle$ scattering rate of $0.39$ MHz.
+The optical pumping is performed with a $\sigma^-$-polarized beam aligned with an 8.8 G bias magnetic field.
+There are two frequencies in the beam: one is on resonance with
+the $|F=2,m_F=-1\rangle$ of $3^2S_{1/2}$ to $|F'=2,m_{F'}=-2\rangle$ of $3^2P_{1/2}$ D1 transition
+and the other is on resonance with the $|F=1,m_F=-1\rangle$ of $3^2S_{1/2}$ to $|F'=2,m_{F'}=-2\rangle$ of $3^2P_{3/2}$ D2 transition.
+All optical pumping pulses have the length of $40\,\mu$s
+with a scattering rate of $0.14$ MHz for atoms in $|F=1,m_F=-1\rangle$
+and a scattering rate of $0.39$ MHz for atoms in $|F=2,m_F=-1\rangle$.
 
 \subsection{Raman pulse parameters}
-Each of the Raman pulse in the cooling sequence is followed immediately by an optical pumping
-pulse with the parameters given above.
-The parameters for the Raman pulses are different between different groups and are listed below.
-The full Rabi frequency is the two-photon Rabi frequency $\Omega$ excluding the matrix element
-from wavefunction overlap.
+Each Raman pulse in the cooling sequence is followed immediately by an optical pumping
+pulse.
+The full parameters for the Raman pulses, including the cooling ``axis'', the sideband ``order ($\Delta n$)'', the cooling frequency ``$\delta '$", the carrier ($\Delta n=0$) frequency ``$\delta_0'$'', the pulse ``duration'', the pulse strength in ``$\Omega_0$'', and the beam of which a non-uniform ``power ramp'' is applied,   are listed in 9 groups below.
+The applied cooling frequency, $\delta'$,  is the two-photon detuning given relative to the zero-field $F=1$ and $F=2$ hyperfine splitting
+of $1.7716261288(10)$GHz~\cite{SteckNa}.
+%All of the relative detunings are negative indicating that the frequency difference is smaller than the zero-field hyperfine splitting. Higher-order sidebands for cooling
+%A more negative number corresponds to lower order cooling sidebands
+%and a more negative number corresponds to higher order ones.
+Due to the Stark shifts of the Raman beams, the carrier transition, $\delta'_0$, varies with the power of the Raman beams. $\delta'_0$ is given also relative to the zero-field hyperfine splitting.
+The strength of the pulses given in $\Omega_0$ determines the two-photon Rabi frequency, $\Omega_{n,\Delta n}=\Omega_0 \langle n|e^{i \vec{k} \cdot \vec{r}}|n+\Delta n\rangle$.
+We adopt the convention that a $\pi$-pulse between state $n$ and $n+\Delta n$ requires a duration $\pi/\Omega_{n,\Delta n}$.
+ The difference between $\delta'$ and $\delta'_0$ gives the motional sideband frequency, $\delta$.
+%The full Rabi frequency is given as the two-photon Rabi frequency $\Omega$ including only electronic dipole matrix element excluding the matrix element
+%from wavefunction overlap.
+Many Raman pulses include a ``power ramp'' with a Blackman envelope~\cite{Kasevich1992} to minimize off-resonant excitations.
+Because each Raman pulse is a product of two spatial- and temporal-overlapped laser beams, the ``power ramp'' is applied only to the beam that has the smaller light shift (we label the beam by the corresponding $F$ number) while the other beam has a square-pulse shape.
 For a Raman pulse with a power ramp,
-the full Rabi frequency gives the arithmetics mean over the duration of the pulse.
-The power ramp field gives, if any,
-the beam (in terms of their corresponding $F$ number)
-that ramps with a Blackman profile during the pulse~\cite{Kasevich1992}.
-$\delta'$ is the two photon detuning relative to the zero field hyperfine splitting
-of $1.7716261288(10)$GHz.
-All of the relative detunings are negetive indicating that the frequency difference is smaller
-than the zero field hyperfine splitting.
-A more negative number corresponds to lower order cooling sidebands
-and a more negative number corresponds to higher order ones.
-$\delta'_0$ the relative detuning for the carrier with the specific powers in the Raman beams.
+the Rabi frequency gives the arithmetic mean over the duration of the pulse.
+
+%The power ramp field gives, if any,
+%the beam (in terms of their corresponding $F$ number)
+%that ramps with a Blackman profile during the pulse~\cite{Kasevich1992}.
+\newpage
+
 \subsubsection{Group 1}
@@
     \hline
-    Axis&Order&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
+    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
     $x$&-2&$-17.6375$&$-18.42$&25&$2\pi\times34$&F1\\\hline
@@
     \hline
-    Axis&Order&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
+    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
     $z$&-8&$-17.966$&$-18.506$&80&$2\pi\times14$&\\\hline
@@
     \hline
-    Axis&Order&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
+    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
     $z$&-7&$-18.0335$&$-18.506$&80&$2\pi\times14$&\\\hline
@@
     \hline
-    Axis&Order&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
+    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
     $z$&-6&$-18.101$&$-18.506$&80&$2\pi\times14$&\\\hline
@@
     \hline
-    Axis&Order&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
+    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
     $z$&-5&$-18.1685$&$-18.506$&90&$2\pi\times17$&F2\\\hline
@@
     \hline
-    Axis&Order&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
+    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
     $z$&-4&$-18.236$&$-18.506$&75&$2\pi\times17$&F2\\\hline
@@
     \hline
-    Axis&Order&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
+    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
     $z$&-3&$-18.3035$&$-18.506$&60&$2\pi\times17$&F2\\\hline
@@
     \hline
-    Axis&Order&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
+    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
     $z$&-2&$-18.371$&$-18.506$&60&$2\pi\times17$&F2\\\hline
@@
     \hline
-    Axis&Order&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
+    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
     $z$&-1&$-18.3615$&$-18.429$&70&$2\pi\times9$&F2\\\hline

### 2017-08-15 paper.tex
Clean recompilation, format tweaks

@@
   We demonstrate that Raman sideband cooling to the 3D motional ground state is possible, even without tight confinement and low initial temperature.
-  % This is particularly relevant for systems which are challenging to laser-cool, such as molecules and exotic atoms, and opens up the possibility to gain quantum motional control of these systems.
 \end{abstract}
@@
 
-% Systems of trapped neutral atoms assembled from the bottom-up in an array of optical tweezers are a promising platform to study quantum information and quantum simulations~
 Trapped neutral atoms, assembled in an array of optical tweezers, are a promising platform to study quantum information and quantum simulations~
@@
 used to address them.
-Systems with a large position spread ($z_{rms}$), either due to small mass or high initial temperature,
+Systems with a large position spread ($z_{\textrm{rms}}$), either due to small mass or high initial temperature,
 fall outside of the LD regime and undergo strong recoil heating during RSC.
 In this letter we demonstrate cooling of single sodium atoms in optical tweezers,
-initially outside the LD regime ($z_{rms}/\lambdabar=4.0$), to the motional ground state.
+initially outside the LD regime ($z_{\textrm{rms}}/\lambdabar=4.0$), to the motional ground state.
 We achieve a 3D ground state population of $P_0=81(4)$\% by cooling via
  high-order sidebands in a carefully optimized cooling sequence.
-Our approach is general and applicable to %opens up ground state cooling for
+Our approach is general and applicable to
 other systems. Extending RSC beyond the LD regime opens the possibility
-for ground state cooling of systems such as light atoms and %systems with poor cooling such as
+for ground state cooling of systems such as light atoms and
 molecules that can be laser-cooled.
@@
 begins by loading a single sodium atom into an optical tweezer from a MOT~\cite{Hutzler2017-LightShifts}.
-%for $250$ ms~\cite{Hutzler2017-LightShifts}.
 The tweezer is created by focussing a $700$ nm wavelength laser beam through an NA=$0.55$ objective to an elliptical waist with radii $\{w_{0,x},w_{0,y}\}\approx \{0.79,0.57\}\,\mu$m.
@@
 to determine success, which occurs about 50\% of the time due to the loading mechanism~\cite{Schlosser2001}.
-%After attempting to load a single atom from the MOT, an image with 1.5 ms exposure time is taken to determine if the attempt was successful, which occurs about 50% of the time due to the loading mechanism [ref].
 During imaging, the atom is cooled via polarization gradient cooling (PGC),
@@
 The data analysis includes only those experiments where the first image reveals successful atom loading.
-%a repetition of the experiment that was initially bright and remained bright after the pulse sequence is interpreted as a final F=1 atomic state.}.
-
-%\footnote{We were able to load into larger tweezers with waist $> 1$ micron with an unmodulated tweezer and MOT beams, though the loading was only a few percent efficient.}
-%, while a bright image that turned dark is interpreted as F=2.
-%The hyperfine state detection is performed by pushing out atoms in the stretched state with a strong beam on resonance with the $|F=2, m_F=-2\rangle$ to $|F'=3, m_{F'}=-3\rangle$ transition before taking the second image to determine if the atom was pushed out.
-The state preparation and detection have a combined fidelity of larger than $99$\%.
 
@@
 R3 and R4 address the axial $z$-mode, where the beams also couple to radial motion, but this coupling can be neglected when the atoms is cooled to the ground state of motion.
-%, which also couples to the radial $y$ mode.
-The radial $x$-mode is addressed by turning on beams R1 and R4, $y$ is addressed by R1 and R2, and $z$ is addressed by R3 and R4.
-In this geometry, the radial mode directions coincide with the respective $k$-vector differences.
-The ``axial'' Raman beams also couple to radial motion, but this coupling can be neglected when the atoms is cooled to the ground state of motion.
     (C) Schematic of the cooling pulse sequence. The tweezer is strobed at 3 MHz to
@@
 Subsequently, an OP pulse, which consists of two frequencies both with $\sigma^-$-polarization, is applied to bring the atom out of the $F=1$ manifold and back to $|2, -2\rangle$ via spontaneous emission (Fig.~\ref{f-setup}A).
-%brings the atom back to $|F=2, m_F=-2\rangle$ via spontaneous emission.
-%, which consists of two frequencies with $\sigma^-$-polarization for the to bring the atom out of $F=1$ manifold and back to $|F=2, m_F=-2\rangle$ via spontaneous emission.
 It is important that the optical pumping step scatter as few photons as possible to minimize recoil heating.
-%The OP consists of driving a $|F=1, m_F=-1\rangle$ into the $F=2$ manifold via the transition of $3P_{3/2} D2 line$
 Therefore, to optically pump atoms from $|2,-1\rangle$ into $|2, -2\rangle$ while keeping the target state dark, we apply light resonant with $3^2P_{1/2}$~\cite{Monroe1995, Grobner2017}~\footnote{We find a reduction in the scattering rate by a factor of $130(20)$, as compared to using an OP resonant with $3^2P_{3/2}$, from which the $|2, -2>$ state could always scatter a photon via the excited $|F'=3, m_{F'}=-3>$ state.}.
-%~\footnote{We find a reduction in the scattering rate by a factor of $130(20)$, as compared to using an OP resonant with $3P_{3/2}$, from which the $|2, -2 \rangle$}
 
@@
   \caption{Optical pumping motional-state redistribution and Raman coupling for large LD parameters for the axial direction ($z$). The range plotted covers $95$\% of the initial thermal distribution.
-   % The range plotted covers $95$\% of the initial thermal distribution.
-    (A) Motional state distribution %averaged over photon emission pattern
-    after one OP cycle
-    for different initial states motion, $n_{\textrm{init}}$. Due to photon-recoil and the large LD parameter, $\eta^{OP}_z=0.6$,
-    there is a high probability of $n$ changing.         (B) Matrix elements for Raman transition deviate from
+    (A) Motional state distribution after one OP cycle for different initial states motion,
+    $n_{\textrm{init}}$. Due to photon-recoil and the large LD parameter, $\eta^{OP}_z=0.6$,
+    there is a high probability of $n$ changing.
+    (B) Matrix elements for Raman transition deviate from
     $\sqrt{n}$ scaling with multiple minima. During cooling, we utilize the fact that high motional states couple most effectively to sidebands with large $|\Delta n|$.
@@
 
-%During optical pumping, for an atom starting in motional level $n_{\textrm{init}}$, the probability of recoil to another state $n$ is determined by the squared matrix element $|\langle n_{\textrm{init}}|e^{i \Delta k z}| n\rangle|^2$ and causes motional-state redistribution as shown in Fig.~\ref{f-ld}A.
-Here $\Delta k$ is the wave vector difference between absorbed and emitted photons.
-The LD parameters for OP are $\{\eta^{\textrm{OP}}_x,\eta^{\textrm{OP}}_y,\eta^{\textrm{OP}}_z\} = \{0.241(2), 0.206(1), 0.602(5)\}$.
-As noted already, prior to RSC, the weak axial direction %, $(\eta^{\textrm{OP}}_{z,\textrm{eff}})^2>1$ is far outside of the LD regime, and the probability of recoil per OP step is large, possibly leading to runaway heating.
-
-%Fortunately, the large LD parameters also provide opportunities to overcome OP heating.
-%The LD parameter for Raman transitions is defined as $\eta^R\equiv\Delta k z_0$,
-%where the wave vector is replaced by the wave vector difference $\Delta k$
-%between the two beams that drive the Raman transition.
-%The Raman transitions in our configuration have LD parameters of
-%$\{\eta^R_x,\eta^R_y,\eta^R_z\} = \{0.341(2), 0.291(1), 0.40(1)\}$.
-%To offset heating from OP initially when $n$ is large, higher-order Raman sidebands ($\Delta n <-1$)   remove several motional quanta in a single cooling pulse (see Fig.~\ref{f-ld}B).
-%Because the coupling strengths of different orders do not reach minima for the same state of motion $n$,
-%using multiple orders of sidebands avoids accumulations of population
-%near the coupling minima.
-
-During optical pumping, photon recoil can lead to significant heating, especially along the weakly-confined axial direction ($z$).
-For an atom starting in an axial motional level $n_{\textrm{init}}$, the probability to end in another axial state $n$ after absorbing and re-emitting one photon is approximated by an angular integral of the squared matrix element $|\langle n_{\textrm{init}}|e^{i \Delta k_{OP} z}| n\rangle|^2$ \cite{ItanoWineland1979}.
-Here $\Delta k_{OP}$ is the wave vector difference between absorbed and emitted photons, projected onto the $z$-axis.
-As shown in Fig.~\ref{f-ld}A, the probability of gaining motional energy during OP grows with $n_{\textrm{init}}$, and is an important effect for sideband-cooling outside the Lamb-Dicke regime.
+During optical pumping, photon recoil can lead to significant heating,
+especially along the weakly-confined axial direction ($z$).
+For an atom starting in an axial motional level $n_{\textrm{init}}$,
+the probability to end in another axial state $n$ after absorbing and
+re-emitting one photon is approximated by an angular integral of the squared matrix element
+$|\langle n_{\textrm{init}}|e^{i \Delta k_{\textrm{OP}} z}| n\rangle|^2$~\cite{ItanoWineland1979}.
+Here $\Delta k_{\textrm{OP}}$ is the wave vector difference between absorbed and emitted photons,
+projected onto the $z$-axis.
+As shown in Fig.~\ref{f-ld}A,
+the probability of gaining motional energy during OP grows with $n_{\textrm{init}}$,
+and is an important effect for sideband-cooling outside the Lamb-Dicke regime.
 
@@
 where $\Delta k$ is the wave vector difference
-between the two beams that drive the Raman transition.  Here $z_0=\sqrt{\hbar/(2 m \omega)}$ is the ground state wavefunction spread ($m$ is the atomic mass).
+between the two beams that drive the Raman transition.
+Here $z_0=\sqrt{\hbar/(2 m \omega)}$ is the ground state wavefunction spread
+($m$ is the atomic mass).
 The Raman transitions in our configuration have LD parameters of
 $\{\eta^R_x,\eta^R_y,\eta^R_z\} = \{0.341(2), 0.291(1), 0.40(1)\}$.
-To offset heating from OP initially when $n$ is large, higher-order Raman sidebands ($|\Delta n| > 1$)   remove several motional quanta in a single cooling pulse (see Fig.~\ref{f-ld}B).
-Because the coupling strengths of different orders do not reach minima for the same state of motion $n$,
+To offset heating from OP initially when $n$ is large, higher-order Raman sidebands
+($|\Delta n| > 1$) remove several motional quanta in a single cooling pulse (see Fig.~\ref{f-ld}B).
+Because the coupling strengths of different orders do not reach minima
+for the same state of motion $n$,
 using multiple orders of sidebands avoids accumulations of population
@@
 
-Taking the large motional-state changing heating and cooling sources
- into account,
+Taking the large motional-state changing heating and cooling sources into account,
 it is not immediately clear that ground-state cooling can be achieved.
 We therefore use a Monte-Carlo simulation to guide our search~\cite{Dalibard1992}.
-%and to find a robust cooling sequence~\footnote{See supplemental material}.
 In particular, we find that alternating the cooling pulses (Fig.~\ref{f-setup}C) between two
-neighboring orders for the axial direction and $\Delta n=-2$ and $\Delta n=-1$ for the radial directions
-eliminates the accumulation of population in motional states that have zero Raman coupling, which would halt the cooling process.
+neighboring orders for the axial direction and $\Delta n=-2$ and $\Delta n=-1$
+for the radial directions
+eliminates the accumulation of population in motional states that have zero Raman coupling,
+which would halt the cooling process.
 The simulation also indicates that setting the coupling strength of each sideband
@@
 The efficiency of cooling on higher-order sidebands diminishes
-as the atom approaches the ground state, so the final cycles utilize only the $\Delta n=-1$ sideband while alternating between the three axes.
+as the atom approaches the ground state, so the final cycles utilize only
+the $\Delta n=-1$ sideband while alternating between the three axes.
 
@@
 and decreasing the orders to the next pair after every $6$ to $15$ cycles.
-This process is repeated until $\Delta n=-1$, and most of the
-population is in the first few excited states. We then switch to cooling only on $\Delta n=-1$ with two different pulse lengths in order to efficiently cool atoms in the
-few remaining motional states.
-Radial cooling is performed similarly to axial cooling with the initial cooling of $\Delta n=-2$ and $\Delta n=-1$ and switching to $\Delta n=-1$ only after $20$ to $30$ pulses.
+This process is repeated until $\Delta n=-1$,
+and most of the population is in the first few excited states.
+We then switch to cooling only on $\Delta n=-1$ with two different pulse lengths
+in order to efficiently cool atoms in the few remaining motional states.
+Radial cooling is performed similarly to axial cooling with the initial cooling
+of $\Delta n=-2$ and $\Delta n=-1$ and switching to $\Delta n=-1$ only after $20$ to $30$ pulses.
 This sequence gives good initial cooling performance, which is then used to calibrate experimental
@@
 causing the atoms to sample the anharmonicity of the trap away from the center.
-Anharmonicity may be defined as $A_{i,n}=(E_{i,n+1}-E_{i,n})/h - \omega_i/(2\pi)$ for each trap axis $i$, and calculated from the quartic term of the optical tweezers via perturbation theory.
-In the paraxial approximation, we find $A_{i,n}=\frac{-3n\hbar}{4\pi m d_i^2}$, where $d_i$ equals the beam radius for the radial directions and $d_z\approx\pi w_{0,x}w_{0,y}/\lambda_{\textrm{trap}}$.
-%We find $A_{i,n}=\frac{3n \hbar}{4 \pi m d_i^2}$  where $d_i=w_{0,x},w_{0,y}$ for the radial directions and $d_z\approx \pi w_{0,x}w_{0,y}/\lambda$ for the axial direction.
-Numerically, $\{A_{x,n},A_{y,n},A_{z,n}\}=\{-1.1, -2.0, -0.16\}n$~kHz. For mixed states, this broadens high-order sidebands due to the $n$-dependence of the transitions.
+Anharmonicity may be defined as $A_{i,n}=(E_{i,n+1}-E_{i,n})/h - \omega_i/(2\pi)$
+for each trap axis $i$, and calculated from the quartic term
+of the optical tweezers via perturbation theory.
+In the paraxial approximation, we find $A_{i,n}=\frac{-3n\hbar}{4\pi m d_i^2}$,
+where $d_i$ equals the beam radius for the radial directions and
+$d_z\approx\pi w_{0,x}w_{0,y}/\lambda_{\textrm{trap}}$.
+Numerically, $\{A_{x,n},A_{y,n},A_{z,n}\}=\{-1.1, -2.0, -0.16\}n$~kHz.
+For mixed states, this broadens high-order sidebands due to the $n$-dependence of the transitions.
 In order to mitigate this, we drive the sidebands with a large Rabi frequency
-and short pulses to Fourier broaden the spectrum. %, and use Blackman pulse envelopes to avoid unwanted coupling to the carrier and heating sidebands~\cite{Kasevich1992}.
-However, anharmonicity may still shift high-$n$ states out of resonance and prevent effective cooling.
-%Anharmonicity may be defined as $A_{i,n}=(E_{i,n+1}-E_{i,n})/h - \omega_i/(2\pi)$ for each trap axis $i$, and calculated from the quartic term of the optical tweezers via perturbation theory.
-We find $A_{i,n}=\frac{3n \hbar}{2 m d_i^2}$  where $d_i=w_0$ for the radial directions and $d_z=\pi w_0^2/\lambda$  Numerically, $\{A_{x,n},A_{y,n},A_{z,n}\}=\{1.3, 1.2, 0.2\}n$~kHz.
-Anharmonicity broadens the high-order axial transitions and may shift high-$n$ states out of resonance to prevent effective cooling.
-
-%The anharmonicity in the radial directions is calculated to be 1kHz/n, meaning that a Rabi frequency of at least $15$ kHz is needed to couple to $99$\% population up to $n=15$.
+and short pulses to Fourier broaden the spectrum.
+However, anharmonicity may still shift high-$n$ states out of resonance
+and prevent effective cooling.
 
@@
     before (red circle) and after (blue square) RSC.
-    Solid lines in (B) and (C) are
-    fits to a Rabi-flopping that includes a thermal distribution of motional states~\cite{Meekhof1996}  as well as off-resonant scattering from the Raman beams.
-The curves reach a maximum contrast of 85\% (horizontal dashed line) because 5\% of atoms are lost from one imaging step to the next, and 10\% of atoms are additionally lost during Raman cooling.
-    The blue lines correspond to a 1D ground state probability of $93$\% after cooling (not including loss) and
+    Solid lines in (B) and (C) are fits to a Rabi-flopping
+    that includes a thermal distribution of motional states~\cite{Meekhof1996}
+    as well as off-resonant scattering from the Raman beams.
+    The curves reach a maximum contrast of 85\% (horizontal dashed line)
+    because 5\% of atoms are lost from one imaging step to the next,
+    and 10\% of atoms are additionally lost during Raman cooling.
+    The blue lines correspond to a 1D ground state probability of $93$\%
+    after cooling (not including loss) and
     the red lines correspond to a thermal distribution of $70$ $\mu$K before RSC.
-    %The horizontal dashed line shows the overall survival after cooling and imaging.
     \label{f-radial}}
@@
   \includegraphics[height=4.2cm]{imgs/rabi_flop_a1_p1.pdf}
-  \caption{(A) Left to right: Axial Raman sideband spectrum from $\Delta n_z=1,0,-1,\ldots,-8$    before and after Raman sideband cooling.
-    %The data for the 2nd- and higher-orders of cooling sidebands are taken with 150 $\mu$s pulse duration and the rest are taken with 125 $\mu$s pulse duration.
+  \caption{(A) Left to right: Axial Raman sideband spectrum from $\Delta n_z=1,0,-1,\ldots,-8$
+    before and after Raman sideband cooling.
     (B,C) Rabi flopping on axial (B) carrier $\Delta n_z=0$  and (C) $\Delta n_z=1$ sideband
     before (red circle) and after (blue square) RSC.
-    Solid blue lines in (B) and (C), similar to Fig.~\ref{f-radial}B and C, are fits to the Rabi flopping and yield a ground state probability of $92$\% after cooling (not including the 15\% population loss) and
+    Solid blue lines in (B) and (C), similar to Fig.~\ref{f-radial}B and C,
+    are fits to the Rabi flopping and yield a ground state probability of $92$\%
+    after cooling (not including the 15\% population loss) and
     the red lines correspond to a thermal distribution of $70$ $\mu$K before RSC.
-    %The blue lines do not take into account the effect of decoherence due to resonance fluctuation.
-    %By comparing it to
-    The green line in (C), includes the additional decoherence due to a fluctuation of the hyperfine splitting of magnitude 3kHz. %a $3$ kHz fluctuation of the hyperfine splitting.
+    The green line in (C), includes the additional decoherence due to
+    a fluctuation of the hyperfine splitting of magnitude $3$ kHz.
     We see that the decoherence effect is strongest for the post-cooling data on
     the $\Delta n_z=1$ sideband where the Rabi frequency is the lowest.
-    %The asymptotic values for the red lines are low also because of resonance fluctuation.
-    %Similar to the Figure~\ref{f-radial},
     The horizontal dashed line shows the overall survival after cooling and imaging.
@@
 
-Second, the tweezers cause a large light shift (as large as $300$ MHz)
-in the excited state. %This causes position-dependent OP detuning
-%and mixes the excited-state hyperfine levels,  reducing optical pumping fidelity.
-We address this by strobing the trapping light at a rate of 3 MHz during the whole cooling sequence,
+Second, the tweezers cause a large light shift (as large as $300$ MHz) in the excited state.
+We address this by strobing the trapping light at a rate of 3 MHz
+during the whole cooling sequence,
 similar to our loading and imaging process~\cite{Hutzler2017-LightShifts},
@@
 Due to the large light shift, the OP is effectively off whenever the trap light is on.
-Since the atom is still addressed by optical pumping light when the trap light is off, OP remains effective.
-%  However, the selection rules that make the state |2,-2> dark to OP light are only approximately true when the tweezer light is on, and turning off the OP light during this period is expected to reduce spontaneous emission.
+Since the atom is still addressed by optical pumping light when the trap light is off,
+OP remains effective.
 
@@
 For the more tightly confined (non-degenerate) radial directions,
-we observe clear $\Delta n=1$, $\Delta n=-1$, and $\Delta n=-2$ sidebands before RSC, as is shown in Fig.~\ref{f-radial}A.
+we observe clear $\Delta n=1$, $\Delta n=-1$, and $\Delta n=-2$ sidebands before RSC,
+as is shown in Fig.~\ref{f-radial}A.
 After RSC, the $\Delta n=-1$ and $\Delta n=-2$ sidebands on both radial axes are strongly reduced.
-%It is important to note that the simple sideband thermometry formula, which predicts the ratio of the cooling and heating sideband heights to be $\bar n / (\bar n + 1)$~\cite{Monroe1995}, assumes that the coupling strength for different motional states is proportional to $\sqrt{n}$.
-However, outside of the LD regime, the coupling strength rapidly deviates from this simple scaling rule, as shown in Figure \ref{f-ld}A.
-Since the Raman spectroscopy is performed with relatively large Raman LD parameters $\eta^R$, we cannot use this formula to measure $\bar n$.
-The formula that equates the ratio of $\Delta n=-1$ and $\Delta n=1$ sideband heights to $\bar{n}/(\bar{n}+1)$ ($\bar{n}$ is the mean motional quantum number of the assumed thermal state) was derived in the LD regime~\cite{Monroe1995}.
+The formula that equates the ratio of $\Delta n=-1$ and $\Delta n=1$ sideband heights to
+$\bar{n}/(\bar{n}+1)$ ($\bar{n}$ is the mean motional quantum number of the assumed thermal state)
+was derived in the LD regime~\cite{Monroe1995}.
 However, it is also valid outside the LD regime.
-The resulting $\bar{n}_x=0.09(3)$ and $\bar{n}_y=0.05(2)$ correspond to ground-state fractions of 92(2)\% and 95(2)\%,  in agreement with fitted values of 89(2)\% and 92(2)\% from the Rabi flopping curves~ \cite{Meekhof1996} in Fig.~\ref{f-radial}B and \ref{f-radial}C.
-%Instead, given the absence of the second order cooling sideband, we assume that the atoms are cold enough to have stronger coupling to the first order cooling sideband than the second order, i.e.
-below where the matrix element for the two orders cross, in which case the lower bound of the ground state population can be computed from the heights of the sidebands by assuming all of the excitations are in the $n=1$ state.
-In doing this, we found a ground state population of $90(2)$\% and $94(3)$\% along the two radial directions.
-We also use measurements of Rabi flopping on the carrier (Fig.
-\ref{f-radial}B) and first-order heating(Fig.
-\ref{f-radial}C) sidebands to verify our assumption about the distribution and the ground state population~\cite{Meekhof1996}.
-The data is fitted using the same Monte-Carlo simulation we used to simulate the cooling which yields $89(2)$\% and $92(2)$\% and show good agreement with the population extracted from the sideband thermometry.
-The initial temperature of $70\,\mu$K before RSC is obtained
-from similar fits. %the motional-state decohered Rabi flopping.
+The resulting $\bar{n}_x=0.09(3)$ and $\bar{n}_y=0.05(2)$ correspond to
+ground-state fractions of 92(2)\% and 95(2)\%,
+in agreement with fitted values of 89(2)\% and 92(2)\%
+from the Rabi flopping curves~\cite{Meekhof1996} in Fig.~\ref{f-radial}B and \ref{f-radial}C.
+The initial temperature of $70\,\mu$K before RSC is obtained from similar fits.
 
@@
 after RSC (Fig.~\ref{f-axial}A).
-Using the ratio of first-order sideband heights, we obtain $\bar{n}_z=0.07(3)$, which corresponds to a ground state population of
+Using the ratio of first-order sideband heights, we obtain $\bar{n}_z=0.07(3)$,
+which corresponds to a ground state population of
 93(3)\%, in agreement with a ground state population of 91(2)\% extracted from Rabi flopping
@@
 we observe additional decoherence that is more pronounced due to the slower Rabi frequency.
-The decoherence rate is consistent with magnetic field fluctuations of $1.5$ mG measured independently in the lab, which would produce a Zeeman shift of $\sim 3$ kHz.
+The decoherence rate is consistent with magnetic field fluctuations of $1.5$ mG
+measured independently in the lab, which would produce a Zeeman shift of $\sim 3$ kHz.
 
@@
 but instead heated out of the trap by off-resonant scattering from the Raman beams.
-The cooling efficiency is limited by spontaneous scattering rate (0.5-1 kHz) from the Raman beams, as well as spectral broadening from magnetic field fluctuations and trap anharmonicity.
+The cooling efficiency is limited by spontaneous scattering rate (0.5-1 kHz) from the Raman beams,
+as well as spectral broadening from magnetic field fluctuations and trap anharmonicity.
 
-We measure a heating rate that corresponds to decreasing 3D ground state population at a rate of $\sim0.9$\%/ms.
-The rate is consistent with off-resonant scattering of the trapping light~\cite{Grimm2000}, and is predominantly in the axial direction where the trapping beam propagates.
-%The ground state probability achieved is currently limited by off-resonant scattering from the Raman beams, which are measured to be between $3$ to $15$ kHz for the detuning and power we use, and the resonance shift caused by magnetic field fluctuations.
+We measure a heating rate that corresponds to decreasing 3D ground state population
+at a rate of $\sim0.9$\%/ms.
+The rate is consistent with off-resonant scattering of the trapping light~\cite{Grimm2000},
+and is predominantly in the axial direction where the trapping beam propagates.
 
-%Taking into account the population loss, from each successful single atom loading event, we can currently prepared a single \textit{Na} atom in the 3D ground-state with an overall $66(3)$\% fidelity.
 We expect to reduce atom losses and enhance the ground state probability after RSC
 by increasing the detuning of the Raman beams,
-addressing a wider range of axial trap anharmonicity, % by frequency sweeps,
+addressing a wider range of axial trap anharmonicity,
 implementing better control of the magnetic field, and optimizing imaging.
@@
 a lower starting temperature before RSC~\cite{Colzi2016}.
-
-%\fxnote{The distinction between 77 and 66 percent is confusing, we should discuss it}
 
@@
 These techniques are well-suited for a large variety of systems
-and open up a route to ground state cooling for other species, including molecules and exotic atoms.
+and open up a route to ground state cooling for other species,
+including molecules and exotic atoms.
 
@@
 
-% Lamb-Dicke parameter square explain
-% why not just molecules instead of polar molecules
-% use entropy to describe the effect of large \eta_{eff}
-% 1 sentence to explain why anisotropy?
-% Mention after cooling is non-thermal?
-
 \bibliography{paper}

### 2017-08-15 paper.tex
More sub/superscript font

@@
     (A) Motional state distribution after one OP cycle for different initial states motion,
-    $n_{\textrm{init}}$. Due to photon-recoil and the large LD parameter, $\eta^{OP}_z=0.6$,
+    $n_{\textrm{init}}$. Due to photon-recoil and the large LD parameter, $\eta^{\textrm{OP}}_z=0.6$,
     there is a high probability of $n$ changing.
@@
 Fortunately, the large LD parameters in our system also provide opportunities to overcome OP heating.
-The LD parameter for Raman transitions is defined as $\eta^R\equiv\Delta k z_0$,
+The LD parameter for Raman transitions is defined as $\eta^{\textrm{R}}\equiv\Delta k z_0$,
 where $\Delta k$ is the wave vector difference
@@
 The Raman transitions in our configuration have LD parameters of
-$\{\eta^R_x,\eta^R_y,\eta^R_z\} = \{0.341(2), 0.291(1), 0.40(1)\}$.
+$\{\eta^{\textrm{R}}_x,\eta^{\textrm{R}}_y,\eta^{\textrm{R}}_z\} = \{0.341(2), 0.291(1), 0.40(1)\}$.
 To offset heating from OP initially when $n$ is large, higher-order Raman sidebands

### 2017-08-15 paper.tex
Cover letter
Move figures for PRL submission

@@
 \begin{figure}[b]
-  \includegraphics[width=8.5cm]{imgs/fig2_raman_op.pdf}
+  \includegraphics[width=8.5cm]{fig2_raman_op.pdf}
   \caption{Optical pumping motional-state redistribution and Raman coupling for large LD parameters for the axial direction ($z$). The range plotted covers $95$\% of the initial thermal distribution.
@@
 \begin{figure*}
-  \includegraphics[height=4.2cm]{imgs/spectrum_r.pdf}
-  \includegraphics[height=4.2cm]{imgs/rabi_flop_r3_0.pdf}
-  \includegraphics[height=4.2cm]{imgs/rabi_flop_r3_p1.pdf}
+  \includegraphics[height=4.2cm]{spectrum_r.pdf}
+  \includegraphics[height=4.2cm]{rabi_flop_r3_0.pdf}
+  \includegraphics[height=4.2cm]{rabi_flop_r3_p1.pdf}
   \caption{(A) Left to right: Radial Raman sideband spectrum of $\Delta n_y=1,\,\Delta n_x=1,\,\Delta n_x=-1,\,\Delta n_y=-1,\,\Delta n_x=-2,\,\Delta n_y=-2$ before and after Raman sideband cooling.
@@
 \begin{figure*}
-  \includegraphics[height=4.2cm]{imgs/spectrum_a1.pdf}
-  \includegraphics[height=4.2cm]{imgs/rabi_flop_a1_0.pdf}
-  \includegraphics[height=4.2cm]{imgs/rabi_flop_a1_p1.pdf}
+  \includegraphics[height=4.2cm]{spectrum_a1.pdf}
+  \includegraphics[height=4.2cm]{rabi_flop_a1_0.pdf}
+  \includegraphics[height=4.2cm]{rabi_flop_a1_p1.pdf}
   \caption{(A) Left to right: Axial Raman sideband spectrum from $\Delta n_z=1,0,-1,\ldots,-8$

### 2017-08-15 plot_rabi_flop.jl

@@ -127,7 +127,7 @@ function maybe_show()
     end
 end
 
-const prefix = joinpath(@__DIR__, "imgs/rabi_flop")
+const prefix = joinpath(@__DIR__, "rabi_flop")
 
 data_before_r2_0 = [data_a[:after][1][1]; data_a[:before][1]]
 data_before_r3_0 = [data_a[:after][1][1]; data_a[:before][2]]

### 2017-08-15 plot_raman_op.jl

@@ -180,6 +180,6 @@ text(60, 0.632, "(B)")
 ax2[:get_yaxis]()[:set_label_coords](-0.105, 0.5)
 xlabel("Motional state \$n\$")
 
-maybe_save(joinpath(@__DIR__, "imgs/fig2_raman_op"))
+maybe_save(joinpath(@__DIR__, "fig2_raman_op"))
 
 maybe_show()

### 2017-08-15 plot_spectrum.jl

@@ -96,7 +96,7 @@ function maybe_show()
     end
 end
 
-const prefix = joinpath(@__DIR__, "imgs/spectrum")
+const prefix = joinpath(@__DIR__, "spectrum")
 
 to_sideband(f) = (i, v)->(v - f) * 1000
 

### 2018-01-29 paper.tex
WIP: update for new results

@@
   large differential light shifts between the excited state and the ground state,
-  we achieve a ground state population of $81(4)$\% after $100$ ms of cooling, for the 85\% of atoms that survive cooling and re-imaging.
-  Our technique includes addressing high-order sidebands, where several motional quanta are removed by a single laser pulse, and
+  we achieve a ground state population of $93.5(7)$\% after $100$ ms of cooling,
+  for the 96\% of atoms that survive re-imaging. %% survives the first image?
+  Our technique includes addressing high-order sidebands,
+  where several motional quanta are removed by a single laser pulse, and
   fast modulation of the optical tweezer intensity.
-  We demonstrate that Raman sideband cooling to the 3D motional ground state is possible, even without tight confinement and low initial temperature.
+  We demonstrate that Raman sideband cooling to the 3D motional ground state is possible,
+  even without tight confinement and low initial temperature.
 \end{abstract}
@@
 
-Trapped neutral atoms, assembled in an array of optical tweezers, are a promising platform to study quantum information and quantum simulations~
+Trapped neutral atoms, assembled in an array of optical tweezers,
+are a promising platform to study quantum information and quantum simulations~
 \cite{Schlosser2001,Weiss2004,Isenhower2010,Wilk2010,Kaufman2015,Labuhn2016,Murmann2015}.
@@
 However, RSC in these systems takes place in the Lamb-Dicke (LD) regime, where
-the spread of the initial wavefunctions is smaller than the reduced wavelength of light ($\lambdabar$)
-used to address them.
-Systems with a large position spread ($z_{\textrm{rms}}$), either due to small mass or high initial temperature,
+the spread of the initial wavefunctions is smaller than the reduced wavelength of light
+($\lambdabar$) used to address them.
+Systems with a large position spread ($z_{\textrm{rms}}$),
+either due to small mass or high initial temperature,
 fall outside of the LD regime and undergo strong recoil heating during RSC.
@@
 initially outside the LD regime ($z_{\textrm{rms}}/\lambdabar=4.0$), to the motional ground state.
-We achieve a 3D ground state population of $P_0=81(4)$\% by cooling via
+We achieve a 3D ground state population of $P_0=93.5(7)$\% by cooling via
 high-order sidebands in a carefully optimized cooling sequence.
@@
 For $45$ mW of optical power, the trapping frequencies along the three axes are
-$\{\omega_x,\omega_y,\omega_z\}/2\pi = \{430(4), 590(5), 69(1)\}\ \text{\text{kHz}}$,
+$\{\omega_x,\omega_y,\omega_z\}/2\pi = \{479(4), 492(5), 86(1)\}\ \text{\text{kHz}}$,
 where $z$ is the weakly confined axial direction,
@@
 During imaging, the atom is cooled via polarization gradient cooling (PGC),
-which reduces the temperature of the single atom to $70$ $\mu$K,
+which reduces the temperature of the single atom to $80$ $\mu$K,
 corresponding to mean motional states along the three trap axes of
-$\{\bar n_x, \bar n_y, \bar n_z\}=\{3.4(2),\, 2.5(2),\, 21(2)\}$, and therefore initial 3D ground state probability of $P_0=0.3$\%.
+$\{\bar n_x, \bar n_y, \bar n_z\}=\{3.5(3),\, 3.2(3),\, 20(4)\}$, and therefore initial 3D ground state probability of $P_0=0.4$\%.
 The atom is then initialized into
-the $|F=2, m_F=-2\rangle$ stretched state via optical pumping (OP).
+the $|F=2, m_F=2\rangle$ stretched state via optical pumping (OP).
 Each experimental cycle ends with a second imaging sequence that measures the hyperfine state of the atom as $|F=2\rangle$ or $|F=1\rangle$~\footnote{The final hyperfine state sensitive detection employs a strong beam that is resonant with the $F=2$ to $F'=3$ cycling transition, to heat the $F=2$ population out of the trap.
@@
   \caption{Single Na atom Raman sideband cooling scheme and sequence. (A)
-    The Raman transitions between $|2,-2;n\rangle$ and $|1,-1;n+\Delta n\rangle$ have a one-photon detuning $\Delta=25$ GHz below the $3^2S_{1/2}$ to $3^2P_{3/2}$ transition.
+    The Raman transitions between $|2,2;n\rangle$ and $|1,1;n+\Delta n\rangle$ have a one-photon detuning $\Delta=75$ GHz below the $3^2S_{1/2}$ to $3^2P_{3/2}$ transition.
 Two-photon detuning, $\delta$, is defined relative to the $\Delta n=0$ carrier transition.
-For optical pumping, we use two $\sigma^-$ polarized transitions, one to pump the atom state out of $|1,-1\rangle$ via $3^2P_{3/2}$ and one to pump atoms out of $|2,-1\rangle$ via $3^2P_{1/2}$
-     to minimize heating of the $|2,-2\rangle$ state.
+For optical pumping, we use two $\sigma^+$ polarized transitions, one to pump the atom state out of $|1,1\rangle$ via $3^2P_{3/2}$ and one to pump atoms out of $|2,1\rangle$ via $3^2P_{1/2}$
+     to minimize heating of the $|2,2\rangle$ state.
     (B) Geometry and polarizations of the Raman and optical pumping beams relative to the
@@
     or have different durations to drive $\Delta n=-1$, at the end of the cooling sequence when most of the population is below $n=3$.
-    The Raman cooling and spectroscopy pulses (excluding $\Delta n=-8$ to $-5$ pulses) have Blackman envelopes~\cite{Kasevich1992}
+    The Raman cooling and spectroscopy pulses have Blackman envelopes~\cite{Kasevich1992}
     to reduce off-resonant coupling,
@@
 Specifically, Raman transitions are driven in $^{23}$Na between the hyperfine states
-$|2, -2\rangle$ and $|1, -1\rangle$ in the presence of an $8.8$ G magnetic field. The external field is
-orthogonal to the effective magnetic field of the tweezer, to reduce vector light shifts~\cite{Kaufman2012,Thompson2013}.
-Subsequently, an OP pulse, which consists of two frequencies both with $\sigma^-$-polarization, is applied to bring the atom out of the $F=1$ manifold and back to $|2, -2\rangle$ via spontaneous emission (Fig.~\ref{f-setup}A).
+$|2, 2\rangle$ and $|1, 1\rangle$ in the presence of an $8.8$ G magnetic field.
+The external field is orthogonal to the effective magnetic field of the tweezer,
+to reduce vector light shifts~\cite{Kaufman2012,Thompson2013}.
+Subsequently, an OP pulse, which consists of two frequencies both with $\sigma^+$-polarization,
+is applied to bring the atom out of the $F=1$ manifold and back to $|2, 2\rangle$
+via spontaneous emission (Fig.~\ref{f-setup}A).
 It is important that the optical pumping step scatter as few photons as possible to minimize recoil heating.
-Therefore, to optically pump atoms from $|2,-1\rangle$ into $|2, -2\rangle$ while keeping the target state dark, we apply light resonant with $3^2P_{1/2}$~\cite{Monroe1995, Grobner2017}~\footnote{We find a reduction in the scattering rate by a factor of $130(20)$, as compared to using an OP resonant with $3^2P_{3/2}$, from which the $|2, -2>$ state could always scatter a photon via the excited $|F'=3, m_{F'}=-3>$ state.}.
+Therefore, to optically pump atoms from $|2, 1\rangle$ into $|2, 2\rangle$
+while keeping the target state dark, we apply light resonant with $3^2P_{1/2}$~\cite{Monroe1995, Grobner2017}~\footnote{We find a reduction in the scattering rate by a factor of $130(20)$, as compared to using an OP resonant with $3^2P_{3/2}$, from which the $|2, 2>$ state could always scatter a photon via the excited $|F'=3, m_{F'}=3>$ state.}.
 
@@
 The Raman transitions in our configuration have LD parameters of
-$\{\eta^{\textrm{R}}_x,\eta^{\textrm{R}}_y,\eta^{\textrm{R}}_z\} = \{0.341(2), 0.291(1), 0.40(1)\}$.
+$\{\eta^{\textrm{R}}_x,\eta^{\textrm{R}}_y,\eta^{\textrm{R}}_z\} = \{0.323(2), 0.319(1), 0.36(1)\}$.
 To offset heating from OP initially when $n$ is large, higher-order Raman sidebands
@@
 we construct our axial cooling sequence by starting at the two highest
-observed sideband orders ($\Delta n=-8$ and $\Delta n=-7$)
+observed sideband orders ($\Delta n=-5$ and $\Delta n=-4$)
 and decreasing the orders to the next pair after every $6$ to $15$ cycles.
@@
     are fits to the Rabi flopping and yield a ground state probability of $92$\%
-    after cooling (not including the 15\% population loss) and
-    the red lines correspond to a thermal distribution of $70$ $\mu$K before RSC.
+    after cooling and
+    the red lines correspond to a thermal distribution of $80$ $\mu$K before RSC.
     The green line in (C), includes the additional decoherence due to

### 2018-01-29 paper.tex
WIP: Update cooling results

@@
   large differential light shifts between the excited state and the ground state,
-  we achieve a ground state population of $93.5(7)$\% after $100$ ms of cooling,
+  we achieve a ground state population of $93.5(7)$\% after $53$ ms of cooling,
   for the 96\% of atoms that survive re-imaging. %% survives the first image?
@@
 begins by loading a single sodium atom into an optical tweezer from a MOT~\cite{Hutzler2017-LightShifts}.
-The tweezer is created by focussing a $700$ nm wavelength laser beam through an NA=$0.55$ objective to an elliptical waist with radii $\{w_{0,x},w_{0,y}\}\approx \{0.79,0.57\}\,\mu$m.
+The tweezer is created by focussing a $700$ nm wavelength laser beam through an NA=$0.55$ objective to an elliptical waist with radii $\{w_{0,x},w_{0,y}\}\approx \{0.70,0.69\}\,\mu$m.
 For $45$ mW of optical power, the trapping frequencies along the three axes are
@@
     (A) Motional state distribution after one OP cycle for different initial states motion,
-    $n_{\textrm{init}}$. Due to photon-recoil and the large LD parameter, $\eta^{\textrm{OP}}_z=0.6$,
+    $n_{\textrm{init}}$. Due to photon-recoil and the large LD parameter, $\eta^{\textrm{OP}}_z=0.55$,
     there is a high probability of $n$ changing.
@@
 $d_z\approx\pi w_{0,x}w_{0,y}/\lambda_{\textrm{trap}}$.
-Numerically, $\{A_{x,n},A_{y,n},A_{z,n}\}=\{-1.1, -2.0, -0.16\}n$~kHz.
+Numerically, $\{A_{x,n},A_{y,n},A_{z,n}\}=\{-1.4, -1.4, -0.16\}n$~kHz.
 For mixed states, this broadens high-order sidebands due to the $n$-dependence of the transitions.
@@
     as well as off-resonant scattering from the Raman beams.
-    The curves reach a maximum contrast of 85\% (horizontal dashed line)
-    because 5\% of atoms are lost from one imaging step to the next,
-    and 10\% of atoms are additionally lost during Raman cooling.
-    The blue lines correspond to a 1D ground state probability of $93$\%
-    after cooling (not including loss) and
-    the red lines correspond to a thermal distribution of $70$ $\mu$K before RSC.
+    The blue lines correspond to a 1D ground state probability of $98.1$\% after cooling
+    and the red lines correspond to a thermal distribution of $80$ $\mu$K before RSC.
     \label{f-radial}}
@@
   \includegraphics[height=4.2cm]{rabi_flop_a1_p1.pdf}
-  \caption{(A) Left to right: Axial Raman sideband spectrum from $\Delta n_z=1,0,-1,\ldots,-8$
+  \caption{(A) Left to right: Axial Raman sideband spectrum from $\Delta n_z=1,0,-1,\ldots,-5$
     before and after Raman sideband cooling.
@@
     Solid blue lines in (B) and (C), similar to Fig.~\ref{f-radial}B and C,
-    are fits to the Rabi flopping and yield a ground state probability of $92$\%
+    are fits to the Rabi flopping and yield a ground state probability of $95$\%
     after cooling and
@@
     the $\Delta n_z=1$ sideband where the Rabi frequency is the lowest.
-    The horizontal dashed line shows the overall survival after cooling and imaging.
     \label{f-axial}}
@@
 Our final cooling results are shown in Fig.~\ref{f-radial} and \ref{f-axial}.
-In total, $1000$ cooling pulses (total duration $100$ ms) are applied
+In total, $540$ cooling pulses (total duration $53$ ms) are applied
 along three axes with cooling beginning on the radial second order and axial eighth order.
@@
 However, it is also valid outside the LD regime.
-The resulting $\bar{n}_x=0.09(3)$ and $\bar{n}_y=0.05(2)$ correspond to
-ground-state fractions of 92(2)\% and 95(2)\%,
-in agreement with fitted values of 89(2)\% and 92(2)\%
+The resulting $\bar{n}_x=0.019(4)$ and $\bar{n}_y=0.024(3)$ correspond to
+ground-state fractions of 98.1(5)\% and 97.6(3)\%,
+in agreement with fitted values of 98(1)\% and 95(3)\%
 from the Rabi flopping curves~\cite{Meekhof1996} in Fig.~\ref{f-radial}B and \ref{f-radial}C.
-The initial temperature of $70\,\mu$K before RSC is obtained from similar fits.
+The initial temperature of $80\,\mu$K before RSC is obtained from similar fits.
 
 For the weak axial direction, cooling is challenging because the atom starts outside the LD regime.
-We observe up to 8th-order Raman cooling sidebands initially,
+We observe up to 5th-order Raman cooling sidebands initially,
 which indicates population in highly-excited motional states.
@@
 after RSC (Fig.~\ref{f-axial}A).
-Using the ratio of first-order sideband heights, we obtain $\bar{n}_z=0.07(3)$,
+Using the ratio of first-order sideband heights, we obtain $\bar{n}_z=0.024(5)$,
 which corresponds to a ground state population of
-93(3)\%, in agreement with a ground state population of 91(2)\% extracted from Rabi flopping
+97.6(5)\%, in agreement with a ground state population of 95(4)\% extracted from Rabi flopping
 when $\Delta n=0$ (Fig.~\ref{f-axial}B).
@@
 Combining the axial and radial cooling results,
- a single Na atom is in the 3D ground state with a probability of 81(4)\% after RSC.
- We note that there is an additional 5\% population loss from imaging and 10\% loss
-from high-lying initial motional states that are not efficiently cooled by RSC,
-but instead heated out of the trap by off-resonant scattering from the Raman beams.
-The cooling efficiency is limited by spontaneous scattering rate (0.5-1 kHz) from the Raman beams,
+a single Na atom is in the 3D ground state with a probability of 93.5(7)\% after RSC.
+We note that there is an additional 4\% population loss from imaging.
+The cooling efficiency is limited by spontaneous scattering rate
+(0.1-0.2 kHz) from the Raman beams,
 as well as spectral broadening from magnetic field fluctuations and trap anharmonicity.
@@
 
-We expect to reduce atom losses and enhance the ground state probability after RSC
+We expect to enhance the ground state probability after RSC
 by increasing the detuning of the Raman beams,

### 2018-01-29 sm.tex
WIP: Update SM

@@
 A step of RSC contains a Raman pulse and an optical pumping pulse.
-The full RSC sequence includes about 1000 pulses in 100 ms.
+The full RSC sequence includes 540 pulses in 53 ms.
 
 \subsection{Optical pumping parameters}
-The optical pumping is performed with a $\sigma^-$-polarized beam aligned with an 8.8 G bias magnetic field.
+The optical pumping is performed with a $\sigma^+$-polarized beam aligned with an 8.8 G bias magnetic field.
 There are two frequencies in the beam: one is on resonance with
-the $|F=2,m_F=-1\rangle$ of $3^2S_{1/2}$ to $|F'=2,m_{F'}=-2\rangle$ of $3^2P_{1/2}$ D1 transition
-and the other is on resonance with the $|F=1,m_F=-1\rangle$ of $3^2S_{1/2}$ to $|F'=2,m_{F'}=-2\rangle$ of $3^2P_{3/2}$ D2 transition.
-All optical pumping pulses have the length of $40\,\mu$s
-with a scattering rate of $0.14$ MHz for atoms in $|F=1,m_F=-1\rangle$
-and a scattering rate of $0.39$ MHz for atoms in $|F=2,m_F=-1\rangle$.
+the $|F=2,m_F=1\rangle$ of $3^2S_{1/2}$ to $|F'=2,m_{F'}=2\rangle$ of $3^2P_{1/2}$ D1 transition
+and the other is on resonance with the $|F=1,m_F=1\rangle$ of $3^2S_{1/2}$ to $|F'=2,m_{F'}=2\rangle$ of $3^2P_{3/2}$ D2 transition.
+All optical pumping pulses have the length of $30\,\mu$s
+with a scattering rate of $0.14$ MHz for atoms in $|F=1,m_F=1\rangle$
+and a scattering rate of $0.39$ MHz for atoms in $|F=2,m_F=1\rangle$.
 
 \subsection{Raman pulse parameters}
-Each Raman pulse in the cooling sequence is followed immediately by an optical pumping
-pulse.
-The full parameters for the Raman pulses, including the cooling ``axis'', the sideband ``order ($\Delta n$)'', the cooling frequency ``$\delta '$", the carrier ($\Delta n=0$) frequency ``$\delta_0'$'', the pulse ``duration'', the pulse strength in ``$\Omega_0$'', and the beam of which a non-uniform ``power ramp'' is applied,   are listed in 9 groups below.
-The applied cooling frequency, $\delta'$,  is the two-photon detuning given relative to the zero-field $F=1$ and $F=2$ hyperfine splitting
+Each Raman pulse in the cooling sequence is followed immediately by an optical pumping pulse.
+The full parameters for the Raman pulses, including the cooling ``axis'',
+the sideband ``order ($\Delta n$)'', the cooling frequency ``$\delta '$",
+the carrier ($\Delta n=0$) frequency ``$\delta_0'$'', the pulse ``duration'',
+the pulse strength in ``$\Omega_0$'',
+and the beam of which a non-uniform ``power ramp'' is applied, are listed in 6 groups below.
+The applied cooling frequency, $\delta'$,
+is the two-photon detuning given relative to the zero-field $F=1$ and $F=2$ hyperfine splitting
 of $1.7716261288(10)$GHz~\cite{SteckNa}.
-%All of the relative detunings are negative indicating that the frequency difference is smaller than the zero-field hyperfine splitting. Higher-order sidebands for cooling
-%A more negative number corresponds to lower order cooling sidebands
-%and a more negative number corresponds to higher order ones.
-Due to the Stark shifts of the Raman beams, the carrier transition, $\delta'_0$, varies with the power of the Raman beams. $\delta'_0$ is given also relative to the zero-field hyperfine splitting.
-The strength of the pulses given in $\Omega_0$ determines the two-photon Rabi frequency, $\Omega_{n,\Delta n}=\Omega_0 \langle n|e^{i \vec{k} \cdot \vec{r}}|n+\Delta n\rangle$.
+Due to the Stark shifts of the Raman beams, the carrier transition, $\delta'_0$,
+varies with the power of the Raman beams.
+$\delta'_0$ is given also relative to the zero-field hyperfine splitting.
+The strength of the pulses given in $\Omega_0$ determines the two-photon Rabi frequency,
+$\Omega_{n,\Delta n}=\Omega_0 \langle n|e^{i \vec{k} \cdot \vec{r}}|n+\Delta n\rangle$.
 We adopt the convention that a $\pi$-pulse between state $n$ and $n+\Delta n$ requires a duration $\pi/\Omega_{n,\Delta n}$.
 The difference between $\delta'$ and $\delta'_0$ gives the motional sideband frequency, $\delta$.
-%The full Rabi frequency is given as the two-photon Rabi frequency $\Omega$ including only electronic dipole matrix element excluding the matrix element
-%from wavefunction overlap.
 Many Raman pulses include a ``power ramp'' with a Blackman envelope~\cite{Kasevich1992} to minimize off-resonant excitations.
-Because each Raman pulse is a product of two spatial- and temporal-overlapped laser beams, the ``power ramp'' is applied only to the beam that has the smaller light shift (we label the beam by the corresponding $F$ number) while the other beam has a square-pulse shape.
+Because each Raman pulse is a product of two spatial- and temporal-overlapped laser beams,
+the ``power ramp'' is applied only to the beam that has the smaller light shift
+(we label the beam by the corresponding $F$ number) while the other beam has a square-pulse shape.
 For a Raman pulse with a power ramp,
@@
 
-%The power ramp field gives, if any,
-%the beam (in terms of their corresponding $F$ number)
-%that ramps with a Blackman profile during the pulse~\cite{Kasevich1992}.
 \newpage
@@
 \subsubsection{Group 1}
-This group is repeated 5 times.
+This group is repeated 4 times.
 \begin{center}
@@
     Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
-    $x$&-2&$-17.6375$&$-18.42$&25&$2\pi\times34$&F1\\\hline
-    $y$&-2&$-17.2825$&$-18.47$&25&$2\pi\times34$&F1\\\hline
-    $x$&-1&$-18.03$&$-18.42$&25&$2\pi\times34$&F1\\\hline
-    $y$&-1&$-17.875$&$-18.47$&21&$2\pi\times34$&F1\\\hline
+    $x$&-2&$19.625$&$18.649$&44.1&$2\pi\times23$&F1\\\hline
+    $y$&-2&$19.615$&$18.648$&28.6&$2\pi\times35$&F1\\\hline
+    $x$&-1&$19.130$&$18.649$&36.9&$2\pi\times23$&F1\\\hline
+    $y$&-1&$19.615$&$18.648$&24.0&$2\pi\times35$&F1\\\hline
   \end{tabular}
 \end{center}
+
 \subsubsection{Group 2}
@@
     Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
-    $z$&-8&$-17.966$&$-18.506$&80&$2\pi\times14$&\\\hline
-    $x$&-2&$-17.6375$&$-18.42$&25&$2\pi\times34$&F1\\\hline
-    $z$&-7&$-18.0335$&$-18.506$&80&$2\pi\times14$&\\\hline
-    $y$&-2&$-17.2825$&$-18.47$&25&$2\pi\times34$&F1\\\hline
-    $z$&-8&$-17.966$&$-18.506$&80&$2\pi\times14$&\\\hline
-    $x$&-1&$-18.03$&$-18.42$&25&$2\pi\times34$&F1\\\hline
-    $z$&-7&$-18.0335$&$-18.506$&80&$2\pi\times14$&\\\hline
-    $y$&-1&$-17.875$&$-18.47$&21&$2\pi\times34$&F1\\\hline
+    $z$&-5&$19.030$&$18.605$&81.5&$2\pi\times16$&F2\\\hline
+    $x$&-2&$19.625$&$18.649$&44.1&$2\pi\times23$&F1\\\hline
+    $z$&-4&$18.940$&$18.605$&76.3&$2\pi\times16$&F2\\\hline
+    $y$&-2&$19.615$&$18.648$&28.6&$2\pi\times35$&F1\\\hline
+    $z$&-5&$19.030$&$18.605$&81.5&$2\pi\times16$&F2\\\hline
+    $x$&-1&$19.130$&$18.649$&36.9&$2\pi\times23$&F1\\\hline
+    $z$&-4&$18.940$&$18.605$&76.3&$2\pi\times16$&F2\\\hline
+    $y$&-1&$19.130$&$18.648$&24.0&$2\pi\times35$&F1\\\hline
   \end{tabular}
@@
     Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
-    $z$&-7&$-18.0335$&$-18.506$&80&$2\pi\times14$&\\\hline
-    $x$&-2&$-17.6375$&$-18.42$&25&$2\pi\times34$&F1\\\hline
-    $z$&-6&$-18.101$&$-18.506$&80&$2\pi\times14$&\\\hline
-    $y$&-2&$-17.2825$&$-18.47$&25&$2\pi\times34$&F1\\\hline
-    $z$&-7&$-18.0335$&$-18.506$&80&$2\pi\times14$&\\\hline
-    $x$&-1&$-18.03$&$-18.42$&25&$2\pi\times34$&F1\\\hline
-    $z$&-6&$-18.101$&$-18.506$&80&$2\pi\times14$&\\\hline
-    $y$&-1&$-17.875$&$-18.47$&21&$2\pi\times34$&F1\\\hline
+    $z$&-4&$18.940$&$18.605$&76.3&$2\pi\times16$&F2\\\hline
+    $x$&-2&$19.625$&$18.649$&44.1&$2\pi\times23$&F1\\\hline
+    $z$&-3&$18.858$&$18.605$&70.2&$2\pi\times16$&F2\\\hline
+    $y$&-2&$19.615$&$18.648$&28.6&$2\pi\times35$&F1\\\hline
+    $z$&-4&$18.940$&$18.605$&76.3&$2\pi\times16$&F2\\\hline
+    $x$&-1&$19.130$&$18.649$&36.9&$2\pi\times23$&F1\\\hline
+    $z$&-3&$18.858$&$18.605$&70.2&$2\pi\times16$&F2\\\hline
+    $y$&-1&$19.130$&$18.648$&24.0&$2\pi\times35$&F1\\\hline
   \end{tabular}
@@
     Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
-    $z$&-6&$-18.101$&$-18.506$&80&$2\pi\times14$&\\\hline
-    $x$&-2&$-17.6375$&$-18.42$&25&$2\pi\times34$&F1\\\hline
-    $z$&-5&$-18.1685$&$-18.506$&60&$2\pi\times14$&\\\hline
-    $y$&-2&$-17.2825$&$-18.47$&25&$2\pi\times34$&F1\\\hline
-    $z$&-6&$-18.101$&$-18.506$&80&$2\pi\times14$&\\\hline
-    $x$&-1&$-18.03$&$-18.42$&25&$2\pi\times34$&F1\\\hline
-    $z$&-5&$-18.1685$&$-18.506$&60&$2\pi\times14$&\\\hline
-    $y$&-1&$-17.875$&$-18.47$&21&$2\pi\times34$&F1\\\hline
+    $z$&-3&$18.858$&$18.605$&70.2&$2\pi\times16$&F2\\\hline
+    $x$&-2&$19.625$&$18.649$&44.1&$2\pi\times23$&F1\\\hline
+    $z$&-2&$18.773$&$18.605$&62.7&$2\pi\times16$&F2\\\hline
+    $y$&-2&$19.615$&$18.648$&28.6&$2\pi\times35$&F1\\\hline
+    $z$&-3&$18.858$&$18.605$&70.2&$2\pi\times16$&F2\\\hline
+    $x$&-1&$19.130$&$18.649$&36.9&$2\pi\times23$&F1\\\hline
+    $z$&-2&$18.773$&$18.605$&62.7&$2\pi\times16$&F2\\\hline
+    $y$&-1&$19.130$&$18.648$&24.0&$2\pi\times35$&F1\\\hline
   \end{tabular}
@@
 \subsubsection{Group 5}
-This group is repeated 7 times.
-\begin{center}
-  \begin{tabular}{|c|c|c|c|c|c|c|}
-    \hline
-    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
-    $z$&-5&$-18.1685$&$-18.506$&90&$2\pi\times17$&F2\\\hline
-    $x$&-1&$-18.03$&$-18.42$&38&$2\pi\times34$&F1\\\hline
-    $z$&-4&$-18.236$&$-18.506$&75&$2\pi\times17$&F2\\\hline
-    $y$&-1&$-17.875$&$-18.47$&25&$2\pi\times34$&F1\\\hline
-    $z$&-5&$-18.1685$&$-18.506$&90&$2\pi\times17$&F2\\\hline
-    $x$&-1&$-18.03$&$-18.42$&43&$2\pi\times34$&F1\\\hline
-    $z$&-4&$-18.236$&$-18.506$&75&$2\pi\times17$&F2\\\hline
-    $y$&-1&$-17.875$&$-18.47$&28&$2\pi\times34$&F1\\\hline
-  \end{tabular}
-\end{center}
-\subsubsection{Group 6}
-This group is repeated 8 times.
-\begin{center}
-  \begin{tabular}{|c|c|c|c|c|c|c|}
-    \hline
-    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
-    $z$&-4&$-18.236$&$-18.506$&75&$2\pi\times17$&F2\\\hline
-    $x$&-1&$-18.03$&$-18.42$&38&$2\pi\times34$&F1\\\hline
-    $z$&-3&$-18.3035$&$-18.506$&60&$2\pi\times17$&F2\\\hline
-    $y$&-1&$-17.875$&$-18.47$&25&$2\pi\times34$&F1\\\hline
-    $z$&-4&$-18.236$&$-18.506$&75&$2\pi\times17$&F2\\\hline
-    $x$&-1&$-18.03$&$-18.42$&43&$2\pi\times34$&F1\\\hline
-    $z$&-3&$-18.3035$&$-18.506$&60&$2\pi\times17$&F2\\\hline
-    $y$&-1&$-17.875$&$-18.47$&28&$2\pi\times34$&F1\\\hline
-  \end{tabular}
-\end{center}
-
-\newpage
-\subsubsection{Group 7}
 This group is repeated 10 times.
@@
     Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
-    $z$&-3&$-18.3035$&$-18.506$&60&$2\pi\times17$&F2\\\hline
-    $x$&-1&$-18.03$&$-18.42$&38&$2\pi\times34$&F1\\\hline
-    $z$&-2&$-18.371$&$-18.506$&60&$2\pi\times17$&F2\\\hline
-    $y$&-1&$-17.875$&$-18.47$&25&$2\pi\times34$&F1\\\hline
-    $z$&-3&$-18.3035$&$-18.506$&60&$2\pi\times17$&F2\\\hline
-    $x$&-1&$-18.03$&$-18.42$&43&$2\pi\times34$&F1\\\hline
-    $z$&-2&$-18.371$&$-18.506$&60&$2\pi\times17$&F2\\\hline
-    $y$&-1&$-17.875$&$-18.47$&28&$2\pi\times34$&F1\\\hline
+    $z$&-2&$18.773$&$18.605$&62.7&$2\pi\times16$&F2\\\hline
+    $x$&-1&$19.130$&$18.649$&36.9&$2\pi\times23$&F1\\\hline
+    $z$&-1&$18.685$&$18.605$&52.5&$2\pi\times16$&F2\\\hline
+    $y$&-1&$19.130$&$18.648$&24.0&$2\pi\times35$&F1\\\hline
+    $z$&-2&$18.773$&$18.605$&62.7&$2\pi\times16$&F2\\\hline
+    $x$&-1&$19.130$&$18.649$&70.0&$2\pi\times23$&F1\\\hline
+    $z$&-1&$18.685$&$18.605$&52.5&$2\pi\times16$&F2\\\hline
+    $y$&-1&$19.130$&$18.648$&46.0&$2\pi\times35$&F1\\\hline
   \end{tabular}
 \end{center}
-\subsubsection{Group 8}
-This group is repeated 10 times.
+\subsubsection{Group 6}
+This group is repeated 30 times.
 \begin{center}
@@
     Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
-    $z$&-2&$-18.371$&$-18.506$&60&$2\pi\times17$&F2\\\hline
-    $x$&-1&$-18.03$&$-18.42$&38&$2\pi\times34$&F1\\\hline
-    $z$&-1&$-18.4385$&$-18.506$&60&$2\pi\times17$&F2\\\hline
-    $y$&-1&$-17.875$&$-18.47$&25&$2\pi\times34$&F1\\\hline
-    $z$&-2&$-18.371$&$-18.506$&60&$2\pi\times17$&F2\\\hline
-    $x$&-1&$-18.03$&$-18.42$&43&$2\pi\times34$&F1\\\hline
-    $z$&-1&$-18.4385$&$-18.506$&60&$2\pi\times17$&F2\\\hline
-    $y$&-1&$-17.875$&$-18.47$&28&$2\pi\times34$&F1\\\hline
-  \end{tabular}
-\end{center}
-\subsubsection{Group 9}
-This group is repeated 40 times.
-\begin{center}
-  \begin{tabular}{|c|c|c|c|c|c|c|}
-    \hline
-    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
-    $z$&-1&$-18.3615$&$-18.429$&70&$2\pi\times9$&F2\\\hline
-    $z$&-1&$-18.3615$&$-18.429$&100&$2\pi\times9$&F2\\\hline
-    $x$&-1&$-18.03$&$-18.42$&38&$2\pi\times34$&F1\\\hline
-    $z$&-1&$-18.3615$&$-18.429$&70&$2\pi\times9$&F2\\\hline
-    $z$&-1&$-18.3615$&$-18.429$&100&$2\pi\times9$&F2\\\hline
-    $y$&-1&$-17.875$&$-18.47$&25&$2\pi\times34$&F1\\\hline
-    $z$&-1&$-18.3615$&$-18.429$&70&$2\pi\times9$&F2\\\hline
-    $z$&-1&$-18.3615$&$-18.429$&100&$2\pi\times9$&F2\\\hline
-    $x$&-1&$-18.03$&$-18.42$&43&$2\pi\times34$&F1\\\hline
-    $z$&-1&$-18.3615$&$-18.429$&70&$2\pi\times9$&F2\\\hline
-    $z$&-1&$-18.3615$&$-18.429$&100&$2\pi\times9$&F2\\\hline
-    $y$&-1&$-17.875$&$-18.47$&28&$2\pi\times34$&F1\\\hline
+    $z$&-1&$18.683$&$18.605$&78.7&$2\pi\times11$&F2\\\hline
+    $z$&-1&$18.683$&$18.605$&135.0&$2\pi\times11$&F2\\\hline
+    $z$&-1&$18.685$&$18.605$&78.7&$2\pi\times11$&F2\\\hline
+    $x$&-1&$19.130$&$18.649$&36.9&$2\pi\times23$&F1\\\hline
+    $y$&-1&$19.130$&$18.648$&24.0&$2\pi\times35$&F1\\\hline
+    $z$&-1&$18.685$&$18.605$&78.7&$2\pi\times11$&F2\\\hline
+    $z$&-1&$18.685$&$18.605$&135.0&$2\pi\times11$&F2\\\hline
+    $z$&-1&$18.685$&$18.605$&78.7&$2\pi\times11$&F2\\\hline
+    $x$&-1&$19.130$&$18.649$&70.0&$2\pi\times23$&F1\\\hline
+    $y$&-1&$19.130$&$18.648$&46.0&$2\pi\times35$&F1\\\hline
   \end{tabular}

### 2018-01-29 plot_spectrum.jl
Update plot_spectrum.jl to use new library functions

@@ -4,11 +4,9 @@ push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
 
 using NaCsCalc.Utils: interactive
 using NaCsData
+using NaCsPlot
 using PyPlot
 using DataStructures
-matplotlib["rcParams"][:update](Dict("font.size" => 20))
-matplotlib[:rc]("xtick", labelsize=15)
-matplotlib[:rc]("ytick", labelsize=15)
 
 const iname_a = joinpath(@__DIR__, "../../experiments/misc/data/data_20170402_205344.csv")
 const iname_b = joinpath(@__DIR__, "../../experiments/misc/data/data_20170404_133229.csv")
@@ -72,30 +70,6 @@ const split_b = NaCsData.split_data(data_b, spec_b)
 const split_c = NaCsData.split_data(data_c, spec_c)
 const split_d = NaCsData.split_data(data_d, spec_d)
 
-function plot_data(data, scale=1; kws...)
-    params, ratios, uncs = NaCsData.get_values(data)
-    perm = sortperm(params)
-    params = params[perm]
-    ratios = ratios[perm, 2] .* scale
-    uncs = uncs[perm, 2] .* scale
-    errorbar(params, ratios, uncs; kws...)
-end
-
-function maybe_save(name)
-    if !interactive()
-        savefig("$name.pdf"; bbox_inches="tight", transparent=true)
-        savefig("$name.png"; bbox_inches="tight", transparent=true)
-        savefig("$name.svg", bbox_inches="tight", transparent=true)
-        close()
-    end
-end
-
-function maybe_show()
-    if interactive()
-        show()
-    end
-end
-
 const prefix = joinpath(@__DIR__, "spectrum")
 
 to_sideband(f) = (i, v)->(v - f) * 1000
@@ -119,24 +93,24 @@ fig = figure(figsize=[1.6, 1] * 4.8)
 
 # Without cooling
 # Radial 2
-plot_data(data_nocool_r2[1], 1, fmt="C3^-", label="\$x\$ initial")
-plot_data(data_nocool_r2[2], 1, fmt="C3^-")
[…]

### 2018-01-29 calc_ground.jl
Switch naming conventions

@@ -3,23 +3,23 @@
 push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
 import NaCsCalc.Format: Unc
 
-const a1m1 = [0.0410, 0.0182]
-const a1p1 = [0.476, 0.411]
+const azm1 = [0.0410, 0.0182]
+const azp1 = [0.476, 0.411]
 
-const r2m1 = [0.0656, 0.0366]
-const r2p1 = [0.656, 0.593]
+const rxm1 = [0.0656, 0.0366]
+const rxp1 = [0.656, 0.593]
 
-const r3m1 = [0.0310, 0.0121]
-const r3p1 = [0.459, 0.395]
+const rym1 = [0.0310, 0.0121]
+const ryp1 = [0.459, 0.395]
 
-const a1m10 = [0.419, 0.317]
-const a1p10 = [0.497, 0.396]
+const azm10 = [0.419, 0.317]
+const azp10 = [0.497, 0.396]
 
-const r2m10 = [0.599, 0.500]
-const r2p10 = [0.820, 0.740]
+const rxm10 = [0.599, 0.500]
+const rxp10 = [0.820, 0.740]
 
-const r3m10 = [0.455, 0.355]
-const r3p10 = [0.664, 0.574]
+const rym10 = [0.455, 0.355]
+const ryp10 = [0.664, 0.574]
 
 function naive_ground(m1, p1)
     avg_m1 = (m1[1] + m1[2]) / 2
@@ -46,10 +46,10 @@ function show_ground(m1, p1, name)
     println("  nbar: ", n)
 end
 
-show_ground(a1m1, a1p1, "Axial (z) cooled")
-show_ground(r2m1, r2p1, "Radial (x) cooled")
-show_ground(r3m1, r3p1, "Radial (y) cooled")
+show_ground(rxm1, rxp1, "Radial (x) cooled")
+show_ground(rym1, ryp1, "Radial (y) cooled")
+show_ground(azm1, azp1, "Axial (z) cooled")
 
-show_ground(a1m10, a1p10, "Axial (z) initial")
-show_ground(r2m10, r2p10, "Radial (x) initial")
-show_ground(r3m10, r3p10, "Radial (y) initial")
+show_ground(rxm10, rxp10, "Radial (x) initial")
+show_ground(rym10, ryp10, "Radial (y) initial")
+show_ground(azm10, azp10, "Axial (z) initial")

### 2018-01-29 plot_rabi_flop.jl

@@ -35,28 +35,28 @@ rates_f1_up .*= 1.05e9
 rates_f1_down .*= 8.2e8
 rates_f2_counterop .*= 3.25e9
 
-const rates_r3 = rates_f1_down + rates_f2_counterop
-const rates_r2 = rates_f1_up + rates_f2_counterop
-const rates_a1 = rates_f1_up * 0.52 / 5.3 + rates_f2_coprop * 0.356 / 0.77
+const rates_ry = rates_f1_down + rates_f2_counterop
+const rates_rx = rates_f1_up + rates_f2_counterop
+const rates_az = rates_f1_up * 0.52 / 5.3 + rates_f2_coprop * 0.356 / 0.77
 const rates_coprop = rates_f1_coprop + rates_f2_coprop
 
 # Matrix elements
 const m_Na = 23e-3 / 6.02e23
-const η_a1 = Trap.η(m_Na, 68.8e3, 2π / 589e-9) * 0.67
-const η_r2 = Trap.η(m_Na, 430e3, 2π / 589e-9) * √(2)
-const η_r3 = Trap.η(m_Na, 589.5e3, 2π / 589e-9) * √(2)
+const η_az = Trap.η(m_Na, 68.8e3, 2π / 589e-9) * 0.67
+const η_rx = Trap.η(m_Na, 430e3, 2π / 589e-9) * √(2)
+const η_ry = Trap.η(m_Na, 589.5e3, 2π / 589e-9) * √(2)
 
-const ns_a1 = 0:150
-const meles_a1_0 = Trap.sideband.(ns_a1, ns_a1, η_a1)
-const meles_a1_p1 = Trap.sideband.(ns_a1, ns_a1 .+ 1, η_a1)
+const ns_az = 0:150
+const meles_az_0 = Trap.sideband.(ns_az, ns_az, η_az)
+const meles_az_p1 = Trap.sideband.(ns_az, ns_az .+ 1, η_az)
 
-const ns_r2 = 0:50
-const meles_r2_0 = Trap.sideband.(ns_r2, ns_r2, η_r2)
-const meles_r2_p1 = Trap.sideband.(ns_r2, ns_r2 .+ 1, η_r2)
+const ns_rx = 0:50
+const meles_rx_0 = Trap.sideband.(ns_rx, ns_rx, η_rx)
+const meles_rx_p1 = Trap.sideband.(ns_rx, ns_rx .+ 1, η_rx)
 
-const ns_r3 = 0:50
[…]

### 2018-01-29 plot_raman_op.jl

@@ -12,10 +12,10 @@ PyPlot.matplotlib[:rc]("xtick", labelsize=15)
 PyPlot.matplotlib[:rc]("ytick", labelsize=15)
 
 const m_Na = 23e-3 / 6.02e23
-const η_ax = Trap.η(m_Na, 67e3, 2π / 589e-9) / √(2)
-const η_ax_op = Trap.η(m_Na, 67e3, 2π / 589e-9)
-const η_ra1 = Trap.η(m_Na, 430e3, 2π / 589e-9)
-const η_ra2 = Trap.η(m_Na, 590e3, 2π / 589e-9)
+const η_az = Trap.η(m_Na, 67e3, 2π / 589e-9) / √(2)
+const η_az_op = Trap.η(m_Na, 67e3, 2π / 589e-9)
+const η_rx = Trap.η(m_Na, 430e3, 2π / 589e-9)
+const η_ry = Trap.η(m_Na, 590e3, 2π / 589e-9)
 
 """
     emission(v, isσ::Bool) -> (sinθ, cosθ)
@@ -74,12 +74,12 @@ function op_coupling(n1, n2, η::T, v::T, φ::T, isσ::Bool, cosθ_dri::T,
     return Trap.sideband(n1, n2, abs(η_eff))^2 / π
 end
 
-function op_heating_ax(n1, n2, η::T, isσ) where T
+function op_heating_az(n1, n2, η::T, isσ) where T
     hcubature(x->op_coupling(n1, n2, η, T(x[1]), T(x[2]), isσ, T(0), (T(1), T(0))),
               [0.0, 0.0], [1.0, π], abstol=1e-6)[1]
 end
 
-function op_heating_ra(n1, n2, η::T, isσ) where T
+function op_heating_r(n1, n2, η::T, isσ) where T
     hcubature(x->op_coupling(n1, n2, η, T(x[1]), T(x[2]), isσ,
                              sqrt(T(0.5)), (sqrt(T(0.5)), sqrt(T(0.5)))),
               [0.0, 0.0], [1.0, π], abstol=1e-6)[1]
@@ -105,12 +105,12 @@ function op_heating_all(cb::Function, sz1, sz2, η::T, isσ) where T
     res
 end
 
-const coupling_ax = (op_heating_all(op_heating_ax, 100, 100, Float32(η_ax_op), false) *
-                     op_heating_all(op_heating_ax, 100, 100, Float32(η_ax_op), true))
[…]

### 2018-01-29 plot_spectrum.jl

@@ -74,43 +74,43 @@ const prefix = joinpath(@__DIR__, "spectrum")
 
 to_sideband(f) = (i, v)->(v - f) * 1000
 
-data_nocool_r2 = NaCsData.map_params(to_sideband(-18.4625), split_a[:nocool_pm12][1])
-data_nocool_r2_0 = NaCsData.map_params(to_sideband(-18.4625), split_a[:nocool_0][1])
-data_cool_r2 =  NaCsData.map_params(to_sideband(-18.4575), split_d[1])
+data_nocool_rx = NaCsData.map_params(to_sideband(-18.4625), split_a[:nocool_pm12][1])
+data_nocool_rx_0 = NaCsData.map_params(to_sideband(-18.4625), split_a[:nocool_0][1])
+data_cool_rx =  NaCsData.map_params(to_sideband(-18.4575), split_d[1])
 
-data_nocool_r3 = NaCsData.map_params(to_sideband(-18.485), split_a[:nocool_pm12][2])
-data_nocool_r3_0 = NaCsData.map_params(to_sideband(-18.485), split_a[:nocool_0][2])
-data_cool_r3 =  NaCsData.map_params(to_sideband(-18.480), split_d[2])
+data_nocool_ry = NaCsData.map_params(to_sideband(-18.485), split_a[:nocool_pm12][2])
+data_nocool_ry_0 = NaCsData.map_params(to_sideband(-18.485), split_a[:nocool_0][2])
+data_cool_ry =  NaCsData.map_params(to_sideband(-18.480), split_d[2])
 
-data_nocool_a1 = NaCsData.map_params(to_sideband(-18.4965), split_a[:nocool_pm12][3])
-data_nocool_a1_0 = NaCsData.map_params(to_sideband(-18.4965), split_a[:nocool_0][3])
-data_nocool_a1_hi = [NaCsData.map_params(to_sideband(-18.5015), split_a[:nocool_a8]);
+data_nocool_az = NaCsData.map_params(to_sideband(-18.4965), split_a[:nocool_pm12][3])
+data_nocool_az_0 = NaCsData.map_params(to_sideband(-18.4965), split_a[:nocool_0][3])
+data_nocool_az_hi = [NaCsData.map_params(to_sideband(-18.5015), split_a[:nocool_a8]);
[…]

### 2018-01-29 plot_spectrum.jl
New spectrum plot

@@ -8,135 +8,176 @@ using NaCsPlot
 using PyPlot
 using DataStructures
 
-const iname_a = joinpath(@__DIR__, "../../experiments/misc/data/data_20170402_205344.csv")
-const iname_b = joinpath(@__DIR__, "../../experiments/misc/data/data_20170404_133229.csv")
-const iname_c = joinpath(@__DIR__, "../../experiments/misc/data/data_20170409_005850.csv")
-const iname_d = joinpath(@__DIR__, "../../experiments/misc/data/data_20170409_082523.csv")
+matplotlib["rcParams"][:update](Dict("font.weight" => "normal"))
 
-const data_a = NaCsData.load_count_csv(iname_a)
-const data_b = NaCsData.load_count_csv(iname_b)
-const data_c = NaCsData.load_count_csv(iname_c)
-const data_d = NaCsData.load_count_csv(iname_d)
+function selector(logicals)
+    @assert size(logicals, 2) == 1
+    if logicals[1, 1] == 0
+        return Int[1, 0, 0]
+    end
+    return Int[1, 1, logicals[3, 1]]
+end
 
+function fit(model, data, p0; plotx=nothing, use_unc=false, plot_scale=1.1)
+    if use_unc
+        params, ratios, uncs = NaCsData.get_values(data)
+    else
+        params, ratios, uncs = NaCsData.get_values(data, 0.0)
+    end
+    if plotx === nothing
+        lo = minimum(params)
+        hi = maximum(params)
+        span = hi - lo
+        mid = (hi + lo) / 2
+        plotx = linspace(mid - span * plot_scale / 2, mid + span * plot_scale / 2, 10000)
+    end
+    if use_unc
+        fit = curve_fit(model, params, ratios[:, 2], 1 ./ uncs[:, 2].^2, p0)
+    else
+        fit = curve_fit(model, params, ratios[:, 2], p0)
+    end
+    return (param=fit.param, unc=estimate_errors(fit),
+            plotx=plotx, ploty=model.(plotx, (fit.param,)))
+end
+
+model_peak(x, p) = p[1] .* exp.(.-((x .- p[2]) ./ p[3]).^2)
+
[…]

### 2018-01-29 plot_raman_op.jl
New sideband coupling plot

@@ -4,18 +4,18 @@ push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
 
 import NaCsCalc.Utils: interactive
 import NaCsCalc: Trap
+using NaCsPlot
 using Cubature
 using PyPlot
 
-PyPlot.matplotlib["rcParams"][:update](Dict("font.size" => 20))
-PyPlot.matplotlib[:rc]("xtick", labelsize=15)
-PyPlot.matplotlib[:rc]("ytick", labelsize=15)
+matplotlib["rcParams"][:update](Dict("font.weight" => "normal"))
 
 const m_Na = 23e-3 / 6.02e23
-const η_az = Trap.η(m_Na, 67e3, 2π / 589e-9) / √(2)
-const η_az_op = Trap.η(m_Na, 67e3, 2π / 589e-9)
-const η_rx = Trap.η(m_Na, 430e3, 2π / 589e-9)
-const η_ry = Trap.η(m_Na, 590e3, 2π / 589e-9)
+const m_Na = 23e-3 / 6.02e23
+const η_rx = Trap.η(m_Na, 479e3, 2π / 589e-9) * √(2) * 0.96
+const η_ry = Trap.η(m_Na, 492e3, 2π / 589e-9) * √(2) * 0.933
+const η_az = Trap.η(m_Na, 85.7e3, 2π / 589e-9) * 0.67
+const η_az_op = Trap.η(m_Na, 85.7e3, 2π / 589e-9)
 
 """
     emission(v, isσ::Bool) -> (sinθ, cosθ)
@@ -107,34 +107,19 @@ end
 
 const coupling_az = (op_heating_all(op_heating_az, 100, 100, Float32(η_az_op), false) *
                      op_heating_all(op_heating_az, 100, 100, Float32(η_az_op), true))
-const coupling_rx = (op_heating_all(op_heating_r, 30, 30, Float32(η_rx), false) *
-                     op_heating_all(op_heating_r, 30, 30, Float32(η_rx), true))
-const coupling_ry = (op_heating_all(op_heating_r, 30, 30, Float32(η_ry), false) *
-                     op_heating_all(op_heating_r, 30, 30, Float32(η_ry), true))
[…]

### 2018-01-29 plot_raman_op.jl
duplicated assignment...

@@ -11,7 +11,6 @@ using PyPlot
 matplotlib["rcParams"][:update](Dict("font.weight" => "normal"))
 
 const m_Na = 23e-3 / 6.02e23
-const m_Na = 23e-3 / 6.02e23
 const η_rx = Trap.η(m_Na, 479e3, 2π / 589e-9) * √(2) * 0.96
 const η_ry = Trap.η(m_Na, 492e3, 2π / 589e-9) * √(2) * 0.933
 const η_az = Trap.η(m_Na, 85.7e3, 2π / 589e-9) * 0.67

### 2018-01-29 paper.tex
Switch naming conventions
New Rabi flopping data

@@
   \includegraphics[height=4.2cm]{spectrum_r.pdf}
-  \includegraphics[height=4.2cm]{rabi_flop_r3_0.pdf}
-  \includegraphics[height=4.2cm]{rabi_flop_r3_p1.pdf}
+  \includegraphics[height=4.2cm]{rabi_flop_rx_0.pdf}
+  \includegraphics[height=4.2cm]{rabi_flop_rx_p1.pdf}
   \caption{(A) Left to right: Radial Raman sideband spectrum of $\Delta n_y=1,\,\Delta n_x=1,\,\Delta n_x=-1,\,\Delta n_y=-1,\,\Delta n_x=-2,\,\Delta n_y=-2$ before and after Raman sideband cooling.
-    (B,C) Rabi flopping on axis $y$ (B) carrier and (C) $\Delta n_y=1$ sideband
+    (B,C) Rabi flopping on axis $x$ (B) carrier and (C) $\Delta n_x=1$ sideband
     before (red circle) and after (blue square) RSC.
@@
 \begin{figure*}
-  \includegraphics[height=4.2cm]{spectrum_a1.pdf}
-  \includegraphics[height=4.2cm]{rabi_flop_a1_0.pdf}
-  \includegraphics[height=4.2cm]{rabi_flop_a1_p1.pdf}
+  \includegraphics[height=4.2cm]{spectrum_az.pdf}
+  \includegraphics[height=4.2cm]{rabi_flop_az_0.pdf}
+  \includegraphics[height=4.2cm]{rabi_flop_az_p1.pdf}
   \caption{(A) Left to right: Axial Raman sideband spectrum from $\Delta n_z=1,0,-1,\ldots,-5$

### 2018-01-29 plot_rabi_flop.jl

@@ -4,47 +4,49 @@
 # The Hamiltonian is assumed to be time independent and the Rabi drive is on-resonance
 
 push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
-using NaCsCalc.Utils: binomial_estimate, thread_rng, interactive
 using NaCsCalc.Atomic: all_scatter_D
 import NaCsCalc: Trap
-using NaCsSim.DecayRabi: propagate_multistates, average_multistates, Γ_to_rates
+using NaCsCalc.Utils: binomial_estimate, thread_rng, interactive
 using NaCsData
+using NaCsSim.DecayRabi: propagate_multistates, average_multistates, Γ_to_rates
 using DataStructures
 using PyPlot
-matplotlib["rcParams"][:update](Dict("font.size" => 20))
-matplotlib[:rc]("xtick", labelsize=15)
-matplotlib[:rc]("ytick", labelsize=15)
+using NaCsPlot
+matplotlib["rcParams"][:update](Dict("font.weight" => "normal"))
 
 # Scattering rates
-const δf1 = -25.0e9
-const δf2 = -25.0e9 - 1.77e9
+# (detunings)
+const δf1 = -75.0e9
+const δf2 = -75.0e9 - 1.77e9
 const rlof_f1 = (61.542e6 / (δf1 - 1.107266e9))^2
 const rlof_f2 = (61.542e6 / (δf2 - 1.107266e9))^2
 const rhif_f1 = (61.542e6 / (δf1 + 664.360e6))^2
 const rhif_f2 = (61.542e6 / (δf2 + 664.360e6))^2
 
+# polarizations of Raman beam, estimated
 const rates_f1_coprop = all_scatter_D(true, 3, (0.5, 0.0, 0.5), rhif_f1, rlof_f1)
 const rates_f1_up = all_scatter_D(true, 3, (0.25, 0.5, 0.25), rhif_f1, rlof_f1)
 const rates_f1_down = all_scatter_D(true, 3, (0.25, 0.5, 0.25), rhif_f1, rlof_f1)
 const rates_f2_coprop = all_scatter_D(true, 3, (0.25, 0.5, 0.25), rhif_f2, rlof_f2)
 const rates_f2_counterop = all_scatter_D(true, 3, (0.1, 0.0, 0.9), rhif_f2, rlof_f2)
 
-rates_f1_coprop .*= 4.46e8
-rates_f2_coprop .*= 4.1e8
[…]

### 2018-01-29 plot_rabi_flop.jl
Add plot label

@@ -209,22 +209,6 @@ const nbar_hot_rx = 3.459
 const τ_hot_rx = 19.926e-6
 
 figure()
-ts_rx_p1 = linspace(0, 280e-6, 1001)
-ts_rx_p1_hot = linspace(0, 150e-6, 501)
-plot_f1(f_rx, ts_rx_p1, 2π / τ_rx * meles_rx_p1[1:3], p_rx, color="C0")
-NaCsPlot.plot_survival_data(data_cold_xp1, fmt="C0o", label="Cold")
-plot_f1_thermal(f_rx, ts_rx_p1_hot, 2π / τ_hot_rx * meles_rx_p1, nbar_hot_rx,
-                δΩ_rx, 0.956528, color="C3")
-NaCsPlot.plot_survival_data(data_hot_xp1, fmt="C3o", label="Hot")
-grid()
-ylim([0, 1])
-title("X heating")
-legend()
-xlabel("Time (\$\\mu s\$)")
-ylabel("Survival")
-NaCsPlot.maybe_save("$(prefix)_rx_p1")
-
-figure()
 ts_rx_0 = linspace(0, 144e-6, 1001)
 ts_rx_0_hot = linspace(0, 60e-6, 501)
 plot_f1(f_rx, ts_rx_0, 2π / τ_rx * meles_rx_0[1:3], p_rx, color="C0")
@@ -233,12 +217,32 @@ plot_f1_thermal(f_rx, ts_rx_0_hot, 2π / τ_hot_rx * meles_rx_0, nbar_hot_rx,
                 δΩ_rx, 0.956528, color="C3")
 NaCsPlot.plot_survival_data(data_hot_x0, fmt="C3o", label="Hot")
 grid()
+xlim([0, 144])
 ylim([0, 1])
 title("X carrier")
-legend()
+text(129, 0.9, "(C)")
+legend(loc="right")
 xlabel("Time (\$\\mu s\$)")
 ylabel("Survival")
 NaCsPlot.maybe_save("$(prefix)_rx_0")
+
+figure()
+ts_rx_p1 = linspace(0, 280e-6, 1001)
+ts_rx_p1_hot = linspace(0, 150e-6, 501)
+plot_f1(f_rx, ts_rx_p1, 2π / τ_rx * meles_rx_p1[1:3], p_rx, color="C0")
+NaCsPlot.plot_survival_data(data_cold_xp1, fmt="C0o", label="Cold")
[…]

### 2018-01-29 paper.tex
Disable decoherence term for non axial heating sideband to match what we say in the paper

@@
   \includegraphics[height=4.2cm]{rabi_flop_rx_p1.pdf}
-  \caption{(A) Left to right: Radial Raman sideband spectrum of $\Delta n_y=1,\,\Delta n_x=1,\,\Delta n_x=-1,\,\Delta n_y=-1,\,\Delta n_x=-2,\,\Delta n_y=-2$ before and after Raman sideband cooling.
-    (B,C) Rabi flopping on axis $x$ (B) carrier and (C) $\Delta n_x=1$ sideband
+  \caption{(A,B) Left to right: Radial Raman sideband spectrum of $\Delta n=1,\,\Delta n=0,\,\Delta n=-1,\,\Delta n=-2$ before and after Raman sideband cooling for $x$ and $y$ axis.
+    (C,D) Rabi flopping on axis $x$ (B) carrier and (C) $\Delta n_x=1$ sideband
     before (red circle) and after (blue square) RSC.
-    Solid lines in (B) and (C) are fits to a Rabi-flopping
+    Solid lines in (C) and (D) are fits to a Rabi-flopping
     that includes a thermal distribution of motional states~\cite{Meekhof1996}

### 2018-01-29 plot_rabi_flop.jl

@@ -203,7 +203,7 @@ end
 
 const τ_rx = 18.451e-6
 const p_rx = [0.975, 0.10, 0.0]
-const δΩ_rx = 15.54e3
+const δΩ_rx = 0 * 15.54e3
 
 const nbar_hot_rx = 3.459
 const τ_hot_rx = 19.926e-6
@@ -249,7 +249,7 @@ NaCsPlot.maybe_save("$(prefix)_rx_p1")
 
 const τ_ry = 12.3e-6
 const p_ry = [0.95, 0.10, 0.0]
-const δΩ_ry = 15.54e3
+const δΩ_ry = 0 * 15.54e3
 
 const nbar_hot_ry = 3.224
 const τ_hot_ry = 12.347e-6
@@ -307,7 +307,7 @@ figure()
 ts_az_0 = linspace(0, 285e-6, 1001)
 ts_az_0_hot = linspace(0, 120e-6, 501)
 plot_f1(f_az, ts_az_0, 2π / τ_az * (meles_az_0[1:3] * meles_ry_0[1:3]'),
-        p_az * p_ry', δΩ_az, offsetΩ=offsetΩ_az, color="C0")
+        p_az * p_ry', δΩ_az * 0, offsetΩ=offsetΩ_az * 0, color="C0")
 NaCsPlot.plot_survival_data(data_cold_z0, fmt="C0o", label="Cold")
 plot_f1_thermal2(f_az, ts_az_0_hot, 2π / τ_hot_az * meles_az_0, nbar_hot_az,
                  meles_ry_0, nbar_hot_ry, δΩ_hot_az2, offset=0.027, offsetΩ=30e3, color="C3")

### 2018-01-30 paper.tex
Remove some out-of-date points

@@
 \author{L. R. Liu}
+\author{J. D. Hood}
 \author{T. Rosenband}
@@
 and short pulses to Fourier broaden the spectrum.
-However, anharmonicity may still shift high-$n$ states out of resonance
-and prevent effective cooling.
 
@@
 In total, $540$ cooling pulses (total duration $53$ ms) are applied
-along three axes with cooling beginning on the radial second order and axial eighth order.
+along three axes with cooling beginning on the radial second order and axial fifth order.
 The full RSC pulse sequence is given in~\footnote{See supplemental material}.
@@
 we perform Raman sideband thermometry~\cite{Monroe1995, Meekhof1996}.
-For the more tightly confined (non-degenerate) radial directions,
+For the more tightly confined radial directions,
 we observe clear $\Delta n=1$, $\Delta n=-1$, and $\Delta n=-2$ sidebands before RSC,
@@
 (0.1-0.2 kHz) from the Raman beams,
-as well as spectral broadening from magnetic field fluctuations and trap anharmonicity.
+as well as spectral broadening from magnetic field fluctuations.
 
@@
 by increasing the detuning of the Raman beams,
-addressing a wider range of axial trap anharmonicity,
 implementing better control of the magnetic field, and optimizing imaging.
@@
 \end{document}
+
+%% TODO
+% Plot marker
+% Remove plot title
+% Remove mention of imaging loss in the text and move it to the figure caption
+% Add 96% survival line.
+% 94(1) ?

### 2018-01-30 plot_rabi_flop.jl
Fix plot

@@ -212,16 +212,14 @@ figure()
 ts_rx_0 = linspace(0, 144e-6, 1001)
 ts_rx_0_hot = linspace(0, 60e-6, 501)
 plot_f1(f_rx, ts_rx_0, 2π / τ_rx * meles_rx_0[1:3], p_rx, color="C0")
-NaCsPlot.plot_survival_data(data_cold_x0, fmt="C0o", label="Cold")
+NaCsPlot.plot_survival_data(data_cold_x0, fmt="C0s")
 plot_f1_thermal(f_rx, ts_rx_0_hot, 2π / τ_hot_rx * meles_rx_0, nbar_hot_rx,
                 δΩ_rx, 0.956528, color="C3")
-NaCsPlot.plot_survival_data(data_hot_x0, fmt="C3o", label="Hot")
+NaCsPlot.plot_survival_data(data_hot_x0, fmt="C3o")
 grid()
 xlim([0, 144])
 ylim([0, 1])
-title("X carrier")
 text(129, 0.9, "(C)")
-legend(loc="right")
 xlabel("Time (\$\\mu s\$)")
 ylabel("Survival")
 NaCsPlot.maybe_save("$(prefix)_rx_0")
@@ -230,16 +228,14 @@ figure()
 ts_rx_p1 = linspace(0, 280e-6, 1001)
 ts_rx_p1_hot = linspace(0, 150e-6, 501)
 plot_f1(f_rx, ts_rx_p1, 2π / τ_rx * meles_rx_p1[1:3], p_rx, color="C0")
-NaCsPlot.plot_survival_data(data_cold_xp1, fmt="C0o", label="Cold")
+NaCsPlot.plot_survival_data(data_cold_xp1, fmt="C0s")
 plot_f1_thermal(f_rx, ts_rx_p1_hot, 2π / τ_hot_rx * meles_rx_p1, nbar_hot_rx,
                 δΩ_rx, 0.956528, color="C3")
-NaCsPlot.plot_survival_data(data_hot_xp1, fmt="C3o", label="Hot")
+NaCsPlot.plot_survival_data(data_hot_xp1, fmt="C3o")
 grid()
 xlim([0, 280])
 ylim([0, 1])
-title("X heating")
 text(250, 0.9, "(D)")
-legend(loc="right")
 xlabel("Time (\$\\mu s\$)")
 ylabel("Survival")
 NaCsPlot.maybe_save("$(prefix)_rx_p1")
[…]

### 2018-01-30 plot_spectrum.jl

@@ -125,11 +125,11 @@ ax0[:get_yaxis]()[:set_label_coords](-0.105, 0.5)
 ax1 = fig[:add_subplot](211)
 # Radial x
 # Without cooling
-NaCsPlot.plot_survival_data(data_hot_rx, fmt="C3.-", label="\$x\$ initial")
+NaCsPlot.plot_survival_data(data_hot_rx, fmt="C3o-", label="\$x\$ initial")
 # With cooling
-NaCsPlot.plot_survival_data(data_cold_rx[1], fmt="C0.-", label="\$x\$ cooled")
-NaCsPlot.plot_survival_data(data_cold_rx[2], fmt="C0.-")
-NaCsPlot.plot_survival_data(data_cold_rx[3], fmt="C0.-")
+NaCsPlot.plot_survival_data(data_cold_rx[1], fmt="C0s-", label="\$x\$ cooled")
+NaCsPlot.plot_survival_data(data_cold_rx[2], fmt="C0s-")
+NaCsPlot.plot_survival_data(data_cold_rx[3], fmt="C0s-")
 grid()
 text(-670, 0.84, "(A)")
 ylim([0, 1])
@@ -143,11 +143,11 @@ yticks([0, 0.25, 0.5, 0.75, 1.0], ["", "0.25", "0.50", "0.75", "1.00"])
 ax2 = fig[:add_subplot](212)
 subplots_adjust(hspace=0.0)
 # Without cooling
-NaCsPlot.plot_survival_data(data_hot_ry, fmt="C3.-", label="\$y\$ initial")
+NaCsPlot.plot_survival_data(data_hot_ry, fmt="C3o-", label="\$y\$ initial")
 # With cooling
-NaCsPlot.plot_survival_data(data_cold_ry[1], fmt="C0.-", label="\$y\$ cooled")
-NaCsPlot.plot_survival_data(data_cold_ry[2], fmt="C0.-")
-NaCsPlot.plot_survival_data(data_cold_ry[3], fmt="C0.-")
+NaCsPlot.plot_survival_data(data_cold_ry[1], fmt="C0s-", label="\$y\$ cooled")
+NaCsPlot.plot_survival_data(data_cold_ry[2], fmt="C0s-")
+NaCsPlot.plot_survival_data(data_cold_ry[3], fmt="C0s-")
 grid()
 text(-670, 0.84, "(B)")
 ylim([0, 1])
[…]

### 2018-01-30 plot_rabi_flop.jl
Add dashed line for imaging survival

@@ -222,6 +222,7 @@ ylim([0, 1])
 text(129, 0.9, "(C)")
 xlabel("Time (\$\\mu s\$)")
 ylabel("Survival")
+axhline(0.96, c="#99aaaa", ls="-.")
 NaCsPlot.maybe_save("$(prefix)_rx_0")
 
 figure()
@@ -238,6 +239,7 @@ ylim([0, 1])
 text(250, 0.9, "(D)")
 xlabel("Time (\$\\mu s\$)")
 ylabel("Survival")
+axhline(0.96, c="#99aaaa", ls="-.")
 NaCsPlot.maybe_save("$(prefix)_rx_p1")
 
 ## Y cold
@@ -264,6 +266,7 @@ ylim([0, 1])
 text(94, 0.9, "(C)")
 xlabel("Time (\$\\mu s\$)")
 ylabel("Survival")
+axhline(0.96, c="#99aaaa", ls="-.")
 NaCsPlot.maybe_save("$(prefix)_ry_0")
 
 figure()
@@ -280,6 +283,7 @@ ylim([0, 1])
 text(170, 0.9, "(D)")
 xlabel("Time (\$\\mu s\$)")
 ylabel("Survival")
+axhline(0.96, c="#99aaaa", ls="-.")
 NaCsPlot.maybe_save("$(prefix)_ry_p1")
 
 ## Z cold
@@ -310,6 +314,7 @@ ylim([0, 1])
 text(254, 0.9, "(B)")
 xlabel("Time (\$\\mu s\$)")
 ylabel("Survival")
+axhline(0.96, c="#99aaaa", ls="-.")
 NaCsPlot.maybe_save("$(prefix)_az_0")
 
 figure()
@@ -329,6 +334,7 @@ ylim([0, 1])
 text(464, 0.9, "(C)")
 xlabel("Time (\$\\mu s\$)")
 ylabel("Survival")
+axhline(0.96, c="#99aaaa", ls="-.")
 NaCsPlot.maybe_save("$(prefix)_az_p1")
 
 NaCsPlot.maybe_show()

### 2018-01-30 plot_spectrum.jl

@@ -130,6 +130,7 @@ NaCsPlot.plot_survival_data(data_hot_rx, fmt="C3o-", label="\$x\$ initial")
 NaCsPlot.plot_survival_data(data_cold_rx[1], fmt="C0s-", label="\$x\$ cooled")
 NaCsPlot.plot_survival_data(data_cold_rx[2], fmt="C0s-")
 NaCsPlot.plot_survival_data(data_cold_rx[3], fmt="C0s-")
+axhline(0.96, c="#99aaaa", ls="-.")
 grid()
 text(-670, 0.84, "(A)")
 ylim([0, 1])
@@ -148,6 +149,7 @@ NaCsPlot.plot_survival_data(data_hot_ry, fmt="C3o-", label="\$y\$ initial")
 NaCsPlot.plot_survival_data(data_cold_ry[1], fmt="C0s-", label="\$y\$ cooled")
 NaCsPlot.plot_survival_data(data_cold_ry[2], fmt="C0s-")
 NaCsPlot.plot_survival_data(data_cold_ry[3], fmt="C0s-")
+axhline(0.96, c="#99aaaa", ls="-.")
 grid()
 text(-670, 0.84, "(B)")
 ylim([0, 1])
@@ -171,6 +173,7 @@ NaCsPlot.plot_survival_data(data_cold_az[4], fmt="C0s-")
 NaCsPlot.plot_survival_data(data_cold_az[5], fmt="C0s-")
 NaCsPlot.plot_survival_data(data_cold_az[6], fmt="C0s-")
 NaCsPlot.plot_survival_data(data_cold_az[7], fmt="C0s-")
+axhline(0.96, c="#99aaaa", ls="-.")
 grid()
 ylim([0, 1])
 xlim([-145, 470])

### 2018-01-30 paper.tex
Fix plot
Add dashed line for imaging survival
Remove mentioning of 96% imaging survival in the text and move it to the caption

@@
   large differential light shifts between the excited state and the ground state,
-  we achieve a ground state population of $93.5(7)$\% after $53$ ms of cooling,
-  for the 96\% of atoms that survive re-imaging. %% survives the first image?
+  we achieve a ground state population of $93.5(7)$\% after $53$ ms of cooling.
   Our technique includes addressing high-order sidebands,
@@
     and the red lines correspond to a thermal distribution of $80$ $\mu$K before RSC.
+    The horizontal dashed line in the plot corresponds to the $96\%$ survival probability
+    after the first image.
     \label{f-radial}}
@@
 a single Na atom is in the 3D ground state with a probability of 93.5(7)\% after RSC.
-We note that there is an additional 4\% population loss from imaging.
 The cooling efficiency is limited by spontaneous scattering rate
@@
 \end{document}
-
-%% TODO
-% Plot marker
-% Remove plot title
-% Remove mention of imaging loss in the text and move it to the figure caption
-% Add 96% survival line.
-% 94(1) ?

### 2018-01-30 paper.tex
Update by Kang-Kuen

@@
 begins by loading a single sodium atom into an optical tweezer from a MOT~\cite{Hutzler2017-LightShifts}.
-The tweezer is created by focussing a $700$ nm wavelength laser beam through an NA=$0.55$ objective to an elliptical waist with radii $\{w_{0,x},w_{0,y}\}\approx \{0.70,0.69\}\,\mu$m.
+The tweezer is created by focussing a $700$ nm wavelength laser beam through an NA=$0.55$ objective to a waist with slight elliptical radii $\{w_{0,x},w_{0,y}\}\approx \{0.70,0.69\}\,\mu$m.
 For $45$ mW of optical power, the trapping frequencies along the three axes are
@@
 
-We thank J. D. Hood for discussions.
 This work is supported by the Arnold and Mabel Beckman Foundation, the AFOSR Young Investigator Program, the NSF through the CUA,

### 2018-01-30 plot_rabi_flop.jl
Fix axial rabi flopping plotting

@@ -321,9 +321,9 @@ figure()
 ts_az_p1 = linspace(0, 520e-6, 1001)
 ts_az_p1_hot = linspace(0, 280e-6, 501)
 plot_f1(f_az, ts_az_p1, 2π / τ_az * (meles_az_p1[1:3] * meles_ry_0[1:3]'),
-        p_az * p_ry', δΩ_az, offsetΩ=offsetΩ_az, color="C0")
+        p_az * p_ry', δΩ_az, offsetΩ=offsetΩ_az, color="C2", ls="-.")
 plot_f1(f_az, ts_az_p1, 2π / τ_az * (meles_az_p1[1:3] * meles_ry_0[1:3]'),
-        p_az * p_ry', 0, offsetΩ=0, color="C2", ls="-.")
+        p_az * p_ry', 0, offsetΩ=0, color="C0")
 NaCsPlot.plot_survival_data(data_cold_zp1, fmt="C0s")
 plot_f1_thermal2(f_az, ts_az_p1_hot, 2π / τ_hot_az * meles_az_p1, nbar_hot_az,
                  meles_ry_0, nbar_hot_ry, δΩ_hot_az, offset=0.027, color="C3")

### 2018-02-01 paper.tex
Update from Kang-Kuen and use dashed line for the Rabi flopping fit with decoherence instead

@@
     the red lines correspond to a thermal distribution of $80$ $\mu$K before RSC.
-    The green line in (C), includes the additional decoherence due to
+    The green dashed line in (C) includes the additional decoherence due to
     a fluctuation of the hyperfine splitting of magnitude $3$ kHz.
@@
 
-We expect to enhance the ground state probability after RSC
-by increasing the detuning of the Raman beams,
-implementing better control of the magnetic field, and optimizing imaging.
+We expect and have verified with Monte-Carlo simulation
+to enhance the ground state probability after RSC
+by increasing the detuning of the Raman beams and
+implementing better control of the magnetic field.
 Another improvement could be to implement grey molasses cooling to achieve

### 2018-02-01 plot_rabi_flop.jl

@@ -321,7 +321,7 @@ figure()
 ts_az_p1 = linspace(0, 520e-6, 1001)
 ts_az_p1_hot = linspace(0, 280e-6, 501)
 plot_f1(f_az, ts_az_p1, 2π / τ_az * (meles_az_p1[1:3] * meles_ry_0[1:3]'),
-        p_az * p_ry', δΩ_az, offsetΩ=offsetΩ_az, color="C2", ls="-.")
+        p_az * p_ry', δΩ_az, offsetΩ=offsetΩ_az, color="C2", ls="--")
 plot_f1(f_az, ts_az_p1, 2π / τ_az * (meles_az_p1[1:3] * meles_ry_0[1:3]'),
         p_az * p_ry', 0, offsetΩ=0, color="C0")
 NaCsPlot.plot_survival_data(data_cold_zp1, fmt="C0s")

### 2018-02-05 paper.tex
Kang-Kuen's edit

--- 2018-01-30 paper.tex
@@
 The data analysis includes only those experiments where the first image reveals successful atom loading.
+It should be noted that 4~\% of atoms are lost from one image to the next due to recoil heating.
 
@@
 Numerically, $\{A_{x,n},A_{y,n},A_{z,n}\}=\{-1.4, -1.4, -0.16\}n$~kHz.
-For mixed states, this broadens high-order sidebands due to the $n$-dependence of the transitions.
-In order to mitigate this, we drive the sidebands with a large Rabi frequency
-and short pulses to Fourier broaden the spectrum.
+For thermal states, this broadens and shifts high-order sidebands due to the $n$-dependence of the transitions.
+To mitigate this, we calibrate the frequency of each sideband order individually, and drive the sidebands with a large Rabi frequency and short pulses to Fourier broaden the spectrum.
 
@@
     and the red lines correspond to a thermal distribution of $80$ $\mu$K before RSC.
-    The horizontal dashed line in the plot corresponds to the $96\%$ survival probability
-    after the first image.
+    The horizontal dashed line in the plot corresponds to the $4\,\%$ probability
+    of imaging loss.
     \label{f-radial}}
@@
 
-We expect to enhance the ground state probability after RSC
-by increasing the detuning of the Raman beams,
-implementing better control of the magnetic field, and optimizing imaging.
-Another improvement could be to implement grey molasses cooling to achieve
-a lower starting temperature before RSC~\cite{Colzi2016}.
+Monte-Carlo simulations show that the ground state probability after RSC
+could be enhanced by increasing the detuning of the Raman beams and implementing
+better control of the magnetic field. Another improvement could come from
+grey molasses cooling, to achieve a lower starting temperature before RSC~\cite{Colzi2016}.
 

### 2018-04-17 plot_spectrum.jl
Smaller marker for sideband spectrum

@@ -123,11 +123,11 @@ ax0[:get_yaxis]()[:set_label_coords](-0.105, 0.5)
 ax1 = fig[:add_subplot](211)
 # Radial x
 # Without cooling
-NaCsPlot.plot_survival_data(data_hot_rx, fmt="C3o-", label="\$x\$ initial")
+NaCsPlot.plot_survival_data(data_hot_rx, fmt="C3o-", label="\$x\$ initial", markersize=1)
 # With cooling
-NaCsPlot.plot_survival_data(data_cold_rx[1], fmt="C0s-", label="\$x\$ cooled")
-NaCsPlot.plot_survival_data(data_cold_rx[2], fmt="C0s-")
-NaCsPlot.plot_survival_data(data_cold_rx[3], fmt="C0s-")
+NaCsPlot.plot_survival_data(data_cold_rx[1], fmt="C0s-", label="\$x\$ cooled", markersize=1)
+NaCsPlot.plot_survival_data(data_cold_rx[2], fmt="C0s-", markersize=1)
+NaCsPlot.plot_survival_data(data_cold_rx[3], fmt="C0s-", markersize=1)
 axhline(0.96, c="#99aaaa", ls="-.")
 grid()
 text(-670, 0.84, "(A)")
@@ -142,11 +142,11 @@ yticks([0, 0.25, 0.5, 0.75, 1.0], ["", "0.25", "0.50", "0.75", "1.00"])
 ax2 = fig[:add_subplot](212)
 subplots_adjust(hspace=0.0)
 # Without cooling
-NaCsPlot.plot_survival_data(data_hot_ry, fmt="C3o-", label="\$y\$ initial")
+NaCsPlot.plot_survival_data(data_hot_ry, fmt="C3o-", label="\$y\$ initial", markersize=1)
 # With cooling
-NaCsPlot.plot_survival_data(data_cold_ry[1], fmt="C0s-", label="\$y\$ cooled")
-NaCsPlot.plot_survival_data(data_cold_ry[2], fmt="C0s-")
-NaCsPlot.plot_survival_data(data_cold_ry[3], fmt="C0s-")
+NaCsPlot.plot_survival_data(data_cold_ry[1], fmt="C0s-", label="\$y\$ cooled", markersize=1)
+NaCsPlot.plot_survival_data(data_cold_ry[2], fmt="C0s-", markersize=1)
[…]

### 2018-04-17 sm.tex
Zoomed in plots

@@
 
+\section{Zooming into the cooling sidebands}
+The height of the cooling sidebands decreases to about $2\%$ after the Raman sideband cooling,
+making them very hard to see on when plotting on the same scale as the heating sideband
+as well as the spectra before cooling. A zoom-in of the spectra after cooling
+is included here so that they can be seen more clearly.
+Only the cooling orders ($\Delta n=-1,-2$ for radial X and Y axes and $\Delta n=-1, \dots, -5$ for axial Z axis) are shown.
+
+\includegraphics[height=4cm]{spectrum_zoom_cool_rx.pdf}
+\includegraphics[height=4cm]{spectrum_zoom_cool_ry.pdf}
+\includegraphics[height=4cm]{spectrum_zoom_cool_az.pdf}
+
 \bibliography{paper}

### 2018-04-17 plot_spectrum.jl

@@ -252,4 +252,40 @@ xlabel("\$\\delta\$, Detuning from carrier (kHz)")
 ylabel("F=1 population")
 NaCsPlot.maybe_save("$(prefix)_nolabel_az")
 
+figure()
+NaCsPlot.plot_survival_data(data_cold_rx[2], fmt="C0s-")
+NaCsPlot.plot_survival_data(data_cold_rx[3], fmt="C0s-")
+grid()
+ylim([0, 0.035])
+xlim([250, 1400])
+xlabel("\$\\delta\$, Detuning from carrier (kHz)")
+ylabel("F=1 population")
+title("X cooling sideband after RSC")
+NaCsPlot.maybe_save("$(prefix)_zoom_cool_rx")
+
+figure()
+NaCsPlot.plot_survival_data(data_cold_ry[2], fmt="C0s-")
+NaCsPlot.plot_survival_data(data_cold_ry[3], fmt="C0s-")
+grid()
+ylim([0, 0.035])
+xlim([250, 1400])
+xlabel("\$\\delta\$, Detuning from carrier (kHz)")
+ylabel("F=1 population")
+title("Y cooling sideband after RSC")
+NaCsPlot.maybe_save("$(prefix)_zoom_cool_ry")
+
+fig = figure(figsize=[1.6, 1] * 4.8)
+NaCsPlot.plot_survival_data(data_cold_az[3], fmt="C0s-")
+NaCsPlot.plot_survival_data(data_cold_az[4], fmt="C0s-")
+NaCsPlot.plot_survival_data(data_cold_az[5], fmt="C0s-")
+NaCsPlot.plot_survival_data(data_cold_az[6], fmt="C0s-")
+NaCsPlot.plot_survival_data(data_cold_az[7], fmt="C0s-")
+grid()
+ylim([0, 0.035])
+xlim([50, 470])
+xlabel("\$\\delta\$, Detuning from carrier (kHz)")
+ylabel("F=1 population")
+title("Z cooling sideband after RSC")
+NaCsPlot.maybe_save("$(prefix)_zoom_cool_az")
+
 NaCsPlot.maybe_show()

### 2018-04-17 plot_rabi_flop.jl
Update plot labels

@@ -221,7 +221,7 @@ xlim([0, 144])
 ylim([0, 1])
 text(129, 0.9, "(C)")
 xlabel("Time (\$\\mu s\$)")
-ylabel("Survival")
+ylabel("F=1 population")
 axhline(0.96, c="#99aaaa", ls="-.")
 NaCsPlot.maybe_save("$(prefix)_rx_0")
 
@@ -238,7 +238,7 @@ xlim([0, 280])
 ylim([0, 1])
 text(250, 0.9, "(D)")
 xlabel("Time (\$\\mu s\$)")
-ylabel("Survival")
+ylabel("F=1 population")
 axhline(0.96, c="#99aaaa", ls="-.")
 NaCsPlot.maybe_save("$(prefix)_rx_p1")
 
@@ -265,7 +265,7 @@ xlim([0, 105])
 ylim([0, 1])
 text(94, 0.9, "(C)")
 xlabel("Time (\$\\mu s\$)")
-ylabel("Survival")
+ylabel("F=1 population")
 axhline(0.96, c="#99aaaa", ls="-.")
 NaCsPlot.maybe_save("$(prefix)_ry_0")
 
@@ -282,7 +282,7 @@ xlim([0, 190])
 ylim([0, 1])
 text(170, 0.9, "(D)")
 xlabel("Time (\$\\mu s\$)")
-ylabel("Survival")
+ylabel("F=1 population")
 axhline(0.96, c="#99aaaa", ls="-.")
 NaCsPlot.maybe_save("$(prefix)_ry_p1")
 
@@ -313,7 +313,7 @@ xlim([0, 285])
 ylim([0, 1])
 text(254, 0.9, "(B)")
 xlabel("Time (\$\\mu s\$)")
-ylabel("Survival")
+ylabel("F=1 population")
 axhline(0.96, c="#99aaaa", ls="-.")
 NaCsPlot.maybe_save("$(prefix)_az_0")
 
@@ -333,7 +333,7 @@ xlim([0, 520])
 ylim([0, 1])
 text(464, 0.9, "(C)")
 xlabel("Time (\$\\mu s\$)")
-ylabel("Survival")
+ylabel("F=1 population")
 axhline(0.96, c="#99aaaa", ls="-.")
 NaCsPlot.maybe_save("$(prefix)_az_p1")
 

### 2018-04-17 plot_spectrum.jl

@@ -253,29 +253,29 @@ ylabel("F=1 population")
 NaCsPlot.maybe_save("$(prefix)_nolabel_az")
 
 figure()
-NaCsPlot.plot_survival_data(data_cold_rx[2], fmt="C0s-")
+NaCsPlot.plot_survival_data(data_cold_rx[2], fmt="C0s-", label="\$x\$ initial")
 NaCsPlot.plot_survival_data(data_cold_rx[3], fmt="C0s-")
 grid()
 ylim([0, 0.035])
 xlim([250, 1400])
 xlabel("\$\\delta\$, Detuning from carrier (kHz)")
-ylabel("F=1 population")
-title("X cooling sideband after RSC")
+ylabel("F=1 population fraction")
+legend()
 NaCsPlot.maybe_save("$(prefix)_zoom_cool_rx")
 
 figure()
-NaCsPlot.plot_survival_data(data_cold_ry[2], fmt="C0s-")
+NaCsPlot.plot_survival_data(data_cold_ry[2], fmt="C0s-", label="\$y\$ initial")
 NaCsPlot.plot_survival_data(data_cold_ry[3], fmt="C0s-")
 grid()
 ylim([0, 0.035])
 xlim([250, 1400])
 xlabel("\$\\delta\$, Detuning from carrier (kHz)")
-ylabel("F=1 population")
-title("Y cooling sideband after RSC")
+ylabel("F=1 population fraction")
+legend()
 NaCsPlot.maybe_save("$(prefix)_zoom_cool_ry")
 
 fig = figure(figsize=[1.6, 1] * 4.8)
-NaCsPlot.plot_survival_data(data_cold_az[3], fmt="C0s-")
+NaCsPlot.plot_survival_data(data_cold_az[3], fmt="C0s-", label="\$z\$ initial")
 NaCsPlot.plot_survival_data(data_cold_az[4], fmt="C0s-")
 NaCsPlot.plot_survival_data(data_cold_az[5], fmt="C0s-")
 NaCsPlot.plot_survival_data(data_cold_az[6], fmt="C0s-")
@@ -284,8 +284,8 @@ grid()
 ylim([0, 0.035])
 xlim([50, 470])
 xlabel("\$\\delta\$, Detuning from carrier (kHz)")
-ylabel("F=1 population")
-title("Z cooling sideband after RSC")
+ylabel("F=1 population fraction")
+legend()
 NaCsPlot.maybe_save("$(prefix)_zoom_cool_az")
 
 NaCsPlot.maybe_show()

### 2018-04-17 sm.tex
sm update from Kang-Kuen

--- 2018-01-29 sm.tex
@@
 \end{center}
+\newpage
+
+\section{Zoomed data for Raman Sideband Cooling}
+Efficient RSC enables the preparation of single atoms with a high probability of being in the trap ground state.  That probability can be measured by Raman sideband spectroscopy.
+Here we show a zoomed spectra after RSC for clarity.  The cooling orders ($\Delta n=-1,-2$ for radial x and y axes and $\Delta n=-1, \dots, -5$ for axial z axis) are shown.
+Each data point comes from repeated measurements with more than 450 single atoms loaded.
+The heights of these sidebands are about $2.5\%$. \\
+
+\includegraphics[height=4cm]{spectrum_zoom_cool_rx.pdf}
+\includegraphics[height=4cm]{spectrum_zoom_cool_ry.pdf}
+\includegraphics[height=4cm]{spectrum_zoom_cool_az.pdf}
 

### 2018-04-18 plot_spectrum.jl
Fix legend in sm.......

@@ -253,7 +253,7 @@ ylabel("F=1 population")
 NaCsPlot.maybe_save("$(prefix)_nolabel_az")
 
 figure()
-NaCsPlot.plot_survival_data(data_cold_rx[2], fmt="C0s-", label="\$x\$ initial")
+NaCsPlot.plot_survival_data(data_cold_rx[2], fmt="C0s-", label="\$x\$ cooled")
 NaCsPlot.plot_survival_data(data_cold_rx[3], fmt="C0s-")
 grid()
 ylim([0, 0.035])
@@ -264,7 +264,7 @@ legend()
 NaCsPlot.maybe_save("$(prefix)_zoom_cool_rx")
 
 figure()
-NaCsPlot.plot_survival_data(data_cold_ry[2], fmt="C0s-", label="\$y\$ initial")
+NaCsPlot.plot_survival_data(data_cold_ry[2], fmt="C0s-", label="\$y\$ cooled")
 NaCsPlot.plot_survival_data(data_cold_ry[3], fmt="C0s-")
 grid()
 ylim([0, 0.035])
@@ -275,7 +275,7 @@ legend()
 NaCsPlot.maybe_save("$(prefix)_zoom_cool_ry")
 
 fig = figure(figsize=[1.6, 1] * 4.8)
-NaCsPlot.plot_survival_data(data_cold_az[3], fmt="C0s-", label="\$z\$ initial")
+NaCsPlot.plot_survival_data(data_cold_az[3], fmt="C0s-", label="\$z\$ cooled")
 NaCsPlot.plot_survival_data(data_cold_az[4], fmt="C0s-")
 NaCsPlot.plot_survival_data(data_cold_az[5], fmt="C0s-")
 NaCsPlot.plot_survival_data(data_cold_az[6], fmt="C0s-")

### 2018-08-09 paper.tex
paper update from Kang-Kuen
Fix footnotes

@@
 Therefore, to optically pump atoms from $|2, 1\rangle$ into $|2, 2\rangle$
-while keeping the target state dark, we apply light resonant with $3^2P_{1/2}$~\cite{Monroe1995, Grobner2017}~\footnote{We find a reduction in the scattering rate by a factor of $130(20)$, as compared to using an OP resonant with $3^2P_{3/2}$, from which the $|2, 2>$ state could always scatter a photon via the excited $|F'=3, m_{F'}=3>$ state.}.
+while keeping the target state dark, we apply light resonant with $3^2P_{1/2}$~\cite{Monroe1995, Grobner2017}~\footnote{We find a reduction in the scattering rate by a factor of $130(20)$, as compared to using an OP resonant with $3^2P_{3/2}$, from which the $|2, 2\rangle$ state could always scatter a photon via the excited $|F'=3, m_{F'}=3\rangle$ state.}.
 
@@
   \caption{(A,B) Left to right: Radial Raman sideband spectrum of $\Delta n=1,\,\Delta n=0,\,\Delta n=-1,\,\Delta n=-2$ before and after Raman sideband cooling for $x$ and $y$ axis.
+    See supplemental material for zoomed figures.
     (C,D) Rabi flopping on axis $x$ (B) carrier and (C) $\Delta n_x=1$ sideband
@@
 
-This work is supported by the Arnold and Mabel Beckman Foundation, the AFOSR Young Investigator Program, the NSF through the CUA,
+We thank A. Gerakis for early experimental assistance.
+This work is supported by the Arnold and Mabel Beckman Foundation,
+the AFOSR Young Investigator Program, the NSF through the CUA,
 and the Alfred P. Sloan Foundation.
